### 2019-07-03 submission/manuscript.Rmd
start drafting manuscript with mbio formatting

---
title: '**Invited Speaker Diversity Does Not Reflect Trainee Diversity**'
csl: mbio.csl
fontsize: 11pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  word_document: default
geometry: margin=1.0in
bibliography: references.bib
---

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE}
######################################################################
#----------------- Read in necessary libraries -------------------#
######################################################################
deps = c("kableExtra","knitr","rmarkdown","hexbin","lubridate", "tidyverse", "markdown", "formattable");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
######################################################################
#-------------- Define the chunk options ----------------#
######################################################################
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

inline_hook <- function(x){
	print(x)

	if(is.list(x)){
		x <- unlist(x)
	}

	if(is.numeric(x)){
		if(abs(x - round(x)) < .Machine$double.eps^0.5){
			paste(format(x,big.mark=',', digits=0, scientific=FALSE))
		} else {
			paste(format(x,big.mark=',', digits=1, nsmall=1, scientific=FALSE))
		}
	} else {
    	paste(x)      
	}
}
knitr::knit_hooks$set(inline=inline_hook)
```

```{r LoadData, eval=TRUE, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
######################################################################
#----------- Read in important functions & load data-----------------#
######################################################################
source("../code/load_data.R")

######################################################################
#----------- Read in analysis and plots-----------------#
######################################################################
source("../code/analyze_micro_immuno.R")

```

\vspace{35mm}

Running title: Invited Speaker Diversity Does Not Reflect Trainee Diversity

\vspace{35mm}

Ada K. Hagan${^1}$^ and Josie Libertucci${^2}$^

\vspace{40mm}

$\dagger$ To whom correspondence should be addressed: akhagan@umich.edu or

1\. Journals Department, American Society for Microbiology, Washington DC

2\. Chemistry and Biology, Ryerson University, Toronto, Ontario

\newpage
\linenumbers

## Abstract

## Importance

\newpage

## Background

## Results

__Model selection and pipeline construction__

[Figure 5].

## Discussion

In this study

##Methods

**Data collection and gender assignment.**

  Historical information on invited speakers and their hosts were obtained from departmental records of five academic years (Fall 2014 - Spring 2019). Each speaker was only counted once and any departmental faculty members or those listed as a "host" at any point were not considered "invited speakers". The list of current trainees (Spring 2019), was obtained from department listservs and included masters students, doctoral students, and post-doctoral fellows.
  Demographics for invited speakers, hosts, and trainees were hand-coded using personal knowledge, photos, and CVs. Presenting gender was assigned using a binary system (man/woman). Race/ethnicity was assigned using the current U.S. Census definition where "Caucasian" includes Middle Eastern, European, and Russian. Because of the small "n" of this dataset, those non-Caucasians are referred to collectively as Men or Women of Color. Individual assignments can be found in the anonymized dataset.

**Code and Data availability.**

  The anonymized data, the code for all analysis steps and an Rmarkdown version of this manuscript is available at https://github.com/LibertucciLab/Hagan_SpDiv_XXXX_2019/.

\newpage
\includegraphics{Figure_1}
**Figure 1. Machine learning pipeline showing predictive model training and evaluation flowchart.  **  We split the data 80%/20% stratified to maintain the overall label distribution, performed five-fold cross-validation on the training data to select the best hyperparameter setting and then using these hyperparameters to train all of the training data. The model was evaluated on a held-out set of data (not used in selecting the model).
Abbreviations: AUROC, area under the receiver operating characteristic curve
\newpage
\includegraphics{Figure_2.png}
**Figure 2. Generalization and classification performance of ML models using AUROC values of all cross validation and testing performances. **   The median AUROC for diagnosing individuals with SRN using bacterial abundances was higher than chance (depicted by horizontal line at 0.50) for all the ML models. Discriminative performance of random forest model was higher than other ML models. The boxplot shows quartiles at the box ends and the statistical median as the horizontal line in the box. The whiskers show the farthest points that are not outliers. Outliers are data points that are not within 3/2 times the interquartile ranges. 
Abbreviations: SRN, screen-relevant neoplasias; AUROC, area under the receiver operating characteristic curve; SVM, support vector machine; XGBoost, extreme gradient boosting
\newpage
\includegraphics{Figure_3.png}
**Figure 3. Interpretation of the linear ML models.** (A) L2 logistic regression coefficients  (B) L1 SVM with linear kernel feature weights (C) L2 SVM with linear kernel feature weights. The means weights and coefficients of the most important five OTUs for each model are shown here with the standard deviation over 100 data-splits. Similar OTUs had the largest impact on the predictive performance of L2 logistic regression and L2 SVM with linear kernel. 
Abbreviations: SVM, support vector machine; OTU, Operational Taxonomic Unit.
\newpage
\includegraphics{Figure_4.png}
**Figure 4. Explanation of the non-linear ML models.** (A) SVM with radial basis kernel (B) decision tree (C) random forest (D) XGboost feaure importances were explanied using permutation importance using held-out test set. The gray rectangle and the dashed line show the IQR range and median of the base testing AUROC without any permutation performed. For all the tree-based models, a *Peptostreptococcus* species (OTU00367) had the largest impact on predictive performance of the model. 
Abbreviations: SVM, support vector machine; OTU, Operational Taxonomic Unit; RBF, radial basis kernel; OTU, Operational Taxonomic Unit.
\newpage
\includegraphics{Figure_5.png}
**Figure 5. Computational efficiency of seven ML models.** The traintimes for training and testing of each data-split showed the differences in computational efficieny of the seven models. The median traintime in hours was the highest for XGBoost and shortest for L2 logistic regression. The boxplot shows quartiles at the box ends and the statistical median as the horizontal line in the box. The whiskers show the farthest points that are not outliers. Outliers are data points that are not within 3/2 times the interquartile ranges. 
Abbreviations: AUROC, area under the receiver operating characteristic curve; SVM, support vector machine; XGBoost, extreme gradient boosting.  
\newpage
\includegraphics{Figure_S1.png}
**Figure S1. Hyperparameter setting performances for linear models.** 
Abbreviations: 
\newpage
\includegraphics{Figure_S2.png}
**Figure S2. Hyperparameter setting performances for non-linear models.** 
Abbreviations: 
\newpage

## References

<div id="refs"></div>

### 2019-08-23 code/data_extraction/compile_mi_speaker_datasets.R
clean and organize

@@ -41,8 +41,8 @@ compiled_data <- raw_data %>% left_join(., host_data, by = "Host") %>%
 
 
 MI_diversify <- compiled_data %>% 
-  mutate(speaker_div = get_diversity_value(Speaker_gender, Speaker_caucasian), 
-         host_div = get_diversity_value(Host_gender, Host_caucasian),
+  mutate(#speaker_div = get_diversity_value(Speaker_gender, Speaker_caucasian), 
+         #host_div = get_diversity_value(Host_gender, Host_caucasian),
          Host = get_host_type(Host), 
          Lectureship = fct_collapse(Lectureship,
                                     "Brockman" = c("Brockman", "BROCKMAN SPEAKER"),
@@ -50,7 +50,7 @@ MI_diversify <- compiled_data %>%
                                     "MMMP" = c("MMMP", "MMMP-invited"),
                                     "Neidhardt/Freter" = c("Neidhardt/Freter", "NEIDHARDT/FRETER SYMPOSIUM", "Neidhart-Freter"),
                                     "Willison" = c("Willison", "WILLISON SPEAKER"))) %>% 
-  select(-Speaker)
+  select(-Speaker, -Host_notes)
 
-write_csv(MI_diversify, "data/micro_immuno/complete_dataset_14-19.csv")  
+write_csv(MI_diversify, "data/speaker_dataset_14-19.csv")  
 

### 2019-08-23 code/data_extraction/compile_mi_trainee_data.R

@@ -1,0 +1,14 @@
+library(tidyverse)
+
+postdoc_data <- read_csv("data/micro_immuno/postdocs_19.csv") %>% 
+  mutate(Trainee_type = "postdoc")
+
+student_data <- read_csv("data/micro_immuno/students_19.csv") %>% 
+  mutate(Trainee_type = "student")
+
+trainee_data <- bind_rows(postdoc_data, student_data) %>% 
+  distinct() %>% 
+  #mutate(train_div = get_diversity_value(Gender, Caucasian)) %>% 
+  select(-Name)
+
+write_csv(trainee_data, "data/trainee_data_19.csv")

### 2019-08-23 code/lectureship_div.R

@@ -1,0 +1,44 @@
+#What are the proportions of M/F, W/POC for lectureships ----
+MI_diversify %>% 
+  filter(!is.na(Lectureship)) %>% 
+  filter(Host != "Student" | Host != "Postdoc") %>% 
+  group_by(speaker_div) %>% summarise(n = n()) %>% 
+  add_row(., speaker_div = "WOC", n = 0) %>% 
+  mutate(percent = (n/sum(n))*100) %>% 
+  ggplot(aes(x = speaker_div))+
+  geom_col(aes(y = percent))+
+  #scale_y_continuous(labels = scales::percent)+
+  #geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
+  labs(y = "Percent of Lectureships", x = "Speaker Demographics")+
+  theme_classic() + 
+  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
+        plot.title = element_text(size=16,face="bold"))
+
+MI_diversify %>% 
+  filter(!is.na(Lectureship)) %>% 
+  filter(Host != "Student" | Host != "Postdoc") %>% 
+  ggplot(aes(x = Speaker_caucasian))+
+  geom_bar(aes(y = (..count..)/sum(..count..)))+
+  scale_y_continuous(labels = scales::percent)+
+  geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
+  labs(y = "Percent of Speakers", x = "Is Speaker Caucasian?")+
+  theme_classic() + 
+  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
+        plot.title = element_text(size=16,face="bold"))
+
+MI_diversify %>% 
+  filter(!is.na(Lectureship)) %>% 
+  filter(Host != "Student") %>% 
+  filter(Host != "Postdoc") %>%
+  ggplot(aes(x = factor(speaker_div, levels = c("Cauc M", "Cauc W", "MOC", "WOC"))))+
+  geom_bar(aes(y = (..count..)/sum(..count..), fill = Lectureship))+
+  scale_x_discrete(drop=FALSE)+
+  scale_y_continuous(labels = scales::percent)+
+  geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
[…]

### 2019-08-23 code/load_data.R

@@ -11,14 +11,6 @@ get_diversity_value <- function(x, y){
 }
 
 #data setup----
-MI_data <- read_csv("data/micro_immuno/complete_dataset_14-19.csv") 
+speaker_data <- read_csv("data/speaker_dataset_14-19.csv") 
 
-postdoc_data <- read_csv("data/micro_immuno/postdocs_19.csv") %>% 
-  mutate(Trainee_type = "postdoc")
-
-student_data <- read_csv("data/micro_immuno/students_19.csv") %>% 
-  mutate(Trainee_type = "student")
-
-trainee_data <- bind_rows(postdoc_data, student_data) %>% 
-  distinct() %>% 
-  mutate(train_div = get_diversity_value(Gender, Caucasian))
+trainee_data <- read_csv("data/trainee_data_19.csv")

### 2019-08-23 code/speaker_cauc.R

@@ -1,0 +1,25 @@
+#speaker caucasian vs not
+
+#What are the proportions of M/F, W/POC for invited speakers----
+MI_diversify %>% #over time
+  group_by(year(Date), speaker_div) %>% summarise(n = n()) %>% 
+  ggplot()+
+  geom_col(aes(x = `year(Date)`, y = n, fill = speaker_div), position = "dodge")+
+  scale_fill_brewer(palette = "Dark2")+
+  labs(x = "Year", y = "Number Invited")+
+  theme_classic() + 
+  theme(axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
+        plot.title = element_text(size=16,face="bold"), 
+        axis.text.x = element_text(angle = 0, hjust = 1))
+
+MI_diversify %>% 
+  ggplot(aes(x = Speaker_caucasian))+
+  geom_bar(aes(y = (..count..)/sum(..count..)))+
+  scale_y_continuous(labels = scales::percent)+
+  geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
+  labs(y = "Percent of Speakers", x = "Caucasian Speaker")+
+  theme_classic() + 
+  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
+        plot.title = element_text(size=16,face="bold"))
+
+ggsave("figures/speaker_cauc.png")

### 2019-08-23 code/speaker_gender.R

@@ -1,0 +1,13 @@
+#speaker gender demographics
+
+MI_diversify %>% 
+  ggplot(aes(x = Speaker_gender))+
+  geom_bar(aes(y = (..count..)/sum(..count..)))+
+  scale_y_continuous(labels = scales::percent)+
+  geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
+  labs(y = "Percent of Speakers", x = "Speaker Gender")+
+  theme_classic() + 
+  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
+        plot.title = element_text(size=16,face="bold"))
+
+ggsave("figures/speaker_gender.png")

### 2019-08-23 code/trainee_demo.R

@@ -1,0 +1,15 @@
+#what are the trainee demographics?----
+
+trainee_data %>% 
+  ggplot(aes(x = train_div))+
+  geom_bar(aes(y = (..count..)/sum(..count..), fill = Trainee_type))+
+  scale_y_continuous(labels = scales::percent)+
+  geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
+  labs(y = "Percent of Trainees", x = "Demographics", 
+       fill = "Trainee Type")+
+  scale_fill_brewer(palette = "Set2")+
+  theme_classic() + 
+  theme(axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
+        plot.title = element_text(size=16,face="bold"))
+
+ggsave("figures/trainee_demog_fill.png")

### 2019-08-23 code/analyze_micro_immuno.R
clean code, work on analysis

@@ -1,123 +1,0 @@
-#what is the frequency of hosting over the past several years -- weighted % of hosting by demographic----
-plot_hosting_freq <- MI_diversify %>% 
-  group_by(Host, host_div) %>% summarise(n = n()) %>% 
-  ggplot()+
-  geom_col(aes(x = reorder(Host, n), y = n, fill = host_div))+
-  theme_classic() + 
-  theme(axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
-        plot.title = element_text(size=16,face="bold"), 
-        axis.text.x = element_text(angle = 45, hjust = 1))
-
-#What are the proportions of M/F, W/POC for invited speakers----
-MI_diversify %>% #over time
-  group_by(year(Date), speaker_div) %>% summarise(n = n()) %>% 
-  ggplot()+
-  geom_col(aes(x = `year(Date)`, y = n, fill = speaker_div), position = "dodge")+
-  scale_fill_brewer(palette = "Dark2")+
-  labs(x = "Year", y = "Number Invited")+
-  theme_classic() + 
-  theme(axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
-        plot.title = element_text(size=16,face="bold"), 
-        axis.text.x = element_text(angle = 0, hjust = 1))
-  
-
-MI_diversify %>% 
-  ggplot(aes(x = Speaker_gender))+
-  geom_bar(aes(y = (..count..)/sum(..count..)))+
-  scale_y_continuous(labels = scales::percent)+
-  geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
-  labs(y = "Percent of Speakers", x = "Speaker Gender")+
-  theme_classic() + 
-  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
-        plot.title = element_text(size=16,face="bold"))
-
-ggsave("figures/speaker_gender.png")
-
-MI_diversify %>% 
-  ggplot(aes(x = Speaker_caucasian))+
-  geom_bar(aes(y = (..count..)/sum(..count..)))+
-  scale_y_continuous(labels = scales::percent)+
-  geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
[…]

### 2019-08-23 code/demo_comp.R

@@ -1,0 +1,17 @@
+#what are the trainee demographics?----
+
+speaker_demo <- tidy_speaker %>% 
+  filter(demographic != "Gender")
+
+trainee_demo <- tidy_trainee %>% 
+  filter(demographic != "Gender") 
+  
+demo_combined <- rbind(trainee_demo, speaker_demo) %>% 
+  group_by(demographic, role, value) %>% summarise(n = n()) %>% 
+  spread(key = value, value = n) %>% 
+  mutate(prop_y = get_percent(y, (y + n)))
+  
+demo_combined %>% 
+  ggplot()+
+  geom_col(aes(x = role, y = prop_y))+
+  facet_wrap(~demographic)

### 2019-08-23 code/gender_comp.R

@@ -1,0 +1,15 @@
+
+trainee_gender <- tidy_trainee %>% 
+  filter(demographic == "Gender")  
+
+speaker_gender <- tidy_speaker %>% 
+  filter(demographic == "Gender")
+
+gender_combined <- rbind(trainee_gender, speaker_gender) %>% 
+  group_by(role, value) %>% summarise(n = n()) %>% 
+  spread(key = value, value = n) %>% 
+  mutate(prop_W = get_percent(woman, (man + woman)))
+
+gender_combined %>% 
+  ggplot()+
+  geom_col(aes(x = role, y = prop_W))

### 2019-08-23 code/load_data.R

@@ -10,7 +10,31 @@ get_diversity_value <- function(x, y){
     x == "woman" & y == "n" ~ paste("WOC"))
 }
 
-#data setup----
-speaker_data <- read_csv("data/speaker_dataset_14-19.csv") 
+#calculate two decimal percentage given num & denom
+get_percent <- function(x, y){
+  z <- (as.numeric(x)/as.numeric(y))*100
+  percent <- round(z, digits = 2)
+  return(percent)
+}
 
-trainee_data <- read_csv("data/trainee_data_19.csv")
+#data setup----
+speaker_data <- read_csv("data/speaker_dataset_14-19.csv") %>% 
+  mutate(Speaker_id = rownames(.)) %>% 
+  rename(Speaker_Caucasian = Speaker_caucasian, 
+         Speaker_Gender = Speaker_gender)
+
+tidy_speaker <- speaker_data %>% 
+  select(contains("Speaker")) %>% 
+  gather(Speaker_Gender:Speaker_Internatl, 
+         key = demographic, value = value) %>% 
+  separate(demographic, into = c("role", "demographic"), sep = "_") %>% 
+  rename(id = Speaker_id) %>% 
+  mutate()
+
+trainee_data <- read_csv("data/trainee_data_19.csv") %>% 
+  mutate(id = rownames(.))
+
+tidy_trainee <- trainee_data %>% 
+  gather(Gender:Internatl, key = demographic, value = value) %>% 
+  rename(role = Trainee_type) %>% 
+  mutate(role = str_to_title(role))

### 2019-08-23 code/speaker_cauc.R

@@ -1,25 +1,0 @@
-#speaker caucasian vs not
-
-#What are the proportions of M/F, W/POC for invited speakers----
-MI_diversify %>% #over time
-  group_by(year(Date), speaker_div) %>% summarise(n = n()) %>% 
-  ggplot()+
-  geom_col(aes(x = `year(Date)`, y = n, fill = speaker_div), position = "dodge")+
-  scale_fill_brewer(palette = "Dark2")+
-  labs(x = "Year", y = "Number Invited")+
-  theme_classic() + 
-  theme(axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
-        plot.title = element_text(size=16,face="bold"), 
-        axis.text.x = element_text(angle = 0, hjust = 1))
-
-MI_diversify %>% 
-  ggplot(aes(x = Speaker_caucasian))+
-  geom_bar(aes(y = (..count..)/sum(..count..)))+
-  scale_y_continuous(labels = scales::percent)+
-  geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
-  labs(y = "Percent of Speakers", x = "Caucasian Speaker")+
-  theme_classic() + 
-  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
-        plot.title = element_text(size=16,face="bold"))
-
-ggsave("figures/speaker_cauc.png")

### 2019-08-23 code/speaker_gender.R

@@ -1,13 +1,0 @@
-#speaker gender demographics
-
-MI_diversify %>% 
-  ggplot(aes(x = Speaker_gender))+
-  geom_bar(aes(y = (..count..)/sum(..count..)))+
-  scale_y_continuous(labels = scales::percent)+
-  geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
-  labs(y = "Percent of Speakers", x = "Speaker Gender")+
-  theme_classic() + 
-  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
-        plot.title = element_text(size=16,face="bold"))
-
-ggsave("figures/speaker_gender.png")

### 2019-08-23 code/trainee_demo.R

@@ -1,15 +1,0 @@
-#what are the trainee demographics?----
-
-trainee_data %>% 
-  ggplot(aes(x = train_div))+
-  geom_bar(aes(y = (..count..)/sum(..count..), fill = Trainee_type))+
-  scale_y_continuous(labels = scales::percent)+
-  geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
-  labs(y = "Percent of Trainees", x = "Demographics", 
-       fill = "Trainee Type")+
-  scale_fill_brewer(palette = "Set2")+
-  theme_classic() + 
-  theme(axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
-        plot.title = element_text(size=16,face="bold"))
-
-ggsave("figures/trainee_demog_fill.png")

### 2019-08-23 code/demo_comp.R
plot gender & demo data

@@ -11,7 +11,13 @@ demo_combined <- rbind(trainee_demo, speaker_demo) %>%
   spread(key = value, value = n) %>% 
   mutate(prop_y = get_percent(y, (y + n)))
   
+demo_combined$role <- fct_relevel(demo_combined$role, dat_levels)
+
 demo_combined %>% 
   ggplot()+
-  geom_col(aes(x = role, y = prop_y))+
-  facet_wrap(~demographic)
+  geom_col(aes(x = role, y = prop_y, fill = role), alpha = 0.75)+
+  facet_wrap(~demographic)+
+  labs(x = "Academic Role", y = "Proportion of Population")+
+  set_role_colors +
+  my_theme_horiz
+

### 2019-08-23 code/gender_comp.R

@@ -1,4 +1,4 @@
-
+#compare gender compositions for trainees and speakers
 trainee_gender <- tidy_trainee %>% 
   filter(demographic == "Gender")  
 
@@ -10,6 +10,12 @@ gender_combined <- rbind(trainee_gender, speaker_gender) %>%
   spread(key = value, value = n) %>% 
   mutate(prop_W = get_percent(woman, (man + woman)))
 
-gender_combined %>% 
+gender_combined$role <- fct_relevel(gender_combined$role, dat_levels)
+
+gender_fig <- gender_combined %>% 
   ggplot()+
-  geom_col(aes(x = role, y = prop_W))
+  geom_col(aes(x = role, y = prop_W, fill = role), alpha = 0.75)+
+  labs(x = "Academic Role", y = "Proportion of Women")+
+  geom_text()+
+  set_role_colors +
+  my_theme_horiz

### 2019-08-23 code/get_plot_options.R

@@ -1,0 +1,63 @@
+library(scales)
+library(RColorBrewer)
+library(cowplot)
+#library(patchwork)
+
+#preferred themes----
+my_theme <- theme_classic() + 
+  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
+        plot.title = element_text(size=16,face="bold"), 
+        axis.text.x = element_text(angle = 45, hjust = 1))
+
+my_theme_horiz <- theme_classic() + 
+  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
+        plot.title = element_text(size=16,face="bold"))
+
+my_theme_leg <- theme_classic() + 
+  theme(axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
+        plot.title = element_text(size=16,face="bold"), 
+        axis.text.x = element_text(angle = 45, hjust = 1))
+
+my_theme_leg_left <- theme_classic() + 
+  theme(axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
+        plot.title = element_text(size=16,face="bold"), 
+        axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "left")
+
+my_theme_leg_horiz <- theme_classic() + 
+  theme(axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
+        plot.title = element_text(size=16,face="bold"))
+
+#adding proportion/count labels to barchart
+prop_lab_low <- geom_text(aes(label = scales::percent((..count..)/sum(..count..)), y= ((..count..)/sum(..count..))), stat = "count", vjust = 1)
+
+count_lab_low <- geom_text(stat = "count", aes(label=..count..), vjust = 1)
+
+prop_lab_high <- geom_text(aes(label = scales::percent((..count..)/sum(..count..)), y= ((..count..)/sum(..count..))), stat = "count", vjust = -1)
+
+count_lab_high <- geom_text(stat = "count", aes(label=..count..), vjust = -1)
+
+#colorblind palettes
+#The palette with grey:
+cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7") #grey, goldenrod, light blue, dark green, gold, navy blue, orange rust, pink
+
[…]

### 2019-08-23 code/load_data.R

@@ -1,13 +1,12 @@
 library(tidyverse)
-library(lubridate)
-library(hexbin)
+
+source("../code/get_plot_options.R")
 
 get_diversity_value <- function(x, y){
   case_when(
     x == "man" & y == "y" ~ paste("Cauc M"),
-    x == "man" & y == "n" ~ paste("MOC"),
-    x == "woman" & y == "y" ~ paste("Cauc W"),
-    x == "woman" & y == "n" ~ paste("WOC"))
+    x == "woman" & y == "y" ~ paste("Cauc W")
+  )
 }
 
 #calculate two decimal percentage given num & denom
@@ -18,7 +17,7 @@ get_percent <- function(x, y){
 }
 
 #data setup----
-speaker_data <- read_csv("data/speaker_dataset_14-19.csv") %>% 
+speaker_data <- read_csv("../data/speaker_dataset_14-19.csv") %>% 
   mutate(Speaker_id = rownames(.)) %>% 
   rename(Speaker_Caucasian = Speaker_caucasian, 
          Speaker_Gender = Speaker_gender)
@@ -29,12 +28,15 @@ tidy_speaker <- speaker_data %>%
          key = demographic, value = value) %>% 
   separate(demographic, into = c("role", "demographic"), sep = "_") %>% 
   rename(id = Speaker_id) %>% 
-  mutate()
+  mutate(demographic = if_else(demographic == "Internatl", 
+                               "International", demographic))
 
-trainee_data <- read_csv("data/trainee_data_19.csv") %>% 
+trainee_data <- read_csv("../data/trainee_data_19.csv") %>% 
   mutate(id = rownames(.))
 
 tidy_trainee <- trainee_data %>% 
   gather(Gender:Internatl, key = demographic, value = value) %>% 
   rename(role = Trainee_type) %>% 
-  mutate(role = str_to_title(role))
+  mutate(role = str_to_title(role)) %>% 
+  mutate(demographic = if_else(demographic == "Internatl", 
+                               "International", demographic))

### 2019-08-23 submission/manuscript.Rmd
format for JMBE

@@
 ---
-title: '**Invited Speaker Diversity Does Not Reflect Trainee Diversity**'
+title: '**Department Invited Speakers Do Not Reflect Trainee Diversity**'
 csl: mbio.csl
-fontsize: 11pt
+fontsize: 10pt
 output:
@@
     keep_tex: yes
-  word_document: default
 geometry: margin=1.0in
-bibliography: references.bib
+
 ---
@@
 for (dep in deps){
-  if (dep %in% installed.packages()[,"Package"] == FALSE){
-    install.packages(as.character(dep), quiet=TRUE);
-  }
   library(dep, verbose=FALSE, character.only=TRUE)
@@
 opts_chunk$set("cache" = FALSE)
-
-inline_hook <- function(x){
-	print(x)
-
-	if(is.list(x)){
-		x <- unlist(x)
-	}
-
-	if(is.numeric(x)){
-		if(abs(x - round(x)) < .Machine$double.eps^0.5){
-			paste(format(x,big.mark=',', digits=0, scientific=FALSE))
-		} else {
-			paste(format(x,big.mark=',', digits=1, nsmall=1, scientific=FALSE))
-		}
-	} else {
-    	paste(x)      
-	}
-}
-knitr::knit_hooks$set(inline=inline_hook)
 ```
@@
 ```{r LoadData, eval=TRUE, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
-######################################################################
-#----------- Read in important functions & load data-----------------#
-######################################################################
 source("../code/load_data.R")
-
-######################################################################
-#----------- Read in analysis and plots-----------------#
-######################################################################
-source("../code/analyze_micro_immuno.R")
-
 ```
 
-\vspace{35mm}
+\vspace{30mm}
 
@@
 
-Ada K. Hagan${^1}$^ and Josie Libertucci${^2}$^
+Ada K. Hagan, Ph.D.${^1}$^ and Josie Libertucci, Ph.D.${^2}$^
 
-\vspace{40mm}
+\vspace{35mm}
 
-$\dagger$ To whom correspondence should be addressed: akhagan@umich.edu or
+$\dagger$ To whom correspondence should be addressed: akhagan@umich.edu or libertj@mcmaster.ca
 
-1\. Journals Department, American Society for Microbiology, Washington DC
+1\. Department of Microbiology & Immunology, University of Michigan, Ann Arbor, Michigan
 
-2\. Chemistry and Biology, Ryerson University, Toronto, Ontario
+2\. Department of Medicine, McMaster University, Hamilton, Ontario, Canada
+
+Figures:
+
+Tables:
+
+Supplemental:
 
@@
 
-## Importance
+## Keywords
+
+inclusion, diversity,
 
@@
 
-## Results
+500 words
 
-__Model selection and pipeline construction__
-
-[Figure 5].
-
-## Discussion
-
-In this study
+Representation of women and underrepresented minorities (URM) in science, technology, engineering, and math (STEM) in the workforce remains low despite equal enrollment in undergraduate STEM majors.
+Longitudinal data indicates that these discrepancies might be partially explained by low retention of women and URM in undergraduate STEM programs where academic performance is a key predictor of retention.
+A growing body of evidence suggests that women and URM underperform in introductory science courses compared to their white male colleagues, even when representation is equal.
+Additionally, there is evidence to suggest that women and URM participate less in class, which could inhibit the learning process and subsequent success.
+A prevailing hypothesis to explain achievement gaps and a lack of participation in class for women and URM is that, many students have an unconscious fear of being seen as a negative stereotype, termed stereotype threat.
+This is prevalent in fields that have historically been dominated by white males, such as in STEM.
+In order to retain a diverse population of students in STEM, in an effort to ensure all students have equal opportunities and resources to be successful, underperformance and a lack of participation in introductory science courses needs to be addressed.
+One mechanism to address the issue is through the use of inclusive teaching practices –teaching methods that promote the full participation, learning, and success of all students.
 
@@
 
-**Data collection and gender assignment.**
-
-  Historical information on invited speakers and their hosts were obtained from departmental records of five academic years (Fall 2014 - Spring 2019).
+**Data collection and demographic determination.** Historical information on invited speakers and their hosts were obtained from the departmental records of five academic years (Fall 2014 - Spring 2019).
 Each speaker was only counted once and any departmental faculty members or those listed as a "host" at any point were not considered "invited speakers".
@@
 Race/ethnicity was assigned using the current U.S.
-Census definition where "Caucasian" includes Middle Eastern, European, and Russian.
-Because of the small "n" of this dataset, those non-Caucasians are referred to collectively as Men or Women of Color.
+Census definition where "Caucasian" includes those of Middle Eastern, European, and Russian descent.
+Historically Underrepresented Minority (HURM) individuals are restricted to those with African-American, Indigenous and/or Hispanic heritage.
+International indviduals were either visiting the US at the time of their talk, or immigrated to the US as an adult.
 Individual assignments can be found in the anonymized dataset.
 
-**Code and Data availability.**
+**Code and data availability.** The anonymized data, code for all analysis steps and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/.
 
-  The anonymized data, the code for all analysis steps and an Rmarkdown version of this manuscript is available at https://github.com/LibertucciLab/Hagan_SpDiv_XXXX_2019/.
+## Results
 
-\newpage
-\includegraphics{Figure_1}
-**Figure 1.
-Machine learning pipeline showing predictive model training and evaluation flowchart.
-**  We split the data 80%/20% stratified to maintain the overall label distribution, performed five-fold cross-validation on the training data to select the best hyperparameter setting and then using these hyperparameters to train all of the training data.
-The model was evaluated on a held-out set of data (not used in selecting the model).
-Abbreviations: AUROC, area under the receiver operating characteristic curve
-\newpage
-\includegraphics{Figure_2.png}
-**Figure 2.
-Generalization and classification performance of ML models using AUROC values of all cross validation and testing performances.
-**   The median AUROC for diagnosing individuals with SRN using bacterial abundances was higher than chance (depicted by horizontal line at 0.50) for all the ML models.
-Discriminative performance of random forest model was higher than other ML models.
-The boxplot shows quartiles at the box ends and the statistical median as the horizontal line in the box.
-The whiskers show the farthest points that are not outliers.
-Outliers are data points that are not within 3/2 times the interquartile ranges.
-Abbreviations: SRN, screen-relevant neoplasias; AUROC, area under the receiver operating characteristic curve; SVM, support vector machine; XGBoost, extreme gradient boosting
-\newpage
-\includegraphics{Figure_3.png}
-**Figure 3.
-Interpretation of the linear ML models.** (A) L2 logistic regression coefficients  (B) L1 SVM with linear kernel feature weights (C) L2 SVM with linear kernel feature weights.
-The means weights and coefficients of the most important five OTUs for each model are shown here with the standard deviation over 100 data-splits.
-Similar OTUs had the largest impact on the predictive performance of L2 logistic regression and L2 SVM with linear kernel.
-Abbreviations: SVM, support vector machine; OTU, Operational Taxonomic Unit.
-\newpage
-\includegraphics{Figure_4.png}
-**Figure 4.
-Explanation of the non-linear ML models.** (A) SVM with radial basis kernel (B) decision tree (C) random forest (D) XGboost feaure importances were explanied using permutation importance using held-out test set.
-The gray rectangle and the dashed line show the IQR range and median of the base testing AUROC without any permutation performed.
-For all the tree-based models, a *Peptostreptococcus* species (OTU00367) had the largest impact on predictive performance of the model.
-Abbreviations: SVM, support vector machine; OTU, Operational Taxonomic Unit; RBF, radial basis kernel; OTU, Operational Taxonomic Unit.
-\newpage
-\includegraphics{Figure_5.png}
-**Figure 5.
-Computational efficiency of seven ML models.** The traintimes for training and testing of each data-split showed the differences in computational efficieny of the seven models.
-The median traintime in hours was the highest for XGBoost and shortest for L2 logistic regression.
-The boxplot shows quartiles at the box ends and the statistical median as the horizontal line in the box.
-The whiskers show the farthest points that are not outliers.
-Outliers are data points that are not within 3/2 times the interquartile ranges.
-Abbreviations: AUROC, area under the receiver operating characteristic curve; SVM, support vector machine; XGBoost, extreme gradient boosting.  
-\newpage
-\includegraphics{Figure_S1.png}
-**Figure S1. Hyperparameter setting performances for linear models.** 
-Abbreviations: 
-\newpage
-\includegraphics{Figure_S2.png}
-**Figure S2. Hyperparameter setting performances for non-linear models.** 
-Abbreviations: 
-\newpage
+__Model selection and pipeline construction__
+
+![Figure 1.]().
+
+## Discussion
+
+500 words. In this study
 

### 2019-08-23 submission/manuscript.tex
format for JMBE

\documentclass[10pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Department Invited Speakers Do Not Reflect Trainee Diversity},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{\textbf{Department Invited Speakers Do Not Reflect Trainee Diversity}}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{caption}

\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}

\usepackage[none]{hyphenat}

\usepackage{setspace}
\doublespacing
\setlength{\parskip}{1em}

\usepackage{lineno}

\usepackage{pdfpages}
\floatplacement{figure}{H} % Keep the figure up top of the page
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}
\maketitle

\vspace{30mm}

Running title: Invited Speaker Diversity Does Not Reflect Trainee
Diversity

\vspace{35mm}

Ada K. Hagan, Ph.D.\({^1}\)\^{} and Josie Libertucci, Ph.D.\({^2}\)\^{}

\vspace{35mm}

\(\dagger\) To whom correspondence should be addressed:
\href{mailto:akhagan@umich.edu}{\nolinkurl{akhagan@umich.edu}} or
\href{mailto:libertj@mcmaster.ca}{\nolinkurl{libertj@mcmaster.ca}}

1. Department of Microbiology \& Immunology, University of Michigan, Ann
Arbor, Michigan

2. Department of Medicine, McMaster University, Hamilton, Ontario,
Canada

Figures:

Tables:

Supplemental:

\newpage

\linenumbers

\subsection{Abstract}\label{abstract}

250 words or less

\subsection{Keywords}\label{keywords}

\newpage

\subsection{Background}\label{background}

\subsection{Results}\label{results}

\textbf{Model selection and pipeline construction}

{[}Figure 5{]}.

\subsection{Discussion}\label{discussion}

In this study

\subsection{Methods}\label{methods}

\textbf{Data collection and demographic determination.} Historical
information on invited speakers and their hosts were obtained from the
departmental records of five academic years (Fall 2014 - Spring 2019).
Each speaker was only counted once and any departmental faculty members
or those listed as a ``host'' at any point were not considered ``invited
speakers''. The list of current trainees (Spring 2019), was obtained
from department listservs and included masters students, doctoral
students, and post-doctoral fellows. Demographics for invited speakers,
hosts, and trainees were hand-coded using personal knowledge, photos,
and CVs. Presenting gender was assigned using a binary system
(man/woman). Race/ethnicity was assigned using the current U.S. Census
definition where ``Caucasian'' includes those of Middle Eastern,
European, and Russian descent. Historically Underrepresented Minority
(HURM) individuals are restricted to those with African-American,
Indigenous and/or Hispanic heritage. International indviduals were
either visiting the US at the time of their talk, or immigrated to the
US as an adult. Individual assignments can be found in the anonymized
dataset.

\textbf{Code and data availability.} The anonymized data, code for all
analysis steps and an Rmarkdown version of this manuscript is available
at
\url{https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/}.

\subsection{References}\label{references}

\hypertarget{refs}{}

\end{document}

### 2019-09-05 code/demo_comp.R
add tidy df to include faculty in plots

@@ -1,12 +1,9 @@
 #what are the trainee demographics?----
 
-speaker_demo <- tidy_speaker %>% 
-  filter(demographic != "Gender")
-
-trainee_demo <- tidy_trainee %>% 
-  filter(demographic != "Gender") 
-  
-demo_combined <- rbind(trainee_demo, speaker_demo) %>% 
+demo_combined <- tidy_host %>% 
+  filter(role == "Faculty") %>% 
+  rbind(., tidy_trainee, tidy_speaker) %>% 
+  filter(demographic != "Gender") %>% 
   group_by(demographic, role, value) %>% summarise(n = n()) %>% 
   spread(key = value, value = n) %>% 
   mutate(prop_y = get_percent(y, (y + n)))
@@ -21,3 +18,4 @@ demo_combined %>%
   set_role_colors +
   my_theme_horiz
 
+#add host demo

### 2019-09-05 code/gender_comp.R

@@ -1,11 +1,9 @@
 #compare gender compositions for trainees and speakers
-trainee_gender <- tidy_trainee %>% 
-  filter(demographic == "Gender")  
 
-speaker_gender <- tidy_speaker %>% 
-  filter(demographic == "Gender")
-
-gender_combined <- rbind(trainee_gender, speaker_gender) %>% 
+gender_combined <- tidy_host %>% 
+  filter(role == "Faculty") %>% 
+  rbind(., tidy_trainee, tidy_speaker) %>% 
+  filter(demographic == "Gender") %>% 
   group_by(role, value) %>% summarise(n = n()) %>% 
   spread(key = value, value = n) %>% 
   mutate(prop_W = get_percent(woman, (man + woman)))
@@ -16,6 +14,8 @@ gender_fig <- gender_combined %>%
   ggplot()+
   geom_col(aes(x = role, y = prop_W, fill = role), alpha = 0.75)+
   labs(x = "Academic Role", y = "Proportion of Women")+
-  geom_text()+
+  #geom_text(prop_W)+
   set_role_colors +
   my_theme_horiz
+
+#add host demo

### 2019-09-05 code/get_plot_options.R

@@ -1,7 +1,15 @@
 library(scales)
 library(RColorBrewer)
-library(cowplot)
+#library(cowplot)
 #library(patchwork)
+
+#settings----
+dat_levels <- c("Student", "Postdoc", "Faculty", "Speaker")
+
+dat_linetype <- c("solid", "dashed", "dotted")
+
+dat_colors <- c("#E69F00", "#0072B2", "#009E73", "#999999")
+
 
 #preferred themes----
 my_theme <- theme_classic() + 
@@ -28,7 +36,7 @@ my_theme_leg_horiz <- theme_classic() +
   theme(axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
         plot.title = element_text(size=16,face="bold"))
 
-#adding proportion/count labels to barchart
+#adding proportion/count labels to barchart----
 prop_lab_low <- geom_text(aes(label = scales::percent((..count..)/sum(..count..)), y= ((..count..)/sum(..count..))), stat = "count", vjust = 1)
 
 count_lab_low <- geom_text(stat = "count", aes(label=..count..), vjust = 1)
@@ -37,26 +45,19 @@ prop_lab_high <- geom_text(aes(label = scales::percent((..count..)/sum(..count..
 
 count_lab_high <- geom_text(stat = "count", aes(label=..count..), vjust = -1)
 
-#colorblind palettes
+#colorblind palettes----
 #The palette with grey:
 cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7") #grey, goldenrod, light blue, dark green, gold, navy blue, orange rust, pink
 
 # The palette with black:
 cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7") #black
 
-#gradient for comparing "performance"
+#plot options----
 gen_gradient <- scale_fill_gradient2(low = "#D55E00", mid='snow3', 
                                      high = "#0072B2", space = "Lab")
 
 set_role_colors <- scale_fill_manual(breaks = dat_levels,
                                      values = dat_colors)
-
-#settings----
-dat_levels <- c("Student", "Postdoc", "Speaker")
-
-dat_linetype <- c("solid", "dashed", "dotted")
-
-dat_colors <- c("#E69F00", "#0072B2", "#999999")
 
 gen_ed_facet <- function(x){
   ifelse(x == "female", "Woman", "Man")

### 2019-09-05 code/load_data.R

@@ -18,7 +18,8 @@ get_percent <- function(x, y){
 
 #data setup----
 speaker_data <- read_csv("../data/speaker_dataset_14-19.csv") %>% 
-  mutate(Speaker_id = rownames(.)) %>% 
+  mutate(Speaker_id = rownames(.),
+         Host_id = rownames(.)) %>% 
   rename(Speaker_Caucasian = Speaker_caucasian, 
          Speaker_Gender = Speaker_gender)
 
@@ -30,7 +31,21 @@ tidy_speaker <- speaker_data %>%
   rename(id = Speaker_id) %>% 
   mutate(demographic = if_else(demographic == "Internatl", 
                                "International", demographic))
-
+tidy_host <- speaker_data %>% 
+  select(contains("Host")) %>% 
+  gather(Host_gender:Host_Internatl, 
+         key = demographic, value = value) %>% 
+  separate(demographic, into = c("role", "demographic"), sep = "_") %>% 
+  rename(id = Host_id) %>% 
+  mutate(demographic = case_when(
+    demographic == "Internatl" ~ "International",
+    demographic == "gender" ~ "Gender",
+    demographic == "caucasian" ~ "Caucasian",
+    TRUE ~ demographic
+  )) %>% 
+  select(-role) %>% 
+  rename(role = Host) 
+  
 trainee_data <- read_csv("../data/trainee_data_19.csv") %>% 
   mutate(id = rownames(.))
 

### 2019-09-05 submission/manuscript.Rmd
work on outline

@@
 ######################################################################
-deps = c("kableExtra","knitr","rmarkdown","hexbin","lubridate", "tidyverse", "markdown", "formattable");
+deps = c("knitr","rmarkdown", "lubridate", "tidyverse", "markdown");
 for (dep in deps){
@@
 
-inclusion, diversity,
+inclusion, diversity, invited speakers, academia, graduate programs
 
@@
 
-Representation of women and underrepresented minorities (URM) in science, technology, engineering, and math (STEM) in the workforce remains low despite equal enrollment in undergraduate STEM majors.
+Representation of white women and historically underrepresented minorities (HURM) in science, technology, engineering, and math (STEM) in the workforce remains low despite equal enrollment in undergraduate STEM majors.
 Longitudinal data indicates that these discrepancies might be partially explained by low retention of women and URM in undergraduate STEM programs where academic performance is a key predictor of retention.
@@
 
-##Methods
+## Methods
 
 **Data collection and demographic determination.** Historical information on invited speakers and their hosts were obtained from the departmental records of five academic years (Fall 2014 - Spring 2019).
-Each speaker was only counted once and any departmental faculty members or those listed as a "host" at any point were not considered "invited speakers".
+Each speaker was only counted once and any departmental faculty members or those listed as a "host" at any point could not also be considered "invited speakers".
 The list of current trainees (Spring 2019), was obtained from department listservs and included masters students, doctoral students, and post-doctoral fellows.
@@
 
-**Code and data availability.** The anonymized data, code for all analysis steps and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/.
+**Code and data availability.** The anonymized data, code for all analysis steps, and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/.
 
-## Results
-
-__Model selection and pipeline construction__
+## Results and Discussion
 
@@
 
-## Discussion
+500 words. In this study
 
-500 words. In this study
++ there are speakers who have URM status, but it wasn't readily apparent from the internet/CV 
++ perspective is often as/more important than self-identification -- in addition to self-selecting on Diversify lists, consider sharing more about their past
++ idea for departments to invite speakers to share about their personal story as well as their science
++ use Diversify sources
++ US-serving institutions, need to pay attention to US-HURM
+
+## Conclusion
+
+## Acknowledgements
+
+We thank Harry Mobley and the Department of Microbiology & Immunology, University of Michigan for their support and input.
+We would also like to acknowledge Nick Lesniak and Dr.
+Ariangela Kozick for their comments and suggestions.
 

### 2019-09-05 submission/manuscript.Rmd
further outline manuscript, add Diversify

@@
 
++ previous examinations have focused on conferences and panels, large number of people in a short period of time -- easy to make comparisons & see trends
+
++ more difficult to see trends over long time period -- asked cumulative trends of speakers over 5 year period, "normative" to trainees in the department
+
 ## Methods
@@
 **Code and data availability.** The anonymized data, code for all analysis steps, and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/.
+Template and complete instructions for generating a field-specific Diversity website are available at https://github.com/diversifymicrobiology/DiversifyMicrobiology.github.io/.
 
@@
 
-![Figure 1.]().
++ Gender
+    + decreasing representation of women in each role (as prestige increases)
+    + compare to global stats of Micro resources 60:40 (Elseiver)
+    + previous study at 50 US universities focusing on genders
+    + discuss factors that decrease speaking invitations to women
 
-500 words. In this study
++ Under represented minorites
+    + overrepresentation of Caucasian individuals as Faculty & Speakers, relative to trainees
+    + decline in HURM & International as Fac/Speak, relative to trainees
+    + inclination to lump HURM & International together to improve diversity stats
+    + important to distinguish separately as both face different issues in the US & academy
 
-+ there are speakers who have URM status, but it wasn't readily apparent from the internet/CV 
-+ perspective is often as/more important than self-identification -- in addition to self-selecting on Diversify lists, consider sharing more about their past
-+ idea for departments to invite speakers to share about their personal story as well as their science
-+ use Diversify sources
-+ US-serving institutions, need to pay attention to US-HURM
++ Improving speaker diversity
+    + US-serving institutions have particular responsibility to those historically supressed populations
+    + to improve retention of white women & HURMs, each group needs equivalent representation to counteract biases and improve self-efficacy
+    + recall bias not the only issue, also not always possible to identify members of historically underserved communities
+    + example: there are speakers who have URM status, but it wasn't readily apparent from the internet/CV 
+    + perspective is often as/more important than self-identification
+
++ Development of Diversify tools
+    + inspired by EEB/Chemistry
+    + tool for members of URM groups to self-identify & for others to use to find diverse candidates
+    + describe maintanence of lists (Rebecca)
+    + describe website creation
+
++ Other resources/ideas
+    + student/lab invited speakers -- improve diversity of suggestions (fields/careers)
+    + departments to invite speakers to share about their personal story as well as their science
 
 ## Conclusion
+
++ increased retention of white women & HURMS -- increasing representation of 
++ tools available to create field specific lists of H underserved
 
@@
 
+## Author Contributions
+A.K.H.
+collected the data, assigned demographics, analyzed the data, and created the website.
+R.P.
+created the lists, forms, and website content.
+J.L.
+wrote the introduction and provided conceptual advice.
+All authors contributed to the final manuscript.
+
+![Figure 1.]().
+
+Table 1. List of Suggestions & Resources
+
 ## References

### 2019-09-05 submission/manuscript.Rmd
work on results & discussion

@@
 
++ introduce invited speaker series - what are the goals, who attends, etc.
+
 + previous examinations have focused on conferences and panels, large number of people in a short period of time -- easy to make comparisons & see trends
@@
 Each speaker was only counted once and any departmental faculty members or those listed as a "host" at any point could not also be considered "invited speakers".
-The list of current trainees (Spring 2019), was obtained from department listservs and included masters students, doctoral students, and post-doctoral fellows.
+The list of faculty hosts was used as a proxy for faculty demographics since each faculty member has the opportunity to invite one speaker per year.
+The list of trainees (Spring 2019), was obtained from department listservs and included masters students, doctoral students, and post-doctoral fellows.
   Demographics for invited speakers, hosts, and trainees were hand-coded using personal knowledge, photos, and CVs.
@@
 
-+ Gender
-    + decreasing representation of women in each role (as prestige increases)
-    + compare to global stats of Micro resources 60:40 (Elseiver)
-    + previous study at 50 US universities focusing on genders
-    + discuss factors that decrease speaking invitations to women
+To understand the representation of women, we compared the proportion of individuals presenting as women in each academic role.
+At the trainee level, more than half of students and postdoctoral fellows were women.
+That dropped to X% of faculty hosts and X% of the invited speakers.
+[what about lectureships?] The proportion of women as faculty hosts and speakers is equvialent to global estimates of women microbiologists (Elseiver).
+Several papers have investigated the representation of women at scientific conferences, however, we only identified one that focused on invited speakers at university-sponsored events (Nittrouer, 2018).
+[Compare to our findings]
 
-+ Under represented minorites
-    + overrepresentation of Caucasian individuals as Faculty & Speakers, relative to trainees
-    + decline in HURM & International as Fac/Speak, relative to trainees
-    + inclination to lump HURM & International together to improve diversity stats
-    + important to distinguish separately as both face different issues in the US & academy
+Assumptions about competency and dedication may negatively impact the liklihood of women microbiologists being invited as speakers.
+The  dedication of women with family to their work is also more likely to be questioned than that of their colleagues, even men who also have children.
+For instance, the percieved prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigous nature of these inviations), causing the faculty member to invite a different colleague who they feel is less likely to turn them down.
+Departments have different processes and criteria for selecting invited speakers, but want to bring the best scientists possible.
+It may be that the definition of "best" poses a problem to women, who need three-times as many publications as their men collegues to be considered equally competent.
+Some departments only invite tenured faculty, which severely limits the number of potential women speakers considerably.
+Alternately, pre-tenure faculty members invite presitgous, tenured faculty in their field to network and secure letters for their own tenure package.
+The increased burden of women to prove competency decreases their likihood to be considered for either tenure and as possible source of tenure letters.
+
+Our analysis identified an overrepresentation of Caucasian individuals as hosting faculty and invited speakers, relative to the proportion of Caucasian trainees.
+Diversity definitions vary according to the goals and population in question.
+However, in the United States, there is an inclination to lump individuals of HURM and international backgrounds together to improve diversity statistics.
+We argue that it is important to distinguish these two groups separately since each face different issues in the US and the academy.
+For instance, international scientists face more issues with visas while HURMs must contend with a country who systematically shuts them out despite an infrastructure that was built on their historical land and labor.
+For this reason, and to provide more resolution to the analysis, individuals were also given additional designations such as HURM and international.
+We observed declines in the representation of HURM and international faculty and speakers relative to the trainees.
+[Lectureships].
 

### 2019-09-09 submission/manuscript.Rmd
generate figure 1

@@
 
-```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE}
+```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE, include=FALSE}
 ######################################################################
@@
 ######################################################################
-deps = c("knitr","rmarkdown", "lubridate", "tidyverse", "markdown");
+deps = c("knitr","rmarkdown", "markdown");
 for (dep in deps){
@@
 opts_chunk$set("tidy" = TRUE)
-opts_chunk$set("echo" = FALSE)
-opts_chunk$set("eval" = TRUE)
-opts_chunk$set("warning" = FALSE)
-opts_chunk$set("cache" = FALSE)
 ```
 
-```{r LoadData, eval=TRUE, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
+```{r LoadData, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
 source("../code/load_data.R")
+source("../code/get_figures.R")
 ```
@@
 
-Ada K. Hagan, Ph.D.${^1}$^ and Josie Libertucci, Ph.D.${^2}$^
+Ada K. Hagan, Ph.D.${^1}$^, Rebecca M. Pollet, Ph.D.${^1}$^, and Josie Libertucci, Ph.D.${^2}$^
 
@@
 Longitudinal data indicates that these discrepancies might be partially explained by low retention of women and URM in undergraduate STEM programs where academic performance is a key predictor of retention.
-A growing body of evidence suggests that women and URM underperform in introductory science courses compared to their white male colleagues, even when representation is equal.
+A growing body of evidence suggests that women and URM under-perform in introductory science courses compared to their white male colleagues, even when representation is equal.
 Additionally, there is evidence to suggest that women and URM participate less in class, which could inhibit the learning process and subsequent success.
@@
 This is prevalent in fields that have historically been dominated by white males, such as in STEM.
-In order to retain a diverse population of students in STEM, in an effort to ensure all students have equal opportunities and resources to be successful, underperformance and a lack of participation in introductory science courses needs to be addressed.
+In order to retain a diverse population of students in STEM, in an effort to ensure all students have equal opportunities and resources to be successful, under-performance and a lack of participation in introductory science courses needs to be addressed.
 One mechanism to address the issue is through the use of inclusive teaching practices –teaching methods that promote the full participation, learning, and success of all students.
@@
 ## Methods
+Each academic year, each faculty member in the Department of Microbiology and Immunology at the University of Michigan has the opportunity to invite one speaker per year for a weekly seminar series.
+Some of these seminar slots are dedicated to named lectureships, which are decided by committee, and three trainee-invited speakers.
+We analyzed the gender and demographics of invited speakers and faculty hosts for five academic years (Fall 2014 - Spring 2019), and the current trainees when the data were analyzed (Spring 2019).
 
-**Data collection and demographic determination.** Historical information on invited speakers and their hosts were obtained from the departmental records of five academic years (Fall 2014 - Spring 2019).
 Each speaker was only counted once and any departmental faculty members or those listed as a "host" at any point could not also be considered "invited speakers".
-The list of faculty hosts was used as a proxy for faculty demographics since each faculty member has the opportunity to invite one speaker per year.
-The list of trainees (Spring 2019), was obtained from department listservs and included masters students, doctoral students, and post-doctoral fellows.
-  Demographics for invited speakers, hosts, and trainees were hand-coded using personal knowledge, photos, and CVs.
-Presenting gender was assigned using a binary system (man/woman).
-Race/ethnicity was assigned using the current U.S.
-Census definition where "Caucasian" includes those of Middle Eastern, European, and Russian descent.
-Historically Underrepresented Minority (HURM) individuals are restricted to those with African-American, Indigenous and/or Hispanic heritage.
-International indviduals were either visiting the US at the time of their talk, or immigrated to the US as an adult.
-Individual assignments can be found in the anonymized dataset.
+The list of faculty hosts was used as a proxy for faculty demographics since as hosts, these faculty members are visible representatives of the department.
+The list of trainees was obtained from department listservs and included masters students, doctoral students, and post-doctoral fellows.
 
-**Code and data availability.** The anonymized data, code for all analysis steps, and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/.
-Template and complete instructions for generating a field-specific Diversity website are available at https://github.com/diversifymicrobiology/DiversifyMicrobiology.github.io/.
+We hand-coded demographics using personal knowledge, photos, and CVs.
+The presenting gender if each invidual was assigned using a binary system (man/woman).
+Other assigned demographics included Caucasian, Historically Under-represented Minority (HURM), and International, each with a binary (yes/no) possibilty.
+Caucasian was assigned using the current U.S.
+Census definition where those of Middle Eastern, European, and Russian descent are included.
+HURM individuals were restricted to those with African-American, Indigenous and/or Hispanic heritage while International individuals were either visiting the US at the time of their talk, or immigrated to the US as an adult.
 
@@
 That dropped to X% of faculty hosts and X% of the invited speakers.
-[what about lectureships?] The proportion of women as faculty hosts and speakers is equvialent to global estimates of women microbiologists (Elseiver).
+10 of 31 lectureships [what about lectureships?] The proportion of women as faculty hosts and speakers is equivalent to global estimates of women microbiologists (Elseiver).
 Several papers have investigated the representation of women at scientific conferences, however, we only identified one that focused on invited speakers at university-sponsored events (Nittrouer, 2018).
@@
 
-Assumptions about competency and dedication may negatively impact the liklihood of women microbiologists being invited as speakers.
+Assumptions about competency and dedication may negatively impact the likelihood of women microbiologists being invited as speakers.
 The dedication of women with family to their work is also more likely to be questioned than that of their colleagues, even men who also have children.
-For instance, the percieved prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigous nature of these inviations), causing the faculty member to invite a different colleague who they feel is less likely to turn them down.
+For instance, the perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigious nature of these invitations), causing the faculty member to invite a different colleague who they feel is less likely to turn them down.
 Departments have different processes and criteria for selecting invited speakers, but want to bring the best scientists possible.
-It may be that the definition of "best" poses a problem to women, who need three-times as many publications as their men collegues to be considered equally competent.
+It may be that the definition of "best" poses a problem to women, who need three-times as many publications as their men colleges to be considered equally competent.
 Some departments only invite tenured faculty, which severely limits the number of potential women speakers considerably.
-Alternately, pre-tenure faculty members invite presitgous, tenured faculty in their field to network and secure letters for their own tenure package.
-The increased burden of women to prove competency decreases their likihood to be considered for either tenure and as possible source of tenure letters.
+Alternately, pre-tenure faculty members invite prestigious, tenured faculty in their field to network and secure letters for their own tenure package.
+The increased burden of women to prove competency decreases their likelihood to be considered for either tenure and as possible source of tenure letters.
 
-Our analysis identified an overrepresentation of Caucasian individuals as hosting faculty and invited speakers, relative to the proportion of Caucasian trainees.
+Our analysis identified an over-representation of Caucasian individuals as hosting faculty and invited speakers, relative to the proportion of Caucasian trainees.
 Diversity definitions vary according to the goals and population in question.
@@
 We observed declines in the representation of HURM and international faculty and speakers relative to the trainees.
-[Lectureships].
 
+[Lectureships]. 22, 3, 6, (cauc, HURM, Internatl, respectively) -- 12, 10, 5, 0 (CaucM, CaucW, Non-CaucM, Non-CaucW)
+
+## Call to Action
 + Improving speaker diversity
-    + US-serving institutions have particular responsibility to those historically supressed populations
+    + US-serving institutions have particular responsibility to those historically suppressed populations
     + to improve retention of white women & HURMs, each group needs equivalent representation to counteract biases and improve self-efficacy
-    + recall bias not the only issue, also not always possible to identify members of historically underserved communities
+    + recall bias not the only issue, also not always possible to identify members of historically under-served communities
     + example: there are speakers who have URM status, but it wasn't readily apparent from the internet/CV 
@@
     + tool for members of URM groups to self-identify & for others to use to find diverse candidates
-    + describe maintanence of lists (Rebecca)
+    + describe maintenance of lists (Rebecca)
     + describe website creation
@@
 + increased retention of white women & HURMS -- increasing representation of 
-+ tools available to create field specific lists of H underserved
++ tools available to create field specific lists of H under-served
 
@@
 R.P.
-created the lists, forms, and website content.
+created the Google lists, forms, and website content and the description of their maintenance.
 J.L.
@@
 All authors contributed to the final manuscript.
+
+## Code and data availability
+The anonymized data, code for all analysis steps, and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/.
+Template and complete instructions for generating a field-specific Diversity website are available at https://github.com/diversifymicrobiology/DiversifyMicrobiology.github.io/.
 

### 2019-09-09 code/demo_comp.R

@@ -10,12 +10,14 @@ demo_combined <- tidy_host %>%
   
 demo_combined$role <- fct_relevel(demo_combined$role, dat_levels)
 
-demo_combined %>% 
+demo_plot <- demo_combined %>% 
   ggplot()+
   geom_col(aes(x = role, y = prop_y, fill = role), alpha = 0.75)+
   facet_wrap(~demographic)+
-  labs(x = "Academic Role", y = "Proportion of Population")+
+  labs(x = "Academic Role\n", y = "Proportion of Population")+
   set_role_colors +
-  my_theme_horiz
+  my_theme_horiz +
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
 
 #add host demo

### 2019-09-09 code/gender_comp.R

@@ -10,12 +10,14 @@ gender_combined <- tidy_host %>%
 
 gender_combined$role <- fct_relevel(gender_combined$role, dat_levels)
 
-gender_fig <- gender_combined %>% 
+gender_plot <- gender_combined %>% 
   ggplot()+
   geom_col(aes(x = role, y = prop_W, fill = role), alpha = 0.75)+
-  labs(x = "Academic Role", y = "Proportion of Women")+
-  #geom_text(prop_W)+
+  labs(x = "Academic Role\n", y = "Proportion of Population", 
+       fill = "Academic Role")+
   set_role_colors +
-  my_theme_horiz
+  my_theme_leg_horiz+
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
 
 #add host demo

### 2019-09-09 code/get_figures.R

@@ -1,0 +1,17 @@
+source("../code/demo_comp.R")
+source("../code/gender_comp.R")
+source("../code/lectureship_div.R")
+
+blank <- ggplot()
+
+top_row <- plot_grid(gender_plot, blank,
+                     rel_widths = c(2,1))
+
+bottom_row <- plot_grid(lectureship_demo_plot, lectureship_gend_plot,
+                        labels = c("C", "D"), label_size = 18)
+
+plot_grid(top_row, demo_plot, bottom_row, labels = c("A", "B", ""),
+          label_size = 18, nrow = 3, rel_widths = c(1, 3, 1))
+
+ggsave("Figure_1.png", device = 'png', 
+       path = 'submission', width = 12, height = 12)

### 2019-09-09 code/get_plot_options.R

@@ -1,6 +1,6 @@
 library(scales)
 library(RColorBrewer)
-#library(cowplot)
+library(cowplot)
 #library(patchwork)
 
 #settings----

### 2019-09-09 code/lectureship_div.R

@@ -1,44 +1,39 @@
-#What are the proportions of M/F, W/POC for lectureships ----
-MI_diversify %>% 
-  filter(!is.na(Lectureship)) %>% 
-  filter(Host != "Student" | Host != "Postdoc") %>% 
-  group_by(speaker_div) %>% summarise(n = n()) %>% 
-  add_row(., speaker_div = "WOC", n = 0) %>% 
-  mutate(percent = (n/sum(n))*100) %>% 
-  ggplot(aes(x = speaker_div))+
-  geom_col(aes(y = percent))+
-  #scale_y_continuous(labels = scales::percent)+
-  #geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
-  labs(y = "Percent of Lectureships", x = "Speaker Demographics")+
-  theme_classic() + 
-  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
-        plot.title = element_text(size=16,face="bold"))
-
-MI_diversify %>% 
-  filter(!is.na(Lectureship)) %>% 
-  filter(Host != "Student" | Host != "Postdoc") %>% 
-  ggplot(aes(x = Speaker_caucasian))+
-  geom_bar(aes(y = (..count..)/sum(..count..)))+
-  scale_y_continuous(labels = scales::percent)+
-  geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
-  labs(y = "Percent of Speakers", x = "Is Speaker Caucasian?")+
-  theme_classic() + 
-  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"), 
-        plot.title = element_text(size=16,face="bold"))
-
-MI_diversify %>% 
+#What are the proportions of each demographic for lectureships ----
+lectureship <- speaker_data %>% 
   filter(!is.na(Lectureship)) %>% 
   filter(Host != "Student") %>% 
-  filter(Host != "Postdoc") %>%
-  ggplot(aes(x = factor(speaker_div, levels = c("Cauc M", "Cauc W", "MOC", "WOC"))))+
-  geom_bar(aes(y = (..count..)/sum(..count..), fill = Lectureship))+
-  scale_x_discrete(drop=FALSE)+
-  scale_y_continuous(labels = scales::percent)+
[…]

### 2019-09-10 code/get_figures.R
fix path

@@ -14,4 +14,4 @@ plot_grid(top_row, demo_plot, bottom_row, labels = c("A", "B", ""),
           label_size = 18, nrow = 3, rel_widths = c(1, 3, 1))
 
 ggsave("Figure_1.png", device = 'png', 
-       path = 'submission', width = 12, height = 12)
+       path = '../submission', width = 12, height = 12)

### 2019-09-10 submission/manuscript.Rmd
knit draft

@@
 The presenting gender if each invidual was assigned using a binary system (man/woman).
-Other assigned demographics included Caucasian, Historically Under-represented Minority (HURM), and International, each with a binary (yes/no) possibilty.
+Diversity definitions vary according to the goals and population in question.
+However, in the United States, there is an inclination to consider both individuals of historically under-represented minority (HURM) and international backgrounds together.
+We argue that it is important to distinguish these two groups separately since each face different issues in the US and the academy and thus require different support systems.
+For instance, international scientists must contend with visa issues while HURMs have the trauma associated with living in a country who systematically shuts them out (despite an infrastructure that was built on their historical land and labor).
+For this reason, other assigned demographics included Caucasian, Historically Under-represented Minority (HURM), and International, each with a binary (yes/no) possibilty.
 Caucasian was assigned using the current U.S.
@@
 Our analysis identified an over-representation of Caucasian individuals as hosting faculty and invited speakers, relative to the proportion of Caucasian trainees.
-Diversity definitions vary according to the goals and population in question.
-However, in the United States, there is an inclination to lump individuals of HURM and international backgrounds together to improve diversity statistics.
-We argue that it is important to distinguish these two groups separately since each face different issues in the US and the academy.
-For instance, international scientists face more issues with visas while HURMs must contend with a country who systematically shuts them out despite an infrastructure that was built on their historical land and labor.
-For this reason, and to provide more resolution to the analysis, individuals were also given additional designations such as HURM and international.
 We observed declines in the representation of HURM and international faculty and speakers relative to the trainees.
@@
 
-We thank Harry Mobley and the Department of Microbiology & Immunology, University of Michigan for their support and input.
+We thank Dr.
+Harry Mobley and the Department of Microbiology & Immunology, University of Michigan for their input and financial support that enabled publication of our manuscript.
 We would also like to acknowledge Nick Lesniak and Dr.
@@
 collected the data, assigned demographics, analyzed the data, and created the website.
-R.P.
+R.M.P.
 created the Google lists, forms, and website content and the description of their maintenance.
@@
 
-![Figure 1.]().
+![Figure 1.](Figure_1.png)
 

### 2019-09-10 submission/manuscript.tex
knit draft

@@
 \floatplacement{figure}{H} % Keep the figure up top of the page
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
 
@@
 
-Ada K. Hagan, Ph.D.\({^1}\)\^{} and Josie Libertucci, Ph.D.\({^2}\)\^{}
+Ada K. Hagan, Ph.D.\({^1}\)\^{}, Rebecca M. Pollet, Ph.D.\({^1}\)\^{},
+and Josie Libertucci, Ph.D.\({^2}\)\^{}
 
@@
 
-250 words or less
+\subsection{Keywords}\label{keywords}
 
-\subsection{Keywords}\label{keywords}
+inclusion, diversity, invited speakers, academia, graduate programs
 
@@
 
-\subsection{Results}\label{results}
+500 words
 
-\textbf{Model selection and pipeline construction}
+Representation of white women and historically underrepresented
+minorities (HURM) in science, technology, engineering, and math (STEM)
+in the workforce remains low despite equal enrollment in undergraduate
+STEM majors. Longitudinal data indicates that these discrepancies might
+be partially explained by low retention of women and URM in
+undergraduate STEM programs where academic performance is a key
+predictor of retention. A growing body of evidence suggests that women
+and URM under-perform in introductory science courses compared to their
+white male colleagues, even when representation is equal. Additionally,
+there is evidence to suggest that women and URM participate less in
+class, which could inhibit the learning process and subsequent success.
+A prevailing hypothesis to explain achievement gaps and a lack of
+participation in class for women and URM is that, many students have an
+unconscious fear of being seen as a negative stereotype, termed
+stereotype threat. This is prevalent in fields that have historically
+been dominated by white males, such as in STEM. In order to retain a
+diverse population of students in STEM, in an effort to ensure all
+students have equal opportunities and resources to be successful,
+under-performance and a lack of participation in introductory science
+courses needs to be addressed. One mechanism to address the issue is
+through the use of inclusive teaching practices --teaching methods that
+promote the full participation, learning, and success of all students.
 
-{[}Figure 5{]}.
-
-\subsection{Discussion}\label{discussion}
-
-In this study
+\begin{itemize}
+\item
+  introduce invited speaker series - what are the goals, who attends,
+  etc.
+\item
+  previous examinations have focused on conferences and panels, large
+  number of people in a short period of time -- easy to make comparisons
+  \& see trends
+\item
+  more difficult to see trends over long time period -- asked cumulative
+  trends of speakers over 5 year period, ``normative'' to trainees in
+  the department
+\end{itemize}
 
@@
 
-\textbf{Data collection and demographic determination.} Historical
-information on invited speakers and their hosts were obtained from the
-departmental records of five academic years (Fall 2014 - Spring 2019).
+Each academic year, each faculty member in the Department of
+Microbiology and Immunology at the University of Michigan has the
+opportunity to invite one speaker per year for a weekly seminar series.
+Some of these seminar slots are dedicated to named lectureships, which
+are decided by committee, and three trainee-invited speakers. We
+analyzed the gender and demographics of invited speakers and faculty
+hosts for five academic years (Fall 2014 - Spring 2019), and the current
+trainees when the data were analyzed (Spring 2019).
+
 Each speaker was only counted once and any departmental faculty members
-or those listed as a ``host'' at any point were not considered ``invited
-speakers''. The list of current trainees (Spring 2019), was obtained
+or those listed as a ``host'' at any point could not also be considered
+``invited speakers''. The list of faculty hosts was used as a proxy for
+faculty demographics since as hosts, these faculty members are visible
+representatives of the department. The list of trainees was obtained
 from department listservs and included masters students, doctoral
-students, and post-doctoral fellows. Demographics for invited speakers,
-hosts, and trainees were hand-coded using personal knowledge, photos,
-and CVs. Presenting gender was assigned using a binary system
-(man/woman). Race/ethnicity was assigned using the current U.S. Census
-definition where ``Caucasian'' includes those of Middle Eastern,
-European, and Russian descent. Historically Underrepresented Minority
-(HURM) individuals are restricted to those with African-American,
-Indigenous and/or Hispanic heritage. International indviduals were
-either visiting the US at the time of their talk, or immigrated to the
-US as an adult. Individual assignments can be found in the anonymized
-dataset.
+students, and post-doctoral fellows.
 
-\textbf{Code and data availability.} The anonymized data, code for all
-analysis steps and an Rmarkdown version of this manuscript is available
-at
+We hand-coded demographics using personal knowledge, photos, and CVs.
+The presenting gender if each invidual was assigned using a binary
+system (man/woman). Diversity definitions vary according to the goals
+and population in question. However, in the United States, there is an
+inclination to consider both individuals of historically
+under-represented minority (HURM) and international backgrounds
+together. We argue that it is important to distinguish these two groups
+separately since each face different issues in the US and the academy
+and thus require different support systems. For instance, international
+scientists must contend with visa issues while HURMs have the trauma
+associated with living in a country who systematically shuts them out
+(despite an infrastructure that was built on their historical land and
+labor). For this reason, other assigned demographics included Caucasian,
+Historically Under-represented Minority (HURM), and International, each
+with a binary (yes/no) possibilty. Caucasian was assigned using the
+current U.S. Census definition where those of Middle Eastern, European,
+and Russian descent are included. HURM individuals were restricted to
+those with African-American, Indigenous and/or Hispanic heritage while
+International individuals were either visiting the US at the time of
+their talk, or immigrated to the US as an adult.
+
+\subsection{Results and Discussion}\label{results-and-discussion}
+
+To understand the representation of women, we compared the proportion of
+individuals presenting as women in each academic role. At the trainee
+level, more than half of students and postdoctoral fellows were women.
+That dropped to X\% of faculty hosts and X\% of the invited speakers. 10
+of 31 lectureships {[}what about lectureships?{]} The proportion of
+women as faculty hosts and speakers is equivalent to global estimates of
+women microbiologists (Elseiver). Several papers have investigated the
+representation of women at scientific conferences, however, we only
+identified one that focused on invited speakers at university-sponsored
+events (Nittrouer, 2018). {[}Compare to our findings{]}
+
+Assumptions about competency and dedication may negatively impact the
+likelihood of women microbiologists being invited as speakers. The
+dedication of women with family to their work is also more likely to be
+questioned than that of their colleagues, even men who also have
+children. For instance, the perceived prioritization and commitments of
+women to family over work may cause faculty to doubt their acceptance of
+a speaking invitation (despite the prestigious nature of these
+invitations), causing the faculty member to invite a different colleague
+who they feel is less likely to turn them down. Departments have
+different processes and criteria for selecting invited speakers, but
+want to bring the best scientists possible. It may be that the
+definition of ``best'' poses a problem to women, who need three-times as
+many publications as their men colleges to be considered equally
+competent. Some departments only invite tenured faculty, which severely
+limits the number of potential women speakers considerably. Alternately,
+pre-tenure faculty members invite prestigious, tenured faculty in their
+field to network and secure letters for their own tenure package. The
+increased burden of women to prove competency decreases their likelihood
+to be considered for either tenure and as possible source of tenure
+letters.
+
+Our analysis identified an over-representation of Caucasian individuals
+as hosting faculty and invited speakers, relative to the proportion of
+Caucasian trainees. We observed declines in the representation of HURM
+and international faculty and speakers relative to the trainees.
+
+{[}Lectureships{]}. 22, 3, 6, (cauc, HURM, Internatl, respectively) --
+12, 10, 5, 0 (CaucM, CaucW, Non-CaucM, Non-CaucW)
+
+\subsection{Call to Action}\label{call-to-action}
+
+\begin{itemize}
+\tightlist
+\item
+  Improving speaker diversity
+
+  \begin{itemize}
+  \tightlist
+  \item
+    US-serving institutions have particular responsibility to those
+    historically suppressed populations
+  \item
+    to improve retention of white women \& HURMs, each group needs
+    equivalent representation to counteract biases and improve
+    self-efficacy
+  \item
+    recall bias not the only issue, also not always possible to identify
+    members of historically under-served communities
+  \item
+    example: there are speakers who have URM status, but it wasn't
+    readily apparent from the internet/CV
+  \item
+    perspective is often as/more important than self-identification
+  \end{itemize}
+\item
+  Development of Diversify tools
+
+  \begin{itemize}
+  \tightlist
+  \item
+    inspired by EEB/Chemistry
+  \item
+    tool for members of URM groups to self-identify \& for others to use
+    to find diverse candidates
+  \item
+    describe maintenance of lists (Rebecca)
+  \item
+    describe website creation
+  \end{itemize}
+\item
+  Other resources/ideas
+
+  \begin{itemize}
+  \tightlist
+  \item
+    student/lab invited speakers -- improve diversity of suggestions
+    (fields/careers)
+  \item
+    departments to invite speakers to share about their personal story
+    as well as their science
+  \end{itemize}
+\end{itemize}
+
+\subsection{Conclusion}\label{conclusion}
+
+\begin{itemize}
+\tightlist
+\item
+  increased retention of white women \& HURMS -- increasing
+  representation of
+\item
+  tools available to create field specific lists of H under-served
+\end{itemize}
+
+\subsection{Acknowledgements}\label{acknowledgements}
+
+We thank Harry Mobley and the Department of Microbiology \& Immunology,
+University of Michigan for their support and input. We would also like
+to acknowledge Nick Lesniak and Dr.~Ariangela Kozick for their comments
+and suggestions.
+
+\subsection{Author Contributions}\label{author-contributions}
+
+A.K.H. collected the data, assigned demographics, analyzed the data, and
+created the website. R.P. created the Google lists, forms, and website
+content and the description of their maintenance. J.L. wrote the
+introduction and provided conceptual advice. All authors contributed to
+the final manuscript.
+
+\subsection{Code and data
+availability}\label{code-and-data-availability}
+
+The anonymized data, code for all analysis steps, and an Rmarkdown
+version of this manuscript is available at
 \url{https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/}.
+Template and complete instructions for generating a field-specific
+Diversity website are available at
+\url{https://github.com/diversifymicrobiology/DiversifyMicrobiology.github.io/}.
+
+\begin{figure}
+\centering
+\includegraphics{Figure_1.png}
+\caption{Figure 1.}
+\end{figure}
+
+Table 1. List of Suggestions \& Resources
 

### 2019-09-10 submission/manuscript.Rmd
work on results

@@
 
-Ada K. Hagan, Ph.D.${^1}$^, Rebecca M. Pollet, Ph.D.${^1}$^, and Josie Libertucci, Ph.D.${^2}$^
+Ada K. Hagan, Ph.D.${^1\dagger}$, Rebecca M. Pollet, Ph.D.${^1}$, and Josie Libertucci, Ph.D.${^2\dagger}$
 
@@
 
-Figures:
+Figures: 1
 
-Tables:
+Tables: 1
 
@@
 Some of these seminar slots are dedicated to named lectureships, which are decided by committee, and three trainee-invited speakers.
-We analyzed the gender and demographics of invited speakers and faculty hosts for five academic years (Fall 2014 - Spring 2019), and the current trainees when the data were analyzed (Spring 2019).
-
-Each speaker was only counted once and any departmental faculty members or those listed as a "host" at any point could not also be considered "invited speakers".
+We analyzed the demographics of invited speakers and faculty hosts for five academic years (Fall 2014 - Spring 2019), and compared them to the current trainees when the data were analyzed (Spring 2019).
+Each speaker was only counted once and those listed as departmental faculty members or as a "host" at any point could not also be considered "invited speakers".
 The list of faculty hosts was used as a proxy for faculty demographics since as hosts, these faculty members are visible representatives of the department.
-The list of trainees was obtained from department listservs and included masters students, doctoral students, and post-doctoral fellows.
+The trainee lists were obtained from department listservs that included masters students, doctoral students, and post-doctoral fellows.
 
 We hand-coded demographics using personal knowledge, photos, and CVs.
-The presenting gender if each invidual was assigned using a binary system (man/woman).
+The presenting gender of each individual was assigned using a binary system (man/woman).
 Diversity definitions vary according to the goals and population in question.
-However, in the United States, there is an inclination to consider both individuals of historically under-represented minority (HURM) and international backgrounds together.
-We argue that it is important to distinguish these two groups separately since each face different issues in the US and the academy and thus require different support systems.
+However, in the United States, there is an inclination to consider both  together.
+We believe that it is important to distinguish between individuals of historically under-represented minority (HURM) and international backgrounds since each face different issues in the US and the academy and thus require different support systems.
 For instance, international scientists must contend with visa issues while HURMs have the trauma associated with living in a country who systematically shuts them out (despite an infrastructure that was built on their historical land and labor).
@@
 Census definition where those of Middle Eastern, European, and Russian descent are included.
-HURM individuals were restricted to those with African-American, Indigenous and/or Hispanic heritage while International individuals were either visiting the US at the time of their talk, or immigrated to the US as an adult.
+HURM individuals were restricted to those with African-American, Indigenous and/or Hispanic heritage while International individuals were either visiting the US at the time of their seminar, or immigrated to the US as an adult.
 
-## Results and Discussion
+## Results
 
-To understand the representation of women, we compared the proportion of individuals presenting as women in each academic role.
+To understand the representation of women, we compared the proportion of women in each academic role.
 At the trainee level, more than half of students and postdoctoral fellows were women.
-That dropped to X% of faculty hosts and X% of the invited speakers.
-10 of 31 lectureships [what about lectureships?] The proportion of women as faculty hosts and speakers is equivalent to global estimates of women microbiologists (Elseiver).
-Several papers have investigated the representation of women at scientific conferences, however, we only identified one that focused on invited speakers at university-sponsored events (Nittrouer, 2018).
-[Compare to our findings]
+That dropped to `r gender_combined[[1,5]]`% of faculty hosts and `r gender_combined[[3,5]]`% of the invited speakers (Fig.
+1A).
+Of 27 lectureships over the five year period, `r get_percent(10, 27)`% were awarded to women.
+The proportion of women as faculty hosts and speakers is equivalent to global estimates that 40% of microbiologists are women (Elseiver), with a slightly lower representation of women in lectureships.
 
-Assumptions about competency and dedication may negatively impact the likelihood of women microbiologists being invited as speakers.
-The dedication of women with family to their work is also more likely to be questioned than that of their colleagues, even men who also have children.
-For instance, the perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigious nature of these invitations), causing the faculty member to invite a different colleague who they feel is less likely to turn them down.
+Our analysis identified an over-representation of Caucasian individuals as hosting faculty and invited speakers, relative to the proportion of Caucasian trainees (Fig.
+1B).
+We also observed declines in the representation of HURM and international faculty and speakers relative to the trainees, particularly postdocs (Fig 1B).
+Caucasian scientists also dominated lectureships, comprising `r get_percent(22, 27)`% of those awarded (Fig.
+1C).
+Three and six lectureships were awarded to HURM and International scientists, respectively.
+Because the intersection of identities can compound biases and outcomes, we further examined the more prestigous lectureships by gender and Caucasian status.
+Caucasian men and women accounted for `r get_percent(12, 27)`% and `r get_percent(10, 27)`% of the lectureships, respectively, compared to `r get_percent(5, 27)`% non-Caucasian men and zero non-Caucasian women (Fig.
+1D).
+
+## Discussion
+
+Several papers have investigated the representation of women at scientific conferences, however, we have only identified one that focused on invited speakers at universities (Nittrouer, 2018).
+In their study, Nittrouer et.
+al., examined 3,652 talks at 50 U.S.
+institutions in 2013 - 2014 and found that women faculty are less likely to be invited speakers, despite similar acceptance rates.
+
+These results suggest that women faculty are less likely to invited as speakers, a decision that may be negatively impacted by assumptions about competency and dedication.
+The dedication of women who have children to their work is perceived to be less than that of their colleagues, e.g., men who also have children.
+The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigious nature of these invitations and evidence to the contrary), causing the faculty member to invite a different colleague who they feel is more likely to agree.
 Departments have different processes and criteria for selecting invited speakers, but want to bring the best scientists possible.
-It may be that the definition of "best" poses a problem to women, who need three-times as many publications as their men colleges to be considered equally competent.
-Some departments only invite tenured faculty, which severely limits the number of potential women speakers considerably.
+It may also be that the definition of "best" poses a problem to women, who need three-times as many publications as their men colleges to be considered equally competent.
+Some departments only invite tenured faculty, which severely limits the number of potential women speakers.
 Alternately, pre-tenure faculty members invite prestigious, tenured faculty in their field to network and secure letters for their own tenure package.
@@
 
-Our analysis identified an over-representation of Caucasian individuals as hosting faculty and invited speakers, relative to the proportion of Caucasian trainees.
-We observed declines in the representation of HURM and international faculty and speakers relative to the trainees.
-
-[Lectureships]. 22, 3, 6, (cauc, HURM, Internatl, respectively) -- 12, 10, 5, 0 (CaucM, CaucW, Non-CaucM, Non-CaucW)
++ studies that go beyond gender -- e.g., race/ethnicity (this seems to be the first)
 
@@
 
-Table 1. List of Suggestions & Resources
+\newpage
+
+\begin{center}
+\captionof{table}{List of suggestions and resources to increase invited speaker diversity.}
+\small
+\begin{tabular}{|l|l|l|}
+\hline
+
+\rowcolor{lightgray}
+\textbf{Suggestion} & \textbf{Description} & \textbf{Resource} \\ \hline
+
+Lab-invited speakers & \makecell[l]{Faculty members can request \\suggestions from trainees} & \\ \hline
+
+Use a list & \makecell[l]{Many lists of scientists from \\under-represented and underserved \\groups are available} &  \makecell[l]{https://DiversifyMicrobiology.\\github.io/resources}\\ \hline
+
+Create a list & \makecell[l]{Use the GitHub template \\ create a self-nomination list and \\resource for your field} & \makecell[l]{https://github.com/diversifymicrobiology/\\DiversifyMicrobiology.github.io} \\ \hline
+
+Highlight the journey & \makecell[l]{Invite all speakers to spend \\a few moments describing their \\personal science journey} & \\ \hline
+
+\end{tabular}
+\end{center}
+
+\newpage
 

### 2019-09-10 submission/manuscript.tex
work on results

@@
 
-Ada K. Hagan, Ph.D.\({^1}\)\^{}, Rebecca M. Pollet, Ph.D.\({^1}\)\^{},
-and Josie Libertucci, Ph.D.\({^2}\)\^{}
+Ada K. Hagan, Ph.D.\({^1\dagger}\), Rebecca M. Pollet, Ph.D.\({^1}\),
+and Josie Libertucci, Ph.D.\({^2\dagger}\)
 
@@
 are decided by committee, and three trainee-invited speakers. We
-analyzed the gender and demographics of invited speakers and faculty
-hosts for five academic years (Fall 2014 - Spring 2019), and the current
-trainees when the data were analyzed (Spring 2019).
-
-Each speaker was only counted once and any departmental faculty members
-or those listed as a ``host'' at any point could not also be considered
-``invited speakers''. The list of faculty hosts was used as a proxy for
-faculty demographics since as hosts, these faculty members are visible
-representatives of the department. The list of trainees was obtained
-from department listservs and included masters students, doctoral
-students, and post-doctoral fellows.
+analyzed the demographics of invited speakers and faculty hosts for five
+academic years (Fall 2014 - Spring 2019), and compared them to the
+current trainees when the data were analyzed (Spring 2019). Each speaker
+was only counted once and those listed as departmental faculty members
+or as a ``host'' at any point could not also be considered ``invited
+speakers''. The list of faculty hosts was used as a proxy for faculty
+demographics since as hosts, these faculty members are visible
+representatives of the department. The trainee lists were obtained from
+department listservs that included masters students, doctoral students,
+and post-doctoral fellows.
 
 We hand-coded demographics using personal knowledge, photos, and CVs.
-The presenting gender if each invidual was assigned using a binary
+The presenting gender of each individual was assigned using a binary
 system (man/woman). Diversity definitions vary according to the goals
 and population in question. However, in the United States, there is an
-inclination to consider both individuals of historically
-under-represented minority (HURM) and international backgrounds
-together. We argue that it is important to distinguish these two groups
-separately since each face different issues in the US and the academy
-and thus require different support systems. For instance, international
-scientists must contend with visa issues while HURMs have the trauma
-associated with living in a country who systematically shuts them out
-(despite an infrastructure that was built on their historical land and
-labor). For this reason, other assigned demographics included Caucasian,
-Historically Under-represented Minority (HURM), and International, each
-with a binary (yes/no) possibilty. Caucasian was assigned using the
-current U.S. Census definition where those of Middle Eastern, European,
-and Russian descent are included. HURM individuals were restricted to
-those with African-American, Indigenous and/or Hispanic heritage while
+inclination to consider both together. We believe that it is important
+to distinguish between individuals of historically under-represented
+minority (HURM) and international backgrounds since each face different
+issues in the US and the academy and thus require different support
+systems. For instance, international scientists must contend with visa
+issues while HURMs have the trauma associated with living in a country
+who systematically shuts them out (despite an infrastructure that was
+built on their historical land and labor). For this reason, other
+assigned demographics included Caucasian, Historically Under-represented
+Minority (HURM), and International, each with a binary (yes/no)
+possibilty. Caucasian was assigned using the current U.S. Census
+definition where those of Middle Eastern, European, and Russian descent
+are included. HURM individuals were restricted to those with
+African-American, Indigenous and/or Hispanic heritage while
 International individuals were either visiting the US at the time of
-their talk, or immigrated to the US as an adult.
+their seminar, or immigrated to the US as an adult.
 
-\subsection{Results and Discussion}\label{results-and-discussion}
+\subsection{Results}\label{results}
 
 To understand the representation of women, we compared the proportion of
-individuals presenting as women in each academic role. At the trainee
-level, more than half of students and postdoctoral fellows were women.
-That dropped to X\% of faculty hosts and X\% of the invited speakers. 10
-of 31 lectureships {[}what about lectureships?{]} The proportion of
-women as faculty hosts and speakers is equivalent to global estimates of
-women microbiologists (Elseiver). Several papers have investigated the
-representation of women at scientific conferences, however, we only
-identified one that focused on invited speakers at university-sponsored
-events (Nittrouer, 2018). {[}Compare to our findings{]}
-
-Assumptions about competency and dedication may negatively impact the
-likelihood of women microbiologists being invited as speakers. The
-dedication of women with family to their work is also more likely to be
-questioned than that of their colleagues, even men who also have
-children. For instance, the perceived prioritization and commitments of
-women to family over work may cause faculty to doubt their acceptance of
-a speaking invitation (despite the prestigious nature of these
-invitations), causing the faculty member to invite a different colleague
-who they feel is less likely to turn them down. Departments have
-different processes and criteria for selecting invited speakers, but
-want to bring the best scientists possible. It may be that the
-definition of ``best'' poses a problem to women, who need three-times as
-many publications as their men colleges to be considered equally
-competent. Some departments only invite tenured faculty, which severely
-limits the number of potential women speakers considerably. Alternately,
-pre-tenure faculty members invite prestigious, tenured faculty in their
-field to network and secure letters for their own tenure package. The
-increased burden of women to prove competency decreases their likelihood
-to be considered for either tenure and as possible source of tenure
-letters.
+women in each academic role. At the trainee level, more than half of
+students and postdoctoral fellows were women. That dropped to 46.77\% of
+faculty hosts and 38.73\% of the invited speakers (Fig. 1A). Of 27
+lectureships over the five year period, 37.04\% were awarded to women.
+The proportion of women as faculty hosts and speakers is equivalent to
+global estimates that 40\% of microbiologists are women (Elseiver), with
+a slightly lower representation of women in lectureships.
 
@@
 as hosting faculty and invited speakers, relative to the proportion of
-Caucasian trainees. We observed declines in the representation of HURM
-and international faculty and speakers relative to the trainees.
+Caucasian trainees (Fig. 1B). We also observed declines in the
+representation of HURM and international faculty and speakers relative
+to the trainees, particularly postdocs (Fig 1B). Caucasian scientists
+also dominated lectureships, comprising 81.48\% of those awarded (Fig.
+1C). Three and six lectureships were awarded to HURM and International
+scientists, respectively. Because the intersection of identities can
+compound biases and outcomes, we further examined the more prestigous
+lectureships by gender and Caucasian status. Caucasian men and women
+accounted for 44.44\% and 37.04\% of the lectureships, respectively,
+compared to 18.52\% non-Caucasian men and zero non-Caucasian women (Fig.
+1D).
 
-{[}Lectureships{]}. 22, 3, 6, (cauc, HURM, Internatl, respectively) --
-12, 10, 5, 0 (CaucM, CaucW, Non-CaucM, Non-CaucW)
+\subsection{Discussion}\label{discussion}
+
+Several papers have investigated the representation of women at
+scientific conferences, however, we have only identified one that
+focused on invited speakers at universities (Nittrouer, 2018). In their
+study, Nittrouer et. al., examined 3,652 talks at 50 U.S. institutions
+in 2013 - 2014 and found that women faculty are less likely to be
+invited speakers, despite similar acceptance rates.
+
+These results suggest that women faculty are less likely to invited as
+speakers, a decision that may be negatively impacted by assumptions
+about competency and dedication. The dedication of women who have
+children to their work is perceived to be less than that of their
+colleagues, e.g., men who also have children. The perceived
+prioritization and commitments of women to family over work may cause
+faculty to doubt their acceptance of a speaking invitation (despite the
+prestigious nature of these invitations and evidence to the contrary),
+causing the faculty member to invite a different colleague who they feel
+is more likely to agree. Departments have different processes and
+criteria for selecting invited speakers, but want to bring the best
+scientists possible. It may also be that the definition of ``best''
+poses a problem to women, who need three-times as many publications as
+their men colleges to be considered equally competent. Some departments
+only invite tenured faculty, which severely limits the number of
+potential women speakers. Alternately, pre-tenure faculty members invite
+prestigious, tenured faculty in their field to network and secure
+letters for their own tenure package. The increased burden of women to
+prove competency decreases their likelihood to be considered for either
+tenure and as possible source of tenure letters.
 
@@
 
-We thank Harry Mobley and the Department of Microbiology \& Immunology,
-University of Michigan for their support and input. We would also like
-to acknowledge Nick Lesniak and Dr.~Ariangela Kozick for their comments
-and suggestions.
+We thank Dr.~Harry Mobley and the Department of Microbiology \&
+Immunology, University of Michigan for their input and financial support
+that enabled publication of our manuscript. We would also like to
+acknowledge Nick Lesniak and Dr.~Ariangela Kozick for their comments and
+suggestions.
 
@@
 A.K.H. collected the data, assigned demographics, analyzed the data, and
-created the website. R.P. created the Google lists, forms, and website
+created the website. R.M.P. created the Google lists, forms, and website
 content and the description of their maintenance. J.L. wrote the
@@
 
-Table 1. List of Suggestions \& Resources
+\newpage
+
+\begin{center}
+\captionof{table}{List of suggestions and resources to increase invited speaker diversity.}
+\small
+\begin{tabular}{|l|l|l|}
+\hline
+
+\rowcolor{lightgray}
+\textbf{Suggestion} & \textbf{Description} & \textbf{Resource} \\ \hline
+
+Lab-invited speakers & \makecell[l]{Faculty members can request \\suggestions from trainees} & \\ \hline
+
+Use a list & \makecell[l]{Many lists of scientists from \\under-represented and underserved \\groups are available} &  \makecell[l]{https://DiversifyMicrobiology.\\github.io/resources}\\ \hline
+
+Create a list & \makecell[l]{Use the GitHub template \\ create a self-nomination list and \\resource for your field} & \makecell[l]{https://github.com/diversifymicrobiology/\\DiversifyMicrobiology.github.io} \\ \hline
+
+Highlight the journey & \makecell[l]{Invite all speakers to spend \\a few moments describing their \\personal science journey} & \\ \hline
+
+\end{tabular}
+\end{center}
+
+\newpage
 

### 2019-09-10 code/lectureship_div.R

@@ -11,6 +11,7 @@ lectureship <- speaker_data %>%
                                "International", demographic))
 
 lectureship_demo_plot <- lectureship %>% 
+  filter(demographic != "Gender") %>% 
   filter(value == "y") %>% 
   ggplot(aes(x = value))+
   geom_bar(aes(y = (..count..)/sum(..count..), fill = value))+

### 2019-09-11 submission/manuscript.Rmd
work on discussion and tool description, draft for comments

@@
 output:
+  word_document: default
   pdf_document:
@@
 geometry: margin=1.0in
-
 ---
@@
 institutions in 2013 - 2014 and found that women faculty are less likely to be invited speakers, despite similar acceptance rates.
+These results suggest that women faculty are less often invited as speakers, a decision that may be negatively impacted by assumptions about competency and dedication.
+The dedication of women who have children to their work is perceived to be less than that of their colleagues, i.e., men who also have children.
+The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigious nature of these invitations and evidence to the contrary).
+As a result, the faculty member invites a different colleague who they feel is more likely to agree (and is a man).
+Departments have different processes and criteria for selecting invited speakers, but it is a matter of pride to bring the best scientists possible.
+It may be that the definition of "best" poses a problem to women, who need three-times as many publications as their men colleges to be considered equally competent.
+Some departments only invite tenured faculty, which severely limits the number of potential women speakers.
+Another scenario is that pre-tenure faculty members invite prestigious, tenured faculty in their field to network and secure letters for their own tenure package.
+The increased burden of women to prove competency decreases their likelihood to be considered for either tenure or as possible source of tenure letters.
 
-These results suggest that women faculty are less likely to invited as speakers, a decision that may be negatively impacted by assumptions about competency and dedication.
-The dedication of women who have children to their work is perceived to be less than that of their colleagues, e.g., men who also have children.
-The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigious nature of these invitations and evidence to the contrary), causing the faculty member to invite a different colleague who they feel is more likely to agree.
-Departments have different processes and criteria for selecting invited speakers, but want to bring the best scientists possible.
-It may also be that the definition of "best" poses a problem to women, who need three-times as many publications as their men colleges to be considered equally competent.
-Some departments only invite tenured faculty, which severely limits the number of potential women speakers.
-Alternately, pre-tenure faculty members invite prestigious, tenured faculty in their field to network and secure letters for their own tenure package.
-The increased burden of women to prove competency decreases their likelihood to be considered for either tenure and as possible source of tenure letters.
+We have not been able to identify any other publications examining scientific speaker diversity beyond gender.
+This seems to be the first.
+This is concerning since conclusions drawn from gender-based studies are often framed, and considered, to be applicable to other marginalized groups (e.g., HURM).
+This is a flawed assumption.
+While there is no doubt some overlap, each group remains marginalized due to a complex set of factors that are unique to each group and cannot always be solved by gender-based solutions.
+US-serving institutions, such as the University of Michigan have a particular responsibility to the historically suppressed populations included in our definition of HURMs.
+We therefore implore US institutions to apply this framing to their discussions and research.
 
-+ studies that go beyond gender -- e.g., race/ethnicity (this seems to be the first)
+Our data support the advancement of social role theory, which states that to improve retention of white women & HURMs, each group needs equivalent representation to counteract biases and improve self-efficacy.
+Implict biases that affect perceptions of marginalized groups are the primary issue, but we must acknowledge that it is not always possible to identify members of historically under-served communities.
+For instance, after data analysis, we learned that at least one speaker in our data set is a member of a HURM group, but it wasn't readily apparent from their internet presence or CV.
+This limitation makes two important points: that perspective is often as, if not more, important than self-identification with regards to biased outcomes, and that we need better tools to identify members of marginalized groups.
 
-## Call to Action
-+ Improving speaker diversity
-    + US-serving institutions have particular responsibility to those historically suppressed populations
-    + to improve retention of white women & HURMs, each group needs equivalent representation to counteract biases and improve self-efficacy
-    + recall bias not the only issue, also not always possible to identify members of historically under-served communities
-    + example: there are speakers who have URM status, but it wasn't readily apparent from the internet/CV 
-    + perspective is often as/more important than self-identification
+## Building Diversify
+
+To help address this issue, we make some suggestions (Table 1) and have developed a resource to identify scientists who are members of marginalized and/or historically under-served groups.
+Motivated by a lack of such resources and inspired by similar resources--DiversifyEEB and DiversifyChemistry--we created DiversifyMicrobiology and DiversifyImmunology.
+These resources are a tool for symposium organziers, award committees, search committees and other scientists to identify individuals to diversify their pools.
+Additionally, we have built these as a tool for use by other fields and organizations to create their own lists.
+Importantly, since these lists are compiled by self-nomination, we can ensure that only scientists comfortable revealing their marginalized identities are included.
 
 + Development of Diversify tools
-    + inspired by EEB/Chemistry
-    + tool for members of URM groups to self-identify & for others to use to find diverse candidates
     + describe maintenance of lists (Rebecca)
-    + describe website creation
 
-+ Other resources/ideas
-    + student/lab invited speakers -- improve diversity of suggestions (fields/careers)
-    + departments to invite speakers to share about their personal story as well as their science
+The website provides an interface to the Google forms and spreadsheets with template pages for viewing the list, adding a name to the list, and finding additional resources.
+Importantly, our website creation tool is hosted for free by GitHub, which provides a free website for each GitHub organization (citation).
+Basic tools and skills required to set up a Diversify site include knowledge of, or experience with, the version control tool git, the webtool GitHub, and a text editor.
+A tutorial in the DiversifyMicrobiology repository on GitHub provides links to these resources and instructions for adapting the tool to your own field.
 
@@
 
-+ increased retention of white women & HURMS -- increasing representation of 
-+ tools available to create field specific lists of H under-served
+To increase the retention of white women and HURMS in STEM, they must also be represented as experts.
+However, the invited speaker diversity at one department does not represent the diversity of trainees.
+There is a lack of research on invited speakers examining factors other than gender.
+To facilite the identification and recruitment of individuals in these historically under-served groups, we have built a tool to create self-nominated, field-specific lists.
 

### 2019-09-11 submission/manuscript.tex
work on discussion and tool description, draft for comments

@@
 in 2013 - 2014 and found that women faculty are less likely to be
-invited speakers, despite similar acceptance rates.
-
-These results suggest that women faculty are less likely to invited as
-speakers, a decision that may be negatively impacted by assumptions
-about competency and dedication. The dedication of women who have
-children to their work is perceived to be less than that of their
-colleagues, e.g., men who also have children. The perceived
-prioritization and commitments of women to family over work may cause
-faculty to doubt their acceptance of a speaking invitation (despite the
-prestigious nature of these invitations and evidence to the contrary),
-causing the faculty member to invite a different colleague who they feel
-is more likely to agree. Departments have different processes and
-criteria for selecting invited speakers, but want to bring the best
-scientists possible. It may also be that the definition of ``best''
+invited speakers, despite similar acceptance rates. These results
+suggest that women faculty are less often invited as speakers, a
+decision that may be negatively impacted by assumptions about competency
+and dedication. The dedication of women who have children to their work
+is perceived to be less than that of their colleagues, i.e., men who
+also have children. The perceived prioritization and commitments of
+women to family over work may cause faculty to doubt their acceptance of
+a speaking invitation (despite the prestigious nature of these
+invitations and evidence to the contrary). As a result, the faculty
+member invites a different colleague who they feel is more likely to
+agree (and is a man). Departments have different processes and criteria
+for selecting invited speakers, but it is a matter of pride to bring the
+best scientists possible. It may be that the definition of ``best''
 poses a problem to women, who need three-times as many publications as
@@
 only invite tenured faculty, which severely limits the number of
-potential women speakers. Alternately, pre-tenure faculty members invite
-prestigious, tenured faculty in their field to network and secure
-letters for their own tenure package. The increased burden of women to
-prove competency decreases their likelihood to be considered for either
-tenure and as possible source of tenure letters.
+potential women speakers. Another scenario is that pre-tenure faculty
+members invite prestigious, tenured faculty in their field to network
+and secure letters for their own tenure package. The increased burden of
+women to prove competency decreases their likelihood to be considered
+for either tenure or as possible source of tenure letters.
 
-\subsection{Call to Action}\label{call-to-action}
+We have not been able to identify any other publications examining
+scientific speaker diversity beyond gender. This seems to be the first.
+This is concerning since conclusions drawn from gender-based studies are
+often framed, and considered, to be applicable to other marginalized
+groups (e.g., HURM). This is a flawed assumption. While there is no
+doubt some overlap, each group remains marginalized due to a complex set
+of factors that are unique to each group and cannot always be solved by
+gender-based solutions. US-serving institutions, such as the University
+of Michigan have a particular responsibility to the historically
+suppressed populations included in our definition of HURMs. We therefore
+implore US institutions to apply this framing to their discussions and
+research.
+
+Our data support the advancement of social role theory, which states
+that to improve retention of white women \& HURMs, each group needs
+equivalent representation to counteract biases and improve
+self-efficacy. Implict biases that affect perceptions of marginalized
+groups are the primary issue, but we must acknowledge that it is not
+always possible to identify members of historically under-served
+communities. For instance, after data analysis, we learned that at least
+one speaker in our data set is a member of a HURM group, but it wasn't
+readily apparent from their internet presence or CV. This limitation
+makes two important points: that perspective is often as, if not more,
+important than self-identification with regards to biased outcomes, and
+that we need better tools to identify members of marginalized groups.
+
+\subsection{Building Diversify}\label{building-diversify}
+
+To help address this issue, we make some suggestions (Table 1) and have
+developed a resource to identify scientists who are members of
+marginalized and/or historically under-served groups. Motivated by a
+lack of such resources and inspired by similar resources--DiversifyEEB
+and DiversifyChemistry--we created DiversifyMicrobiology and
+DiversifyImmunology. These resources are a tool for symposium
+organziers, award committees, search committees and other scientists to
+identify individuals to diversify their pools. Additionally, we have
+built these as a tool for use by other fields and organizations to
+create their own lists. Importantly, since these lists are compiled by
+self-nomination, we can ensure that only scientists comfortable
+revealing their marginalized identities are included.
 
@@
 \tightlist
-\item
-  Improving speaker diversity
-
-  \begin{itemize}
-  \tightlist
-  \item
-    US-serving institutions have particular responsibility to those
-    historically suppressed populations
-  \item
-    to improve retention of white women \& HURMs, each group needs
-    equivalent representation to counteract biases and improve
-    self-efficacy
-  \item
-    recall bias not the only issue, also not always possible to identify
-    members of historically under-served communities
-  \item
-    example: there are speakers who have URM status, but it wasn't
-    readily apparent from the internet/CV
-  \item
-    perspective is often as/more important than self-identification
-  \end{itemize}
 \item
@@
   \item
-    inspired by EEB/Chemistry
-  \item
-    tool for members of URM groups to self-identify \& for others to use
-    to find diverse candidates
-  \item
     describe maintenance of lists (Rebecca)
-  \item
-    describe website creation
-  \end{itemize}
-\item
-  Other resources/ideas
-
-  \begin{itemize}
-  \tightlist
-  \item
-    student/lab invited speakers -- improve diversity of suggestions
-    (fields/careers)
-  \item
-    departments to invite speakers to share about their personal story
-    as well as their science
   \end{itemize}
@@
 
+The website provides an interface to the Google forms and spreadsheets
+with template pages for viewing the list, adding a name to the list, and
+finding additional resources. Importantly, our website creation tool is
+hosted for free by GitHub, which provides a free website for each GitHub
+organization (citation). Basic tools and skills required to set up a
+Diversify site include knowledge of, or experience with, the version
+control tool git, the webtool GitHub, and a text editor. A tutorial in
+the DiversifyMicrobiology repository on GitHub provides links to these
+resources and instructions for adapting the tool to your own field.
+
 \subsection{Conclusion}\label{conclusion}
 
-\begin{itemize}
-\tightlist
-\item
-  increased retention of white women \& HURMS -- increasing
-  representation of
-\item
-  tools available to create field specific lists of H under-served
-\end{itemize}
+To increase the retention of white women and HURMS in STEM, they must
+also be represented as experts. However, the invited speaker diversity
+at one department does not represent the diversity of trainees. There is
+a lack of research on invited speakers examining factors other than
+gender. To facilite the identification and recruitment of individuals in
+these historically under-served groups, we have built a tool to create
+self-nominated, field-specific lists.
 

### 2019-09-13 code/data_extraction/compile_mi_speaker_datasets.R
change race/ethnicity groupings

@@ -18,7 +18,7 @@ get_host_type <- function(x){
   host_type <- case_when(
     x %in% student ~ "Student",
     x %in% postdoc ~ "Postdoc",
-    TRUE ~ "Faculty"
+    TRUE ~ "Host Faculty"
   )
   
   return(host_type)
@@ -26,9 +26,11 @@ get_host_type <- function(x){
 
 raw_data <- read_csv("data/micro_immuno/data_14-19.csv")
 
-host_data <- read_csv("data/micro_immuno/hosts_14-19.csv")
+host_data <- read_csv("data/micro_immuno/hosts_14-19.csv") %>% 
+  select(-Host_Internatl)
 
-speaker_data <- read_csv("data/micro_immuno/speakers_14-19.csv")
+speaker_data <- read_csv("data/micro_immuno/speakers_14-19.csv") %>% 
+  select(-Speaker_Internatl)
 
 compiled_data <- raw_data %>% left_join(., host_data, by = "Host") %>% 
   left_join(., speaker_data, by = "Speaker") %>% 

### 2019-09-13 code/data_extraction/compile_mi_trainee_data.R

@@ -1,9 +1,11 @@
 library(tidyverse)
 
 postdoc_data <- read_csv("data/micro_immuno/postdocs_19.csv") %>% 
+  select(-Internatl) %>% 
   mutate(Trainee_type = "postdoc")
 
 student_data <- read_csv("data/micro_immuno/students_19.csv") %>% 
+  select(-Internatl) %>% 
   mutate(Trainee_type = "student")
 
 trainee_data <- bind_rows(postdoc_data, student_data) %>% 

### 2019-09-13 code/demo_comp.R

@@ -1,9 +1,9 @@
 #what are the trainee demographics?----
 
 demo_combined <- tidy_host %>% 
-  filter(role == "Faculty") %>% 
+  filter(role == "Host Faculty") %>% 
   rbind(., tidy_trainee, tidy_speaker) %>% 
-  filter(demographic != "Gender") %>% 
+  select(-Gender) %>% 
   group_by(demographic, role, value) %>% summarise(n = n()) %>% 
   spread(key = value, value = n) %>% 
   mutate(prop_y = get_percent(y, (y + n)))

### 2019-09-13 code/gender_comp.R

@@ -1,22 +1,30 @@
 #compare gender compositions for trainees and speakers
 
 gender_combined <- tidy_host %>% 
-  filter(role == "Faculty") %>% 
+  filter(role == "Host Faculty") %>% 
   rbind(., tidy_trainee, tidy_speaker) %>% 
-  filter(demographic == "Gender") %>% 
-  group_by(role, value) %>% summarise(n = n()) %>% 
-  spread(key = value, value = n) %>% 
+  select(Gender, role, id) %>% 
+  group_by(role, Gender) %>% summarise(n = n()) %>% 
+  spread(key = Gender, value = n) %>% 
   mutate(prop_W = get_percent(woman, (man + woman)))
 
 gender_combined$role <- fct_relevel(gender_combined$role, dat_levels)
 
+gender_plot_leg <- gender_combined %>% 
+  ggplot()+
+  geom_col(aes(x = role, y = prop_W, fill = role), alpha = 0.75)+
+  labs(x = "Academic Role\n", y = "Proportion of Women\n in the Population", 
+       fill = "Academic Role")+
+  set_role_colors
+
 gender_plot <- gender_combined %>% 
   ggplot()+
   geom_col(aes(x = role, y = prop_W, fill = role), alpha = 0.75)+
-  labs(x = "Academic Role\n", y = "Proportion of Population", 
+  labs(x = "Academic Role\n", 
+       y = "Proportion of Women\n in the Population", 
        fill = "Academic Role")+
   set_role_colors +
-  my_theme_leg_horiz+
+  my_theme_horiz+
   theme(axis.text.x=element_blank(),
         axis.ticks.x=element_blank())
 

### 2019-09-13 code/get_figures.R

@@ -4,10 +4,12 @@ source("../code/lectureship_div.R")
 
 blank <- ggplot()
 
-top_row <- plot_grid(gender_plot, blank,
-                     rel_widths = c(2,1))
+legend <- get_legend(gender_plot_leg)
 
-bottom_row <- plot_grid(lectureship_demo_plot, lectureship_gend_plot,
+top_row <- plot_grid(gender_plot, blank, legend,
+                     rel_widths = c(2, 1, 1), nrow = 1)
+
+bottom_row <- plot_grid(lectureship_demo_plot, lectureship_gend_cauc_plot,
                         labels = c("C", "D"), label_size = 18)
 
 plot_grid(top_row, demo_plot, bottom_row, labels = c("A", "B", ""),

### 2019-09-13 code/get_plot_options.R

@@ -4,7 +4,7 @@ library(cowplot)
 #library(patchwork)
 
 #settings----
-dat_levels <- c("Student", "Postdoc", "Faculty", "Speaker")
+dat_levels <- c("Student", "Postdoc", "Host Faculty", "Speaker")
 
 dat_linetype <- c("solid", "dashed", "dotted")
 

### 2019-09-13 code/lectureship_div.R

@@ -3,15 +3,13 @@ lectureship <- speaker_data %>%
   filter(!is.na(Lectureship)) %>% 
   filter(Host != "Student") %>% 
   filter(Host != "Postdoc") %>% 
-  select(contains("Speaker")) %>% 
-  gather(Speaker_Gender:Speaker_Internatl, 
+  select(contains("Speaker")) %>%
+  gather(Speaker_Caucasian:Speaker_NCNH, -Speaker_id, 
          key = demographic, value = value) %>% 
-  separate(demographic, into = c("role", "demographic"), sep = "_") %>% 
-  mutate(demographic = if_else(demographic == "Internatl", 
-                               "International", demographic))
+  separate(demographic, into = c("role", "demographic"), sep = "_") 
 
 lectureship_demo_plot <- lectureship %>% 
-  filter(demographic != "Gender") %>% 
+  select(-Speaker_Gender) %>% 
   filter(value == "y") %>% 
   ggplot(aes(x = value))+
   geom_bar(aes(y = (..count..)/sum(..count..), fill = value))+
@@ -24,7 +22,7 @@ lectureship_demo_plot <- lectureship %>%
   theme(axis.text.x=element_blank(),
         axis.ticks.x=element_blank())
 
-lectureship_gend_plot <- speaker_data %>% 
+lectureship_gend_cauc_plot <- speaker_data %>% 
   filter(!is.na(Lectureship)) %>% 
   filter(Host != "Student") %>% 
   filter(Host != "Postdoc") %>% 
@@ -34,7 +32,19 @@ lectureship_gend_plot <- speaker_data %>%
                fill = Speaker_Gender))+
   facet_wrap(~if_else(Speaker_Caucasian == "y", "Caucasian", "Non-Caucasian"))+
   scale_y_continuous(labels = scales::percent)+
-  #geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
   labs(y = "\nPercent of Lectureships", x = "Speaker Gender")+
   scale_fill_manual(values = c("grey17", "dark gray"))+
   my_theme_horiz
+  #geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
+  
+lectureship_gend_plot <- lectureship %>% 
+  filter(value == "y") %>% 
+  ggplot(aes(x = Speaker_Gender))+
[…]

### 2019-09-13 code/load_data.R

@@ -2,11 +2,8 @@ library(tidyverse)
 
 source("../code/get_plot_options.R")
 
-get_diversity_value <- function(x, y){
-  case_when(
-    x == "man" & y == "y" ~ paste("Cauc M"),
-    x == "woman" & y == "y" ~ paste("Cauc W")
-  )
+get_NCNH_group <- function(x, y){
+  if_else(x == "n" & y == "n", "y", "n")
 }
 
 #calculate two decimal percentage given num & denom
@@ -21,37 +18,34 @@ speaker_data <- read_csv("../data/speaker_dataset_14-19.csv") %>%
   mutate(Speaker_id = rownames(.),
          Host_id = rownames(.)) %>% 
   rename(Speaker_Caucasian = Speaker_caucasian, 
-         Speaker_Gender = Speaker_gender)
+         Speaker_Gender = Speaker_gender) %>% 
+  mutate(Speaker_NCNH = get_NCNH_group(Speaker_Caucasian, Speaker_HURM),
+         Host_NCNH = get_NCNH_group(Host_caucasian, Host_HURM)) %>% 
+  filter(!is.na(Speaker_Gender))
 
 tidy_speaker <- speaker_data %>% 
-  select(contains("Speaker")) %>% 
-  gather(Speaker_Gender:Speaker_Internatl, 
+  select(contains("Speaker")) %>%
+  gather(Speaker_Caucasian:Speaker_NCNH, -Speaker_id, 
          key = demographic, value = value) %>% 
   separate(demographic, into = c("role", "demographic"), sep = "_") %>% 
-  rename(id = Speaker_id) %>% 
-  mutate(demographic = if_else(demographic == "Internatl", 
-                               "International", demographic))
+  rename(id = Speaker_id, Gender = Speaker_Gender)
+  
 tidy_host <- speaker_data %>% 
-  select(contains("Host")) %>% 
-  gather(Host_gender:Host_Internatl, 
+  select(contains("Host")) %>%
+  gather(Host_caucasian:Host_NCNH, -Host_id, 
          key = demographic, value = value) %>% 
   separate(demographic, into = c("role", "demographic"), sep = "_") %>% 
-  rename(id = Host_id) %>% 
-  mutate(demographic = case_when(
-    demographic == "Internatl" ~ "International",
-    demographic == "gender" ~ "Gender",
-    demographic == "caucasian" ~ "Caucasian",
-    TRUE ~ demographic
-  )) %>% 
[…]

### 2019-09-13 submission/manuscript.Rmd
change methods and results to reflect change in race/ethnicity groupings

@@
 output:
-  word_document: default
   pdf_document:
@@
 
-```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE, include=FALSE}
-######################################################################
+```{r setup, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE, include=FALSE}
 #----------------- Read in necessary libraries -------------------#
-######################################################################
 deps = c("knitr","rmarkdown", "markdown");
@@
 }
-######################################################################
 #-------------- Define the chunk options ----------------#
-######################################################################
 opts_chunk$set("tidy" = TRUE)
-```
 
-```{r LoadData, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
+#-------------- Read in data and figure ----------------#
 source("../code/load_data.R")
@@
 Tables: 1
-
-Supplemental:
 
@@
 
-We hand-coded demographics using personal knowledge, photos, and CVs.
+This is a retrospective study, so individuals were not asked for their identities.
+Instead we hand-coded proxy demographics using personal knowledge, photos, and CVs.
 The presenting gender of each individual was assigned using a binary system (man/woman).
-Diversity definitions vary according to the goals and population in question.
-However, in the United States, there is an inclination to consider both  together.
-We believe that it is important to distinguish between individuals of historically under-represented minority (HURM) and international backgrounds since each face different issues in the US and the academy and thus require different support systems.
-For instance, international scientists must contend with visa issues while HURMs have the trauma associated with living in a country who systematically shuts them out (despite an infrastructure that was built on their historical land and labor).
-For this reason, other assigned demographics included Caucasian, Historically Under-represented Minority (HURM), and International, each with a binary (yes/no) possibilty.
+Due to the low number of individuals in the study, race/ethnicity demographics were split in three groups: Caucasian, Historically Under-represented Minority (HURM), and Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibilty.
 Caucasian was assigned using the current U.S.
 Census definition where those of Middle Eastern, European, and Russian descent are included.
-HURM individuals were restricted to those with African-American, Indigenous and/or Hispanic heritage while International individuals were either visiting the US at the time of their seminar, or immigrated to the US as an adult.
+HURM individuals were restricted to those with African-American, Indigenous, Alaskan/Hawaian Native, Latinx and/or Hispanic heritage.
+All others were placed into the NCNH group.
+We recognize that our proxy demographics are a limitation of the analysis and want to acknowledge that the presenting gender may not reflect the gender(s) that an individual identifies as.
+We also want to acknowledge that there are many other identities that are not captured in this limited analysis.
 
 ## Results
+```{r result, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE, include=FALSE}
+lect_summary <- lectureship %>% filter(value == "y") %>% 
+  group_by(Speaker_Gender, demographic) %>% summarise(n = n()) %>% 
+  mutate(prop = get_percent(n, sum(.$n)))
 
+cauc_lect <- lect_summary %>% 
+  filter(demographic == "Caucasian") %>% 
+  summarise(sum = sum(n))
+```
 To understand the representation of women, we compared the proportion of women in each academic role.
 At the trainee level, more than half of students and postdoctoral fellows were women.
-That dropped to `r gender_combined[[1,5]]`% of faculty hosts and `r gender_combined[[3,5]]`% of the invited speakers (Fig.
+That dropped to `r gender_combined[[1,4]]`% of faculty hosts and `r gender_combined[[3,4]]`% of the invited speakers (Fig.
 1A).
-Of 27 lectureships over the five year period, `r get_percent(10, 27)`% were awarded to women.
+Of `r sum(lect_summary$n)` lectureships over the five year period, `r lect_summary[4,4]`% were awarded to women.
 The proportion of women as faculty hosts and speakers is equivalent to global estimates that 40% of microbiologists are women (Elseiver), with a slightly lower representation of women in lectureships.
@@
 1B).
-We also observed declines in the representation of HURM and international faculty and speakers relative to the trainees, particularly postdocs (Fig 1B).
-Caucasian scientists also dominated lectureships, comprising `r get_percent(22, 27)`% of those awarded (Fig.
+We also observed declines in the representation of HURM and NCNH faculty and speakers relative to the trainees (Fig 1B).
+Caucasian scientists also dominated the more prestigous invited speaker lectureships, comprising `r get_percent(sum(cauc_lect$sum), sum(lect_summary$n))`% of those awarded (Fig.
 1C).
-Three and six lectureships were awarded to HURM and International scientists, respectively.
-Because the intersection of identities can compound biases and outcomes, we further examined the more prestigous lectureships by gender and Caucasian status.
-Caucasian men and women accounted for `r get_percent(12, 27)`% and `r get_percent(10, 27)`% of the lectureships, respectively, compared to `r get_percent(5, 27)`% non-Caucasian men and zero non-Caucasian women (Fig.
+HURM and NCNH scientists were awarded `r lect_summary[[2,3]]` and `r lect_summary[[3,3]]` lectureships, respectively.
+Because the intersection of identities can compound biases and outcomes, we further examined the lectureships by gender and race/ethnicty status.
+Caucasian men and women accounted for `r lect_summary[[1,4]]`% and `r lect_summary[[4,4]]`% of the lectureships, respectively.
+Just `r 100 - get_percent(sum(cauc_lect$sum), sum(lect_summary$n))`% of lectureships were held by non-Caucasian men while none were held by non-Caucasian women (Fig.
 1D).
@@
 
-Our data support the advancement of social role theory, which states that to improve retention of white women & HURMs, each group needs equivalent representation to counteract biases and improve self-efficacy.
+According to social role theory, this department is not adequietly serving their non-Caucasian trainees.
 Implict biases that affect perceptions of marginalized groups are the primary issue, but we must acknowledge that it is not always possible to identify members of historically under-served communities.
-For instance, after data analysis, we learned that at least one speaker in our data set is a member of a HURM group, but it wasn't readily apparent from their internet presence or CV.
-This limitation makes two important points: that perspective is often as, if not more, important than self-identification with regards to biased outcomes, and that we need better tools to identify members of marginalized groups.
+For instance, after data analysis, we learned that at least one speaker in our data set should have been categorized as a HURM instead of Caucasian, but it wasn't readily apparent from their internet presence or CV.
+This limitation makes two important points: that percieved identity often plays a larger role than self-identification, and that we need better tools to identify members of marginalized groups.
 
@@
 
-We thank Dr.
-Harry Mobley and the Department of Microbiology & Immunology, University of Michigan for their input and financial support that enabled publication of our manuscript.
+We thank Drs.
+Beth Moore and Harry Mobley and the Department of Microbiology & Immunology, University of Michigan for their input and financial support that enabled publication of our manuscript.
 We would also like to acknowledge Nick Lesniak and Dr.
@@
 ## Code and data availability
-The anonymized data, code for all analysis steps, and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/.
+The anonymized data, code for all analysis steps, and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_SpeakerDiversity_XXXX_2019/.
 Template and complete instructions for generating a field-specific Diversity website are available at https://github.com/diversifymicrobiology/DiversifyMicrobiology.github.io/.
 
-![Figure 1.](Figure_1.png)
+![**The demographics of invited speakers, hosting faculty, and trainees.** A) The proportion of women in each academic role.
+B) The proportion of each academic role represented by individuals that are Caucasian (left), Historically Underrepresented Minorities (HURM, center) or International (right).
+C-D)The percent of lectureships awarded to individuals that are C) Caucasian, HURM, International or D) Caucasian or Non-Caucasian by gender.](Figure_1.png)
 

### 2019-09-13 submission/manuscript.tex
change methods and results to reflect change in race/ethnicity groupings

@@
 
-Supplemental:
-
 \newpage
@@
 
-We hand-coded demographics using personal knowledge, photos, and CVs.
-The presenting gender of each individual was assigned using a binary
-system (man/woman). Diversity definitions vary according to the goals
-and population in question. However, in the United States, there is an
-inclination to consider both together. We believe that it is important
-to distinguish between individuals of historically under-represented
-minority (HURM) and international backgrounds since each face different
-issues in the US and the academy and thus require different support
-systems. For instance, international scientists must contend with visa
-issues while HURMs have the trauma associated with living in a country
-who systematically shuts them out (despite an infrastructure that was
-built on their historical land and labor). For this reason, other
-assigned demographics included Caucasian, Historically Under-represented
-Minority (HURM), and International, each with a binary (yes/no)
+This is a retrospective study, so individuals were not asked for their
+identities. Instead we hand-coded proxy demographics using personal
+knowledge, photos, and CVs. The presenting gender of each individual was
+assigned using a binary system (man/woman). Due to the low number of
+individuals in the study, race/ethnicity demographics were split in
+three groups: Caucasian, Historically Under-represented Minority (HURM),
+and Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no)
 possibilty. Caucasian was assigned using the current U.S. Census
@@
 are included. HURM individuals were restricted to those with
-African-American, Indigenous and/or Hispanic heritage while
-International individuals were either visiting the US at the time of
-their seminar, or immigrated to the US as an adult.
+African-American, Indigenous, Alaskan/Hawaian Native, Latinx and/or
+Hispanic heritage. All others were placed into the NCNH group. We
+recognize that our proxy demographics are a limitation of the analysis
+and want to acknowledge that the presenting gender may not reflect the
+gender(s) that an individual identifies as. We also want to acknowledge
+that there are many other identities that are not captured in this
+limited analysis.
 
@@
 Caucasian trainees (Fig. 1B). We also observed declines in the
-representation of HURM and international faculty and speakers relative
-to the trainees, particularly postdocs (Fig 1B). Caucasian scientists
-also dominated lectureships, comprising 81.48\% of those awarded (Fig.
-1C). Three and six lectureships were awarded to HURM and International
-scientists, respectively. Because the intersection of identities can
-compound biases and outcomes, we further examined the more prestigous
-lectureships by gender and Caucasian status. Caucasian men and women
-accounted for 44.44\% and 37.04\% of the lectureships, respectively,
-compared to 18.52\% non-Caucasian men and zero non-Caucasian women (Fig.
-1D).
+representation of HURM and NCNH faculty and speakers relative to the
+trainees (Fig 1B). Caucasian scientists also dominated the more
+prestigous invited speaker lectureships, comprising 81.48\% of those
+awarded (Fig. 1C). HURM and NCNH scientists were awarded 3 and 2
+lectureships, respectively. Because the intersection of identities can
+compound biases and outcomes, we further examined the lectureships by
+gender and race/ethnicty status. Caucasian men and women accounted for
+44.44\% and 37.04\% of the lectureships, respectively. Just 18.52\% of
+lectureships were held by non-Caucasian men while none were held by
+non-Caucasian women (Fig. 1D).
 
@@
 
-Our data support the advancement of social role theory, which states
-that to improve retention of white women \& HURMs, each group needs
-equivalent representation to counteract biases and improve
-self-efficacy. Implict biases that affect perceptions of marginalized
-groups are the primary issue, but we must acknowledge that it is not
-always possible to identify members of historically under-served
-communities. For instance, after data analysis, we learned that at least
-one speaker in our data set is a member of a HURM group, but it wasn't
+According to social role theory, this department is not adequietly
+serving their non-Caucasian trainees. Implict biases that affect
+perceptions of marginalized groups are the primary issue, but we must
+acknowledge that it is not always possible to identify members of
+historically under-served communities. For instance, after data
+analysis, we learned that at least one speaker in our data set should
+have been categorized as a HURM instead of Caucasian, but it wasn't
 readily apparent from their internet presence or CV. This limitation
-makes two important points: that perspective is often as, if not more,
-important than self-identification with regards to biased outcomes, and
-that we need better tools to identify members of marginalized groups.
+makes two important points: that percieved identity often plays a larger
+role than self-identification, and that we need better tools to identify
+members of marginalized groups.
 
@@
 
-We thank Dr.~Harry Mobley and the Department of Microbiology \&
-Immunology, University of Michigan for their input and financial support
-that enabled publication of our manuscript. We would also like to
-acknowledge Nick Lesniak and Dr.~Ariangela Kozick for their comments and
-suggestions.
+We thank Drs. Beth Moore and Harry Mobley and the Department of
+Microbiology \& Immunology, University of Michigan for their input and
+financial support that enabled publication of our manuscript. We would
+also like to acknowledge Nick Lesniak and Dr.~Ariangela Kozick for their
+comments and suggestions.
 
@@
 version of this manuscript is available at
-\url{https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/}.
+\url{https://github.com/akhagan/Hagan_SpeakerDiversity_XXXX_2019/}.
 Template and complete instructions for generating a field-specific
@@
 \includegraphics{Figure_1.png}
-\caption{Figure 1.}
+\caption{\textbf{The demographics of invited speakers, hosting faculty,
+and trainees.} A) The proportion of women in each academic role. B) The
+proportion of each academic role represented by individuals that are
+Caucasian (left), Historically Underrepresented Minorities (HURM,
+center) or International (right). C-D)The percent of lectureships
+awarded to individuals that are C) Caucasian, HURM, International or D)
+Caucasian or Non-Caucasian by gender.}
 \end{figure}

### 2019-09-20 submission/manuscript.Rmd
add references and text from JL & RP

@@
 geometry: margin=1.0in
+bibliography: references.bib
 ---
@@
 
-500 words
+Long-standing systemic bias, sexism, and racism have contributed to the underrepresentation of many racial and ethnic groups, as well as women, in science, technology, engineering, and math (STEM) fields (NIH 2015 report, Measuring DEI 2016, [@colloquy_2012]).
+Organization climate and culture that supports inclusion of all individuals is essential to support the retention of historically underrepresented minorities (HURM) in the U.S., as well as non-Caucasian individuals, and women in STEM fields (Schneider, 2013).
+Inclusive organization culture will not suffice in retaining HURM, non-Caucasian individuals, and women without organization policy changes that support their values and goals [@Coe2019].
 
-Representation of white women and historically underrepresented minorities (HURM) in science, technology, engineering, and math (STEM) in the workforce remains low despite equal enrollment in undergraduate STEM majors.
-Longitudinal data indicates that these discrepancies might be partially explained by low retention of women and URM in undergraduate STEM programs where academic performance is a key predictor of retention.
-A growing body of evidence suggests that women and URM under-perform in introductory science courses compared to their white male colleagues, even when representation is equal.
-Additionally, there is evidence to suggest that women and URM participate less in class, which could inhibit the learning process and subsequent success.
-A prevailing hypothesis to explain achievement gaps and a lack of participation in class for women and URM is that, many students have an unconscious fear of being seen as a negative stereotype, termed stereotype threat.
-This is prevalent in fields that have historically been dominated by white males, such as in STEM.
-In order to retain a diverse population of students in STEM, in an effort to ensure all students have equal opportunities and resources to be successful, under-performance and a lack of participation in introductory science courses needs to be addressed.
-One mechanism to address the issue is through the use of inclusive teaching practices –teaching methods that promote the full participation, learning, and success of all students.
+A long-standing issue within STEM fields, specifically within academia, has been a lack of diverse representation of scientists for trainees (graduate students and postdoctoral fellows).
+In order to maintain retention of HURM, non-Caucasian individuals, and women in STEM fields, it is important for trainees to have visual representations of themselves as scientists.
+The importance of representation in retaining a diverse group of individuals in STEM fields is supported by social role theory [@Eagly1984].
+Individuals tend to make inferences about characteristics that are needed to be successful in a given role by examining individuals that most occupy that role [@Eagly1984; @Carter2018].
+Therefore, trainees who do not see representation of themselves in senior scientific positions, or in this case as senior faculty members, may decide that they do not possess the characteristics that are required to succeed.
+In an attempt to make science a more inclusive environment, many individuals have attempted to address this issue by promoting the inclusion of more women speakers at conferences [@kalejta_gender_2017; @casadevall_presence_2014; @klein_speaking_2017].
+However, no study to date has addressed invited speaker seminar series diversity within their own institution.
 
-+ introduce invited speaker series - what are the goals, who attends, etc.
+Within the Department of Microbiology and Immunology at the University of Michigan (Ann Arbor, MI, USA), each year from September to June, faculty members have the opportunity to invite scientists from other institutions to give a one-hour seminar in which all department members attend.
+The invited seminar speaker also has the opportunity to meet with current department faculty members and trainees.
+Scientists who are invited to give seminars are widely regarded as successful and the top in their field.
+Thus, if trainees are constantly being exposed to “the top scientist in their field”, according to social role theory, it is imperative that the selected seminar speakers represent a diverse group of individuals.
 
-+ previous examinations have focused on conferences and panels, large number of people in a short period of time -- easy to make comparisons & see trends
-
-+ more difficult to see trends over long time period -- asked cumulative trends of speakers over 5 year period, "normative" to trainees in the department
+In this study, we examine and compare the proportion of HURM, non-Caucasian/non-HURM, and women invited speakers to white males in the Department of Microbiology and Immunology.
+Additionally, we compare invited-speaker demographics to the current trainee demographics as a means to gauge if trainee demographics are being represented accordingly throughout the seminar series.
+Following our investigation, we proposed a policy change to the Department of Microbiology and Immunology in how invited speakers are selected as a means to promote inclusion in our department and reduce stereotype threat, microaggressions, and unconscious bias.
+In order to facilitate inviting a more diverse group of scientists, we developed a set of resources that allow scientists, within the field of microbiology, to self-identify as an HURM, non-Caucasian/non-HURM, or a woman.
+These resources will promote inclusion and diversity by providing greater representation of all scientists and will provide hosts an opportunity to invite a more diverse group of scientists.
 
@@
 
+Data were analyzed and figures generated in R Statisical Software, using the tidyverse package [@wickham_tidyverse:_2017].
+
 ## Results
@@
 Of `r sum(lect_summary$n)` lectureships over the five year period, `r lect_summary[4,4]`% were awarded to women.
-The proportion of women as faculty hosts and speakers is equivalent to global estimates that 40% of microbiologists are women (Elseiver), with a slightly lower representation of women in lectureships.
+The proportion of women as faculty hosts and speakers is equivalent to global estimates that 40% of microbiologists are women, with a slightly lower representation of women in lectureships [@allagnat_gender_2017].
 
@@
 
++ HURM represent 10% of assistant prof, falls to 5% of full [@whittaker_retention_2015]
+
++ 2017 doctorates in Micro/immuno = 26,250 -- [@nsf_survey_2017]
+HURM = `r get_percent((1350+450+1000),26250)` -- 11%
+NCNH = `r get_percent((5350+450),26250)` -- 22%
+
 ## Discussion
 
-Several papers have investigated the representation of women at scientific conferences, however, we have only identified one that focused on invited speakers at universities (Nittrouer, 2018).
-In their study, Nittrouer et.
-al., examined 3,652 talks at 50 U.S.
+Several papers have investigated the representation of women at scientific conferences, however, we have only identified one that focused on invited speakers at universities [@nittrouer_gender_2018].
+In their study, @nittrouer, examined 3,652 talks at 50 U.S.
 institutions in 2013 - 2014 and found that women faculty are less likely to be invited speakers, despite similar acceptance rates.
@@
 The dedication of women who have children to their work is perceived to be less than that of their colleagues, i.e., men who also have children.
-The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigious nature of these invitations and evidence to the contrary).
+The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigious nature of these invitations and evidence to the contrary)[@nittrouer_gender_2018; @xu_2008].
 As a result, the faculty member invites a different colleague who they feel is more likely to agree (and is a man).
@@
 The increased burden of women to prove competency decreases their likelihood to be considered for either tenure or as possible source of tenure letters.
+
+The desire to invite the “best” scientist to these seminar series also poses a problem for HURM and NCNH scientists.
+Both men and women who identify as HURM and Asian reported having to work harder than their white male colleagues to be perceived as legitimate scholars [@noauthor_seeking_2013].
+The proportion of HURM faculty at the Assistant and Associate Professor level is currently higher than the Full Professor level so it will be difficult to increase speaker diversity if early-career researchers are not being considered [@whittaker_retention_2015].
+These differences in performance expectations and patterns of exclusions are consistent themes in studies characterizing the HURM faculty experience [@pololi_race_2010; @hassouneh_experiences_2014].
+These experiences decrease the opportunities for HURM and NCNH scientists to network, secure letters for their own tenure package, and promote their work for consideration of award nominations.
 
@@
 
+# Instituting policy change within the Department of Microbiology and Immunology
+
+In an attempt to promote inclusion within the Dept.
+M&I these data were presented to faculty members and the dept chair (Harry Mobley).
+Since, trainee demographics were not represented within seminar speaker demographics over the past 5 years, we proposed a policy change as to how seminar speakers were being invited.
+This policy change included switching from PI invited to lab invited in an attempt to allow trainees to choose a speaker that best represented themselves.
+In addition to this we also created resources which allowed scientists to self-identify and provide host faculty with more diverse choices.
+
 ## Building Diversify
@@
 
-+ Development of Diversify tools
-    + describe maintenance of lists (Rebecca)
+The self-nomination form is a Google Form with entries logged in a private Google Sheet.
+This form is embedded within the website and can be linked to directly.
+The use of a Google Forms allows us to maintain this database at no cost and gives us the flexibility to add questions or change response options without disrupting previous responses.
+Entries are logged in a private spreadsheet so that entries can be screened before being added to the public database.
+This screening currently includes two steps: 1.
+Confirming that each person is listed in the database only once.
+2.
+Verifying that the submitted website is a professional website for the person being listed.
+If a person has not been listed in the database previously and passes step 2, a new entry is added to the public database spreadsheet.
+If a person is already listed in the database, their information is updated to the most recent submission.
+
+This public spreadsheet is embedded in the website and can be open separately as a locked (uneditable) Google Sheet.
+Importantly, this allows the list to be easily searched.
+We have chosen to list individuals’ academic information first in the spreadsheet to encourage a focus on academic achievement rather than tokenization of marginalized identities.
+Currently the database lists individuals in order of self-nomination but future versions will be re-sorted based on name and/or academic field to varying the individuals who may receive more attention for simply being at the top of the list.
 
 The website provides an interface to the Google forms and spreadsheets with template pages for viewing the list, adding a name to the list, and finding additional resources.
-Importantly, our website creation tool is hosted for free by GitHub, which provides a free website for each GitHub organization (citation).
+Importantly, our website creation tool is hosted for free by GitHub, which provides a free website for each GitHub organization.
 Basic tools and skills required to set up a Diversify site include knowledge of, or experience with, the version control tool git, the webtool GitHub, and a text editor.
@@
 wrote the introduction and provided conceptual advice.
-All authors contributed to the final manuscript.
+All authors contributed to preparing the final manuscript.
 

### 2019-09-20 submission/manuscript.tex
add references and text from JL & RP

@@
 
-500 words
+Long-standing systemic bias, sexism, and racism have contributed to the
+underrepresentation of many racial and ethnic groups, as well as women,
+in science, technology, engineering, and math (STEM) fields (NIH 2015
+report, Measuring DEI 2016, (1)). Organization climate and culture that
+supports inclusion of all individuals is essential to support the
+retention of historically underrepresented minorities (HURM) in the
+U.S., as well as non-Caucasian individuals, and women in STEM fields
+(Schneider, 2013). Inclusive organization culture will not suffice in
+retaining HURM, non-Caucasian individuals, and women without
+organization policy changes that support their values and goals (2).
 
-Representation of white women and historically underrepresented
-minorities (HURM) in science, technology, engineering, and math (STEM)
-in the workforce remains low despite equal enrollment in undergraduate
-STEM majors. Longitudinal data indicates that these discrepancies might
-be partially explained by low retention of women and URM in
-undergraduate STEM programs where academic performance is a key
-predictor of retention. A growing body of evidence suggests that women
-and URM under-perform in introductory science courses compared to their
-white male colleagues, even when representation is equal. Additionally,
-there is evidence to suggest that women and URM participate less in
-class, which could inhibit the learning process and subsequent success.
-A prevailing hypothesis to explain achievement gaps and a lack of
-participation in class for women and URM is that, many students have an
-unconscious fear of being seen as a negative stereotype, termed
-stereotype threat. This is prevalent in fields that have historically
-been dominated by white males, such as in STEM. In order to retain a
-diverse population of students in STEM, in an effort to ensure all
-students have equal opportunities and resources to be successful,
-under-performance and a lack of participation in introductory science
-courses needs to be addressed. One mechanism to address the issue is
-through the use of inclusive teaching practices --teaching methods that
-promote the full participation, learning, and success of all students.
+A long-standing issue within STEM fields, specifically within academia,
+has been a lack of diverse representation of scientists for trainees
+(graduate students and postdoctoral fellows). In order to maintain
+retention of HURM, non-Caucasian individuals, and women in STEM fields,
+it is important for trainees to have visual representations of
+themselves as scientists. The importance of representation in retaining
+a diverse group of individuals in STEM fields is supported by social
+role theory (3). Individuals tend to make inferences about
+characteristics that are needed to be successful in a given role by
+examining individuals that most occupy that role (3, 4). Therefore,
+trainees who do not see representation of themselves in senior
+scientific positions, or in this case as senior faculty members, may
+decide that they do not possess the characteristics that are required to
+succeed. In an attempt to make science a more inclusive environment,
+many individuals have attempted to address this issue by promoting the
+inclusion of more women speakers at conferences (5--7). However, no
+study to date has addressed invited speaker seminar series diversity
+within their own institution.
 
-\begin{itemize}
-\item
-  introduce invited speaker series - what are the goals, who attends,
-  etc.
-\item
-  previous examinations have focused on conferences and panels, large
-  number of people in a short period of time -- easy to make comparisons
-  \& see trends
-\item
-  more difficult to see trends over long time period -- asked cumulative
-  trends of speakers over 5 year period, ``normative'' to trainees in
-  the department
-\end{itemize}
+Within the Department of Microbiology and Immunology at the University
+of Michigan (Ann Arbor, MI, USA), each year from September to June,
+faculty members have the opportunity to invite scientists from other
+institutions to give a one-hour seminar in which all department members
+attend. The invited seminar speaker also has the opportunity to meet
+with current department faculty members and trainees. Scientists who are
+invited to give seminars are widely regarded as successful and the top
+in their field. Thus, if trainees are constantly being exposed to ``the
+top scientist in their field'', according to social role theory, it is
+imperative that the selected seminar speakers represent a diverse group
+of individuals.
+
+In this study, we examine and compare the proportion of HURM,
+non-Caucasian/non-HURM, and women invited speakers to white males in the
+Department of Microbiology and Immunology. Additionally, we compare
+invited-speaker demographics to the current trainee demographics as a
+means to gauge if trainee demographics are being represented accordingly
+throughout the seminar series. Following our investigation, we proposed
+a policy change to the Department of Microbiology and Immunology in how
+invited speakers are selected as a means to promote inclusion in our
+department and reduce stereotype threat, microaggressions, and
+unconscious bias. In order to facilitate inviting a more diverse group
+of scientists, we developed a set of resources that allow scientists,
+within the field of microbiology, to self-identify as an HURM,
+non-Caucasian/non-HURM, or a woman. These resources will promote
+inclusion and diversity by providing greater representation of all
+scientists and will provide hosts an opportunity to invite a more
+diverse group of scientists.
 
@@
 
+Data were analyzed and figures generated in R Statisical Software, using
+the tidyverse package ({\textbf{???}}).
+
 \subsection{Results}\label{results}
@@
 The proportion of women as faculty hosts and speakers is equivalent to
-global estimates that 40\% of microbiologists are women (Elseiver), with
-a slightly lower representation of women in lectureships.
+global estimates that 40\% of microbiologists are women, with a slightly
+lower representation of women in lectureships (8).
 
@@
 
+\begin{itemize}
+\item
+  HURM represent 10\% of assistant prof, falls to 5\% of full (9)
+\item
+  2017 doctorates in Micro/immuno = 26,250 -- ({\textbf{???}}) HURM =
+  10.67 -- 11\% NCNH = 22.1 -- 22\%
+\end{itemize}
+
 \subsection{Discussion}\label{discussion}
@@
 scientific conferences, however, we have only identified one that
-focused on invited speakers at universities (Nittrouer, 2018). In their
-study, Nittrouer et. al., examined 3,652 talks at 50 U.S. institutions
-in 2013 - 2014 and found that women faculty are less likely to be
-invited speakers, despite similar acceptance rates. These results
-suggest that women faculty are less often invited as speakers, a
-decision that may be negatively impacted by assumptions about competency
-and dedication. The dedication of women who have children to their work
-is perceived to be less than that of their colleagues, i.e., men who
-also have children. The perceived prioritization and commitments of
-women to family over work may cause faculty to doubt their acceptance of
-a speaking invitation (despite the prestigious nature of these
-invitations and evidence to the contrary). As a result, the faculty
+focused on invited speakers at universities (10). In their study,
+\textbf{???}, examined 3,652 talks at 50 U.S. institutions in 2013 -
+2014 and found that women faculty are less likely to be invited
+speakers, despite similar acceptance rates. These results suggest that
+women faculty are less often invited as speakers, a decision that may be
+negatively impacted by assumptions about competency and dedication. The
+dedication of women who have children to their work is perceived to be
+less than that of their colleagues, i.e., men who also have children.
+The perceived prioritization and commitments of women to family over
+work may cause faculty to doubt their acceptance of a speaking
+invitation (despite the prestigious nature of these invitations and
+evidence to the contrary)({\textbf{???}}, 10). As a result, the faculty
 member invites a different colleague who they feel is more likely to
@@
 for either tenure or as possible source of tenure letters.
+
+The desire to invite the ``best'' scientist to these seminar series also
+poses a problem for HURM and NCNH scientists. Both men and women who
+identify as HURM and Asian reported having to work harder than their
+white male colleagues to be perceived as legitimate scholars (11). The
+proportion of HURM faculty at the Assistant and Associate Professor
+level is currently higher than the Full Professor level so it will be
+difficult to increase speaker diversity if early-career researchers are
+not being considered (9). These differences in performance expectations
+and patterns of exclusions are consistent themes in studies
+characterizing the HURM faculty experience (12, 13). These experiences
+decrease the opportunities for HURM and NCNH scientists to network,
+secure letters for their own tenure package, and promote their work for
+consideration of award nominations.
 
@@
 
+\section{Instituting policy change within the Department of Microbiology
+and
+Immunology}\label{instituting-policy-change-within-the-department-of-microbiology-and-immunology}
+
+In an attempt to promote inclusion within the Dept. M\&I these data were
+presented to faculty members and the dept chair (Harry Mobley). Since,
+trainee demographics were not represented within seminar speaker
+demographics over the past 5 years, we proposed a policy change as to
+how seminar speakers were being invited. This policy change included
+switching from PI invited to lab invited in an attempt to allow trainees
+to choose a speaker that best represented themselves. In addition to
+this we also created resources which allowed scientists to self-identify
+and provide host faculty with more diverse choices.
+
 \subsection{Building Diversify}\label{building-diversify}
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Development of Diversify tools
+The self-nomination form is a Google Form with entries logged in a
+private Google Sheet. This form is embedded within the website and can
+be linked to directly. The use of a Google Forms allows us to maintain
+this database at no cost and gives us the flexibility to add questions
+or change response options without disrupting previous responses.
+Entries are logged in a private spreadsheet so that entries can be
+screened before being added to the public database. This screening
+currently includes two steps: 1. Confirming that each person is listed
+in the database only once. 2. Verifying that the submitted website is a
+professional website for the person being listed. If a person has not
+been listed in the database previously and passes step 2, a new entry is
+added to the public database spreadsheet. If a person is already listed
+in the database, their information is updated to the most recent
+submission.
 
-  \begin{itemize}
-  \tightlist
-  \item
-    describe maintenance of lists (Rebecca)
-  \end{itemize}
-\end{itemize}
+This public spreadsheet is embedded in the website and can be open
+separately as a locked (uneditable) Google Sheet. Importantly, this
+allows the list to be easily searched. We have chosen to list
+individuals' academic information first in the spreadsheet to encourage
+a focus on academic achievement rather than tokenization of marginalized
+identities. Currently the database lists individuals in order of
+self-nomination but future versions will be re-sorted based on name
+and/or academic field to varying the individuals who may receive more
+attention for simply being at the top of the list.
 
@@
 hosted for free by GitHub, which provides a free website for each GitHub
-organization (citation). Basic tools and skills required to set up a
-Diversify site include knowledge of, or experience with, the version
-control tool git, the webtool GitHub, and a text editor. A tutorial in
-the DiversifyMicrobiology repository on GitHub provides links to these
+organization. Basic tools and skills required to set up a Diversify site
+include knowledge of, or experience with, the version control tool git,
+the webtool GitHub, and a text editor. A tutorial in the
+DiversifyMicrobiology repository on GitHub provides links to these
 resources and instructions for adapting the tool to your own field.
@@
 introduction and provided conceptual advice. All authors contributed to
-the final manuscript.
+preparing the final manuscript.
 
@@
 \hypertarget{refs}{}
+\hypertarget{ref-colloquy_2012}{}
+1. 2012. Colloquy on minority males in science, technology, engineering,
+and mathematics. National Academies Press.
+
+\hypertarget{ref-Coe2019}{}
+2. \textbf{Coe IR}, \textbf{Wiley R}, \textbf{Bekker L-G}. 2019.
+Organisational best practices towards gender equality in science and
+medicine. The Lancet \textbf{393}:587--593.
+doi:\href{https://doi.org/10.1016/s0140-6736(18)33188-x}{10.1016/s0140-6736(18)33188-x}.
+
+\hypertarget{ref-Eagly1984}{}
+3. \textbf{Eagly AH}, \textbf{Steffen VJ}. 1984. Gender stereotypes stem
+from the distribution of women and men into social roles. Journal of
+Personality and Social Psychology \textbf{46}:735--754.
+doi:\href{https://doi.org/10.1037/0022-3514.46.4.735}{10.1037/0022-3514.46.4.735}.
+
+\hypertarget{ref-Carter2018}{}
+4. \textbf{Carter AJ}, \textbf{Croft A}, \textbf{Lukas D},
+\textbf{Sandstrom GM}. 2018. Women's visibility in academic seminars:
+Women ask fewer questions than men. PLOS ONE \textbf{13}:e0202743.
+doi:\href{https://doi.org/10.1371/journal.pone.0202743}{10.1371/journal.pone.0202743}.
+
+\hypertarget{ref-kalejta_gender_2017}{}
+5. \textbf{Kalejta RF}, \textbf{Palmenberg AC}. 2017. Gender Parity
+Trends for Invited Speakers at Four Prominent Virology Conference
+Series. Journal of Virology \textbf{91}.
+doi:\href{https://doi.org/10.1128/JVI.00739-17}{10.1128/JVI.00739-17}.
+
+\hypertarget{ref-casadevall_presence_2014}{}
+6. \textbf{Casadevall A}, \textbf{Handelsman J}. 2014. The Presence of
+Female Conveners Correlates with a Higher Proportion of Female Speakers
+at Scientific Symposia. mBio \textbf{5}.
+doi:\href{https://doi.org/10.1128/mBio.00846-13}{10.1128/mBio.00846-13}.
+
+\hypertarget{ref-klein_speaking_2017}{}
+7. \textbf{Klein RS}, \textbf{Voskuhl R}, \textbf{Segal BM},
+\textbf{Dittel BN}, \textbf{Lane TE}, \textbf{Bethea JR}, \textbf{Carson
+MJ}, \textbf{Colton C}, \textbf{Rosi S}, \textbf{Anderson A},
+\textbf{Piccio L}, \textbf{Goverman JM}, \textbf{Benveniste EN},
+\textbf{Brown MA}, \textbf{Tiwari-Woodruff SK}, \textbf{Harris TH},
+\textbf{Cross AH}. 2017. Speaking out about gender imbalance in invited
+speakers improves diversity. Nature Immunology \textbf{18}:475--478.
+doi:\href{https://doi.org/10.1038/ni.3707}{10.1038/ni.3707}.
+
+\hypertarget{ref-allagnat_gender_2017}{}
+8. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
+HJ}, \textbf{Hanafi S}, \textbf{Herbert R}, \textbf{Huggett S},
+\textbf{Tobin S}. 2017. Gender in the global research landscape.
+
+\hypertarget{ref-whittaker_retention_2015}{}
+9. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
+Acosta VG}. 2015. Retention of Underrepresented Minority Faculty:
+Strategic Initiatives for Institutional Value Proposition Based on
+Perspectives from a Range of Academic Institutions. Journal of
+undergraduate neuroscience education: JUNE: a publication of FUN,
+Faculty for Undergraduate Neuroscience \textbf{13}:A136--145.
+
+\hypertarget{ref-nittrouer_gender_2018}{}
+10. \textbf{Nittrouer CL}, \textbf{Hebl MR}, \textbf{Ashburn-Nardo L},
+\textbf{Trump-Steele RCE}, \textbf{Lane DM}, \textbf{Valian V}. 2018.
+Gender disparities in colloquium speakers at top universities.
+Proceedings of the National Academy of Sciences \textbf{115}:104--108.
+doi:\href{https://doi.org/10.1073/pnas.1708414115}{10.1073/pnas.1708414115}.
+
+\hypertarget{ref-noauthor_seeking_2013}{}
+11. 2013. Seeking Solutions: Maximizing American Talent by Advancing
+Women of Color in Academia: Summary of a Conference. National Academies
+Press, Washington, D.C.
+
+\hypertarget{ref-pololi_race_2010}{}
+12. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
+Disadvantage and Faculty Experiences in Academic Medicine. Journal of
+General Internal Medicine \textbf{25}:1363--1369.
+doi:\href{https://doi.org/10.1007/s11606-010-1478-7}{10.1007/s11606-010-1478-7}.
+
+\hypertarget{ref-hassouneh_experiences_2014}{}
+13. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
+\textbf{Junkins EP}, \textbf{Horton LL}. 2014. The experiences of
+underrepresented minority faculty in schools of medicine. Medical
+Education Online \textbf{19}:24768.
+doi:\href{https://doi.org/10.3402/meo.v19.24768}{10.3402/meo.v19.24768}.
 

### 2019-09-21 submission/manuscript.Rmd
work on results, add references

@@
 
-Data were analyzed and figures generated in R Statisical Software, using the tidyverse package [@wickham_tidyverse:_2017].
+Data were analyzed and figures generated in R Statisical Software, using relevant packages [@R_software_2017; @wickham_tidyverse_2017; @cowplot; @markdown; @rmd_book; @rmd_rstudio; @knitr_2014; @knitr_2018; @lubridate; @readxl; @pdftools; @wickham_scales_2018; @neuwirth_rcolorbrewer_2014].
 
@@
   summarise(sum = sum(n))
+
+trainee_summary <- tidy_trainee %>% 
+  select(-Gender) %>% 
+  filter(value == "y") %>% distinct_() %>% 
+  group_by(demographic) %>% summarise(n = n()) %>% 
+  mutate(prop = get_percent(n, sum(.$n)))
 ```
@@
 
-Our analysis identified an over-representation of Caucasian individuals as hosting faculty and invited speakers, relative to the proportion of Caucasian trainees (Fig.
+Our analysis identified an over-representation of Caucasian individuals as hosting faculty and invited speakers (80% each), relative to the proportion of Caucasian trainees, which was 55% (Fig.
 1B).
 We also observed declines in the representation of HURM and NCNH faculty and speakers relative to the trainees (Fig 1B).
-Caucasian scientists also dominated the more prestigous invited speaker lectureships, comprising `r get_percent(sum(cauc_lect$sum), sum(lect_summary$n))`% of those awarded (Fig.
+HURM trainees made up 11% of the department, on track with the 11% of microbiology and immunology doctorates awarded in 2017 [@nsf_survey_2017].
+However, only 8.5% of invited speakers, and none of the hosting faculty, were HURM scientists.
+NCNH trainees were 34% of department students and postdocs (22% of microbiology and immunology doctorates in 2017), but only 19% of hosting faculty and 10.5% of invited speakers [@nsf_survey_2017].
+
+The more prestigous invited speaker lectureships were also dominated by caucasian scientists, who comprised `r get_percent(sum(cauc_lect$sum), sum(lect_summary$n))`% of those awarded (Fig.
 1C).
 HURM and NCNH scientists were awarded `r lect_summary[[2,3]]` and `r lect_summary[[3,3]]` lectureships, respectively.
-Because the intersection of identities can compound biases and outcomes, we further examined the lectureships by gender and race/ethnicty status.
+Because the intersection of identities can compound biases and outcomes, we further examined the lectureships by gender and race/ethnicity status.
 Caucasian men and women accounted for `r lect_summary[[1,4]]`% and `r lect_summary[[4,4]]`% of the lectureships, respectively.
@@
 
-+ HURM represent 10% of assistant prof, falls to 5% of full [@whittaker_retention_2015]
-
-+ 2017 doctorates in Micro/immuno = 26,250 -- [@nsf_survey_2017]
-HURM = `r get_percent((1350+450+1000),26250)` -- 11%
-NCNH = `r get_percent((5350+450),26250)` -- 22%
-
 ## Discussion
@@
 Several papers have investigated the representation of women at scientific conferences, however, we have only identified one that focused on invited speakers at universities [@nittrouer_gender_2018].
-In their study, @nittrouer, examined 3,652 talks at 50 U.S.
+In their study, Nittrouer et al, examined 3,652 talks at 50 U.S.
 institutions in 2013 - 2014 and found that women faculty are less likely to be invited speakers, despite similar acceptance rates.
@@
 
-The desire to invite the “best” scientist to these seminar series also poses a problem for HURM and NCNH scientists.
-Both men and women who identify as HURM and Asian reported having to work harder than their white male colleagues to be perceived as legitimate scholars [@noauthor_seeking_2013].
-The proportion of HURM faculty at the Assistant and Associate Professor level is currently higher than the Full Professor level so it will be difficult to increase speaker diversity if early-career researchers are not being considered [@whittaker_retention_2015].
-These differences in performance expectations and patterns of exclusions are consistent themes in studies characterizing the HURM faculty experience [@pololi_race_2010; @hassouneh_experiences_2014].
-These experiences decrease the opportunities for HURM and NCNH scientists to network, secure letters for their own tenure package, and promote their work for consideration of award nominations.
+The desire to invite the “best” scientist to these seminar series also poses a problem for HURM
+and NCNH scientists.
+A large portion of the NCNH cohort in our sample are Asian/Asian American individuals.
+Although Asian scientists are well-represented in the US scientific workforce, they face significant bias and barriers to inclusion in society and academia [@Hwang2008; @Tran2019].
+Both men and women who identify as HURM and Asian reported having to work harder than white men to be perceived as legitimate scholars [@noauthor_seeking_2013].
+This expectation of higher productivity may result in fewer HURM and NCNH individuals being invited as seminar speakers.
+This is particularly striking in the low number of NCNH individuals in the more prestigious lectureships of our sample despite the higher employment rate of Asian scientists.
+
+While HURM and NCNH share some experiences, differences including varying rates of hiring
+and tenure promotion mean unique considerations are important for inclusion of each group
+(doi:10.1001/jama.284.9.1085). For instance, the proportion of HURM faculty at the Assistant and
+Associate Professor level is currently higher than the Full Professor level so it will be difficult to increase speaker diversity if early-career researchers are not being considered [@whittaker_retention_2015].
+Increased performance expectations and patterns of exclusions are consistent themes in studies characterizing the HURM faculty experience [@pololi_race_2010; @hassouneh_experiences_2014].
+Therefore, inclusion of HURM faculty in seminar series is likely
+essential to increasing the number of HURM Associate and Full Professors. More significantly, a
+major barrier to inclusion of HURM faculty at similar proportions to HURM trainees is the low
+transition rate of scientists from HURM backgrounds to faculty positions and the associated low
+proportion of HURM faculty [@Gibbs2016].
+Even when HURM speaker rates match the proportion of HURM faculty employment, HURM trainees will be represented at a significantly higher proportion.
+Inclusion of HURM faculty in these seminarseries is just one aspect of larger institutional change that is needed [@johnson_msphere_2019].
 
@@
 This is a flawed assumption.
-While there is no doubt some overlap, each group remains marginalized due to a complex set of factors that are unique to each group and cannot always be solved by gender-based solutions.
+While there is no doubt some overlap, each group remains marginalized due to a unique complex set of factors that cannot always be solved by gender-based solutions.
 US-serving institutions, such as the University of Michigan have a particular responsibility to the historically suppressed populations included in our definition of HURMs.
@@
 
-# Instituting policy change within the Department of Microbiology and Immunology
+## Instituting policy change within the Department of Microbiology and Immunology
 

### 2019-09-21 submission/manuscript.tex
work on results, add references

@@
 Data were analyzed and figures generated in R Statisical Software, using
-the tidyverse package ({\textbf{???}}).
+relevant packages (8--20).
 
@@
 global estimates that 40\% of microbiologists are women, with a slightly
-lower representation of women in lectureships (8).
+lower representation of women in lectureships (21).
 
 Our analysis identified an over-representation of Caucasian individuals
-as hosting faculty and invited speakers, relative to the proportion of
-Caucasian trainees (Fig. 1B). We also observed declines in the
-representation of HURM and NCNH faculty and speakers relative to the
-trainees (Fig 1B). Caucasian scientists also dominated the more
-prestigous invited speaker lectureships, comprising 81.48\% of those
-awarded (Fig. 1C). HURM and NCNH scientists were awarded 3 and 2
-lectureships, respectively. Because the intersection of identities can
-compound biases and outcomes, we further examined the lectureships by
-gender and race/ethnicty status. Caucasian men and women accounted for
-44.44\% and 37.04\% of the lectureships, respectively. Just 18.52\% of
-lectureships were held by non-Caucasian men while none were held by
-non-Caucasian women (Fig. 1D).
+as hosting faculty and invited speakers (80\% each), relative to the
+proportion of Caucasian trainees, which was 55\% (Fig. 1B). We also
+observed declines in the representation of HURM and NCNH faculty and
+speakers relative to the trainees (Fig 1B). HURM trainees made up 11\%
+of the department, on track with the 11\% of microbiology and immunology
+doctorates awarded in 2017 (22). However, only 8.5\% of invited
+speakers, and none of the hosting faculty, were HURM scientists. NCNH
+trainees were 34\% of department students and postdocs (22\% of
+microbiology and immunology doctorates in 2017), but only 19\% of
+hosting faculty and 10.5\% of invited speakers (22).
 
-\begin{itemize}
-\item
-  HURM represent 10\% of assistant prof, falls to 5\% of full (9)
-\item
-  2017 doctorates in Micro/immuno = 26,250 -- ({\textbf{???}}) HURM =
-  10.67 -- 11\% NCNH = 22.1 -- 22\%
-\end{itemize}
+The more prestigous invited speaker lectureships were also dominated by
+caucasian scientists, who comprised 81.48\% of those awarded (Fig. 1C).
+HURM and NCNH scientists were awarded 3 and 2 lectureships,
+respectively. Because the intersection of identities can compound biases
+and outcomes, we further examined the lectureships by gender and
+race/ethnicity status. Caucasian men and women accounted for 44.44\% and
+37.04\% of the lectureships, respectively. Just 18.52\% of lectureships
+were held by non-Caucasian men while none were held by non-Caucasian
+women (Fig. 1D).
 
@@
 scientific conferences, however, we have only identified one that
-focused on invited speakers at universities (10). In their study,
-\textbf{???}, examined 3,652 talks at 50 U.S. institutions in 2013 -
+focused on invited speakers at universities (23). In their study,
+Nittrouer et al, examined 3,652 talks at 50 U.S. institutions in 2013 -
 2014 and found that women faculty are less likely to be invited
@@
 invitation (despite the prestigious nature of these invitations and
-evidence to the contrary)({\textbf{???}}, 10). As a result, the faculty
+evidence to the contrary)({\textbf{???}}, 23). As a result, the faculty
 member invites a different colleague who they feel is more likely to
@@
 The desire to invite the ``best'' scientist to these seminar series also
-poses a problem for HURM and NCNH scientists. Both men and women who
-identify as HURM and Asian reported having to work harder than their
-white male colleagues to be perceived as legitimate scholars (11). The
-proportion of HURM faculty at the Assistant and Associate Professor
-level is currently higher than the Full Professor level so it will be
-difficult to increase speaker diversity if early-career researchers are
-not being considered (9). These differences in performance expectations
-and patterns of exclusions are consistent themes in studies
-characterizing the HURM faculty experience (12, 13). These experiences
-decrease the opportunities for HURM and NCNH scientists to network,
-secure letters for their own tenure package, and promote their work for
-consideration of award nominations.
+poses a problem for HURM and NCNH scientists. A large portion of the
+NCNH cohort in our sample are Asian/Asian American individuals. Although
+Asian scientists are well-represented in the US scientific workforce,
+they face significant bias and barriers to inclusion in society and
+academia (24, 25). Both men and women who identify as HURM and Asian
+reported having to work harder than white men to be perceived as
+legitimate scholars (26). This expectation of higher productivity may
+result in fewer HURM and NCNH individuals being invited as seminar
+speakers. This is particularly striking in the low number of NCNH
+individuals in the more prestigious lectureships of our sample despite
+the higher employment rate of Asian scientists.
+
+While HURM and NCNH share some experiences, differences including
+varying rates of hiring and tenure promotion mean unique considerations
+are important for inclusion of each group
+(\url{doi:10.1001/jama.284.9.1085}). For instance, the proportion of
+HURM faculty at the Assistant and Associate Professor level is currently
+higher than the Full Professor level so it will be difficult to increase
+speaker diversity if early-career researchers are not being considered
+(27). Increased performance expectations and patterns of exclusions are
+consistent themes in studies characterizing the HURM faculty experience
+(28, 29). Therefore, inclusion of HURM faculty in seminar series is
+likely essential to increasing the number of HURM Associate and Full
+Professors. More significantly, a major barrier to inclusion of HURM
+faculty at similar proportions to HURM trainees is the low transition
+rate of scientists from HURM backgrounds to faculty positions and the
+associated low proportion of HURM faculty (30). Even when HURM speaker
+rates match the proportion of HURM faculty employment, HURM trainees
+will be represented at a significantly higher proportion. Inclusion of
+HURM faculty in these seminarseries is just one aspect of larger
+institutional change that is needed (31).
 
@@
 groups (e.g., HURM). This is a flawed assumption. While there is no
-doubt some overlap, each group remains marginalized due to a complex set
-of factors that are unique to each group and cannot always be solved by
-gender-based solutions. US-serving institutions, such as the University
-of Michigan have a particular responsibility to the historically
-suppressed populations included in our definition of HURMs. We therefore
-implore US institutions to apply this framing to their discussions and
-research.
+doubt some overlap, each group remains marginalized due to a unique
+complex set of factors that cannot always be solved by gender-based
+solutions. US-serving institutions, such as the University of Michigan
+have a particular responsibility to the historically suppressed
+populations included in our definition of HURMs. We therefore implore US
+institutions to apply this framing to their discussions and research.
 
@@
 
-\section{Instituting policy change within the Department of Microbiology
-and
+\subsection{Instituting policy change within the Department of
+Microbiology and
 Immunology}\label{instituting-policy-change-within-the-department-of-microbiology-and-immunology}
@@
 
+\hypertarget{ref-R_software_2017}{}
+8. \textbf{R Core Team}. 2017. R: A language and environment for
+statistical computing. R Foundation for Statistical Computing, Vienna,
+Austria.
+
+\hypertarget{ref-wickham_tidyverse_2017}{}
+9. \textbf{Wickham H}. 2017. Tidyverse: Easily Install and Load the
+'Tidyverse'.
+
+\hypertarget{ref-cowplot}{}
+10. \textbf{Wilke CO}. 2019. Cowplot: Streamlined plot theme and plot
+annotations for 'ggplot2'.
+
+\hypertarget{ref-markdown}{}
+11. \textbf{Allaire J}, \textbf{Horner J}, \textbf{Xie Y}, \textbf{Marti
+V}, \textbf{Porte N}. 2018. Markdown: 'Markdown' rendering for r.
+
+\hypertarget{ref-rmd_book}{}
+12. \textbf{Xie Y}, \textbf{Allaire J}, \textbf{Grolemund G}. 2018. R
+markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida.
+
+\hypertarget{ref-rmd_rstudio}{}
+13. \textbf{Allaire J}, \textbf{Xie Y}, \textbf{McPherson J},
+\textbf{Luraschi J}, \textbf{Ushey K}, \textbf{Atkins A},
+\textbf{Wickham H}, \textbf{Cheng J}, \textbf{Chang W}, \textbf{Iannone
+R}. 2018. Rmarkdown: Dynamic documents for r.
+
+\hypertarget{ref-knitr_2014}{}
+14. \textbf{Xie Y}. 2014. Knitr: A comprehensive tool for reproducible
+research in R. \emph{In} Stodden, V, Leisch, F, Peng, RD (eds.),
+Implementing reproducible computational research. Chapman; Hall/CRC.
+
+\hypertarget{ref-knitr_2018}{}
+15. \textbf{Xie Y}. 2018. Knitr: A general-purpose package for dynamic
+report generation in r.
+
+\hypertarget{ref-lubridate}{}
+16. \textbf{Grolemund G}, \textbf{Wickham H}. 2011. Dates and times made
+easy with lubridate. Journal of Statistical Software \textbf{40}:1--25.
+
+\hypertarget{ref-readxl}{}
+17. \textbf{Wickham H}, \textbf{Bryan J}. 2018. Readxl: Read excel
+files.
+
+\hypertarget{ref-pdftools}{}
+18. \textbf{Ooms J}. 2019. Pdftools: Text extraction, rendering and
+converting of pdf documents.
+
+\hypertarget{ref-wickham_scales_2018}{}
+19. \textbf{Wickham H}. 2018. Scales: Scale Functions for Visualization.
+
+\hypertarget{ref-neuwirth_rcolorbrewer_2014}{}
+20. \textbf{Neuwirth E}. 2014. RColorBrewer: ColorBrewer Palettes.
+
 \hypertarget{ref-allagnat_gender_2017}{}
-8. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
+21. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
 HJ}, \textbf{Hanafi S}, \textbf{Herbert R}, \textbf{Huggett S},
@@
 
+\hypertarget{ref-nsf_survey_2017}{}
+22. \textbf{Science and Engineering Statistics NC for}. 2017. Survey of
+Doctorate Recipients, Survey Year 2017. National Science Foundation,
+Alexandria, VA.
+
+\hypertarget{ref-nittrouer_gender_2018}{}
+23. \textbf{Nittrouer CL}, \textbf{Hebl MR}, \textbf{Ashburn-Nardo L},
+\textbf{Trump-Steele RCE}, \textbf{Lane DM}, \textbf{Valian V}. 2018.
+Gender disparities in colloquium speakers at top universities.
+Proceedings of the National Academy of Sciences \textbf{115}:104--108.
+doi:\href{https://doi.org/10.1073/pnas.1708414115}{10.1073/pnas.1708414115}.
+
+\hypertarget{ref-Hwang2008}{}
+24. \textbf{Hwang W-C}, \textbf{Goto S}. 2008. The impact of perceived
+racial discrimination on the mental health of asian american and latino
+college students. Cultural Diversity and Ethnic Minority Psychology
+\textbf{14}:326--335.
+doi:\href{https://doi.org/10.1037/1099-9809.14.4.326}{10.1037/1099-9809.14.4.326}.
+
+\hypertarget{ref-Tran2019}{}
+25. \textbf{Tran VC}, \textbf{Lee J}, \textbf{Huang TJ}. 2019.
+Revisiting the asian second-generation advantage. Ethnic and Racial
+Studies \textbf{42}:2248--2269.
+doi:\href{https://doi.org/10.1080/01419870.2019.1579920}{10.1080/01419870.2019.1579920}.
+
+\hypertarget{ref-noauthor_seeking_2013}{}
+26. 2013. Seeking Solutions: Maximizing American Talent by Advancing
+Women of Color in Academia: Summary of a Conference. National Academies
+Press, Washington, D.C.
+
 \hypertarget{ref-whittaker_retention_2015}{}
-9. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
+27. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
 Acosta VG}. 2015. Retention of Underrepresented Minority Faculty:
@@
 
-\hypertarget{ref-nittrouer_gender_2018}{}
-10. \textbf{Nittrouer CL}, \textbf{Hebl MR}, \textbf{Ashburn-Nardo L},
-\textbf{Trump-Steele RCE}, \textbf{Lane DM}, \textbf{Valian V}. 2018.
-Gender disparities in colloquium speakers at top universities.
-Proceedings of the National Academy of Sciences \textbf{115}:104--108.
-doi:\href{https://doi.org/10.1073/pnas.1708414115}{10.1073/pnas.1708414115}.
-
-\hypertarget{ref-noauthor_seeking_2013}{}
-11. 2013. Seeking Solutions: Maximizing American Talent by Advancing
-Women of Color in Academia: Summary of a Conference. National Academies
-Press, Washington, D.C.
-
 \hypertarget{ref-pololi_race_2010}{}
-12. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
+28. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
 Disadvantage and Faculty Experiences in Academic Medicine. Journal of
@@
 \hypertarget{ref-hassouneh_experiences_2014}{}
-13. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
+29. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
 \textbf{Junkins EP}, \textbf{Horton LL}. 2014. The experiences of
@@
 
+\hypertarget{ref-Gibbs2016}{}
+30. \textbf{Gibbs KD}, \textbf{Basson J}, \textbf{Xierali IM},
+\textbf{Broniatowski DA}. 2016. Decoupling of the minority PhD talent
+pool and assistant professor hiring in medical school basic science
+departments in the US. eLife \textbf{5}.
+doi:\href{https://doi.org/10.7554/elife.21393}{10.7554/elife.21393}.
+
+\hypertarget{ref-johnson_msphere_2019}{}
+31. \textbf{Johnson MDL}. 2019. mSphere of Influence: Hiring of
+Underrepresented Minority Assistant Professors in Medical School Basic
+Science Departments Has a Long Way To Go. mSphere \textbf{4}.
+doi:\href{https://doi.org/10.1128/mSphere.00599-19}{10.1128/mSphere.00599-19}.
+
 \end{document}

### 2019-09-24 code/demo_comp.R
clean up figures

@@ -14,7 +14,8 @@ demo_plot <- demo_combined %>%
   ggplot()+
   geom_col(aes(x = role, y = prop_y, fill = role), alpha = 0.75)+
   facet_wrap(~demographic)+
-  labs(x = "Academic Role\n", y = "Proportion of Population")+
+  labs(x = "Academic Role\n", y = "Race/Ethnicity (%)")+
+  coord_cartesian(ylim = c(0, 100))+
   set_role_colors +
   my_theme_horiz +
   theme(axis.text.x=element_blank(),

### 2019-09-24 code/gender_comp.R

@@ -13,7 +13,7 @@ gender_combined$role <- fct_relevel(gender_combined$role, dat_levels)
 gender_plot_leg <- gender_combined %>% 
   ggplot()+
   geom_col(aes(x = role, y = prop_W, fill = role), alpha = 0.75)+
-  labs(x = "Academic Role\n", y = "Proportion of Women\n in the Population", 
+  labs(x = "Academic Role\n", y = "Women (%)", 
        fill = "Academic Role")+
   set_role_colors
 
@@ -21,8 +21,9 @@ gender_plot <- gender_combined %>%
   ggplot()+
   geom_col(aes(x = role, y = prop_W, fill = role), alpha = 0.75)+
   labs(x = "Academic Role\n", 
-       y = "Proportion of Women\n in the Population", 
+       y = "Women (%)", 
        fill = "Academic Role")+
+  coord_cartesian(ylim = c(0, 100))+
   set_role_colors +
   my_theme_horiz+
   theme(axis.text.x=element_blank(),

### 2019-09-24 code/get_figures.R

@@ -9,7 +9,7 @@ legend <- get_legend(gender_plot_leg)
 top_row <- plot_grid(gender_plot, blank, legend,
                      rel_widths = c(2, 1, 1), nrow = 1)
 
-bottom_row <- plot_grid(lectureship_demo_plot, lectureship_gend_cauc_plot,
+bottom_row <- plot_grid(lectureship_demo_plot, lectureship_gend_plot,
                         labels = c("C", "D"), label_size = 18)
 
 plot_grid(top_row, demo_plot, bottom_row, labels = c("A", "B", ""),

### 2019-09-24 code/lectureship_div.R

@@ -14,37 +14,22 @@ lectureship_demo_plot <- lectureship %>%
   ggplot(aes(x = value))+
   geom_bar(aes(y = (..count..)/sum(..count..), fill = value))+
   facet_grid(~demographic)+
-  scale_y_continuous(labels = scales::percent)+
+  scale_y_continuous(labels = multiply, limits = c(0, 1))+
   #geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
-  labs(y = "Percent of Lectureships", x = "Speaker Demographics")+
+  labs(y = "Lectureships (%)", x = "Speaker Demographics")+
   scale_fill_manual(values = "grey17")+
   my_theme_horiz+
   theme(axis.text.x=element_blank(),
         axis.ticks.x=element_blank())
 
-lectureship_gend_cauc_plot <- speaker_data %>% 
-  filter(!is.na(Lectureship)) %>% 
-  filter(Host != "Student") %>% 
-  filter(Host != "Postdoc") %>% 
-  select(Speaker_Gender, Speaker_Caucasian) %>% 
-  ggplot(aes(x = Speaker_Gender))+
-  geom_bar(aes(y = (..count..)/sum(..count..), 
-               fill = Speaker_Gender))+
-  facet_wrap(~if_else(Speaker_Caucasian == "y", "Caucasian", "Non-Caucasian"))+
-  scale_y_continuous(labels = scales::percent)+
-  labs(y = "\nPercent of Lectureships", x = "Speaker Gender")+
-  scale_fill_manual(values = c("grey17", "dark gray"))+
-  my_theme_horiz
-  #geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
-  
 lectureship_gend_plot <- lectureship %>% 
   filter(value == "y") %>% 
   ggplot(aes(x = Speaker_Gender))+
   geom_bar(aes(y = (..count..)/sum(..count..), 
                fill = Speaker_Gender), position = "dodge")+
   facet_grid(~demographic)+
-  scale_y_continuous(labels = scales::percent)+
-  labs(y = "\nPercent of Lectureships", x = "Speaker Gender")+
+  scale_y_continuous(labels = multiply, limits = c(0, 1))+
+  labs(y = "\nLectureships (%)", x = "Speaker Gender")+
   scale_fill_manual(values = c("grey17", "dark gray"))+
   my_theme_horiz
 

### 2019-09-24 code/load_data.R

@@ -13,6 +13,12 @@ get_percent <- function(x, y){
   return(percent)
 }
 
+#function to remove % & decimal labels from figs C & D
+multiply <- function(x){
+  percent <- x * 100
+  return(percent)
+}
+
 #data setup----
 speaker_data <- read_csv("../data/speaker_dataset_14-19.csv") %>% 
   mutate(Speaker_id = rownames(.),

### 2019-09-24 submission/manuscript.Rmd
revise discussion, add references

@@
 \newpage
+
+## Conflicts of Interest
+
+\vspace{40mm}
+
+All authors affirm that there are no conflicts of interest.
+
+\newpage
 \linenumbers
@@
 ## Abstract
+
+Social role theory emphasizes the importance of "like" representation to improve feelings of self-efficacy and belonging.
+This is an issue for trainees in the biological sciences who are either white women or underrepresented minorities, since there is a lack of faculty who look like them in biology academic settings.
+One way to improve representation is through invited speaker series.
+In this persepective, we compare the diversity of invited speakers at one microbiology and immunology department to the diversity of their post-Baccalaurate trainees.
+We find that trainees are not proportionally represented by the invited speakers and provide policy suggestions and tools to address this issue.
 
@@
 The list of faculty hosts was used as a proxy for faculty demographics since as hosts, these faculty members are visible representatives of the department.
-The trainee lists were obtained from department listservs that included masters students, doctoral students, and post-doctoral fellows.
+The trainees were identified using from departmental email lists that included masters students, doctoral students, and post-doctoral fellows.
 
-This is a retrospective study, so individuals were not asked for their identities.
+This is a retrospective study, thus speakers were not asked for their identities at the time of visit.
 Instead we hand-coded proxy demographics using personal knowledge, photos, and CVs.
@@
 All others were placed into the NCNH group.
-We recognize that our proxy demographics are a limitation of the analysis and want to acknowledge that the presenting gender may not reflect the gender(s) that an individual identifies as.
-We also want to acknowledge that there are many other identities that are not captured in this limited analysis.
+We recognize that our proxy demographics are a limitation of the analysis and want to acknowledge that biological sex (male/female) is not always equivalent to the gender that an individual presents as (man/woman), which is also distinct from the gender(s) that an individual
+self-identifies as. We also want to acknowledge that there are many other identities that are not captured in this limited analysis.
 
@@
 
-The more prestigous invited speaker lectureships were also dominated by caucasian scientists, who comprised `r get_percent(sum(cauc_lect$sum), sum(lect_summary$n))`% of those awarded (Fig.
+The more prestigous invited speaker lectureships were also dominated by Caucasian scientists, who comprised `r get_percent(sum(cauc_lect$sum), sum(lect_summary$n))`% of those awarded (Fig.
 1C).
@@
 
+[Add paragraph summarizing findings ] According to social role theory, this department is not adequately serving their non-Caucasian trainees.
+
 Several papers have investigated the representation of women at scientific conferences, however, we have only identified one that focused on invited speakers at universities [@nittrouer_gender_2018].
@@
 institutions in 2013 - 2014 and found that women faculty are less likely to be invited speakers, despite similar acceptance rates.
-These results suggest that women faculty are less often invited as speakers, a decision that may be negatively impacted by assumptions about competency and dedication.
-The dedication of women who have children to their work is perceived to be less than that of their colleagues, i.e., men who also have children.
-The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigious nature of these invitations and evidence to the contrary)[@nittrouer_gender_2018; @xu_2008].
-As a result, the faculty member invites a different colleague who they feel is more likely to agree (and is a man).
-Departments have different processes and criteria for selecting invited speakers, but it is a matter of pride to bring the best scientists possible.
-It may be that the definition of "best" poses a problem to women, who need three-times as many publications as their men colleges to be considered equally competent.
-Some departments only invite tenured faculty, which severely limits the number of potential women speakers.
-Another scenario is that pre-tenure faculty members invite prestigious, tenured faculty in their field to network and secure letters for their own tenure package.
-The increased burden of women to prove competency decreases their likelihood to be considered for either tenure or as possible source of tenure letters.
-
-The desire to invite the “best” scientist to these seminar series also poses a problem for HURM
-and NCNH scientists.
-A large portion of the NCNH cohort in our sample are Asian/Asian American individuals.
-Although Asian scientists are well-represented in the US scientific workforce, they face significant bias and barriers to inclusion in society and academia [@Hwang2008; @Tran2019].
-Both men and women who identify as HURM and Asian reported having to work harder than white men to be perceived as legitimate scholars [@noauthor_seeking_2013].
-This expectation of higher productivity may result in fewer HURM and NCNH individuals being invited as seminar speakers.
-This is particularly striking in the low number of NCNH individuals in the more prestigious lectureships of our sample despite the higher employment rate of Asian scientists.
-
-While HURM and NCNH share some experiences, differences including varying rates of hiring
-and tenure promotion mean unique considerations are important for inclusion of each group
-(doi:10.1001/jama.284.9.1085). For instance, the proportion of HURM faculty at the Assistant and
-Associate Professor level is currently higher than the Full Professor level so it will be difficult to increase speaker diversity if early-career researchers are not being considered [@whittaker_retention_2015].
-Increased performance expectations and patterns of exclusions are consistent themes in studies characterizing the HURM faculty experience [@pololi_race_2010; @hassouneh_experiences_2014].
-Therefore, inclusion of HURM faculty in seminar series is likely
-essential to increasing the number of HURM Associate and Full Professors. More significantly, a
-major barrier to inclusion of HURM faculty at similar proportions to HURM trainees is the low
-transition rate of scientists from HURM backgrounds to faculty positions and the associated low
-proportion of HURM faculty [@Gibbs2016].
-Even when HURM speaker rates match the proportion of HURM faculty employment, HURM trainees will be represented at a significantly higher proportion.
-Inclusion of HURM faculty in these seminarseries is just one aspect of larger institutional change that is needed [@johnson_msphere_2019].
-
+These results suggest that women faculty are less often invited as speakers.
 We have not been able to identify any other publications examining scientific speaker diversity beyond gender.
@@
 
-According to social role theory, this department is not adequietly serving their non-Caucasian trainees.
-Implict biases that affect perceptions of marginalized groups are the primary issue, but we must acknowledge that it is not always possible to identify members of historically under-served communities.
-For instance, after data analysis, we learned that at least one speaker in our data set should have been categorized as a HURM instead of Caucasian, but it wasn't readily apparent from their internet presence or CV.
-This limitation makes two important points: that percieved identity often plays a larger role than self-identification, and that we need better tools to identify members of marginalized groups.
+Departments have different processes and criteria for selecting invited speakers, but it is a matter of pride to bring the best scientists possible.
+It may be that the definition of "best" poses a problem to women, who need three-times as many publications as their men colleges to be considered equally competent [@BlairLoy2017, @?], and those that identify as HURM and Asian, who report having to work harder than white men to be perceived as legitimate scholars [@noauthor_seeking_2013].
+Some departments only invite tenured faculty, which severely limits the number of potential speakers who are white women or non-Caucasian.
+Yet, another scenario is that pre-tenure faculty members invite prestigious, tenured faculty in their field to network and secure letters for their own tenure package.
+The increased burden of white women and non-Caucasian scientists to prove competency decreases their likelihood to be considered for either tenure or as possible source of tenure letters.
+
+Each underrepresented group in our cohort faces a complex set of barriers to achieving faculty status.
+For instance, the decision to invite a woman may also be negatively impacted by assumptions about competency and dedication.
+The dedication of women who have children to their work is perceived to be less than that of their colleagues, i.e., men who also have children [@Firth1982; @Correll2007; @Fuegen2004].
+The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation, despite the prestigious nature of these invitations and evidence that men and women accept at similar rates [@nittrouer_gender_2018; @xu_2008].
+As a result, the faculty member invites a different colleague who they feel is more likely to agree (and is a man).
+Another large portion of our sample were the NCNH cohort, who are predominately Asian/Asian American individuals.
+Although Asian scientists are well-represented in the US scientific workforce, they face significant bias and barriers to inclusion in society and academia [@Hwang2008; @Tran2019].
+For instance, despite the higher employment rate of Asian scientists, they were not well-represented in the more prestigious lectureships.
+
+While HURM and NCNH share some experiences, differences including varying rates of hiring and tenure promotion mean unique considerations are important for inclusion of each group [@Fang2000].
+For instance, a major barrier to inclusion of HURM faculty at similar proportions to HURM trainees is the low transition rate of scientists from HURM backgrounds to faculty positions and the associated low proportion of HURM faculty [@Gibbs2016].
+The proportion of HURM faculty at the Assistant and Associate Professor level is currently higher than at Full Professor so it will be difficult to increase speaker diversity if early-career researchers are not being considered [@whittaker_retention_2015].
+Increased performance expectations and patterns of exclusions are consistent themes in studies characterizing the HURM faculty experience [@pololi_race_2010; @hassouneh_experiences_2014].
+Therefore, inclusion of HURM faculty in seminar series is likely essential to increasing the number of HURM Associate and Full Professors.
+Even when HURM speaker rates match the proportion of HURM faculty employment, HURM trainees will be represented at a significantly higher proportion.
+Inclusion of HURM faculty in these seminarseries is just one aspect of larger institutional change that is needed [@johnson_msphere_2019].
 
@@
 This policy change included switching from PI invited to lab invited in an attempt to allow trainees to choose a speaker that best represented themselves.
-In addition to this we also created resources which allowed scientists to self-identify and provide host faculty with more diverse choices.
+
+Implict biases that affect perceptions of marginalized groups are the primary issue, but we must acknowledge that it is not always possible to identify members of historically under-served communities.
+For instance, after data analysis, we learned that at least one speaker in our data set should have been categorized as a HURM instead of Caucasian, but it wasn't readily apparent from their internet presence or CV.
+This limitation makes two important points: that percieved identity often plays a larger role than self-identification, and that we need better tools to identify members of marginalized groups.
+So in addition to our policy change, we also created resources that allow scientists to self-identify and provide host faculty with more diverse choices.
 
@@
 Additionally, we have built these as a tool for use by other fields and organizations to create their own lists.
-Importantly, since these lists are compiled by self-nomination, we can ensure that only scientists comfortable revealing their marginalized identities are included.
+Since these lists are compiled by self-nomination, we can ensure that only scientists comfortable revealing their marginalized identities are included.
 
@@
 Entries are logged in a private spreadsheet so that entries can be screened before being added to the public database.
-This screening currently includes two steps: 1.
-Confirming that each person is listed in the database only once.
-2.
-Verifying that the submitted website is a professional website for the person being listed.
-If a person has not been listed in the database previously and passes step 2, a new entry is added to the public database spreadsheet.
+This screening includes two steps: confirming that each person is listed in the database only once and that any submitted website is a personal, professional website.
+If both criteria are met, a new entry is added to the public database spreadsheet.
 If a person is already listed in the database, their information is updated to the most recent submission.
 
-This public spreadsheet is embedded in the website and can be open separately as a locked (uneditable) Google Sheet.
-Importantly, this allows the list to be easily searched.
+This public spreadsheet is embedded in the website and can be open separately as a locked (uneditable) Google Sheet, allowing the list to be easily searched.
 We have chosen to list individuals’ academic information first in the spreadsheet to encourage a focus on academic achievement rather than tokenization of marginalized identities.
@@
 wrote the introduction and provided conceptual advice.
+A.K.H.
+and J.L facilited the policy change to the UM Department of Microbiology and Immunology.
 All authors contributed to preparing the final manuscript.
@@
 Template and complete instructions for generating a field-specific Diversity website are available at https://github.com/diversifymicrobiology/DiversifyMicrobiology.github.io/.
-
-![**The demographics of invited speakers, hosting faculty, and trainees.** A) The proportion of women in each academic role.
-B) The proportion of each academic role represented by individuals that are Caucasian (left), Historically Underrepresented Minorities (HURM, center) or International (right).
-C-D)The percent of lectureships awarded to individuals that are C) Caucasian, HURM, International or D) Caucasian or Non-Caucasian by gender.](Figure_1.png)
 
@@
 
+![**The demographics of invited speakers, hosting faculty, and trainees.** A) The proportion of women in each academic role.
+B) The proportion of each academic role represented by individuals that are Caucasian (left), Historically Underrepresented Minorities (HURM, center) or International (right).
+C-D)The percent of lectureships awarded to individuals that are C) Caucasian, HURM, International or D) Caucasian or Non-Caucasian by gender.](Figure_1.png)
+
 \newpage

### 2019-09-24 submission/manuscript.tex
revise discussion, add references

@@
 
+\subsection{Conflicts of Interest}\label{conflicts-of-interest}
+
+\vspace{40mm}
+
+All authors affirm that there are no conflicts of interest.
+
+\newpage
+
 \linenumbers
@@
 \subsection{Abstract}\label{abstract}
+
+Social role theory emphasizes the importance of ``like'' representation
+to improve feelings of self-efficacy and belonging. This is an issue for
+trainees in the biological sciences who are either white women or
+underrepresented minorities, since there is a lack of faculty who look
+like them in biology academic settings. One way to improve
+representation is through invited speaker series. In this persepective,
+we compare the diversity of invited speakers at one microbiology and
+immunology department to the diversity of their post-Baccalaurate
+trainees. We find that trainees are not proportionally represented by
+the invited speakers and provide policy suggestions and tools to address
+this issue.
 
@@
 demographics since as hosts, these faculty members are visible
-representatives of the department. The trainee lists were obtained from
-department listservs that included masters students, doctoral students,
-and post-doctoral fellows.
+representatives of the department. The trainees were identified using
+from departmental email lists that included masters students, doctoral
+students, and post-doctoral fellows.
 
-This is a retrospective study, so individuals were not asked for their
-identities. Instead we hand-coded proxy demographics using personal
-knowledge, photos, and CVs. The presenting gender of each individual was
-assigned using a binary system (man/woman). Due to the low number of
-individuals in the study, race/ethnicity demographics were split in
-three groups: Caucasian, Historically Under-represented Minority (HURM),
-and Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no)
-possibilty. Caucasian was assigned using the current U.S. Census
-definition where those of Middle Eastern, European, and Russian descent
-are included. HURM individuals were restricted to those with
-African-American, Indigenous, Alaskan/Hawaian Native, Latinx and/or
-Hispanic heritage. All others were placed into the NCNH group. We
-recognize that our proxy demographics are a limitation of the analysis
-and want to acknowledge that the presenting gender may not reflect the
-gender(s) that an individual identifies as. We also want to acknowledge
-that there are many other identities that are not captured in this
-limited analysis.
+This is a retrospective study, thus speakers were not asked for their
+identities at the time of visit. Instead we hand-coded proxy
+demographics using personal knowledge, photos, and CVs. The presenting
+gender of each individual was assigned using a binary system
+(man/woman). Due to the low number of individuals in the study,
+race/ethnicity demographics were split in three groups: Caucasian,
+Historically Under-represented Minority (HURM), and
+Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibilty.
+Caucasian was assigned using the current U.S. Census definition where
+those of Middle Eastern, European, and Russian descent are included.
+HURM individuals were restricted to those with African-American,
+Indigenous, Alaskan/Hawaian Native, Latinx and/or Hispanic heritage. All
+others were placed into the NCNH group. We recognize that our proxy
+demographics are a limitation of the analysis and want to acknowledge
+that biological sex (male/female) is not always equivalent to the gender
+that an individual presents as (man/woman), which is also distinct from
+the gender(s) that an individual self-identifies as. We also want to
+acknowledge that there are many other identities that are not captured
+in this limited analysis.
 
@@
 The more prestigous invited speaker lectureships were also dominated by
-caucasian scientists, who comprised 81.48\% of those awarded (Fig. 1C).
+Caucasian scientists, who comprised 81.48\% of those awarded (Fig. 1C).
 HURM and NCNH scientists were awarded 3 and 2 lectureships,
@@
 
+{[}Add paragraph summarizing findings {]} According to social role
+theory, this department is not adequately serving their non-Caucasian
+trainees.
+
 Several papers have investigated the representation of women at
@@
 speakers, despite similar acceptance rates. These results suggest that
-women faculty are less often invited as speakers, a decision that may be
-negatively impacted by assumptions about competency and dedication. The
-dedication of women who have children to their work is perceived to be
-less than that of their colleagues, i.e., men who also have children.
-The perceived prioritization and commitments of women to family over
-work may cause faculty to doubt their acceptance of a speaking
-invitation (despite the prestigious nature of these invitations and
-evidence to the contrary)({\textbf{???}}, 23). As a result, the faculty
-member invites a different colleague who they feel is more likely to
-agree (and is a man). Departments have different processes and criteria
-for selecting invited speakers, but it is a matter of pride to bring the
-best scientists possible. It may be that the definition of ``best''
-poses a problem to women, who need three-times as many publications as
-their men colleges to be considered equally competent. Some departments
-only invite tenured faculty, which severely limits the number of
-potential women speakers. Another scenario is that pre-tenure faculty
-members invite prestigious, tenured faculty in their field to network
-and secure letters for their own tenure package. The increased burden of
-women to prove competency decreases their likelihood to be considered
-for either tenure or as possible source of tenure letters.
+women faculty are less often invited as speakers. We have not been able
+to identify any other publications examining scientific speaker
+diversity beyond gender. This seems to be the first. This is concerning
+since conclusions drawn from gender-based studies are often framed, and
+considered, to be applicable to other marginalized groups (e.g., HURM).
+This is a flawed assumption. While there is no doubt some overlap, each
+group remains marginalized due to a unique complex set of factors that
+cannot always be solved by gender-based solutions. US-serving
+institutions, such as the University of Michigan have a particular
+responsibility to the historically suppressed populations included in
+our definition of HURMs. We therefore implore US institutions to apply
+this framing to their discussions and research.
 
-The desire to invite the ``best'' scientist to these seminar series also
-poses a problem for HURM and NCNH scientists. A large portion of the
-NCNH cohort in our sample are Asian/Asian American individuals. Although
-Asian scientists are well-represented in the US scientific workforce,
-they face significant bias and barriers to inclusion in society and
-academia (24, 25). Both men and women who identify as HURM and Asian
-reported having to work harder than white men to be perceived as
-legitimate scholars (26). This expectation of higher productivity may
-result in fewer HURM and NCNH individuals being invited as seminar
-speakers. This is particularly striking in the low number of NCNH
-individuals in the more prestigious lectureships of our sample despite
-the higher employment rate of Asian scientists.
+Departments have different processes and criteria for selecting invited
+speakers, but it is a matter of pride to bring the best scientists
+possible. It may be that the definition of ``best'' poses a problem to
+women, who need three-times as many publications as their men colleges
+to be considered equally competent (24), and those that identify as HURM
+and Asian, who report having to work harder than white men to be
+perceived as legitimate scholars (25). Some departments only invite
+tenured faculty, which severely limits the number of potential speakers
+who are white women or non-Caucasian. Yet, another scenario is that
+pre-tenure faculty members invite prestigious, tenured faculty in their
+field to network and secure letters for their own tenure package. The
+increased burden of white women and non-Caucasian scientists to prove
+competency decreases their likelihood to be considered for either tenure
+or as possible source of tenure letters.
+
+Each underrepresented group in our cohort faces a complex set of
+barriers to achieving faculty status. For instance, the decision to
+invite a woman may also be negatively impacted by assumptions about
+competency and dedication. The dedication of women who have children to
+their work is perceived to be less than that of their colleagues, i.e.,
+men who also have children (26--28). The perceived prioritization and
+commitments of women to family over work may cause faculty to doubt
+their acceptance of a speaking invitation, despite the prestigious
+nature of these invitations and evidence that men and women accept at
+similar rates ({\textbf{???}}, 23). As a result, the faculty member
+invites a different colleague who they feel is more likely to agree (and
+is a man). Another large portion of our sample were the NCNH cohort, who
+are predominately Asian/Asian American individuals. Although Asian
+scientists are well-represented in the US scientific workforce, they
+face significant bias and barriers to inclusion in society and academia
+(29, 30). For instance, despite the higher employment rate of Asian
+scientists, they were not well-represented in the more prestigious
+lectureships.
 
@@
 varying rates of hiring and tenure promotion mean unique considerations
-are important for inclusion of each group
-(\url{doi:10.1001/jama.284.9.1085}). For instance, the proportion of
-HURM faculty at the Assistant and Associate Professor level is currently
-higher than the Full Professor level so it will be difficult to increase
-speaker diversity if early-career researchers are not being considered
-(27). Increased performance expectations and patterns of exclusions are
-consistent themes in studies characterizing the HURM faculty experience
-(28, 29). Therefore, inclusion of HURM faculty in seminar series is
-likely essential to increasing the number of HURM Associate and Full
-Professors. More significantly, a major barrier to inclusion of HURM
-faculty at similar proportions to HURM trainees is the low transition
-rate of scientists from HURM backgrounds to faculty positions and the
-associated low proportion of HURM faculty (30). Even when HURM speaker
-rates match the proportion of HURM faculty employment, HURM trainees
-will be represented at a significantly higher proportion. Inclusion of
-HURM faculty in these seminarseries is just one aspect of larger
-institutional change that is needed (31).
-
-We have not been able to identify any other publications examining
-scientific speaker diversity beyond gender. This seems to be the first.
-This is concerning since conclusions drawn from gender-based studies are
-often framed, and considered, to be applicable to other marginalized
-groups (e.g., HURM). This is a flawed assumption. While there is no
-doubt some overlap, each group remains marginalized due to a unique
-complex set of factors that cannot always be solved by gender-based
-solutions. US-serving institutions, such as the University of Michigan
-have a particular responsibility to the historically suppressed
-populations included in our definition of HURMs. We therefore implore US
-institutions to apply this framing to their discussions and research.
-
-According to social role theory, this department is not adequietly
-serving their non-Caucasian trainees. Implict biases that affect
-perceptions of marginalized groups are the primary issue, but we must
-acknowledge that it is not always possible to identify members of
-historically under-served communities. For instance, after data
-analysis, we learned that at least one speaker in our data set should
-have been categorized as a HURM instead of Caucasian, but it wasn't
-readily apparent from their internet presence or CV. This limitation
-makes two important points: that percieved identity often plays a larger
-role than self-identification, and that we need better tools to identify
-members of marginalized groups.
+are important for inclusion of each group (31). For instance, a major
+barrier to inclusion of HURM faculty at similar proportions to HURM
+trainees is the low transition rate of scientists from HURM backgrounds
+to faculty positions and the associated low proportion of HURM faculty
+(32). The proportion of HURM faculty at the Assistant and Associate
+Professor level is currently higher than at Full Professor so it will be
+difficult to increase speaker diversity if early-career researchers are
+not being considered (33). Increased performance expectations and
+patterns of exclusions are consistent themes in studies characterizing
+the HURM faculty experience (34, 35). Therefore, inclusion of HURM
+faculty in seminar series is likely essential to increasing the number
+of HURM Associate and Full Professors. Even when HURM speaker rates
+match the proportion of HURM faculty employment, HURM trainees will be
+represented at a significantly higher proportion. Inclusion of HURM
+faculty in these seminarseries is just one aspect of larger
+institutional change that is needed (36).
 
@@
 switching from PI invited to lab invited in an attempt to allow trainees
-to choose a speaker that best represented themselves. In addition to
-this we also created resources which allowed scientists to self-identify
-and provide host faculty with more diverse choices.
+to choose a speaker that best represented themselves.
+
+Implict biases that affect perceptions of marginalized groups are the
+primary issue, but we must acknowledge that it is not always possible to
+identify members of historically under-served communities. For instance,
+after data analysis, we learned that at least one speaker in our data
+set should have been categorized as a HURM instead of Caucasian, but it
+wasn't readily apparent from their internet presence or CV. This
+limitation makes two important points: that percieved identity often
+plays a larger role than self-identification, and that we need better
+tools to identify members of marginalized groups. So in addition to our
+policy change, we also created resources that allow scientists to
+self-identify and provide host faculty with more diverse choices.
 
@@
 built these as a tool for use by other fields and organizations to
-create their own lists. Importantly, since these lists are compiled by
+create their own lists. Since these lists are compiled by
 self-nomination, we can ensure that only scientists comfortable
@@
 screened before being added to the public database. This screening
-currently includes two steps: 1. Confirming that each person is listed
-in the database only once. 2. Verifying that the submitted website is a
-professional website for the person being listed. If a person has not
-been listed in the database previously and passes step 2, a new entry is
-added to the public database spreadsheet. If a person is already listed
-in the database, their information is updated to the most recent
-submission.
+includes two steps: confirming that each person is listed in the
+database only once and that any submitted website is a personal,
+professional website. If both criteria are met, a new entry is added to
+the public database spreadsheet. If a person is already listed in the
+database, their information is updated to the most recent submission.
 
 This public spreadsheet is embedded in the website and can be open
-separately as a locked (uneditable) Google Sheet. Importantly, this
-allows the list to be easily searched. We have chosen to list
-individuals' academic information first in the spreadsheet to encourage
-a focus on academic achievement rather than tokenization of marginalized
-identities. Currently the database lists individuals in order of
-self-nomination but future versions will be re-sorted based on name
-and/or academic field to varying the individuals who may receive more
-attention for simply being at the top of the list.
+separately as a locked (uneditable) Google Sheet, allowing the list to
+be easily searched. We have chosen to list individuals' academic
+information first in the spreadsheet to encourage a focus on academic
+achievement rather than tokenization of marginalized identities.
+Currently the database lists individuals in order of self-nomination but
+future versions will be re-sorted based on name and/or academic field to
+varying the individuals who may receive more attention for simply being
+at the top of the list.
 
@@
 content and the description of their maintenance. J.L. wrote the
-introduction and provided conceptual advice. All authors contributed to
-preparing the final manuscript.
+introduction and provided conceptual advice. A.K.H. and J.L facilited
+the policy change to the UM Department of Microbiology and Immunology.
+All authors contributed to preparing the final manuscript.
 
@@
 \url{https://github.com/diversifymicrobiology/DiversifyMicrobiology.github.io/}.
-
-\begin{figure}
-\centering
-\includegraphics{Figure_1.png}
-\caption{\textbf{The demographics of invited speakers, hosting faculty,
-and trainees.} A) The proportion of women in each academic role. B) The
-proportion of each academic role represented by individuals that are
-Caucasian (left), Historically Underrepresented Minorities (HURM,
-center) or International (right). C-D)The percent of lectureships
-awarded to individuals that are C) Caucasian, HURM, International or D)
-Caucasian or Non-Caucasian by gender.}
-\end{figure}
 
@@
 \end{center}
+
+\begin{figure}
+\centering
+\includegraphics{Figure_1.png}
+\caption{\textbf{The demographics of invited speakers, hosting faculty,
+and trainees.} A) The proportion of women in each academic role. B) The
+proportion of each academic role represented by individuals that are
+Caucasian (left), Historically Underrepresented Minorities (HURM,
+center) or International (right). C-D)The percent of lectureships
+awarded to individuals that are C) Caucasian, HURM, International or D)
+Caucasian or Non-Caucasian by gender.}
+\end{figure}
 
@@
 
+\hypertarget{ref-BlairLoy2017}{}
+24. \textbf{Blair-Loy M}, \textbf{Rogers L}, \textbf{Glaser D},
+\textbf{Wong Y}, \textbf{Abraham D}, \textbf{Cosman P}. 2017. Gender in
+engineering departments: Are there gender differences in interruptions
+of academic job talks? Social Sciences \textbf{6}:29.
+doi:\href{https://doi.org/10.3390/socsci6010029}{10.3390/socsci6010029}.
+
+\hypertarget{ref-noauthor_seeking_2013}{}
+25. 2013. Seeking Solutions: Maximizing American Talent by Advancing
+Women of Color in Academia: Summary of a Conference. National Academies
+Press, Washington, D.C.
+
+\hypertarget{ref-Firth1982}{}
+26. \textbf{Firth M}. 1982. Sex discrimination in job opportunities for
+women. Sex Roles \textbf{8}:891--901.
+doi:\href{https://doi.org/10.1007/bf00287858}{10.1007/bf00287858}.
+
+\hypertarget{ref-Correll2007}{}
+27. \textbf{Correll SJ}, \textbf{Benard S}, \textbf{Paik I}. 2007.
+Getting a job: Is there a motherhood penalty? American Journal of
+Sociology \textbf{112}:1297--1339.
+doi:\href{https://doi.org/10.1086/511799}{10.1086/511799}.
+
+\hypertarget{ref-Fuegen2004}{}
+28. \textbf{Fuegen K}, \textbf{Biernat M}, \textbf{Haines E},
+\textbf{Deaux K}. 2004. Mothers and fathers in the workplace: How gender
+and parental status influence judgments of job-related competence.
+Journal of Social Issues \textbf{60}:737--754.
+doi:\href{https://doi.org/10.1111/j.0022-4537.2004.00383.x}{10.1111/j.0022-4537.2004.00383.x}.
+
 \hypertarget{ref-Hwang2008}{}
-24. \textbf{Hwang W-C}, \textbf{Goto S}. 2008. The impact of perceived
+29. \textbf{Hwang W-C}, \textbf{Goto S}. 2008. The impact of perceived
 racial discrimination on the mental health of asian american and latino
@@
 \hypertarget{ref-Tran2019}{}
-25. \textbf{Tran VC}, \textbf{Lee J}, \textbf{Huang TJ}. 2019.
+30. \textbf{Tran VC}, \textbf{Lee J}, \textbf{Huang TJ}. 2019.
 Revisiting the asian second-generation advantage. Ethnic and Racial
@@
 
-\hypertarget{ref-noauthor_seeking_2013}{}
-26. 2013. Seeking Solutions: Maximizing American Talent by Advancing
-Women of Color in Academia: Summary of a Conference. National Academies
-Press, Washington, D.C.
+\hypertarget{ref-Fang2000}{}
+31. \textbf{Fang D}. 2000. Racial and ethnic disparities in faculty
+promotion in academic medicine. JAMA \textbf{284}:1085.
+doi:\href{https://doi.org/10.1001/jama.284.9.1085}{10.1001/jama.284.9.1085}.
+
+\hypertarget{ref-Gibbs2016}{}
+32. \textbf{Gibbs KD}, \textbf{Basson J}, \textbf{Xierali IM},
+\textbf{Broniatowski DA}. 2016. Decoupling of the minority PhD talent
+pool and assistant professor hiring in medical school basic science
+departments in the US. eLife \textbf{5}.
+doi:\href{https://doi.org/10.7554/elife.21393}{10.7554/elife.21393}.
 
 \hypertarget{ref-whittaker_retention_2015}{}
-27. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
+33. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
 Acosta VG}. 2015. Retention of Underrepresented Minority Faculty:
@@
 \hypertarget{ref-pololi_race_2010}{}
-28. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
+34. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
 Disadvantage and Faculty Experiences in Academic Medicine. Journal of
@@
 \hypertarget{ref-hassouneh_experiences_2014}{}
-29. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
+35. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
 \textbf{Junkins EP}, \textbf{Horton LL}. 2014. The experiences of
@@
 
-\hypertarget{ref-Gibbs2016}{}
-30. \textbf{Gibbs KD}, \textbf{Basson J}, \textbf{Xierali IM},
-\textbf{Broniatowski DA}. 2016. Decoupling of the minority PhD talent
-pool and assistant professor hiring in medical school basic science
-departments in the US. eLife \textbf{5}.
-doi:\href{https://doi.org/10.7554/elife.21393}{10.7554/elife.21393}.
-
 \hypertarget{ref-johnson_msphere_2019}{}
-31. \textbf{Johnson MDL}. 2019. mSphere of Influence: Hiring of
+36. \textbf{Johnson MDL}. 2019. mSphere of Influence: Hiring of
 Underrepresented Minority Assistant Professors in Medical School Basic

### 2019-09-26 code/get_plot_options.R
update legends

@@ -4,7 +4,7 @@ library(cowplot)
 #library(patchwork)
 
 #settings----
-dat_levels <- c("Student", "Postdoc", "Host Faculty", "Speaker")
+dat_levels <- c("Graduate Student", "Postdoctoral Fellow", "Host Faculty", "Invited Speaker")
 
 dat_linetype <- c("solid", "dashed", "dotted")
 

### 2019-09-26 code/lectureship_div.R

@@ -16,7 +16,7 @@ lectureship_demo_plot <- lectureship %>%
   facet_grid(~demographic)+
   scale_y_continuous(labels = multiply, limits = c(0, 1))+
   #geom_text(aes(y = ((..count..)/sum(..count..)), label = ..count..), stat = "count", vjust = -0.25)+
-  labs(y = "Lectureships (%)", x = "Speaker Demographics")+
+  labs(y = "Lectureships (%)", x = "Invited Speaker Demographics")+
   scale_fill_manual(values = "grey17")+
   my_theme_horiz+
   theme(axis.text.x=element_blank(),
@@ -29,7 +29,7 @@ lectureship_gend_plot <- lectureship %>%
                fill = Speaker_Gender), position = "dodge")+
   facet_grid(~demographic)+
   scale_y_continuous(labels = multiply, limits = c(0, 1))+
-  labs(y = "\nLectureships (%)", x = "Speaker Gender")+
+  labs(y = "\nLectureships (%)", x = "Invited Speaker Gender")+
   scale_fill_manual(values = c("grey17", "dark gray"))+
   my_theme_horiz
 

### 2019-09-26 submission/manuscript.Rmd
update discussion and abstract

@@
 ---
-title: '**Department Invited Speakers Do Not Reflect Trainee Diversity**'
+title: '**Policy should change to improve invited speaker diversity and retain trainees**'
 csl: mbio.csl
@@
 
-Running title: Invited Speaker Diversity Does Not Reflect Trainee Diversity
+Running title: Suggestions to improve invited speaker diversity
 
@@
 
-Ada K. Hagan, Ph.D.${^1\dagger}$, Rebecca M. Pollet, Ph.D.${^1}$, and Josie Libertucci, Ph.D.${^2\dagger}$
+Ada K. Hagan, Ph.D.${^1\dagger}$, Rebecca M. Pollet, Ph.D.${^1}$, and Josie Libertucci, Ph.D.${^2}$
 
@@
 
-$\dagger$ To whom correspondence should be addressed: akhagan@umich.edu or libertj@mcmaster.ca
+$\dagger$ To whom correspondence should be addressed: akhagan@umich.edu
 
@@
 
-2\. Department of Medicine, McMaster University, Hamilton, Ontario, Canada
+2\. Farncombe Family Digestive Health Research Institute, Department of Medicine, McMaster University, Hamilton, Ontario, Canada
 
@@
 Tables: 1
+
+Financial support: Department of Microbiology & Immunology, University of Michigan
 
@@
 
-Social role theory emphasizes the importance of "like" representation to improve feelings of self-efficacy and belonging.
-This is an issue for trainees in the biological sciences who are either white women or underrepresented minorities, since there is a lack of faculty who look like them in biology academic settings.
-One way to improve representation is through invited speaker series.
-In this persepective, we compare the diversity of invited speakers at one microbiology and immunology department to the diversity of their post-Baccalaurate trainees.
-We find that trainees are not proportionally represented by the invited speakers and provide policy suggestions and tools to address this issue.
+The biological sciences have a problem retaining white women and underrepresented minorities in academia.
+Despite increases in the representation of these groups in faculty candidate pools, they are still underrepresented at the faculty level, particularly at the Full professor level.
+Faculty are often invited to departments at other universities to present on their research, a highly valued offer that provides an opportunity for collaborations and networking.
+This is also an opportunity for trainees to interact with additional faculty from underrepresented groups.
+In this manuscript, we compare invited-speaker demographics to the current trainee demographics and find that trainees are not proportionally represented by speakers invited to the department.
+Our investigation prompted changes in policy for how invited speakers are selected in the future to invite a more diverse group of scientists.
+To facilitate this process, we developed a set of tips and a web-based resource that allows scientists, committees, and moderators to identify members of under-served groups.
+These resources can be easily adapted by other fields or sub-fields to promote inclusion and diversity at seminar series’, conferences, and colloquia.
 
@@
 
-Long-standing systemic bias, sexism, and racism have contributed to the underrepresentation of many racial and ethnic groups, as well as women, in science, technology, engineering, and math (STEM) fields (NIH 2015 report, Measuring DEI 2016, [@colloquy_2012]).
+**waiting for updated version**
+
+Long-standing systemic bias, sexism, and racism have contributed to the under-representation of many racial and ethnic groups, as well as women, in science, technology, engineering, and math (STEM) fields (NIH 2015 report, Measuring DEI 2016, [@colloquy_2012]).
 Organization climate and culture that supports inclusion of all individuals is essential to support the retention of historically underrepresented minorities (HURM) in the U.S., as well as non-Caucasian individuals, and women in STEM fields (Schneider, 2013).
@@
 The presenting gender of each individual was assigned using a binary system (man/woman).
-Due to the low number of individuals in the study, race/ethnicity demographics were split in three groups: Caucasian, Historically Under-represented Minority (HURM), and Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibilty.
+Due to the low number of individuals in the study, race/ethnicity demographics were split in three groups: Caucasian, Historically Under-represented Minority (HURM), and Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibility.
 Caucasian was assigned using the current U.S.
 Census definition where those of Middle Eastern, European, and Russian descent are included.
-HURM individuals were restricted to those with African-American, Indigenous, Alaskan/Hawaian Native, Latinx and/or Hispanic heritage.
+HURM individuals were restricted to those with African-American, Indigenous, Alaskan/Hawaiian Native, Latinx and/or Hispanic heritage.
 All others were placed into the NCNH group.
@@
 
-Data were analyzed and figures generated in R Statisical Software, using relevant packages [@R_software_2017; @wickham_tidyverse_2017; @cowplot; @markdown; @rmd_book; @rmd_rstudio; @knitr_2014; @knitr_2018; @lubridate; @readxl; @pdftools; @wickham_scales_2018; @neuwirth_rcolorbrewer_2014].
+Data were analyzed and figures generated in R Statistical Software, using relevant packages [@R_software_2017; @wickham_tidyverse_2017; @cowplot; @markdown; @rmd_book; @rmd_rstudio; @knitr_2014; @knitr_2018; @lubridate; @readxl; @pdftools; @wickham_scales_2018; @neuwirth_rcolorbrewer_2014].
 
@@
 Of `r sum(lect_summary$n)` lectureships over the five year period, `r lect_summary[4,4]`% were awarded to women.
-The proportion of women as faculty hosts and speakers is equivalent to global estimates that 40% of microbiologists are women, with a slightly lower representation of women in lectureships [@allagnat_gender_2017].
 
@@
 However, only 8.5% of invited speakers, and none of the hosting faculty, were HURM scientists.
-NCNH trainees were 34% of department students and postdocs (22% of microbiology and immunology doctorates in 2017), but only 19% of hosting faculty and 10.5% of invited speakers [@nsf_survey_2017].
+NCNH trainees were 34% of department students and postdoc (22% of microbiology and immunology doctorates in 2017), but only 19% of hosting faculty and 10.5% of invited speakers [@nsf_survey_2017].
 
-The more prestigous invited speaker lectureships were also dominated by Caucasian scientists, who comprised `r get_percent(sum(cauc_lect$sum), sum(lect_summary$n))`% of those awarded (Fig.
+The more prestigious invited speaker lectureships were also dominated by Caucasian scientists, who comprised `r get_percent(sum(cauc_lect$sum), sum(lect_summary$n))`% of those awarded (Fig.
 1C).
@@
 
-[Add paragraph summarizing findings ] According to social role theory, this department is not adequately serving their non-Caucasian trainees.
+In our study population, the proportion of women as faculty hosts and speakers is equivalent to global estimates that 40% of microbiologists are women, with a slightly lower representation of women in lectureships [@allagnat_gender_2017].
+In that regard, women are over-represented as graduate students and postdoctoral fellows in the department.
+Caucasian scientists are over-represented as host faculty and invited speakers, compared to their presence as trainees, particularly when lectureships were considered.
+Conversely, the proportion of HURM and NCNH invited speakers were under-representative of the trainee populations for each group.
+Thus, according to social role theory, this department is not adequately serving their non-Caucasian trainees.
 
@@
 We have not been able to identify any other publications examining scientific speaker diversity beyond gender.
-This seems to be the first.
-This is concerning since conclusions drawn from gender-based studies are often framed, and considered, to be applicable to other marginalized groups (e.g., HURM).
+This seems to be the first, which is concerning since conclusions drawn from gender-based studies are often framed, and considered, to be applicable to other marginalized groups (e.g., HURM).
 This is a flawed assumption.
@@
 Even when HURM speaker rates match the proportion of HURM faculty employment, HURM trainees will be represented at a significantly higher proportion.
-Inclusion of HURM faculty in these seminarseries is just one aspect of larger institutional change that is needed [@johnson_msphere_2019].
+Inclusion of HURM faculty in these seminar series is just one aspect of larger institutional change that is needed [@johnson_msphere_2019].
 
-## Instituting policy change within the Department of Microbiology and Immunology
+## Instituting Policy Change
 
-In an attempt to promote inclusion within the Dept.
-M&I these data were presented to faculty members and the dept chair (Harry Mobley).
-Since, trainee demographics were not represented within seminar speaker demographics over the past 5 years, we proposed a policy change as to how seminar speakers were being invited.
-This policy change included switching from PI invited to lab invited in an attempt to allow trainees to choose a speaker that best represented themselves.
+In an attempt to promote inclusion within the Department of Microbiology and Immunology at the University of Michigan, these data were presented to faculty members and the department chair (Dr.
+Mobley).
+Since trainee demographics were not represented within seminar speaker demographics over the past five years, we proposed a policy change as to how seminar speakers were being invited.
+One suggestion was to switch from faculty-invited to lab-invited speakers in an attempt to allow trainees to choose a speaker that best represented themselves (Table 1).
 
-Implict biases that affect perceptions of marginalized groups are the primary issue, but we must acknowledge that it is not always possible to identify members of historically under-served communities.
+The implicit biases that affect perceptions of marginalized groups are an issue, but we must acknowledge that it is not always possible to identify members of historically under-served communities.
 For instance, after data analysis, we learned that at least one speaker in our data set should have been categorized as a HURM instead of Caucasian, but it wasn't readily apparent from their internet presence or CV.
-This limitation makes two important points: that percieved identity often plays a larger role than self-identification, and that we need better tools to identify members of marginalized groups.
-So in addition to our policy change, we also created resources that allow scientists to self-identify and provide host faculty with more diverse choices.
+This limitation makes two important points: that perceived identity often plays a larger role than self-identification, and that we need better tools to identify members of marginalized groups.
+Another policy suggestion is for departments to invite their speakers to spend a time discussing their personal journeys through science, in addition to their scientific stories (Table 1).
+This would enable those who wish, feel welcomed to discuss how their identity(ies) interacted with their careers.
+In addition to these suggestions for policy change, we have created resources that allow scientists to self-identify as under-served groups and thus provide host faculty with more diverse choices (Table 1).
 
@@
 
-To help address this issue, we make some suggestions (Table 1) and have developed a resource to identify scientists who are members of marginalized and/or historically under-served groups.
-Motivated by a lack of such resources and inspired by similar resources--DiversifyEEB and DiversifyChemistry--we created DiversifyMicrobiology and DiversifyImmunology.
-These resources are a tool for symposium organziers, award committees, search committees and other scientists to identify individuals to diversify their pools.
-Additionally, we have built these as a tool for use by other fields and organizations to create their own lists.
+Motivated by a lack of resources to identify scientists who are members of marginalized and/or historically under-served groups, and inspired by resources in other fields--DiversifyEEB and DiversifyChemistry--we created DiversifyMicrobiology and DiversifyImmunology.
+These resources are a tool for symposium organizers, award committees, search committees, and other scientists to identify individuals to diversify their pools.
+Additionally, we have built these as a template to be used as a tool for other fields and organizations that wish to create their own lists.
 Since these lists are compiled by self-nomination, we can ensure that only scientists comfortable revealing their marginalized identities are included.
@@
 Importantly, our website creation tool is hosted for free by GitHub, which provides a free website for each GitHub organization.
-Basic tools and skills required to set up a Diversify site include knowledge of, or experience with, the version control tool git, the webtool GitHub, and a text editor.
+Basic tools and skills required to set up a Diversify site include knowledge of, or experience with, the version control tool git, the web-tool GitHub, and a text editor.
 A tutorial in the DiversifyMicrobiology repository on GitHub provides links to these resources and instructions for adapting the tool to your own field.
@@
 
-To increase the retention of white women and HURMS in STEM, they must also be represented as experts.
+To increase the retention of white women and HURM trainees in the biological sciences, they must also be represented as experts.
 However, the invited speaker diversity at one department does not represent the diversity of trainees.
-There is a lack of research on invited speakers examining factors other than gender.
-To facilite the identification and recruitment of individuals in these historically under-served groups, we have built a tool to create self-nominated, field-specific lists.
+To facilitate the identification and recruitment of individuals in these historically under-served groups, we have built a tool to create self-nominated, field-specific lists.
 
@@
 Beth Moore and Harry Mobley and the Department of Microbiology & Immunology, University of Michigan for their input and financial support that enabled publication of our manuscript.
-We would also like to acknowledge Nick Lesniak and Dr.
+We thank Bonnie Krey and former speaker series coordinators Drs.
+Nicole Koropatkin and Kathy Spindler for access to invited speaker data.
+We would also like to acknowledge and thank Nick Lesniak and Dr.
 Ariangela Kozick for their comments and suggestions.
@@
 A.K.H.
-collected the data, assigned demographics, analyzed the data, and created the website.
+collected the data, assigned demographics, analyzed the data, created the website, and wrote the methods and results.
 R.M.P.
@@
 A.K.H.
-and J.L facilited the policy change to the UM Department of Microbiology and Immunology.
+and J.L facilitated the policy change to the UM Department of Microbiology and Immunology.
 All authors contributed to preparing the final manuscript.
@@
 
-Use a list & \makecell[l]{Many lists of scientists from \\under-represented and underserved \\groups are available} &  \makecell[l]{https://DiversifyMicrobiology.\\github.io/resources}\\ \hline
+Use a list & \makecell[l]{Many lists of scientists from \\under-represented and under-served \\groups are available} &  \makecell[l]{https://DiversifyMicrobiology.\\github.io/resources}\\ \hline
 
@@
 ![**The demographics of invited speakers, hosting faculty, and trainees.** A) The proportion of women in each academic role.
-B) The proportion of each academic role represented by individuals that are Caucasian (left), Historically Underrepresented Minorities (HURM, center) or International (right).
-C-D)The percent of lectureships awarded to individuals that are C) Caucasian, HURM, International or D) Caucasian or Non-Caucasian by gender.](Figure_1.png)
+B) The proportion of each academic role represented by individuals that are Caucasian (left), Historically Underrepresented Minorities (HURM, center) or Non-Caucasian/Non-HURM (NCNH, right).
+C-D)The percent of lectureships awarded to individuals that are C) Caucasian, HURM, or NCNH and D) Caucasian, HURM, or NCNH by gender.](Figure_1.png)
 

### 2019-09-26 submission/manuscript.tex
update discussion and abstract

@@
 \hypersetup{unicode=true,
-            pdftitle={Department Invited Speakers Do Not Reflect Trainee Diversity},
+            pdftitle={Policy should change to improve invited speaker diversity and retain trainees},
             pdfborder={0 0 0},
@@
 
-  \title{\textbf{Department Invited Speakers Do Not Reflect Trainee Diversity}}
+  \title{\textbf{Policy should change to improve invited speaker diversity and
+retain trainees}}
     \pretitle{\vspace{\droptitle}\centering\huge}
@@
 
-Running title: Invited Speaker Diversity Does Not Reflect Trainee
-Diversity
+Running title: Suggestions to improve invited speaker diversity
 
@@
 Ada K. Hagan, Ph.D.\({^1\dagger}\), Rebecca M. Pollet, Ph.D.\({^1}\),
-and Josie Libertucci, Ph.D.\({^2\dagger}\)
+and Josie Libertucci, Ph.D.\({^2}\)
 
@@
 \(\dagger\) To whom correspondence should be addressed:
-\href{mailto:akhagan@umich.edu}{\nolinkurl{akhagan@umich.edu}} or
-\href{mailto:libertj@mcmaster.ca}{\nolinkurl{libertj@mcmaster.ca}}
+\href{mailto:akhagan@umich.edu}{\nolinkurl{akhagan@umich.edu}}
 
@@
 
-2. Department of Medicine, McMaster University, Hamilton, Ontario,
-Canada
+2. Farncombe Family Digestive Health Research Institute, Department of
+Medicine, McMaster University, Hamilton, Ontario, Canada
 
@@
 Tables: 1
+
+Financial support: Department of Microbiology \& Immunology, University
+of Michigan
 
@@
 
-Social role theory emphasizes the importance of ``like'' representation
-to improve feelings of self-efficacy and belonging. This is an issue for
-trainees in the biological sciences who are either white women or
-underrepresented minorities, since there is a lack of faculty who look
-like them in biology academic settings. One way to improve
-representation is through invited speaker series. In this persepective,
-we compare the diversity of invited speakers at one microbiology and
-immunology department to the diversity of their post-Baccalaurate
-trainees. We find that trainees are not proportionally represented by
-the invited speakers and provide policy suggestions and tools to address
-this issue.
+The biological sciences have a problem retaining white women and
+underrepresented minorities in academia. Despite increases in the
+representation of these groups in faculty candidate pools, they are
+still underrepresented at the faculty level, particularly at the Full
+professor level. Faculty are often invited to departments at other
+universities to present on their research, a highly valued offer that
+provides an opportunity for collaborations and networking. This is also
+an opportunity for trainees to interact with additional faculty from
+underrepresented groups. In this manuscript, we compare invited-speaker
+demographics to the current trainee demographics and find that trainees
+are not proportionally represented by speakers invited to the
+department. Our investigation prompted changes in policy for how invited
+speakers are selected in the future to invite a more diverse group of
+scientists. To facilitate this process, we developed a set of tips and a
+web-based resource that allows scientists, committees, and moderators to
+identify members of under-served groups. These resources can be easily
+adapted by other fields or sub-fields to promote inclusion and diversity
+at seminar series', conferences, and colloquia.
 
@@
 Long-standing systemic bias, sexism, and racism have contributed to the
-underrepresentation of many racial and ethnic groups, as well as women,
+under-representation of many racial and ethnic groups, as well as women,
 in science, technology, engineering, and math (STEM) fields (NIH 2015
@@
 Historically Under-represented Minority (HURM), and
-Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibilty.
+Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibility.
 Caucasian was assigned using the current U.S. Census definition where
@@
 HURM individuals were restricted to those with African-American,
-Indigenous, Alaskan/Hawaian Native, Latinx and/or Hispanic heritage. All
-others were placed into the NCNH group. We recognize that our proxy
+Indigenous, Alaskan/Hawaiian Native, Latinx and/or Hispanic heritage.
+All others were placed into the NCNH group. We recognize that our proxy
 demographics are a limitation of the analysis and want to acknowledge
@@
 
-Data were analyzed and figures generated in R Statisical Software, using
-relevant packages (8--20).
+Data were analyzed and figures generated in R Statistical Software,
+using relevant packages (8--20).
 
@@
 lectureships over the five year period, 37.04\% were awarded to women.
-The proportion of women as faculty hosts and speakers is equivalent to
-global estimates that 40\% of microbiologists are women, with a slightly
-lower representation of women in lectureships (21).
 
@@
 of the department, on track with the 11\% of microbiology and immunology
-doctorates awarded in 2017 (22). However, only 8.5\% of invited
+doctorates awarded in 2017 (21). However, only 8.5\% of invited
 speakers, and none of the hosting faculty, were HURM scientists. NCNH
-trainees were 34\% of department students and postdocs (22\% of
+trainees were 34\% of department students and postdoc (22\% of
 microbiology and immunology doctorates in 2017), but only 19\% of
-hosting faculty and 10.5\% of invited speakers (22).
+hosting faculty and 10.5\% of invited speakers (21).
 
-The more prestigous invited speaker lectureships were also dominated by
+The more prestigious invited speaker lectureships were also dominated by
 Caucasian scientists, who comprised 81.48\% of those awarded (Fig. 1C).
@@
 
-{[}Add paragraph summarizing findings {]} According to social role
-theory, this department is not adequately serving their non-Caucasian
-trainees.
+In our study population, the proportion of women as faculty hosts and
+speakers is equivalent to global estimates that 40\% of microbiologists
+are women, with a slightly lower representation of women in lectureships
+(22). In that regard, women are over-represented as graduate students
+and postdoctoral fellows in the department. Caucasian scientists are
+over-represented as host faculty and invited speakers, compared to their
+presence as trainees, particularly when lectureships were considered.
+Conversely, the proportion of HURM and NCNH invited speakers were
+under-representative of the trainee populations for each group. Thus,
+according to social role theory, this department is not adequately
+serving their non-Caucasian trainees.
 
@@
 to identify any other publications examining scientific speaker
-diversity beyond gender. This seems to be the first. This is concerning
+diversity beyond gender. This seems to be the first, which is concerning
 since conclusions drawn from gender-based studies are often framed, and
@@
 represented at a significantly higher proportion. Inclusion of HURM
-faculty in these seminarseries is just one aspect of larger
+faculty in these seminar series is just one aspect of larger
 institutional change that is needed (36).
 
-\subsection{Instituting policy change within the Department of
-Microbiology and
-Immunology}\label{instituting-policy-change-within-the-department-of-microbiology-and-immunology}
+\subsection{Instituting Policy Change}\label{instituting-policy-change}
 
-In an attempt to promote inclusion within the Dept. M\&I these data were
-presented to faculty members and the dept chair (Harry Mobley). Since,
-trainee demographics were not represented within seminar speaker
-demographics over the past 5 years, we proposed a policy change as to
-how seminar speakers were being invited. This policy change included
-switching from PI invited to lab invited in an attempt to allow trainees
-to choose a speaker that best represented themselves.
+In an attempt to promote inclusion within the Department of Microbiology
+and Immunology at the University of Michigan, these data were presented
+to faculty members and the department chair (Dr.~Mobley). Since trainee
+demographics were not represented within seminar speaker demographics
+over the past five years, we proposed a policy change as to how seminar
+speakers were being invited. One suggestion was to switch from
+faculty-invited to lab-invited speakers in an attempt to allow trainees
+to choose a speaker that best represented themselves (Table 1).
 
-Implict biases that affect perceptions of marginalized groups are the
-primary issue, but we must acknowledge that it is not always possible to
+The implicit biases that affect perceptions of marginalized groups are
+an issue, but we must acknowledge that it is not always possible to
 identify members of historically under-served communities. For instance,
@@
 wasn't readily apparent from their internet presence or CV. This
-limitation makes two important points: that percieved identity often
+limitation makes two important points: that perceived identity often
 plays a larger role than self-identification, and that we need better
-tools to identify members of marginalized groups. So in addition to our
-policy change, we also created resources that allow scientists to
-self-identify and provide host faculty with more diverse choices.
+tools to identify members of marginalized groups. Another policy
+suggestion is for departments to invite their speakers to spend a time
+discussing their personal journeys through science, in addition to their
+scientific stories (Table 1). This would enable those who wish, feel
+welcomed to discuss how their identity(ies) interacted with their
+careers. In addition to these suggestions for policy change, we have
+created resources that allow scientists to self-identify as under-served
+groups and thus provide host faculty with more diverse choices (Table
+1).
 
@@
 
-To help address this issue, we make some suggestions (Table 1) and have
-developed a resource to identify scientists who are members of
-marginalized and/or historically under-served groups. Motivated by a
-lack of such resources and inspired by similar resources--DiversifyEEB
-and DiversifyChemistry--we created DiversifyMicrobiology and
-DiversifyImmunology. These resources are a tool for symposium
-organziers, award committees, search committees and other scientists to
-identify individuals to diversify their pools. Additionally, we have
-built these as a tool for use by other fields and organizations to
-create their own lists. Since these lists are compiled by
-self-nomination, we can ensure that only scientists comfortable
-revealing their marginalized identities are included.
+Motivated by a lack of resources to identify scientists who are members
+of marginalized and/or historically under-served groups, and inspired by
+resources in other fields--DiversifyEEB and DiversifyChemistry--we
+created DiversifyMicrobiology and DiversifyImmunology. These resources
+are a tool for symposium organizers, award committees, search
+committees, and other scientists to identify individuals to diversify
+their pools. Additionally, we have built these as a template to be used
+as a tool for other fields and organizations that wish to create their
+own lists. Since these lists are compiled by self-nomination, we can
+ensure that only scientists comfortable revealing their marginalized
+identities are included.
 
@@
 include knowledge of, or experience with, the version control tool git,
-the webtool GitHub, and a text editor. A tutorial in the
+the web-tool GitHub, and a text editor. A tutorial in the
 DiversifyMicrobiology repository on GitHub provides links to these
@@
 
-To increase the retention of white women and HURMS in STEM, they must
-also be represented as experts. However, the invited speaker diversity
-at one department does not represent the diversity of trainees. There is
-a lack of research on invited speakers examining factors other than
-gender. To facilite the identification and recruitment of individuals in
-these historically under-served groups, we have built a tool to create
-self-nominated, field-specific lists.
+To increase the retention of white women and HURM trainees in the
+biological sciences, they must also be represented as experts. However,
+the invited speaker diversity at one department does not represent the
+diversity of trainees. To facilitate the identification and recruitment
+of individuals in these historically under-served groups, we have built
+a tool to create self-nominated, field-specific lists.
 
@@
 Microbiology \& Immunology, University of Michigan for their input and
-financial support that enabled publication of our manuscript. We would
-also like to acknowledge Nick Lesniak and Dr.~Ariangela Kozick for their
-comments and suggestions.
+financial support that enabled publication of our manuscript. We thank
+Bonnie Krey and former speaker series coordinators Drs. Nicole
+Koropatkin and Kathy Spindler for access to invited speaker data. We
+would also like to acknowledge and thank Nick Lesniak and Dr.~Ariangela
+Kozick for their comments and suggestions.
 
@@
 content and the description of their maintenance. J.L. wrote the
-introduction and provided conceptual advice. A.K.H. and J.L facilited
+introduction and provided conceptual advice. A.K.H. and J.L facilitated
 the policy change to the UM Department of Microbiology and Immunology.
@@
 Caucasian (left), Historically Underrepresented Minorities (HURM,
-center) or International (right). C-D)The percent of lectureships
-awarded to individuals that are C) Caucasian, HURM, International or D)
-Caucasian or Non-Caucasian by gender.}
+center) or Non-Caucasian/Non-HURM (NCNH, right). C-D)The percent of
+lectureships awarded to individuals that are C) Caucasian, HURM, or NCNH
+and D) Caucasian, HURM, or NCNH by gender.}
 \end{figure}
@@
 
+\hypertarget{ref-nsf_survey_2017}{}
+21. \textbf{Science and Engineering Statistics NC for}. 2017. Survey of
+Doctorate Recipients, Survey Year 2017. National Science Foundation,
+Alexandria, VA.
+
 \hypertarget{ref-allagnat_gender_2017}{}
-21. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
+22. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
 HJ}, \textbf{Hanafi S}, \textbf{Herbert R}, \textbf{Huggett S},
 \textbf{Tobin S}. 2017. Gender in the global research landscape.
-
-\hypertarget{ref-nsf_survey_2017}{}
-22. \textbf{Science and Engineering Statistics NC for}. 2017. Survey of
-Doctorate Recipients, Survey Year 2017. National Science Foundation,
-Alexandria, VA.
 

### 2019-09-26 code/get_plot_options.R
revert legends

@@ -4,7 +4,7 @@ library(cowplot)
 #library(patchwork)
 
 #settings----
-dat_levels <- c("Graduate Student", "Postdoctoral Fellow", "Host Faculty", "Invited Speaker")
+dat_levels <- c("Student", "Postdoc", "Host Faculty", "Speaker")
 
 dat_linetype <- c("solid", "dashed", "dotted")
 

### 2019-09-27 submission/manuscript.Rmd
minor edits, prep for biorxiv submission

@@
 ---
-title: '**Policy should change to improve invited speaker diversity and retain trainees**'
+title: '**Policy should change to improve invited speaker diversity and reflect trainee diversity**'
 csl: mbio.csl
@@
 
-The biological sciences have a problem retaining white women and underrepresented minorities in academia.
-Despite increases in the representation of these groups in faculty candidate pools, they are still underrepresented at the faculty level, particularly at the Full professor level.
-Faculty are often invited to departments at other universities to present on their research, a highly valued offer that provides an opportunity for collaborations and networking.
-This is also an opportunity for trainees to interact with additional faculty from underrepresented groups.
-In this manuscript, we compare invited-speaker demographics to the current trainee demographics and find that trainees are not proportionally represented by speakers invited to the department.
+The biomedical sciences have a problem retaining white women and underrepresented minorities in academia.
+Despite increases in the representation of these groups in faculty candidate pools, they are still underrepresented at the faculty level, particularly at the Full Professor level.
+The lack of diverse individuals at the Full Professor level contributes to the attrition of women and under-represented minorities, as it confirms unconscious biases.
+The presence of unconscious biases contribute to feelings of not belonging by trainees and are amplified by visual representation of who is presented as the “top scientist in their field”.
+Top scientists are not only defined by the attainment of Full Professorships, but also through invited seminar series.
+Invitations for faculty to present their research at other university departments is highly valued offer that provides an opportunity for collaborations and networking.
+However, if invited speakers do not represent the demographics of current trainees, these visual representations of successful scientists may contribute to decreased attitudes of self-identification as a scientist, ultimately resulting in trainees leaving the field or the academy.
+In this study, we compare invited-speaker demographics to the current trainee demographics in one microbiology and immunology department and find that trainees are not proportionally represented by speakers invited to the department.
 Our investigation prompted changes in policy for how invited speakers are selected in the future to invite a more diverse group of scientists.
@@
 
-**waiting for updated version**
+Long-standing systemic bias, sexism, and racism have contributed to the under-representation of many racial and ethnic groups, as well as women, in science, technology, engineering, and math (STEM) fields [@Martinez2018; @AllenRamdial2014; @Fang2000; @Gibbs2014].
+Specifically, within the field of biomedical research in the United States, the proportion of underrepresented minorities at the full professor level has remained consistently low at 4% (survey data taken from the NIH from 2001 to 2013), compared to the U.S.
+population, which is 32.3% [@Meyers2018;@nsf_2014].
+Similar discrepancies exist for women in biomedical sciences as full professorships are currently held mostly by men [@Jena2015; @Rotbart2012].
+As demographics of faculty within the biomedical sciences remains skewed towards Caucasian men, the demographics of trainees (graduate students and postdocs) are becoming more diverse [@Meyers2018].
 
-Long-standing systemic bias, sexism, and racism have contributed to the under-representation of many racial and ethnic groups, as well as women, in science, technology, engineering, and math (STEM) fields (NIH 2015 report, Measuring DEI 2016, [@colloquy_2012]).
-Organization climate and culture that supports inclusion of all individuals is essential to support the retention of historically underrepresented minorities (HURM) in the U.S., as well as non-Caucasian individuals, and women in STEM fields (Schneider, 2013).
-Inclusive organization culture will not suffice in retaining HURM, non-Caucasian individuals, and women without organization policy changes that support their values and goals [@Coe2019].
+Policy changes are needed to support inclusion of all individuals, particularly in the biomedical sciences[@Coe2019].
+To increase retention of historically under-represented minorities (HURM), non-Caucasian/non-HURM (NCNH) individuals, and white women in biomedical fields, it is important for trainees to have visual representations of themselves as scientists.
+The importance of representation in retaining a diverse group of individuals in STEM fields is supported by social role theory [@Eagly1984].
+Individuals make inferences about characteristics that are needed to be successful in a given role by examining individuals that most occupy that role [@Eagly1984; @Carter2018].
+However, there is a lack of diverse scientific experts in academia so underrepresented minorities are not seeing adequate visual representations of themselves at the faculty level.
+Therefore, trainees who do not see representation of themselves in senior faculty positions, may decide that they do not possess the characteristics that are required to succeed.
 
-A long-standing issue within STEM fields, specifically within academia, has been a lack of diverse representation of scientists for trainees (graduate students and postdoctoral fellows).
-In order to maintain retention of HURM, non-Caucasian individuals, and women in STEM fields, it is important for trainees to have visual representations of themselves as scientists.
-The importance of representation in retaining a diverse group of individuals in STEM fields is supported by social role theory [@Eagly1984].
-Individuals tend to make inferences about characteristics that are needed to be successful in a given role by examining individuals that most occupy that role [@Eagly1984; @Carter2018].
-Therefore, trainees who do not see representation of themselves in senior scientific positions, or in this case as senior faculty members, may decide that they do not possess the characteristics that are required to succeed.
-In an attempt to make science a more inclusive environment, many individuals have attempted to address this issue by promoting the inclusion of more women speakers at conferences [@kalejta_gender_2017; @casadevall_presence_2014; @klein_speaking_2017].
-However, no study to date has addressed invited speaker seminar series diversity within their own institution.
+Invited seminar series are common within biomedical departments across the United States [@nittrouer_gender_2018].
+Usually, seminar series' consist of faculty members selecting a scientist from another institution to visit their university and present their research, as well as meet with other faculty members and trainees.
+Named lectureships follow the same format but are decided by committee and are considered more prestigious because they are named in honor of prominent local scientists.
+These seminar series and lectureships provide an opportunity for trainees to be exposed to research outside of their department.
+Additionally, being an invited speaker provides the scientist with an opportunity to make future collaborations and build their own _curriculum vitae_ (CV).
+Scientists invited to give seminars are widely regarded as successful and the top in their field.
+Thus, if trainees are constantly being exposed to “the top scientist in their field”, according to social role theory, it signals who is successful in that field.
+While some have examined this issue by studying and promoting the inclusion of more women speakers at conferences, how department speaker series compare to the trainee diversity of that department is unknown [@kalejta_gender_2017; @casadevall_presence_2014; @klein_speaking_2017].
 
-Within the Department of Microbiology and Immunology at the University of Michigan (Ann Arbor, MI, USA), each year from September to June, faculty members have the opportunity to invite scientists from other institutions to give a one-hour seminar in which all department members attend.
-The invited seminar speaker also has the opportunity to meet with current department faculty members and trainees.
-Scientists who are invited to give seminars are widely regarded as successful and the top in their field.
-Thus, if trainees are constantly being exposed to “the top scientist in their field”, according to social role theory, it is imperative that the selected seminar speakers represent a diverse group of individuals.
-
-In this study, we examine and compare the proportion of HURM, non-Caucasian/non-HURM, and women invited speakers to white males in the Department of Microbiology and Immunology.
+In this study, we examine and compare the proportion of HURM, NCNH, and women invited speakers to white men in the Department of Microbiology and Immunology at the University of Michigan.
 Additionally, we compare invited-speaker demographics to the current trainee demographics as a means to gauge if trainee demographics are being represented accordingly throughout the seminar series.
-Following our investigation, we proposed a policy change to the Department of Microbiology and Immunology in how invited speakers are selected as a means to promote inclusion in our department and reduce stereotype threat, microaggressions, and unconscious bias.
-In order to facilitate inviting a more diverse group of scientists, we developed a set of resources that allow scientists, within the field of microbiology, to self-identify as an HURM, non-Caucasian/non-HURM, or a woman.
+Following our investigation, we proposed a policy change to the Department of Microbiology and Immunology in how invited speakers are selected as a means to promote inclusion in our department and reduce unconscious bias.
+In order to facilitate inviting a more diverse group of scientists, we developed a set of resources that allow scientists, within the fields of microbiology and immunology, to self-identify as having an under-represented or under-served identity including: HURM, non-Caucasian/non-HURM, or a white woman.
 These resources will promote inclusion and diversity by providing greater representation of all scientists and will provide hosts an opportunity to invite a more diverse group of scientists.
@@
 The list of faculty hosts was used as a proxy for faculty demographics since as hosts, these faculty members are visible representatives of the department.
-The trainees were identified using from departmental email lists that included masters students, doctoral students, and post-doctoral fellows.
+The trainees were identified using departmental email lists that included masters students, doctoral students, and post-doctoral fellows.
 
@@
 All others were placed into the NCNH group.
-We recognize that our proxy demographics are a limitation of the analysis and want to acknowledge that biological sex (male/female) is not always equivalent to the gender that an individual presents as (man/woman), which is also distinct from the gender(s) that an individual
-self-identifies as. We also want to acknowledge that there are many other identities that are not captured in this limited analysis.
+We recognize that our proxy demographics are a limitation of the analysis and want to acknowledge that biological sex (male/female) is not always equivalent to the gender that an individual presents as (man/woman), which is also distinct from the gender(s) that an individual self-identifies as.
+We also want to acknowledge that there are many other identities that are not captured in this limited analysis.
 
@@
 We also observed declines in the representation of HURM and NCNH faculty and speakers relative to the trainees (Fig 1B).
-HURM trainees made up 11% of the department, on track with the 11% of microbiology and immunology doctorates awarded in 2017 [@nsf_survey_2017].
+HURM trainees made up 11% of the department, on track with the 11% of U.S.
+microbiology and immunology doctorates awarded in 2017 [@nsf_survey_2017].
 However, only 8.5% of invited speakers, and none of the hosting faculty, were HURM scientists.
-NCNH trainees were 34% of department students and postdoc (22% of microbiology and immunology doctorates in 2017), but only 19% of hosting faculty and 10.5% of invited speakers [@nsf_survey_2017].
+NCNH trainees were 34% of department students and postdocs (versus 22% of U.S.
+microbiology and immunology doctorates in 2017), but only 19% of hosting faculty and 10.5% of invited speakers [@nsf_survey_2017].
 
@@
 HURM and NCNH scientists were awarded `r lect_summary[[2,3]]` and `r lect_summary[[3,3]]` lectureships, respectively.
-Because the intersection of identities can compound biases and outcomes, we further examined the lectureships by gender and race/ethnicity status.
+Because the intersection of identities can compound biases and outcomes, we further examined the lectureships by gender and race/ethnicity status [@Crenshaw1989].
 Caucasian men and women accounted for `r lect_summary[[1,4]]`% and `r lect_summary[[4,4]]`% of the lectureships, respectively.
@@
 
-In our study population, the proportion of women as faculty hosts and speakers is equivalent to global estimates that 40% of microbiologists are women, with a slightly lower representation of women in lectureships [@allagnat_gender_2017].
-In that regard, women are over-represented as graduate students and postdoctoral fellows in the department.
-Caucasian scientists are over-represented as host faculty and invited speakers, compared to their presence as trainees, particularly when lectureships were considered.
-Conversely, the proportion of HURM and NCNH invited speakers were under-representative of the trainee populations for each group.
-Thus, according to social role theory, this department is not adequately serving their non-Caucasian trainees.
+This study found that the proportion of HURM and NCNH invited speakers were under-representative of the trainee populations for each group.
+Additionally, within the last 5 years, no HURM or NCNH woman was awarded a lectureship.
+This means that the department is not providing non-Caucasian trainees with adequate representation of successful scientists.
+Taking this into context of social role theory, by not adequately representing the diversity of all trainees, the department is not supporting an inclusive environment in terms of visual faculty representation.
+We also  found that the proportion of women as faculty hosts and speakers in our study population is equivalent to global estimates that 40% of microbiologists are women, though women only represent about 30% of academic biomedical faculty [@allagnat_gender_2017;@Jena2015].
+Women are also over-represented as graduate students and postdoctoral fellows in this department.
+Overall, Caucasian scientists are over-represented as host faculty and invited speakers, compared to their presence as trainees, particularly when lectureships were considered.
 
@@
 In their study, Nittrouer et al, examined 3,652 talks at 50 U.S.
-institutions in 2013 - 2014 and found that women faculty are less likely to be invited speakers, despite similar acceptance rates.
-These results suggest that women faculty are less often invited as speakers.
-We have not been able to identify any other publications examining scientific speaker diversity beyond gender.
+institutions in 2013 - 2014 and found that women faculty are less likely to be invited speakers, despite similar acceptance rates [@nittrouer_gender_2018].
+We have not been able to identify any publications examining scientific speaker diversity beyond gender.
 This seems to be the first, which is concerning since conclusions drawn from gender-based studies are often framed, and considered, to be applicable to other marginalized groups (e.g., HURM).
@@
 While there is no doubt some overlap, each group remains marginalized due to a unique complex set of factors that cannot always be solved by gender-based solutions.
-US-serving institutions, such as the University of Michigan have a particular responsibility to the historically suppressed populations included in our definition of HURMs.
-We therefore implore US institutions to apply this framing to their discussions and research.
+U.S.
+institutions, such as the University of Michigan have a particular responsibility to the historically suppressed populations included in our definition of HURMs.
+We therefore implore U.S.
+institutions to apply this framing to their discussions and research.
 
 Departments have different processes and criteria for selecting invited speakers, but it is a matter of pride to bring the best scientists possible.
-It may be that the definition of "best" poses a problem to women, who need three-times as many publications as their men colleges to be considered equally competent [@BlairLoy2017, @?], and those that identify as HURM and Asian, who report having to work harder than white men to be perceived as legitimate scholars [@noauthor_seeking_2013].
+It may be that the definition of "best" poses a problem to under-represented and under-served groups (e.g., white women, HURM, and Asian) who are held to stricter competency standards and report having to work harder than white men to be perceived as legitimate scholars [@BlairLoy2017;@noauthor_seeking_2013].
 Some departments only invite tenured faculty, which severely limits the number of potential speakers who are white women or non-Caucasian.
@@
 The dedication of women who have children to their work is perceived to be less than that of their colleagues, i.e., men who also have children [@Firth1982; @Correll2007; @Fuegen2004].
-The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation, despite the prestigious nature of these invitations and evidence that men and women accept at similar rates [@nittrouer_gender_2018; @xu_2008].
-As a result, the faculty member invites a different colleague who they feel is more likely to agree (and is a man).
+The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation, despite the prestigious nature of these invitations and evidence that men and women accept at similar rates [@nittrouer_gender_2018; @xu_gender_2008].
+As a result, the faculty member may invite a different colleague who they feel is more likely to agree (and is a man).
 Another large portion of our sample were the NCNH cohort, who are predominately Asian/Asian American individuals.
@@
 Mobley).
-Since trainee demographics were not represented within seminar speaker demographics over the past five years, we proposed a policy change as to how seminar speakers were being invited.
+Since trainee demographics were not represented by the seminar speaker demographics over the past 5 years, we proposed a policy change as to how seminar speakers were being invited.
 One suggestion was to switch from faculty-invited to lab-invited speakers in an attempt to allow trainees to choose a speaker that best represented themselves (Table 1).
@@
 This limitation makes two important points: that perceived identity often plays a larger role than self-identification, and that we need better tools to identify members of marginalized groups.
-Another policy suggestion is for departments to invite their speakers to spend a time discussing their personal journeys through science, in addition to their scientific stories (Table 1).
-This would enable those who wish, feel welcomed to discuss how their identity(ies) interacted with their careers.
+Another policy suggestion is for departments to invite their speakers to spend time discussing their personal journeys through science, in addition to their scientific stories (Table 1).
+This would enable those who wish, to discuss how their identity(ies) interacted with their careers.
 In addition to these suggestions for policy change, we have created resources that allow scientists to self-identify as under-served groups and thus provide host faculty with more diverse choices (Table 1).
@@
 
-Motivated by a lack of resources to identify scientists who are members of marginalized and/or historically under-served groups, and inspired by resources in other fields--DiversifyEEB and DiversifyChemistry--we created DiversifyMicrobiology and DiversifyImmunology.
+Motivated by a lack of resources to identify scientists who are members of marginalized and/or historically under-served groups, and inspired by resources in other fields--DiversifyEEB and DiversifyChemistry--we created DiversifyMicrobiology and DiversifyImmunology [@Baucom_2019; @Duffy_2019; @Hagan2019_micro; @Hagan2019_immuno].
 These resources are a tool for symposium organizers, award committees, search committees, and other scientists to identify individuals to diversify their pools.
-Additionally, we have built these as a template to be used as a tool for other fields and organizations that wish to create their own lists.
+Additionally, we have built these as a template to be used by other fields and organizations that wish to create their own lists.
 Since these lists are compiled by self-nomination, we can ensure that only scientists comfortable revealing their marginalized identities are included.
@@
 Basic tools and skills required to set up a Diversify site include knowledge of, or experience with, the version control tool git, the web-tool GitHub, and a text editor.
-A tutorial in the DiversifyMicrobiology repository on GitHub provides links to these resources and instructions for adapting the tool to your own field.
+A tutorial in the DiversifyMicrobiology repository on GitHub provides links to these resources and instructions for adapting the tool to your own field [@Hagan2019_micro].
 
@@
 
-To increase the retention of white women and HURM trainees in the biological sciences, they must also be represented as experts.
+To increase the retention of white women, HURM and NCNH trainees in the biomedical sciences, they must also be represented as experts.
 However, the invited speaker diversity at one department does not represent the diversity of trainees.
@@
 ## Code and data availability
-The anonymized data, code for all analysis steps, and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_SpeakerDiversity_XXXX_2019/.
+The anonymized data, code for all analysis steps, and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_SpeakerDiversity_JMBE_2019.
 Template and complete instructions for generating a field-specific Diversity website are available at https://github.com/diversifymicrobiology/DiversifyMicrobiology.github.io/.

### 2019-09-27 submission/manuscript.tex
revert legends
minor edits, prep for biorxiv submission

@@
 \hypersetup{unicode=true,
-            pdftitle={Policy should change to improve invited speaker diversity and retain trainees},
+            pdftitle={Policy should change to improve invited speaker diversity and reflect trainee diversity},
             pdfborder={0 0 0},
@@
   \title{\textbf{Policy should change to improve invited speaker diversity and
-retain trainees}}
+reflect trainee diversity}}
     \pretitle{\vspace{\droptitle}\centering\huge}
@@
 
-The biological sciences have a problem retaining white women and
+The biomedical sciences have a problem retaining white women and
 underrepresented minorities in academia. Despite increases in the
@@
 still underrepresented at the faculty level, particularly at the Full
-professor level. Faculty are often invited to departments at other
-universities to present on their research, a highly valued offer that
-provides an opportunity for collaborations and networking. This is also
-an opportunity for trainees to interact with additional faculty from
-underrepresented groups. In this manuscript, we compare invited-speaker
-demographics to the current trainee demographics and find that trainees
-are not proportionally represented by speakers invited to the
+Professor level. The lack of diverse individuals at the Full Professor
+level contributes to the attrition of women and under-represented
+minorities, as it confirms unconscious biases. The presence of
+unconscious biases contribute to feelings of not belonging by trainees
+and are amplified by visual representation of who is presented as the
+``top scientist in their field''. Top scientists are not only defined by
+the attainment of Full Professorships, but also through invited seminar
+series. Invitations for faculty to present their research at other
+university departments is highly valued offer that provides an
+opportunity for collaborations and networking. However, if invited
+speakers do not represent the demographics of current trainees, these
+visual representations of successful scientists may contribute to
+decreased attitudes of self-identification as a scientist, ultimately
+resulting in trainees leaving the field or the academy. In this study,
+we compare invited-speaker demographics to the current trainee
+demographics in one microbiology and immunology department and find that
+trainees are not proportionally represented by speakers invited to the
 department. Our investigation prompted changes in policy for how invited
@@
 under-representation of many racial and ethnic groups, as well as women,
-in science, technology, engineering, and math (STEM) fields (NIH 2015
-report, Measuring DEI 2016, (1)). Organization climate and culture that
-supports inclusion of all individuals is essential to support the
-retention of historically underrepresented minorities (HURM) in the
-U.S., as well as non-Caucasian individuals, and women in STEM fields
-(Schneider, 2013). Inclusive organization culture will not suffice in
-retaining HURM, non-Caucasian individuals, and women without
-organization policy changes that support their values and goals (2).
+in science, technology, engineering, and math (STEM) fields (1--4).
+Specifically, within the field of biomedical research in the United
+States, the proportion of underrepresented minorities at the full
+professor level has remained consistently low at 4\% (survey data taken
+from the NIH from 2001 to 2013), compared to the U.S. population, which
+is 32.3\% (5, 6). Similar discrepancies exist for women in biomedical
+sciences as full professorships are currently held mostly by men (7, 8).
+As demographics of faculty within the biomedical sciences remains skewed
+towards Caucasian men, the demographics of trainees (graduate students
+and postdocs) are becoming more diverse (5).
 
-A long-standing issue within STEM fields, specifically within academia,
-has been a lack of diverse representation of scientists for trainees
-(graduate students and postdoctoral fellows). In order to maintain
-retention of HURM, non-Caucasian individuals, and women in STEM fields,
-it is important for trainees to have visual representations of
-themselves as scientists. The importance of representation in retaining
-a diverse group of individuals in STEM fields is supported by social
-role theory (3). Individuals tend to make inferences about
-characteristics that are needed to be successful in a given role by
-examining individuals that most occupy that role (3, 4). Therefore,
-trainees who do not see representation of themselves in senior
-scientific positions, or in this case as senior faculty members, may
-decide that they do not possess the characteristics that are required to
-succeed. In an attempt to make science a more inclusive environment,
-many individuals have attempted to address this issue by promoting the
-inclusion of more women speakers at conferences (5--7). However, no
-study to date has addressed invited speaker seminar series diversity
-within their own institution.
+Policy changes are needed to support inclusion of all individuals,
+particularly in the biomedical sciences(9). To increase retention of
+historically under-represented minorities (HURM), non-Caucasian/non-HURM
+(NCNH) individuals, and white women in biomedical fields, it is
+important for trainees to have visual representations of themselves as
+scientists. The importance of representation in retaining a diverse
+group of individuals in STEM fields is supported by social role theory
+(10). Individuals make inferences about characteristics that are needed
+to be successful in a given role by examining individuals that most
+occupy that role (10, 11). However, there is a lack of diverse
+scientific experts in academia so underrepresented minorities are not
+seeing adequate visual representations of themselves at the faculty
+level. Therefore, trainees who do not see representation of themselves
+in senior faculty positions, may decide that they do not possess the
+characteristics that are required to succeed.
 
-Within the Department of Microbiology and Immunology at the University
-of Michigan (Ann Arbor, MI, USA), each year from September to June,
-faculty members have the opportunity to invite scientists from other
-institutions to give a one-hour seminar in which all department members
-attend. The invited seminar speaker also has the opportunity to meet
-with current department faculty members and trainees. Scientists who are
-invited to give seminars are widely regarded as successful and the top
-in their field. Thus, if trainees are constantly being exposed to ``the
-top scientist in their field'', according to social role theory, it is
-imperative that the selected seminar speakers represent a diverse group
-of individuals.
+Invited seminar series are common within biomedical departments across
+the United States (12). Usually, seminar series' consist of faculty
+members selecting a scientist from another institution to visit their
+university and present their research, as well as meet with other
+faculty members and trainees. Named lectureships follow the same format
+but are decided by committee and are considered more prestigious because
+they are named in honor of prominent local scientists. These seminar
+series and lectureships provide an opportunity for trainees to be
+exposed to research outside of their department. Additionally, being an
+invited speaker provides the scientist with an opportunity to make
+future collaborations and build their own \emph{curriculum vitae} (CV).
+Scientists invited to give seminars are widely regarded as successful
+and the top in their field. Thus, if trainees are constantly being
+exposed to ``the top scientist in their field'', according to social
+role theory, it signals who is successful in that field. While some have
+examined this issue by studying and promoting the inclusion of more
+women speakers at conferences, how department speaker series compare to
+the trainee diversity of that department is unknown (13--15).
 
-In this study, we examine and compare the proportion of HURM,
-non-Caucasian/non-HURM, and women invited speakers to white males in the
-Department of Microbiology and Immunology. Additionally, we compare
+In this study, we examine and compare the proportion of HURM, NCNH, and
+women invited speakers to white men in the Department of Microbiology
+and Immunology at the University of Michigan. Additionally, we compare
 invited-speaker demographics to the current trainee demographics as a
@@
 invited speakers are selected as a means to promote inclusion in our
-department and reduce stereotype threat, microaggressions, and
-unconscious bias. In order to facilitate inviting a more diverse group
-of scientists, we developed a set of resources that allow scientists,
-within the field of microbiology, to self-identify as an HURM,
-non-Caucasian/non-HURM, or a woman. These resources will promote
-inclusion and diversity by providing greater representation of all
-scientists and will provide hosts an opportunity to invite a more
-diverse group of scientists.
+department and reduce unconscious bias. In order to facilitate inviting
+a more diverse group of scientists, we developed a set of resources that
+allow scientists, within the fields of microbiology and immunology, to
+self-identify as having an under-represented or under-served identity
+including: HURM, non-Caucasian/non-HURM, or a white woman. These
+resources will promote inclusion and diversity by providing greater
+representation of all scientists and will provide hosts an opportunity
+to invite a more diverse group of scientists.
 
@@
 representatives of the department. The trainees were identified using
-from departmental email lists that included masters students, doctoral
+departmental email lists that included masters students, doctoral
 students, and post-doctoral fellows.
@@
 Data were analyzed and figures generated in R Statistical Software,
-using relevant packages (8--20).
+using relevant packages (16--28).
 
@@
 speakers relative to the trainees (Fig 1B). HURM trainees made up 11\%
-of the department, on track with the 11\% of microbiology and immunology
-doctorates awarded in 2017 (21). However, only 8.5\% of invited
-speakers, and none of the hosting faculty, were HURM scientists. NCNH
-trainees were 34\% of department students and postdoc (22\% of
-microbiology and immunology doctorates in 2017), but only 19\% of
-hosting faculty and 10.5\% of invited speakers (21).
+of the department, on track with the 11\% of U.S. microbiology and
+immunology doctorates awarded in 2017 (29). However, only 8.5\% of
+invited speakers, and none of the hosting faculty, were HURM scientists.
+NCNH trainees were 34\% of department students and postdocs (versus 22\%
+of U.S. microbiology and immunology doctorates in 2017), but only 19\%
+of hosting faculty and 10.5\% of invited speakers (29).
 
@@
 and outcomes, we further examined the lectureships by gender and
-race/ethnicity status. Caucasian men and women accounted for 44.44\% and
-37.04\% of the lectureships, respectively. Just 18.52\% of lectureships
-were held by non-Caucasian men while none were held by non-Caucasian
-women (Fig. 1D).
+race/ethnicity status (30). Caucasian men and women accounted for
+44.44\% and 37.04\% of the lectureships, respectively. Just 18.52\% of
+lectureships were held by non-Caucasian men while none were held by
+non-Caucasian women (Fig. 1D).
 
@@
 
-In our study population, the proportion of women as faculty hosts and
-speakers is equivalent to global estimates that 40\% of microbiologists
-are women, with a slightly lower representation of women in lectureships
-(22). In that regard, women are over-represented as graduate students
-and postdoctoral fellows in the department. Caucasian scientists are
-over-represented as host faculty and invited speakers, compared to their
-presence as trainees, particularly when lectureships were considered.
-Conversely, the proportion of HURM and NCNH invited speakers were
-under-representative of the trainee populations for each group. Thus,
-according to social role theory, this department is not adequately
-serving their non-Caucasian trainees.
+This study found that the proportion of HURM and NCNH invited speakers
+were under-representative of the trainee populations for each group.
+Additionally, within the last 5 years, no HURM or NCNH woman was awarded
+a lectureship. This means that the department is not providing
+non-Caucasian trainees with adequate representation of successful
+scientists. Taking this into context of social role theory, by not
+adequately representing the diversity of all trainees, the department is
+not supporting an inclusive environment in terms of visual faculty
+representation. We also found that the proportion of women as faculty
+hosts and speakers in our study population is equivalent to global
+estimates that 40\% of microbiologists are women, though women only
+represent about 30\% of academic biomedical faculty (7, 31). Women are
+also over-represented as graduate students and postdoctoral fellows in
+this department. Overall, Caucasian scientists are over-represented as
+host faculty and invited speakers, compared to their presence as
+trainees, particularly when lectureships were considered.
 
@@
 scientific conferences, however, we have only identified one that
-focused on invited speakers at universities (23). In their study,
+focused on invited speakers at universities (12). In their study,
 Nittrouer et al, examined 3,652 talks at 50 U.S. institutions in 2013 -
 2014 and found that women faculty are less likely to be invited
-speakers, despite similar acceptance rates. These results suggest that
-women faculty are less often invited as speakers. We have not been able
-to identify any other publications examining scientific speaker
-diversity beyond gender. This seems to be the first, which is concerning
-since conclusions drawn from gender-based studies are often framed, and
+speakers, despite similar acceptance rates (12). We have not been able
+to identify any publications examining scientific speaker diversity
+beyond gender. This seems to be the first, which is concerning since
+conclusions drawn from gender-based studies are often framed, and
 considered, to be applicable to other marginalized groups (e.g., HURM).
@@
 group remains marginalized due to a unique complex set of factors that
-cannot always be solved by gender-based solutions. US-serving
-institutions, such as the University of Michigan have a particular
-responsibility to the historically suppressed populations included in
-our definition of HURMs. We therefore implore US institutions to apply
-this framing to their discussions and research.
+cannot always be solved by gender-based solutions. U.S. institutions,
+such as the University of Michigan have a particular responsibility to
+the historically suppressed populations included in our definition of
+HURMs. We therefore implore U.S. institutions to apply this framing to
+their discussions and research.
 
@@
 possible. It may be that the definition of ``best'' poses a problem to
-women, who need three-times as many publications as their men colleges
-to be considered equally competent (24), and those that identify as HURM
-and Asian, who report having to work harder than white men to be
-perceived as legitimate scholars (25). Some departments only invite
-tenured faculty, which severely limits the number of potential speakers
-who are white women or non-Caucasian. Yet, another scenario is that
-pre-tenure faculty members invite prestigious, tenured faculty in their
-field to network and secure letters for their own tenure package. The
-increased burden of white women and non-Caucasian scientists to prove
-competency decreases their likelihood to be considered for either tenure
-or as possible source of tenure letters.
+under-represented and under-served groups (e.g., white women, HURM, and
+Asian) who are held to stricter competency standards and report having
+to work harder than white men to be perceived as legitimate scholars
+(32, 33). Some departments only invite tenured faculty, which severely
+limits the number of potential speakers who are white women or
+non-Caucasian. Yet, another scenario is that pre-tenure faculty members
+invite prestigious, tenured faculty in their field to network and secure
+letters for their own tenure package. The increased burden of white
+women and non-Caucasian scientists to prove competency decreases their
+likelihood to be considered for either tenure or as possible source of
+tenure letters.
 
@@
 their work is perceived to be less than that of their colleagues, i.e.,
-men who also have children (26--28). The perceived prioritization and
+men who also have children (34--36). The perceived prioritization and
 commitments of women to family over work may cause faculty to doubt
@@
 nature of these invitations and evidence that men and women accept at
-similar rates ({\textbf{???}}, 23). As a result, the faculty member
-invites a different colleague who they feel is more likely to agree (and
-is a man). Another large portion of our sample were the NCNH cohort, who
-are predominately Asian/Asian American individuals. Although Asian
+similar rates (12, 37). As a result, the faculty member may invite a
+different colleague who they feel is more likely to agree (and is a
+man). Another large portion of our sample were the NCNH cohort, who are
+predominately Asian/Asian American individuals. Although Asian
 scientists are well-represented in the US scientific workforce, they
 face significant bias and barriers to inclusion in society and academia
-(29, 30). For instance, despite the higher employment rate of Asian
+(38, 39). For instance, despite the higher employment rate of Asian
 scientists, they were not well-represented in the more prestigious
@@
 varying rates of hiring and tenure promotion mean unique considerations
-are important for inclusion of each group (31). For instance, a major
+are important for inclusion of each group (3). For instance, a major
 barrier to inclusion of HURM faculty at similar proportions to HURM
@@
 to faculty positions and the associated low proportion of HURM faculty
-(32). The proportion of HURM faculty at the Assistant and Associate
+(40). The proportion of HURM faculty at the Assistant and Associate
 Professor level is currently higher than at Full Professor so it will be
 difficult to increase speaker diversity if early-career researchers are
-not being considered (33). Increased performance expectations and
+not being considered (41). Increased performance expectations and
 patterns of exclusions are consistent themes in studies characterizing
-the HURM faculty experience (34, 35). Therefore, inclusion of HURM
+the HURM faculty experience (42, 43). Therefore, inclusion of HURM
 faculty in seminar series is likely essential to increasing the number
@@
 faculty in these seminar series is just one aspect of larger
-institutional change that is needed (36).
+institutional change that is needed (44).
 
@@
 to faculty members and the department chair (Dr.~Mobley). Since trainee
-demographics were not represented within seminar speaker demographics
-over the past five years, we proposed a policy change as to how seminar
+demographics were not represented by the seminar speaker demographics
+over the past 5 years, we proposed a policy change as to how seminar
 speakers were being invited. One suggestion was to switch from
@@
 tools to identify members of marginalized groups. Another policy
-suggestion is for departments to invite their speakers to spend a time
+suggestion is for departments to invite their speakers to spend time
 discussing their personal journeys through science, in addition to their
-scientific stories (Table 1). This would enable those who wish, feel
-welcomed to discuss how their identity(ies) interacted with their
-careers. In addition to these suggestions for policy change, we have
-created resources that allow scientists to self-identify as under-served
-groups and thus provide host faculty with more diverse choices (Table
-1).
+scientific stories (Table 1). This would enable those who wish, to
+discuss how their identity(ies) interacted with their careers. In
+addition to these suggestions for policy change, we have created
+resources that allow scientists to self-identify as under-served groups
+and thus provide host faculty with more diverse choices (Table 1).
 
@@
 resources in other fields--DiversifyEEB and DiversifyChemistry--we
-created DiversifyMicrobiology and DiversifyImmunology. These resources
-are a tool for symposium organizers, award committees, search
+created DiversifyMicrobiology and DiversifyImmunology (45--48). These
+resources are a tool for symposium organizers, award committees, search
 committees, and other scientists to identify individuals to diversify
 their pools. Additionally, we have built these as a template to be used
-as a tool for other fields and organizations that wish to create their
-own lists. Since these lists are compiled by self-nomination, we can
-ensure that only scientists comfortable revealing their marginalized
-identities are included.
+by other fields and organizations that wish to create their own lists.
+Since these lists are compiled by self-nomination, we can ensure that
+only scientists comfortable revealing their marginalized identities are
+included.
 
@@
 DiversifyMicrobiology repository on GitHub provides links to these
-resources and instructions for adapting the tool to your own field.
+resources and instructions for adapting the tool to your own field (47).
 
@@
 
-To increase the retention of white women and HURM trainees in the
-biological sciences, they must also be represented as experts. However,
+To increase the retention of white women, HURM and NCNH trainees in the
+biomedical sciences, they must also be represented as experts. However,
 the invited speaker diversity at one department does not represent the
@@
 
-A.K.H. collected the data, assigned demographics, analyzed the data, and
-created the website. R.M.P. created the Google lists, forms, and website
-content and the description of their maintenance. J.L. wrote the
-introduction and provided conceptual advice. A.K.H. and J.L facilitated
-the policy change to the UM Department of Microbiology and Immunology.
-All authors contributed to preparing the final manuscript.
+A.K.H. collected the data, assigned demographics, analyzed the data,
+created the website, and wrote the methods and results. R.M.P. created
+the Google lists, forms, and website content and the description of
+their maintenance. J.L. wrote the introduction and provided conceptual
+advice. A.K.H. and J.L facilitated the policy change to the UM
+Department of Microbiology and Immunology. All authors contributed to
+preparing the final manuscript.
 
@@
 version of this manuscript is available at
-\url{https://github.com/akhagan/Hagan_SpeakerDiversity_XXXX_2019/}.
+\url{https://github.com/akhagan/Hagan_SpeakerDiversity_JMBE_2019}.
 Template and complete instructions for generating a field-specific
@@
 \hypertarget{refs}{}
-\hypertarget{ref-colloquy_2012}{}
-1. 2012. Colloquy on minority males in science, technology, engineering,
-and mathematics. National Academies Press.
+\hypertarget{ref-Martinez2018}{}
+1. \textbf{Martinez LR}, \textbf{Boucaud DW}, \textbf{Casadevall A},
+\textbf{August A}. 2018. Factors contributing to the success of
+NIH-designated underrepresented minorities in academic and nonacademic
+research positions. CBELife Sciences Education \textbf{17}:ar32.
+doi:\href{https://doi.org/10.1187/cbe.16-09-0287}{10.1187/cbe.16-09-0287}.
+
+\hypertarget{ref-AllenRamdial2014}{}
+2. \textbf{Allen-Ramdial S-AA}, \textbf{Campbell AG}. 2014. Reimagining
+the pipeline: Advancing STEM diversity, persistence, and success.
+BioScience \textbf{64}:612--618.
+doi:\href{https://doi.org/10.1093/biosci/biu076}{10.1093/biosci/biu076}.
+
+\hypertarget{ref-Fang2000}{}
+3. \textbf{Fang D}. 2000. Racial and ethnic disparities in faculty
+promotion in academic medicine. JAMA \textbf{284}:1085.
+doi:\href{https://doi.org/10.1001/jama.284.9.1085}{10.1001/jama.284.9.1085}.
+
+\hypertarget{ref-Gibbs2014}{}
+4. \textbf{Gibbs KD}, \textbf{McGready J}, \textbf{Bennett JC},
+\textbf{Griffin K}. 2014. Biomedical science ph.D. career interest
+patterns by race/ethnicity and gender. PLoS ONE \textbf{9}:e114736.
+doi:\href{https://doi.org/10.1371/journal.pone.0114736}{10.1371/journal.pone.0114736}.
+
+\hypertarget{ref-Meyers2018}{}
+5. \textbf{Meyers LC}, \textbf{Brown AM}, \textbf{Moneta-Koehler L},
+\textbf{Chalkley R}. 2018. Survey of checkpoints along the pathway to
+diverse biomedical research faculty. PLOS ONE \textbf{13}:e0190606.
+doi:\href{https://doi.org/10.1371/journal.pone.0190606}{10.1371/journal.pone.0190606}.
+
+\hypertarget{ref-nsf_2014}{}
+6. \textbf{National Center for Science and Engineering Statistics}.
+2014. Women, minorities, and persons with disabilities in science and
+engineering. National Science Foundation, Alexandria, VA.
+
+\hypertarget{ref-Jena2015}{}
+7. \textbf{Jena AB}, \textbf{Khullar D}, \textbf{Ho O}, \textbf{Olenski
+AR}, \textbf{Blumenthal DM}. 2015. Sex differences in academic rank in
+US medical schools in 2014. JAMA \textbf{314}:1149.
+doi:\href{https://doi.org/10.1001/jama.2015.10680}{10.1001/jama.2015.10680}.
+
+\hypertarget{ref-Rotbart2012}{}
+8. \textbf{Rotbart HA}, \textbf{McMillen D}, \textbf{Taussig H},
+\textbf{Daniels SR}. 2012. Assessing gender equity in a large academic
+department of pediatrics. Academic Medicine \textbf{87}:98--104.
+doi:\href{https://doi.org/10.1097/acm.0b013e31823be028}{10.1097/acm.0b013e31823be028}.
 
 \hypertarget{ref-Coe2019}{}
-2. \textbf{Coe IR}, \textbf{Wiley R}, \textbf{Bekker L-G}. 2019.
+9. \textbf{Coe IR}, \textbf{Wiley R}, \textbf{Bekker L-G}. 2019.
 Organisational best practices towards gender equality in science and
@@
 \hypertarget{ref-Eagly1984}{}
-3. \textbf{Eagly AH}, \textbf{Steffen VJ}. 1984. Gender stereotypes stem
-from the distribution of women and men into social roles. Journal of
-Personality and Social Psychology \textbf{46}:735--754.
+10. \textbf{Eagly AH}, \textbf{Steffen VJ}. 1984. Gender stereotypes
+stem from the distribution of women and men into social roles. Journal
+of Personality and Social Psychology \textbf{46}:735--754.
 doi:\href{https://doi.org/10.1037/0022-3514.46.4.735}{10.1037/0022-3514.46.4.735}.
@@
 \hypertarget{ref-Carter2018}{}
-4. \textbf{Carter AJ}, \textbf{Croft A}, \textbf{Lukas D},
+11. \textbf{Carter AJ}, \textbf{Croft A}, \textbf{Lukas D},
 \textbf{Sandstrom GM}. 2018. Women's visibility in academic seminars:
@@
 
+\hypertarget{ref-nittrouer_gender_2018}{}
+12. \textbf{Nittrouer CL}, \textbf{Hebl MR}, \textbf{Ashburn-Nardo L},
+\textbf{Trump-Steele RCE}, \textbf{Lane DM}, \textbf{Valian V}. 2018.
+Gender disparities in colloquium speakers at top universities.
+Proceedings of the National Academy of Sciences \textbf{115}:104--108.
+doi:\href{https://doi.org/10.1073/pnas.1708414115}{10.1073/pnas.1708414115}.
+
 \hypertarget{ref-kalejta_gender_2017}{}
-5. \textbf{Kalejta RF}, \textbf{Palmenberg AC}. 2017. Gender Parity
+13. \textbf{Kalejta RF}, \textbf{Palmenberg AC}. 2017. Gender Parity
 Trends for Invited Speakers at Four Prominent Virology Conference
@@
 \hypertarget{ref-casadevall_presence_2014}{}
-6. \textbf{Casadevall A}, \textbf{Handelsman J}. 2014. The Presence of
+14. \textbf{Casadevall A}, \textbf{Handelsman J}. 2014. The Presence of
 Female Conveners Correlates with a Higher Proportion of Female Speakers
@@
 \hypertarget{ref-klein_speaking_2017}{}
-7. \textbf{Klein RS}, \textbf{Voskuhl R}, \textbf{Segal BM},
+15. \textbf{Klein RS}, \textbf{Voskuhl R}, \textbf{Segal BM},
 \textbf{Dittel BN}, \textbf{Lane TE}, \textbf{Bethea JR}, \textbf{Carson
@@
 \hypertarget{ref-R_software_2017}{}
-8. \textbf{R Core Team}. 2017. R: A language and environment for
+16. \textbf{R Core Team}. 2017. R: A language and environment for
 statistical computing. R Foundation for Statistical Computing, Vienna,
@@
 \hypertarget{ref-wickham_tidyverse_2017}{}
-9. \textbf{Wickham H}. 2017. Tidyverse: Easily Install and Load the
+17. \textbf{Wickham H}. 2017. Tidyverse: Easily Install and Load the
 'Tidyverse'.
@@
 \hypertarget{ref-cowplot}{}
-10. \textbf{Wilke CO}. 2019. Cowplot: Streamlined plot theme and plot
+18. \textbf{Wilke CO}. 2019. Cowplot: Streamlined plot theme and plot
 annotations for 'ggplot2'.
@@
 \hypertarget{ref-markdown}{}
-11. \textbf{Allaire J}, \textbf{Horner J}, \textbf{Xie Y}, \textbf{Marti
+19. \textbf{Allaire J}, \textbf{Horner J}, \textbf{Xie Y}, \textbf{Marti
 V}, \textbf{Porte N}. 2018. Markdown: 'Markdown' rendering for r.
@@
 \hypertarget{ref-rmd_book}{}
-12. \textbf{Xie Y}, \textbf{Allaire J}, \textbf{Grolemund G}. 2018. R
+20. \textbf{Xie Y}, \textbf{Allaire J}, \textbf{Grolemund G}. 2018. R
 markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida.
@@
 \hypertarget{ref-rmd_rstudio}{}
-13. \textbf{Allaire J}, \textbf{Xie Y}, \textbf{McPherson J},
+21. \textbf{Allaire J}, \textbf{Xie Y}, \textbf{McPherson J},
 \textbf{Luraschi J}, \textbf{Ushey K}, \textbf{Atkins A},
@@
 \hypertarget{ref-knitr_2014}{}
-14. \textbf{Xie Y}. 2014. Knitr: A comprehensive tool for reproducible
+22. \textbf{Xie Y}. 2014. Knitr: A comprehensive tool for reproducible
 research in R. \emph{In} Stodden, V, Leisch, F, Peng, RD (eds.),
@@
 \hypertarget{ref-knitr_2018}{}
-15. \textbf{Xie Y}. 2018. Knitr: A general-purpose package for dynamic
+23. \textbf{Xie Y}. 2018. Knitr: A general-purpose package for dynamic
 report generation in r.
@@
 \hypertarget{ref-lubridate}{}
-16. \textbf{Grolemund G}, \textbf{Wickham H}. 2011. Dates and times made
+24. \textbf{Grolemund G}, \textbf{Wickham H}. 2011. Dates and times made
 easy with lubridate. Journal of Statistical Software \textbf{40}:1--25.
@@
 \hypertarget{ref-readxl}{}
-17. \textbf{Wickham H}, \textbf{Bryan J}. 2018. Readxl: Read excel
+25. \textbf{Wickham H}, \textbf{Bryan J}. 2018. Readxl: Read excel
 files.
@@
 \hypertarget{ref-pdftools}{}
-18. \textbf{Ooms J}. 2019. Pdftools: Text extraction, rendering and
+26. \textbf{Ooms J}. 2019. Pdftools: Text extraction, rendering and
 converting of pdf documents.
@@
 \hypertarget{ref-wickham_scales_2018}{}
-19. \textbf{Wickham H}. 2018. Scales: Scale Functions for Visualization.
+27. \textbf{Wickham H}. 2018. Scales: Scale Functions for Visualization.
 
 \hypertarget{ref-neuwirth_rcolorbrewer_2014}{}
-20. \textbf{Neuwirth E}. 2014. RColorBrewer: ColorBrewer Palettes.
+28. \textbf{Neuwirth E}. 2014. RColorBrewer: ColorBrewer Palettes.
 
 \hypertarget{ref-nsf_survey_2017}{}
-21. \textbf{Science and Engineering Statistics NC for}. 2017. Survey of
-Doctorate Recipients, Survey Year 2017. National Science Foundation,
-Alexandria, VA.
+29. \textbf{National Center for Science and Engineering Statistics}.
+2017. Survey of Doctorate Recipients, Survey Year 2017. National Science
+Foundation, Alexandria, VA.
+
+\hypertarget{ref-Crenshaw1989}{}
+30. \textbf{Crenshaw K}. 1989. Demarginalizing the Intersection of Race
+and Sex: A black feminist critique of antidiscrimination doctrine,
+feminist theory and antiracist politics. University of Chicago Legal
+Forum \textbf{1989}.
+doi:\href{https://doi.org/10.1007/s11162-008-9097-4}{10.1007/s11162-008-9097-4}.
 
 \hypertarget{ref-allagnat_gender_2017}{}
-22. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
+31. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
 HJ}, \textbf{Hanafi S}, \textbf{Herbert R}, \textbf{Huggett S},
@@
 
-\hypertarget{ref-nittrouer_gender_2018}{}
-23. \textbf{Nittrouer CL}, \textbf{Hebl MR}, \textbf{Ashburn-Nardo L},
-\textbf{Trump-Steele RCE}, \textbf{Lane DM}, \textbf{Valian V}. 2018.
-Gender disparities in colloquium speakers at top universities.
-Proceedings of the National Academy of Sciences \textbf{115}:104--108.
-doi:\href{https://doi.org/10.1073/pnas.1708414115}{10.1073/pnas.1708414115}.
-
 \hypertarget{ref-BlairLoy2017}{}
-24. \textbf{Blair-Loy M}, \textbf{Rogers L}, \textbf{Glaser D},
+32. \textbf{Blair-Loy M}, \textbf{Rogers L}, \textbf{Glaser D},
 \textbf{Wong Y}, \textbf{Abraham D}, \textbf{Cosman P}. 2017. Gender in
@@
 \hypertarget{ref-noauthor_seeking_2013}{}
-25. 2013. Seeking Solutions: Maximizing American Talent by Advancing
-Women of Color in Academia: Summary of a Conference. National Academies
-Press, Washington, D.C.
+33. \textbf{National Research Council \textnormal{Policy and Global
+Affairs}}, \textbf{Committee on Women in Science, Engineering, and
+Medicine}, \textbf{Committee on Advancing Institutional Transformation
+for Minority Women in Academia}, \textbf{Rapporteur KM}. 2013. Seeking
+Solutions: Maximizing American Talent by Advancing Women of Color in
+Academia: Summary of a Conference. National Academies Press, Washington,
+D.C.
 
 \hypertarget{ref-Firth1982}{}
-26. \textbf{Firth M}. 1982. Sex discrimination in job opportunities for
+34. \textbf{Firth M}. 1982. Sex discrimination in job opportunities for
 women. Sex Roles \textbf{8}:891--901.
@@
 \hypertarget{ref-Correll2007}{}
-27. \textbf{Correll SJ}, \textbf{Benard S}, \textbf{Paik I}. 2007.
+35. \textbf{Correll SJ}, \textbf{Benard S}, \textbf{Paik I}. 2007.
 Getting a job: Is there a motherhood penalty? American Journal of
@@
 \hypertarget{ref-Fuegen2004}{}
-28. \textbf{Fuegen K}, \textbf{Biernat M}, \textbf{Haines E},
+36. \textbf{Fuegen K}, \textbf{Biernat M}, \textbf{Haines E},
 \textbf{Deaux K}. 2004. Mothers and fathers in the workplace: How gender
@@
 
+\hypertarget{ref-xu_gender_2008}{}
+37. \textbf{Xu YJ}. 2008. Gender Disparity in STEM Disciplines: A Study
+of Faculty Attrition and Turnover Intentions. Research in Higher
+Education \textbf{49}:607--624.
+doi:\href{https://doi.org/10.1007/s11162-008-9097-4}{10.1007/s11162-008-9097-4}.
+
 \hypertarget{ref-Hwang2008}{}
-29. \textbf{Hwang W-C}, \textbf{Goto S}. 2008. The impact of perceived
+38. \textbf{Hwang W-C}, \textbf{Goto S}. 2008. The impact of perceived
 racial discrimination on the mental health of asian american and latino
@@
 \hypertarget{ref-Tran2019}{}
-30. \textbf{Tran VC}, \textbf{Lee J}, \textbf{Huang TJ}. 2019.
+39. \textbf{Tran VC}, \textbf{Lee J}, \textbf{Huang TJ}. 2019.
 Revisiting the asian second-generation advantage. Ethnic and Racial
@@
 
-\hypertarget{ref-Fang2000}{}
-31. \textbf{Fang D}. 2000. Racial and ethnic disparities in faculty
-promotion in academic medicine. JAMA \textbf{284}:1085.
-doi:\href{https://doi.org/10.1001/jama.284.9.1085}{10.1001/jama.284.9.1085}.
-
 \hypertarget{ref-Gibbs2016}{}
-32. \textbf{Gibbs KD}, \textbf{Basson J}, \textbf{Xierali IM},
+40. \textbf{Gibbs KD}, \textbf{Basson J}, \textbf{Xierali IM},
 \textbf{Broniatowski DA}. 2016. Decoupling of the minority PhD talent
@@
 \hypertarget{ref-whittaker_retention_2015}{}
-33. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
+41. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
 Acosta VG}. 2015. Retention of Underrepresented Minority Faculty:
@@
 \hypertarget{ref-pololi_race_2010}{}
-34. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
+42. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
 Disadvantage and Faculty Experiences in Academic Medicine. Journal of
@@
 \hypertarget{ref-hassouneh_experiences_2014}{}
-35. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
+43. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
 \textbf{Junkins EP}, \textbf{Horton LL}. 2014. The experiences of
@@
 \hypertarget{ref-johnson_msphere_2019}{}
-36. \textbf{Johnson MDL}. 2019. mSphere of Influence: Hiring of
+44. \textbf{Johnson MDL}. 2019. mSphere of Influence: Hiring of
 Underrepresented Minority Assistant Professors in Medical School Basic
@@
 
+\hypertarget{ref-Baucom_2019}{}
+45. \textbf{Baucom R}, \textbf{Duffy M}. 2019. DiversifyEEB.
+\url{https://diversifyeeb.com}.
+
+\hypertarget{ref-Duffy_2019}{}
+46. \textbf{Duffy M}, \textbf{McNeil AJ}. 2019. DiversifyChemistry.
+\url{https://diversifychemistry.com}.
+
+\hypertarget{ref-Hagan2019_micro}{}
+47. \textbf{Hagan AK}, \textbf{Pollet RM}. 2019. DiversifyMicrobiology.
+GitHub repository.
+\url{https://github.com/diversifymicrobiology.github.io}; GitHub.
+
+\hypertarget{ref-Hagan2019_immuno}{}
+48. \textbf{Hagan AK}, \textbf{Pollet RM}. 2019. DiversifyImmunology.
+GitHub repository.
+\url{https://github.com/diversifyimmunology.github.io}; GitHub.
+
 \end{document}

### 2019-10-01 code/get_figures.R
change image to jpg

@@ -15,5 +15,5 @@ bottom_row <- plot_grid(lectureship_demo_plot, lectureship_gend_plot,
 plot_grid(top_row, demo_plot, bottom_row, labels = c("A", "B", ""),
           label_size = 18, nrow = 3, rel_widths = c(1, 3, 1))
 
-ggsave("Figure_1.png", device = 'png', 
+ggsave("Figure_1.jpg", device = 'jpg', 
        path = '../submission', width = 12, height = 12)

### 2019-10-01 submission/Table_1.Rmd
format for submission, fix typos

--- 2019-09-24 submission/manuscript.tex
@@
-\documentclass[10pt,]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage[margin=1.0in]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
-            pdftitle={Department Invited Speakers Do Not Reflect Trainee Diversity},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-
-  \title{\textbf{Department Invited Speakers Do Not Reflect Trainee Diversity}}
-    \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-    \author{}
-    \preauthor{}\postauthor{}
-    \date{}
-    \predate{}\postdate{}
-
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage[table]{xcolor}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{caption}
-
-\usepackage{helvet} % Helvetica font
-\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
-\usepackage[T1]{fontenc}
-
-\usepackage[none]{hyphenat}
-
-\usepackage{setspace}
-\doublespacing
-\setlength{\parskip}{1em}
-
-\usepackage{lineno}
-
-\usepackage{pdfpages}
-\floatplacement{figure}{H} % Keep the figure up top of the page
-
-\begin{document}
-\maketitle
-
-\vspace{30mm}
-
-Running title: Invited Speaker Diversity Does Not Reflect Trainee
-Diversity
-
-\vspace{35mm}
-
-Ada K. Hagan, Ph.D.\({^1\dagger}\), Rebecca M. Pollet, Ph.D.\({^1}\),
-and Josie Libertucci, Ph.D.\({^2\dagger}\)
-
-\vspace{35mm}
-
-\(\dagger\) To whom correspondence should be addressed:
-\href{mailto:akhagan@umich.edu}{\nolinkurl{akhagan@umich.edu}} or
-\href{mailto:libertj@mcmaster.ca}{\nolinkurl{libertj@mcmaster.ca}}
-
-1. Department of Microbiology \& Immunology, University of Michigan, Ann
-Arbor, Michigan
-
-2. Department of Medicine, McMaster University, Hamilton, Ontario,
-Canada
-
-Figures: 1
-
-Tables: 1
-
-\newpage
-
-\subsection{Conflicts of Interest}\label{conflicts-of-interest}
-
-\vspace{40mm}
-
-All authors affirm that there are no conflicts of interest.
-
-\newpage
-
-\linenumbers
-
-\subsection{Abstract}\label{abstract}
-
-Social role theory emphasizes the importance of ``like'' representation
-to improve feelings of self-efficacy and belonging. This is an issue for
-trainees in the biological sciences who are either white women or
-underrepresented minorities, since there is a lack of faculty who look
-like them in biology academic settings. One way to improve
-representation is through invited speaker series. In this persepective,
-we compare the diversity of invited speakers at one microbiology and
-immunology department to the diversity of their post-Baccalaurate
-trainees. We find that trainees are not proportionally represented by
-the invited speakers and provide policy suggestions and tools to address
-this issue.
-
-\subsection{Keywords}\label{keywords}
-
-inclusion, diversity, invited speakers, academia, graduate programs
-
-\newpage
-
-\subsection{Background}\label{background}
-
-Long-standing systemic bias, sexism, and racism have contributed to the
-underrepresentation of many racial and ethnic groups, as well as women,
-in science, technology, engineering, and math (STEM) fields (NIH 2015
-report, Measuring DEI 2016, (1)). Organization climate and culture that
-supports inclusion of all individuals is essential to support the
-retention of historically underrepresented minorities (HURM) in the
-U.S., as well as non-Caucasian individuals, and women in STEM fields
-(Schneider, 2013). Inclusive organization culture will not suffice in
-retaining HURM, non-Caucasian individuals, and women without
-organization policy changes that support their values and goals (2).
-
-A long-standing issue within STEM fields, specifically within academia,
-has been a lack of diverse representation of scientists for trainees
-(graduate students and postdoctoral fellows). In order to maintain
-retention of HURM, non-Caucasian individuals, and women in STEM fields,
-it is important for trainees to have visual representations of
-themselves as scientists. The importance of representation in retaining
-a diverse group of individuals in STEM fields is supported by social
-role theory (3). Individuals tend to make inferences about
-characteristics that are needed to be successful in a given role by
-examining individuals that most occupy that role (3, 4). Therefore,
-trainees who do not see representation of themselves in senior
-scientific positions, or in this case as senior faculty members, may
-decide that they do not possess the characteristics that are required to
-succeed. In an attempt to make science a more inclusive environment,
-many individuals have attempted to address this issue by promoting the
-inclusion of more women speakers at conferences (5--7). However, no
-study to date has addressed invited speaker seminar series diversity
-within their own institution.
-
-Within the Department of Microbiology and Immunology at the University
-of Michigan (Ann Arbor, MI, USA), each year from September to June,
-faculty members have the opportunity to invite scientists from other
-institutions to give a one-hour seminar in which all department members
-attend. The invited seminar speaker also has the opportunity to meet
-with current department faculty members and trainees. Scientists who are
-invited to give seminars are widely regarded as successful and the top
-in their field. Thus, if trainees are constantly being exposed to ``the
-top scientist in their field'', according to social role theory, it is
-imperative that the selected seminar speakers represent a diverse group
-of individuals.
-
-In this study, we examine and compare the proportion of HURM,
-non-Caucasian/non-HURM, and women invited speakers to white males in the
-Department of Microbiology and Immunology. Additionally, we compare
-invited-speaker demographics to the current trainee demographics as a
-means to gauge if trainee demographics are being represented accordingly
-throughout the seminar series. Following our investigation, we proposed
-a policy change to the Department of Microbiology and Immunology in how
-invited speakers are selected as a means to promote inclusion in our
-department and reduce stereotype threat, microaggressions, and
-unconscious bias. In order to facilitate inviting a more diverse group
-of scientists, we developed a set of resources that allow scientists,
-within the field of microbiology, to self-identify as an HURM,
-non-Caucasian/non-HURM, or a woman. These resources will promote
-inclusion and diversity by providing greater representation of all
-scientists and will provide hosts an opportunity to invite a more
-diverse group of scientists.
-
-\subsection{Methods}\label{methods}
-
-Each academic year, each faculty member in the Department of
-Microbiology and Immunology at the University of Michigan has the
-opportunity to invite one speaker per year for a weekly seminar series.
-Some of these seminar slots are dedicated to named lectureships, which
-are decided by committee, and three trainee-invited speakers. We
-analyzed the demographics of invited speakers and faculty hosts for five
-academic years (Fall 2014 - Spring 2019), and compared them to the
-current trainees when the data were analyzed (Spring 2019). Each speaker
-was only counted once and those listed as departmental faculty members
-or as a ``host'' at any point could not also be considered ``invited
-speakers''. The list of faculty hosts was used as a proxy for faculty
-demographics since as hosts, these faculty members are visible
-representatives of the department. The trainees were identified using
-from departmental email lists that included masters students, doctoral
-students, and post-doctoral fellows.
-
-This is a retrospective study, thus speakers were not asked for their
-identities at the time of visit. Instead we hand-coded proxy
-demographics using personal knowledge, photos, and CVs. The presenting
-gender of each individual was assigned using a binary system
-(man/woman). Due to the low number of individuals in the study,
-race/ethnicity demographics were split in three groups: Caucasian,
-Historically Under-represented Minority (HURM), and
-Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibilty.
-Caucasian was assigned using the current U.S. Census definition where
-those of Middle Eastern, European, and Russian descent are included.
-HURM individuals were restricted to those with African-American,
-Indigenous, Alaskan/Hawaian Native, Latinx and/or Hispanic heritage. All
-others were placed into the NCNH group. We recognize that our proxy
-demographics are a limitation of the analysis and want to acknowledge
-that biological sex (male/female) is not always equivalent to the gender
-that an individual presents as (man/woman), which is also distinct from
-the gender(s) that an individual self-identifies as. We also want to
-acknowledge that there are many other identities that are not captured
-in this limited analysis.
-
-Data were analyzed and figures generated in R Statisical Software, using
-relevant packages (8--20).
-
-\subsection{Results}\label{results}
-
-To understand the representation of women, we compared the proportion of
-women in each academic role. At the trainee level, more than half of
-students and postdoctoral fellows were women. That dropped to 46.77\% of
-faculty hosts and 38.73\% of the invited speakers (Fig. 1A). Of 27
-lectureships over the five year period, 37.04\% were awarded to women.
-The proportion of women as faculty hosts and speakers is equivalent to
-global estimates that 40\% of microbiologists are women, with a slightly
-lower representation of women in lectureships (21).
-
-Our analysis identified an over-representation of Caucasian individuals
-as hosting faculty and invited speakers (80\% each), relative to the
-proportion of Caucasian trainees, which was 55\% (Fig. 1B). We also
-observed declines in the representation of HURM and NCNH faculty and
-speakers relative to the trainees (Fig 1B). HURM trainees made up 11\%
-of the department, on track with the 11\% of microbiology and immunology
-doctorates awarded in 2017 (22). However, only 8.5\% of invited
-speakers, and none of the hosting faculty, were HURM scientists. NCNH
-trainees were 34\% of department students and postdocs (22\% of
-microbiology and immunology doctorates in 2017), but only 19\% of
-hosting faculty and 10.5\% of invited speakers (22).
-
-The more prestigous invited speaker lectureships were also dominated by
-Caucasian scientists, who comprised 81.48\% of those awarded (Fig. 1C).
-HURM and NCNH scientists were awarded 3 and 2 lectureships,
-respectively. Because the intersection of identities can compound biases
-and outcomes, we further examined the lectureships by gender and
-race/ethnicity status. Caucasian men and women accounted for 44.44\% and
-37.04\% of the lectureships, respectively. Just 18.52\% of lectureships
-were held by non-Caucasian men while none were held by non-Caucasian
-women (Fig. 1D).
-
-\subsection{Discussion}\label{discussion}
-
-{[}Add paragraph summarizing findings {]} According to social role
-theory, this department is not adequately serving their non-Caucasian
-trainees.
-
-Several papers have investigated the representation of women at
-scientific conferences, however, we have only identified one that
-focused on invited speakers at universities (23). In their study,
-Nittrouer et al, examined 3,652 talks at 50 U.S. institutions in 2013 -
-2014 and found that women faculty are less likely to be invited
-speakers, despite similar acceptance rates. These results suggest that
-women faculty are less often invited as speakers. We have not been able
-to identify any other publications examining scientific speaker
-diversity beyond gender. This seems to be the first. This is concerning
-since conclusions drawn from gender-based studies are often framed, and
-considered, to be applicable to other marginalized groups (e.g., HURM).
-This is a flawed assumption. While there is no doubt some overlap, each
-group remains marginalized due to a unique complex set of factors that
-cannot always be solved by gender-based solutions. US-serving
-institutions, such as the University of Michigan have a particular
-responsibility to the historically suppressed populations included in
-our definition of HURMs. We therefore implore US institutions to apply
-this framing to their discussions and research.
-
-Departments have different processes and criteria for selecting invited
-speakers, but it is a matter of pride to bring the best scientists
-possible. It may be that the definition of ``best'' poses a problem to
-women, who need three-times as many publications as their men colleges
-to be considered equally competent (24), and those that identify as HURM
-and Asian, who report having to work harder than white men to be
-perceived as legitimate scholars (25). Some departments only invite
-tenured faculty, which severely limits the number of potential speakers
-who are white women or non-Caucasian. Yet, another scenario is that
-pre-tenure faculty members invite prestigious, tenured faculty in their
-field to network and secure letters for their own tenure package. The
-increased burden of white women and non-Caucasian scientists to prove
-competency decreases their likelihood to be considered for either tenure
-or as possible source of tenure letters.
-
-Each underrepresented group in our cohort faces a complex set of
-barriers to achieving faculty status. For instance, the decision to
-invite a woman may also be negatively impacted by assumptions about
-competency and dedication. The dedication of women who have children to
-their work is perceived to be less than that of their colleagues, i.e.,
-men who also have children (26--28). The perceived prioritization and
-commitments of women to family over work may cause faculty to doubt
-their acceptance of a speaking invitation, despite the prestigious
-nature of these invitations and evidence that men and women accept at
-similar rates ({\textbf{???}}, 23). As a result, the faculty member
-invites a different colleague who they feel is more likely to agree (and
-is a man). Another large portion of our sample were the NCNH cohort, who
-are predominately Asian/Asian American individuals. Although Asian
-scientists are well-represented in the US scientific workforce, they
-face significant bias and barriers to inclusion in society and academia
-(29, 30). For instance, despite the higher employment rate of Asian
-scientists, they were not well-represented in the more prestigious
-lectureships.
-
-While HURM and NCNH share some experiences, differences including
-varying rates of hiring and tenure promotion mean unique considerations
-are important for inclusion of each group (31). For instance, a major
-barrier to inclusion of HURM faculty at similar proportions to HURM
-trainees is the low transition rate of scientists from HURM backgrounds
-to faculty positions and the associated low proportion of HURM faculty
-(32). The proportion of HURM faculty at the Assistant and Associate
-Professor level is currently higher than at Full Professor so it will be
-difficult to increase speaker diversity if early-career researchers are
-not being considered (33). Increased performance expectations and
-patterns of exclusions are consistent themes in studies characterizing
-the HURM faculty experience (34, 35). Therefore, inclusion of HURM
-faculty in seminar series is likely essential to increasing the number
-of HURM Associate and Full Professors. Even when HURM speaker rates
-match the proportion of HURM faculty employment, HURM trainees will be
-represented at a significantly higher proportion. Inclusion of HURM
-faculty in these seminarseries is just one aspect of larger
-institutional change that is needed (36).
-
-\subsection{Instituting policy change within the Department of
-Microbiology and
-Immunology}\label{instituting-policy-change-within-the-department-of-microbiology-and-immunology}
-
-In an attempt to promote inclusion within the Dept. M\&I these data were
-presented to faculty members and the dept chair (Harry Mobley). Since,
-trainee demographics were not represented within seminar speaker
-demographics over the past 5 years, we proposed a policy change as to
-how seminar speakers were being invited. This policy change included
-switching from PI invited to lab invited in an attempt to allow trainees
-to choose a speaker that best represented themselves.
-
-Implict biases that affect perceptions of marginalized groups are the
-primary issue, but we must acknowledge that it is not always possible to
-identify members of historically under-served communities. For instance,
-after data analysis, we learned that at least one speaker in our data
-set should have been categorized as a HURM instead of Caucasian, but it
-wasn't readily apparent from their internet presence or CV. This
-limitation makes two important points: that percieved identity often
-plays a larger role than self-identification, and that we need better
-tools to identify members of marginalized groups. So in addition to our
-policy change, we also created resources that allow scientists to
-self-identify and provide host faculty with more diverse choices.
-
-\subsection{Building Diversify}\label{building-diversify}
-
-To help address this issue, we make some suggestions (Table 1) and have
-developed a resource to identify scientists who are members of
-marginalized and/or historically under-served groups. Motivated by a
-lack of such resources and inspired by similar resources--DiversifyEEB
-and DiversifyChemistry--we created DiversifyMicrobiology and
-DiversifyImmunology. These resources are a tool for symposium
-organziers, award committees, search committees and other scientists to
-identify individuals to diversify their pools. Additionally, we have
-built these as a tool for use by other fields and organizations to
-create their own lists. Since these lists are compiled by
-self-nomination, we can ensure that only scientists comfortable
-revealing their marginalized identities are included.
-
-The self-nomination form is a Google Form with entries logged in a
-private Google Sheet. This form is embedded within the website and can
-be linked to directly. The use of a Google Forms allows us to maintain
-this database at no cost and gives us the flexibility to add questions
-or change response options without disrupting previous responses.
-Entries are logged in a private spreadsheet so that entries can be
-screened before being added to the public database. This screening
-includes two steps: confirming that each person is listed in the
-database only once and that any submitted website is a personal,
-professional website. If both criteria are met, a new entry is added to
-the public database spreadsheet. If a person is already listed in the
-database, their information is updated to the most recent submission.
-
-This public spreadsheet is embedded in the website and can be open
-separately as a locked (uneditable) Google Sheet, allowing the list to
-be easily searched. We have chosen to list individuals' academic
-information first in the spreadsheet to encourage a focus on academic
-achievement rather than tokenization of marginalized identities.
-Currently the database lists individuals in order of self-nomination but
-future versions will be re-sorted based on name and/or academic field to
-varying the individuals who may receive more attention for simply being
-at the top of the list.
-
-The website provides an interface to the Google forms and spreadsheets
-with template pages for viewing the list, adding a name to the list, and
-finding additional resources. Importantly, our website creation tool is
-hosted for free by GitHub, which provides a free website for each GitHub
-organization. Basic tools and skills required to set up a Diversify site
-include knowledge of, or experience with, the version control tool git,
-the webtool GitHub, and a text editor. A tutorial in the
-DiversifyMicrobiology repository on GitHub provides links to these
-resources and instructions for adapting the tool to your own field.
-
-\subsection{Conclusion}\label{conclusion}
-
-To increase the retention of white women and HURMS in STEM, they must
-also be represented as experts. However, the invited speaker diversity
-at one department does not represent the diversity of trainees. There is
-a lack of research on invited speakers examining factors other than
-gender. To facilite the identification and recruitment of individuals in
-these historically under-served groups, we have built a tool to create
-self-nominated, field-specific lists.
-
-\subsection{Acknowledgements}\label{acknowledgements}
-
-We thank Drs. Beth Moore and Harry Mobley and the Department of
-Microbiology \& Immunology, University of Michigan for their input and
-financial support that enabled publication of our manuscript. We would
-also like to acknowledge Nick Lesniak and Dr.~Ariangela Kozick for their
-comments and suggestions.
-
-\subsection{Author Contributions}\label{author-contributions}
-
-A.K.H. collected the data, assigned demographics, analyzed the data, and
-created the website. R.M.P. created the Google lists, forms, and website
-content and the description of their maintenance. J.L. wrote the
-introduction and provided conceptual advice. A.K.H. and J.L facilited
-the policy change to the UM Department of Microbiology and Immunology.
-All authors contributed to preparing the final manuscript.
-
-\subsection{Code and data
-availability}\label{code-and-data-availability}
-
-The anonymized data, code for all analysis steps, and an Rmarkdown
-version of this manuscript is available at
-\url{https://github.com/akhagan/Hagan_SpeakerDiversity_XXXX_2019/}.
-Template and complete instructions for generating a field-specific
-Diversity website are available at
-\url{https://github.com/diversifymicrobiology/DiversifyMicrobiology.github.io/}.
-
-\newpage
-
+---
+geometry: margin=1.0in
+output:
+  pdf_document:
+    includes:
+      in_header: header.tex
+    keep_tex: yes
+---
 \begin{center}
@@
 \end{center}
-
-\begin{figure}
-\centering
-\includegraphics{Figure_1.png}
-\caption{\textbf{The demographics of invited speakers, hosting faculty,
-and trainees.} A) The proportion of women in each academic role. B) The
-proportion of each academic role represented by individuals that are
-Caucasian (left), Historically Underrepresented Minorities (HURM,
-center) or International (right). C-D)The percent of lectureships
-awarded to individuals that are C) Caucasian, HURM, International or D)
-Caucasian or Non-Caucasian by gender.}
-\end{figure}
-
-\newpage
-
-\subsection{References}\label{references}
-
-\hypertarget{refs}{}
-\hypertarget{ref-colloquy_2012}{}
-1. 2012. Colloquy on minority males in science, technology, engineering,
-and mathematics. National Academies Press.
-
-\hypertarget{ref-Coe2019}{}
-2. \textbf{Coe IR}, \textbf{Wiley R}, \textbf{Bekker L-G}. 2019.
-Organisational best practices towards gender equality in science and
-medicine. The Lancet \textbf{393}:587--593.
-doi:\href{https://doi.org/10.1016/s0140-6736(18)33188-x}{10.1016/s0140-6736(18)33188-x}.
-
-\hypertarget{ref-Eagly1984}{}
-3. \textbf{Eagly AH}, \textbf{Steffen VJ}. 1984. Gender stereotypes stem
-from the distribution of women and men into social roles. Journal of
-Personality and Social Psychology \textbf{46}:735--754.
-doi:\href{https://doi.org/10.1037/0022-3514.46.4.735}{10.1037/0022-3514.46.4.735}.
-
-\hypertarget{ref-Carter2018}{}
-4. \textbf{Carter AJ}, \textbf{Croft A}, \textbf{Lukas D},
-\textbf{Sandstrom GM}. 2018. Women's visibility in academic seminars:
-Women ask fewer questions than men. PLOS ONE \textbf{13}:e0202743.
-doi:\href{https://doi.org/10.1371/journal.pone.0202743}{10.1371/journal.pone.0202743}.
-
-\hypertarget{ref-kalejta_gender_2017}{}
-5. \textbf{Kalejta RF}, \textbf{Palmenberg AC}. 2017. Gender Parity
-Trends for Invited Speakers at Four Prominent Virology Conference
-Series. Journal of Virology \textbf{91}.
-doi:\href{https://doi.org/10.1128/JVI.00739-17}{10.1128/JVI.00739-17}.
-
-\hypertarget{ref-casadevall_presence_2014}{}
-6. \textbf{Casadevall A}, \textbf{Handelsman J}. 2014. The Presence of
-Female Conveners Correlates with a Higher Proportion of Female Speakers
-at Scientific Symposia. mBio \textbf{5}.
-doi:\href{https://doi.org/10.1128/mBio.00846-13}{10.1128/mBio.00846-13}.
-
-\hypertarget{ref-klein_speaking_2017}{}
-7. \textbf{Klein RS}, \textbf{Voskuhl R}, \textbf{Segal BM},
-\textbf{Dittel BN}, \textbf{Lane TE}, \textbf{Bethea JR}, \textbf{Carson
-MJ}, \textbf{Colton C}, \textbf{Rosi S}, \textbf{Anderson A},
-\textbf{Piccio L}, \textbf{Goverman JM}, \textbf{Benveniste EN},
-\textbf{Brown MA}, \textbf{Tiwari-Woodruff SK}, \textbf{Harris TH},
-\textbf{Cross AH}. 2017. Speaking out about gender imbalance in invited
-speakers improves diversity. Nature Immunology \textbf{18}:475--478.
-doi:\href{https://doi.org/10.1038/ni.3707}{10.1038/ni.3707}.
-
-\hypertarget{ref-R_software_2017}{}
-8. \textbf{R Core Team}. 2017. R: A language and environment for
-statistical computing. R Foundation for Statistical Computing, Vienna,
-Austria.
-
-\hypertarget{ref-wickham_tidyverse_2017}{}
-9. \textbf{Wickham H}. 2017. Tidyverse: Easily Install and Load the
-'Tidyverse'.
-
-\hypertarget{ref-cowplot}{}
-10. \textbf{Wilke CO}. 2019. Cowplot: Streamlined plot theme and plot
-annotations for 'ggplot2'.
-
-\hypertarget{ref-markdown}{}
-11. \textbf{Allaire J}, \textbf{Horner J}, \textbf{Xie Y}, \textbf{Marti
-V}, \textbf{Porte N}. 2018. Markdown: 'Markdown' rendering for r.
-
-\hypertarget{ref-rmd_book}{}
-12. \textbf{Xie Y}, \textbf{Allaire J}, \textbf{Grolemund G}. 2018. R
-markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida.
-
-\hypertarget{ref-rmd_rstudio}{}
-13. \textbf{Allaire J}, \textbf{Xie Y}, \textbf{McPherson J},
-\textbf{Luraschi J}, \textbf{Ushey K}, \textbf{Atkins A},
-\textbf{Wickham H}, \textbf{Cheng J}, \textbf{Chang W}, \textbf{Iannone
-R}. 2018. Rmarkdown: Dynamic documents for r.
-
-\hypertarget{ref-knitr_2014}{}
-14. \textbf{Xie Y}. 2014. Knitr: A comprehensive tool for reproducible
-research in R. \emph{In} Stodden, V, Leisch, F, Peng, RD (eds.),
-Implementing reproducible computational research. Chapman; Hall/CRC.
-
-\hypertarget{ref-knitr_2018}{}
-15. \textbf{Xie Y}. 2018. Knitr: A general-purpose package for dynamic
-report generation in r.
-
-\hypertarget{ref-lubridate}{}
-16. \textbf{Grolemund G}, \textbf{Wickham H}. 2011. Dates and times made
-easy with lubridate. Journal of Statistical Software \textbf{40}:1--25.
-
-\hypertarget{ref-readxl}{}
-17. \textbf{Wickham H}, \textbf{Bryan J}. 2018. Readxl: Read excel
-files.
-
-\hypertarget{ref-pdftools}{}
-18. \textbf{Ooms J}. 2019. Pdftools: Text extraction, rendering and
-converting of pdf documents.
-
-\hypertarget{ref-wickham_scales_2018}{}
-19. \textbf{Wickham H}. 2018. Scales: Scale Functions for Visualization.
-
-\hypertarget{ref-neuwirth_rcolorbrewer_2014}{}
-20. \textbf{Neuwirth E}. 2014. RColorBrewer: ColorBrewer Palettes.
-
-\hypertarget{ref-allagnat_gender_2017}{}
-21. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
-HJ}, \textbf{Hanafi S}, \textbf{Herbert R}, \textbf{Huggett S},
-\textbf{Tobin S}. 2017. Gender in the global research landscape.
-
-\hypertarget{ref-nsf_survey_2017}{}
-22. \textbf{Science and Engineering Statistics NC for}. 2017. Survey of
-Doctorate Recipients, Survey Year 2017. National Science Foundation,
-Alexandria, VA.
-
-\hypertarget{ref-nittrouer_gender_2018}{}
-23. \textbf{Nittrouer CL}, \textbf{Hebl MR}, \textbf{Ashburn-Nardo L},
-\textbf{Trump-Steele RCE}, \textbf{Lane DM}, \textbf{Valian V}. 2018.
-Gender disparities in colloquium speakers at top universities.
-Proceedings of the National Academy of Sciences \textbf{115}:104--108.
-doi:\href{https://doi.org/10.1073/pnas.1708414115}{10.1073/pnas.1708414115}.
-
-\hypertarget{ref-BlairLoy2017}{}
-24. \textbf{Blair-Loy M}, \textbf{Rogers L}, \textbf{Glaser D},
-\textbf{Wong Y}, \textbf{Abraham D}, \textbf{Cosman P}. 2017. Gender in
-engineering departments: Are there gender differences in interruptions
-of academic job talks? Social Sciences \textbf{6}:29.
-doi:\href{https://doi.org/10.3390/socsci6010029}{10.3390/socsci6010029}.
-
-\hypertarget{ref-noauthor_seeking_2013}{}
-25. 2013. Seeking Solutions: Maximizing American Talent by Advancing
-Women of Color in Academia: Summary of a Conference. National Academies
-Press, Washington, D.C.
-
-\hypertarget{ref-Firth1982}{}
-26. \textbf{Firth M}. 1982. Sex discrimination in job opportunities for
-women. Sex Roles \textbf{8}:891--901.
-doi:\href{https://doi.org/10.1007/bf00287858}{10.1007/bf00287858}.
-
-\hypertarget{ref-Correll2007}{}
-27. \textbf{Correll SJ}, \textbf{Benard S}, \textbf{Paik I}. 2007.
-Getting a job: Is there a motherhood penalty? American Journal of
-Sociology \textbf{112}:1297--1339.
-doi:\href{https://doi.org/10.1086/511799}{10.1086/511799}.
-
-\hypertarget{ref-Fuegen2004}{}
-28. \textbf{Fuegen K}, \textbf{Biernat M}, \textbf{Haines E},
-\textbf{Deaux K}. 2004. Mothers and fathers in the workplace: How gender
-and parental status influence judgments of job-related competence.
-Journal of Social Issues \textbf{60}:737--754.
-doi:\href{https://doi.org/10.1111/j.0022-4537.2004.00383.x}{10.1111/j.0022-4537.2004.00383.x}.
-
-\hypertarget{ref-Hwang2008}{}
-29. \textbf{Hwang W-C}, \textbf{Goto S}. 2008. The impact of perceived
-racial discrimination on the mental health of asian american and latino
-college students. Cultural Diversity and Ethnic Minority Psychology
-\textbf{14}:326--335.
-doi:\href{https://doi.org/10.1037/1099-9809.14.4.326}{10.1037/1099-9809.14.4.326}.
-
-\hypertarget{ref-Tran2019}{}
-30. \textbf{Tran VC}, \textbf{Lee J}, \textbf{Huang TJ}. 2019.
-Revisiting the asian second-generation advantage. Ethnic and Racial
-Studies \textbf{42}:2248--2269.
-doi:\href{https://doi.org/10.1080/01419870.2019.1579920}{10.1080/01419870.2019.1579920}.
-
-\hypertarget{ref-Fang2000}{}
-31. \textbf{Fang D}. 2000. Racial and ethnic disparities in faculty
-promotion in academic medicine. JAMA \textbf{284}:1085.
-doi:\href{https://doi.org/10.1001/jama.284.9.1085}{10.1001/jama.284.9.1085}.
-
-\hypertarget{ref-Gibbs2016}{}
-32. \textbf{Gibbs KD}, \textbf{Basson J}, \textbf{Xierali IM},
-\textbf{Broniatowski DA}. 2016. Decoupling of the minority PhD talent
-pool and assistant professor hiring in medical school basic science
-departments in the US. eLife \textbf{5}.
-doi:\href{https://doi.org/10.7554/elife.21393}{10.7554/elife.21393}.
-
-\hypertarget{ref-whittaker_retention_2015}{}
-33. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
-Acosta VG}. 2015. Retention of Underrepresented Minority Faculty:
-Strategic Initiatives for Institutional Value Proposition Based on
-Perspectives from a Range of Academic Institutions. Journal of
-undergraduate neuroscience education: JUNE: a publication of FUN,
-Faculty for Undergraduate Neuroscience \textbf{13}:A136--145.
-
-\hypertarget{ref-pololi_race_2010}{}
-34. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
-Disadvantage and Faculty Experiences in Academic Medicine. Journal of
-General Internal Medicine \textbf{25}:1363--1369.
-doi:\href{https://doi.org/10.1007/s11606-010-1478-7}{10.1007/s11606-010-1478-7}.
-
-\hypertarget{ref-hassouneh_experiences_2014}{}
-35. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
-\textbf{Junkins EP}, \textbf{Horton LL}. 2014. The experiences of
-underrepresented minority faculty in schools of medicine. Medical
-Education Online \textbf{19}:24768.
-doi:\href{https://doi.org/10.3402/meo.v19.24768}{10.3402/meo.v19.24768}.
-
-\hypertarget{ref-johnson_msphere_2019}{}
-36. \textbf{Johnson MDL}. 2019. mSphere of Influence: Hiring of
-Underrepresented Minority Assistant Professors in Medical School Basic
-Science Departments Has a Long Way To Go. mSphere \textbf{4}.
-doi:\href{https://doi.org/10.1128/mSphere.00599-19}{10.1128/mSphere.00599-19}.
-
-\end{document}

### 2019-10-01 submission/Table_1.tex
format for submission, fix typos

--- 2019-09-24 submission/manuscript.tex
@@
-\documentclass[10pt,]{article}
+\documentclass[]{article}
 \usepackage{lmodern}
@@
 \hypersetup{unicode=true,
-            pdftitle={Department Invited Speakers Do Not Reflect Trainee Diversity},
             pdfborder={0 0 0},
@@
 
-  \title{\textbf{Department Invited Speakers Do Not Reflect Trainee Diversity}}
-    \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
+  \title{}
+    \pretitle{\vspace{\droptitle}}
+  \posttitle{}
     \author{}
@@
 \begin{document}
-\maketitle
-
-\vspace{30mm}
-
-Running title: Invited Speaker Diversity Does Not Reflect Trainee
-Diversity
-
-\vspace{35mm}
-
-Ada K. Hagan, Ph.D.\({^1\dagger}\), Rebecca M. Pollet, Ph.D.\({^1}\),
-and Josie Libertucci, Ph.D.\({^2\dagger}\)
-
-\vspace{35mm}
-
-\(\dagger\) To whom correspondence should be addressed:
-\href{mailto:akhagan@umich.edu}{\nolinkurl{akhagan@umich.edu}} or
-\href{mailto:libertj@mcmaster.ca}{\nolinkurl{libertj@mcmaster.ca}}
-
-1. Department of Microbiology \& Immunology, University of Michigan, Ann
-Arbor, Michigan
-
-2. Department of Medicine, McMaster University, Hamilton, Ontario,
-Canada
-
-Figures: 1
-
-Tables: 1
-
-\newpage
-
-\subsection{Conflicts of Interest}\label{conflicts-of-interest}
-
-\vspace{40mm}
-
-All authors affirm that there are no conflicts of interest.
-
-\newpage
-
-\linenumbers
-
-\subsection{Abstract}\label{abstract}
-
-Social role theory emphasizes the importance of ``like'' representation
-to improve feelings of self-efficacy and belonging. This is an issue for
-trainees in the biological sciences who are either white women or
-underrepresented minorities, since there is a lack of faculty who look
-like them in biology academic settings. One way to improve
-representation is through invited speaker series. In this persepective,
-we compare the diversity of invited speakers at one microbiology and
-immunology department to the diversity of their post-Baccalaurate
-trainees. We find that trainees are not proportionally represented by
-the invited speakers and provide policy suggestions and tools to address
-this issue.
-
-\subsection{Keywords}\label{keywords}
-
-inclusion, diversity, invited speakers, academia, graduate programs
-
-\newpage
-
-\subsection{Background}\label{background}
-
-Long-standing systemic bias, sexism, and racism have contributed to the
-underrepresentation of many racial and ethnic groups, as well as women,
-in science, technology, engineering, and math (STEM) fields (NIH 2015
-report, Measuring DEI 2016, (1)). Organization climate and culture that
-supports inclusion of all individuals is essential to support the
-retention of historically underrepresented minorities (HURM) in the
-U.S., as well as non-Caucasian individuals, and women in STEM fields
-(Schneider, 2013). Inclusive organization culture will not suffice in
-retaining HURM, non-Caucasian individuals, and women without
-organization policy changes that support their values and goals (2).
-
-A long-standing issue within STEM fields, specifically within academia,
-has been a lack of diverse representation of scientists for trainees
-(graduate students and postdoctoral fellows). In order to maintain
-retention of HURM, non-Caucasian individuals, and women in STEM fields,
-it is important for trainees to have visual representations of
-themselves as scientists. The importance of representation in retaining
-a diverse group of individuals in STEM fields is supported by social
-role theory (3). Individuals tend to make inferences about
-characteristics that are needed to be successful in a given role by
-examining individuals that most occupy that role (3, 4). Therefore,
-trainees who do not see representation of themselves in senior
-scientific positions, or in this case as senior faculty members, may
-decide that they do not possess the characteristics that are required to
-succeed. In an attempt to make science a more inclusive environment,
-many individuals have attempted to address this issue by promoting the
-inclusion of more women speakers at conferences (5--7). However, no
-study to date has addressed invited speaker seminar series diversity
-within their own institution.
-
-Within the Department of Microbiology and Immunology at the University
-of Michigan (Ann Arbor, MI, USA), each year from September to June,
-faculty members have the opportunity to invite scientists from other
-institutions to give a one-hour seminar in which all department members
-attend. The invited seminar speaker also has the opportunity to meet
-with current department faculty members and trainees. Scientists who are
-invited to give seminars are widely regarded as successful and the top
-in their field. Thus, if trainees are constantly being exposed to ``the
-top scientist in their field'', according to social role theory, it is
-imperative that the selected seminar speakers represent a diverse group
-of individuals.
-
-In this study, we examine and compare the proportion of HURM,
-non-Caucasian/non-HURM, and women invited speakers to white males in the
-Department of Microbiology and Immunology. Additionally, we compare
-invited-speaker demographics to the current trainee demographics as a
-means to gauge if trainee demographics are being represented accordingly
-throughout the seminar series. Following our investigation, we proposed
-a policy change to the Department of Microbiology and Immunology in how
-invited speakers are selected as a means to promote inclusion in our
-department and reduce stereotype threat, microaggressions, and
-unconscious bias. In order to facilitate inviting a more diverse group
-of scientists, we developed a set of resources that allow scientists,
-within the field of microbiology, to self-identify as an HURM,
-non-Caucasian/non-HURM, or a woman. These resources will promote
-inclusion and diversity by providing greater representation of all
-scientists and will provide hosts an opportunity to invite a more
-diverse group of scientists.
-
-\subsection{Methods}\label{methods}
-
-Each academic year, each faculty member in the Department of
-Microbiology and Immunology at the University of Michigan has the
-opportunity to invite one speaker per year for a weekly seminar series.
-Some of these seminar slots are dedicated to named lectureships, which
-are decided by committee, and three trainee-invited speakers. We
-analyzed the demographics of invited speakers and faculty hosts for five
-academic years (Fall 2014 - Spring 2019), and compared them to the
-current trainees when the data were analyzed (Spring 2019). Each speaker
-was only counted once and those listed as departmental faculty members
-or as a ``host'' at any point could not also be considered ``invited
-speakers''. The list of faculty hosts was used as a proxy for faculty
-demographics since as hosts, these faculty members are visible
-representatives of the department. The trainees were identified using
-from departmental email lists that included masters students, doctoral
-students, and post-doctoral fellows.
-
-This is a retrospective study, thus speakers were not asked for their
-identities at the time of visit. Instead we hand-coded proxy
-demographics using personal knowledge, photos, and CVs. The presenting
-gender of each individual was assigned using a binary system
-(man/woman). Due to the low number of individuals in the study,
-race/ethnicity demographics were split in three groups: Caucasian,
-Historically Under-represented Minority (HURM), and
-Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibilty.
-Caucasian was assigned using the current U.S. Census definition where
-those of Middle Eastern, European, and Russian descent are included.
-HURM individuals were restricted to those with African-American,
-Indigenous, Alaskan/Hawaian Native, Latinx and/or Hispanic heritage. All
-others were placed into the NCNH group. We recognize that our proxy
-demographics are a limitation of the analysis and want to acknowledge
-that biological sex (male/female) is not always equivalent to the gender
-that an individual presents as (man/woman), which is also distinct from
-the gender(s) that an individual self-identifies as. We also want to
-acknowledge that there are many other identities that are not captured
-in this limited analysis.
-
-Data were analyzed and figures generated in R Statisical Software, using
-relevant packages (8--20).
-
-\subsection{Results}\label{results}
-
-To understand the representation of women, we compared the proportion of
-women in each academic role. At the trainee level, more than half of
-students and postdoctoral fellows were women. That dropped to 46.77\% of
-faculty hosts and 38.73\% of the invited speakers (Fig. 1A). Of 27
-lectureships over the five year period, 37.04\% were awarded to women.
-The proportion of women as faculty hosts and speakers is equivalent to
-global estimates that 40\% of microbiologists are women, with a slightly
-lower representation of women in lectureships (21).
-
-Our analysis identified an over-representation of Caucasian individuals
-as hosting faculty and invited speakers (80\% each), relative to the
-proportion of Caucasian trainees, which was 55\% (Fig. 1B). We also
-observed declines in the representation of HURM and NCNH faculty and
-speakers relative to the trainees (Fig 1B). HURM trainees made up 11\%
-of the department, on track with the 11\% of microbiology and immunology
-doctorates awarded in 2017 (22). However, only 8.5\% of invited
-speakers, and none of the hosting faculty, were HURM scientists. NCNH
-trainees were 34\% of department students and postdocs (22\% of
-microbiology and immunology doctorates in 2017), but only 19\% of
-hosting faculty and 10.5\% of invited speakers (22).
-
-The more prestigous invited speaker lectureships were also dominated by
-Caucasian scientists, who comprised 81.48\% of those awarded (Fig. 1C).
-HURM and NCNH scientists were awarded 3 and 2 lectureships,
-respectively. Because the intersection of identities can compound biases
-and outcomes, we further examined the lectureships by gender and
-race/ethnicity status. Caucasian men and women accounted for 44.44\% and
-37.04\% of the lectureships, respectively. Just 18.52\% of lectureships
-were held by non-Caucasian men while none were held by non-Caucasian
-women (Fig. 1D).
-
-\subsection{Discussion}\label{discussion}
-
-{[}Add paragraph summarizing findings {]} According to social role
-theory, this department is not adequately serving their non-Caucasian
-trainees.
-
-Several papers have investigated the representation of women at
-scientific conferences, however, we have only identified one that
-focused on invited speakers at universities (23). In their study,
-Nittrouer et al, examined 3,652 talks at 50 U.S. institutions in 2013 -
-2014 and found that women faculty are less likely to be invited
-speakers, despite similar acceptance rates. These results suggest that
-women faculty are less often invited as speakers. We have not been able
-to identify any other publications examining scientific speaker
-diversity beyond gender. This seems to be the first. This is concerning
-since conclusions drawn from gender-based studies are often framed, and
-considered, to be applicable to other marginalized groups (e.g., HURM).
-This is a flawed assumption. While there is no doubt some overlap, each
-group remains marginalized due to a unique complex set of factors that
-cannot always be solved by gender-based solutions. US-serving
-institutions, such as the University of Michigan have a particular
-responsibility to the historically suppressed populations included in
-our definition of HURMs. We therefore implore US institutions to apply
-this framing to their discussions and research.
-
-Departments have different processes and criteria for selecting invited
-speakers, but it is a matter of pride to bring the best scientists
-possible. It may be that the definition of ``best'' poses a problem to
-women, who need three-times as many publications as their men colleges
-to be considered equally competent (24), and those that identify as HURM
-and Asian, who report having to work harder than white men to be
-perceived as legitimate scholars (25). Some departments only invite
-tenured faculty, which severely limits the number of potential speakers
-who are white women or non-Caucasian. Yet, another scenario is that
-pre-tenure faculty members invite prestigious, tenured faculty in their
-field to network and secure letters for their own tenure package. The
-increased burden of white women and non-Caucasian scientists to prove
-competency decreases their likelihood to be considered for either tenure
-or as possible source of tenure letters.
-
-Each underrepresented group in our cohort faces a complex set of
-barriers to achieving faculty status. For instance, the decision to
-invite a woman may also be negatively impacted by assumptions about
-competency and dedication. The dedication of women who have children to
-their work is perceived to be less than that of their colleagues, i.e.,
-men who also have children (26--28). The perceived prioritization and
-commitments of women to family over work may cause faculty to doubt
-their acceptance of a speaking invitation, despite the prestigious
-nature of these invitations and evidence that men and women accept at
-similar rates ({\textbf{???}}, 23). As a result, the faculty member
-invites a different colleague who they feel is more likely to agree (and
-is a man). Another large portion of our sample were the NCNH cohort, who
-are predominately Asian/Asian American individuals. Although Asian
-scientists are well-represented in the US scientific workforce, they
-face significant bias and barriers to inclusion in society and academia
-(29, 30). For instance, despite the higher employment rate of Asian
-scientists, they were not well-represented in the more prestigious
-lectureships.
-
-While HURM and NCNH share some experiences, differences including
-varying rates of hiring and tenure promotion mean unique considerations
-are important for inclusion of each group (31). For instance, a major
-barrier to inclusion of HURM faculty at similar proportions to HURM
-trainees is the low transition rate of scientists from HURM backgrounds
-to faculty positions and the associated low proportion of HURM faculty
-(32). The proportion of HURM faculty at the Assistant and Associate
-Professor level is currently higher than at Full Professor so it will be
-difficult to increase speaker diversity if early-career researchers are
-not being considered (33). Increased performance expectations and
-patterns of exclusions are consistent themes in studies characterizing
-the HURM faculty experience (34, 35). Therefore, inclusion of HURM
-faculty in seminar series is likely essential to increasing the number
-of HURM Associate and Full Professors. Even when HURM speaker rates
-match the proportion of HURM faculty employment, HURM trainees will be
-represented at a significantly higher proportion. Inclusion of HURM
-faculty in these seminarseries is just one aspect of larger
-institutional change that is needed (36).
-
-\subsection{Instituting policy change within the Department of
-Microbiology and
-Immunology}\label{instituting-policy-change-within-the-department-of-microbiology-and-immunology}
-
-In an attempt to promote inclusion within the Dept. M\&I these data were
-presented to faculty members and the dept chair (Harry Mobley). Since,
-trainee demographics were not represented within seminar speaker
-demographics over the past 5 years, we proposed a policy change as to
-how seminar speakers were being invited. This policy change included
-switching from PI invited to lab invited in an attempt to allow trainees
-to choose a speaker that best represented themselves.
-
-Implict biases that affect perceptions of marginalized groups are the
-primary issue, but we must acknowledge that it is not always possible to
-identify members of historically under-served communities. For instance,
-after data analysis, we learned that at least one speaker in our data
-set should have been categorized as a HURM instead of Caucasian, but it
-wasn't readily apparent from their internet presence or CV. This
-limitation makes two important points: that percieved identity often
-plays a larger role than self-identification, and that we need better
-tools to identify members of marginalized groups. So in addition to our
-policy change, we also created resources that allow scientists to
-self-identify and provide host faculty with more diverse choices.
-
-\subsection{Building Diversify}\label{building-diversify}
-
-To help address this issue, we make some suggestions (Table 1) and have
-developed a resource to identify scientists who are members of
-marginalized and/or historically under-served groups. Motivated by a
-lack of such resources and inspired by similar resources--DiversifyEEB
-and DiversifyChemistry--we created DiversifyMicrobiology and
-DiversifyImmunology. These resources are a tool for symposium
-organziers, award committees, search committees and other scientists to
-identify individuals to diversify their pools. Additionally, we have
-built these as a tool for use by other fields and organizations to
-create their own lists. Since these lists are compiled by
-self-nomination, we can ensure that only scientists comfortable
-revealing their marginalized identities are included.
-
-The self-nomination form is a Google Form with entries logged in a
-private Google Sheet. This form is embedded within the website and can
-be linked to directly. The use of a Google Forms allows us to maintain
-this database at no cost and gives us the flexibility to add questions
-or change response options without disrupting previous responses.
-Entries are logged in a private spreadsheet so that entries can be
-screened before being added to the public database. This screening
-includes two steps: confirming that each person is listed in the
-database only once and that any submitted website is a personal,
-professional website. If both criteria are met, a new entry is added to
-the public database spreadsheet. If a person is already listed in the
-database, their information is updated to the most recent submission.
-
-This public spreadsheet is embedded in the website and can be open
-separately as a locked (uneditable) Google Sheet, allowing the list to
-be easily searched. We have chosen to list individuals' academic
-information first in the spreadsheet to encourage a focus on academic
-achievement rather than tokenization of marginalized identities.
-Currently the database lists individuals in order of self-nomination but
-future versions will be re-sorted based on name and/or academic field to
-varying the individuals who may receive more attention for simply being
-at the top of the list.
-
-The website provides an interface to the Google forms and spreadsheets
-with template pages for viewing the list, adding a name to the list, and
-finding additional resources. Importantly, our website creation tool is
-hosted for free by GitHub, which provides a free website for each GitHub
-organization. Basic tools and skills required to set up a Diversify site
-include knowledge of, or experience with, the version control tool git,
-the webtool GitHub, and a text editor. A tutorial in the
-DiversifyMicrobiology repository on GitHub provides links to these
-resources and instructions for adapting the tool to your own field.
-
-\subsection{Conclusion}\label{conclusion}
-
-To increase the retention of white women and HURMS in STEM, they must
-also be represented as experts. However, the invited speaker diversity
-at one department does not represent the diversity of trainees. There is
-a lack of research on invited speakers examining factors other than
-gender. To facilite the identification and recruitment of individuals in
-these historically under-served groups, we have built a tool to create
-self-nominated, field-specific lists.
-
-\subsection{Acknowledgements}\label{acknowledgements}
-
-We thank Drs. Beth Moore and Harry Mobley and the Department of
-Microbiology \& Immunology, University of Michigan for their input and
-financial support that enabled publication of our manuscript. We would
-also like to acknowledge Nick Lesniak and Dr.~Ariangela Kozick for their
-comments and suggestions.
-
-\subsection{Author Contributions}\label{author-contributions}
-
-A.K.H. collected the data, assigned demographics, analyzed the data, and
-created the website. R.M.P. created the Google lists, forms, and website
-content and the description of their maintenance. J.L. wrote the
-introduction and provided conceptual advice. A.K.H. and J.L facilited
-the policy change to the UM Department of Microbiology and Immunology.
-All authors contributed to preparing the final manuscript.
-
-\subsection{Code and data
-availability}\label{code-and-data-availability}
-
-The anonymized data, code for all analysis steps, and an Rmarkdown
-version of this manuscript is available at
-\url{https://github.com/akhagan/Hagan_SpeakerDiversity_XXXX_2019/}.
-Template and complete instructions for generating a field-specific
-Diversity website are available at
-\url{https://github.com/diversifymicrobiology/DiversifyMicrobiology.github.io/}.
-
-\newpage
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{Figure_1.png}
-\caption{\textbf{The demographics of invited speakers, hosting faculty,
-and trainees.} A) The proportion of women in each academic role. B) The
-proportion of each academic role represented by individuals that are
-Caucasian (left), Historically Underrepresented Minorities (HURM,
-center) or International (right). C-D)The percent of lectureships
-awarded to individuals that are C) Caucasian, HURM, International or D)
-Caucasian or Non-Caucasian by gender.}
-\end{figure}
-
-\newpage
-
-\subsection{References}\label{references}
-
-\hypertarget{refs}{}
-\hypertarget{ref-colloquy_2012}{}
-1. 2012. Colloquy on minority males in science, technology, engineering,
-and mathematics. National Academies Press.
-
-\hypertarget{ref-Coe2019}{}
-2. \textbf{Coe IR}, \textbf{Wiley R}, \textbf{Bekker L-G}. 2019.
-Organisational best practices towards gender equality in science and
-medicine. The Lancet \textbf{393}:587--593.
-doi:\href{https://doi.org/10.1016/s0140-6736(18)33188-x}{10.1016/s0140-6736(18)33188-x}.
-
-\hypertarget{ref-Eagly1984}{}
-3. \textbf{Eagly AH}, \textbf{Steffen VJ}. 1984. Gender stereotypes stem
-from the distribution of women and men into social roles. Journal of
-Personality and Social Psychology \textbf{46}:735--754.
-doi:\href{https://doi.org/10.1037/0022-3514.46.4.735}{10.1037/0022-3514.46.4.735}.
-
-\hypertarget{ref-Carter2018}{}
-4. \textbf{Carter AJ}, \textbf{Croft A}, \textbf{Lukas D},
-\textbf{Sandstrom GM}. 2018. Women's visibility in academic seminars:
-Women ask fewer questions than men. PLOS ONE \textbf{13}:e0202743.
-doi:\href{https://doi.org/10.1371/journal.pone.0202743}{10.1371/journal.pone.0202743}.
-
-\hypertarget{ref-kalejta_gender_2017}{}
-5. \textbf{Kalejta RF}, \textbf{Palmenberg AC}. 2017. Gender Parity
-Trends for Invited Speakers at Four Prominent Virology Conference
-Series. Journal of Virology \textbf{91}.
-doi:\href{https://doi.org/10.1128/JVI.00739-17}{10.1128/JVI.00739-17}.
-
-\hypertarget{ref-casadevall_presence_2014}{}
-6. \textbf{Casadevall A}, \textbf{Handelsman J}. 2014. The Presence of
-Female Conveners Correlates with a Higher Proportion of Female Speakers
-at Scientific Symposia. mBio \textbf{5}.
-doi:\href{https://doi.org/10.1128/mBio.00846-13}{10.1128/mBio.00846-13}.
-
-\hypertarget{ref-klein_speaking_2017}{}
-7. \textbf{Klein RS}, \textbf{Voskuhl R}, \textbf{Segal BM},
-\textbf{Dittel BN}, \textbf{Lane TE}, \textbf{Bethea JR}, \textbf{Carson
-MJ}, \textbf{Colton C}, \textbf{Rosi S}, \textbf{Anderson A},
-\textbf{Piccio L}, \textbf{Goverman JM}, \textbf{Benveniste EN},
-\textbf{Brown MA}, \textbf{Tiwari-Woodruff SK}, \textbf{Harris TH},
-\textbf{Cross AH}. 2017. Speaking out about gender imbalance in invited
-speakers improves diversity. Nature Immunology \textbf{18}:475--478.
-doi:\href{https://doi.org/10.1038/ni.3707}{10.1038/ni.3707}.
-
-\hypertarget{ref-R_software_2017}{}
-8. \textbf{R Core Team}. 2017. R: A language and environment for
-statistical computing. R Foundation for Statistical Computing, Vienna,
-Austria.
-
-\hypertarget{ref-wickham_tidyverse_2017}{}
-9. \textbf{Wickham H}. 2017. Tidyverse: Easily Install and Load the
-'Tidyverse'.
-
-\hypertarget{ref-cowplot}{}
-10. \textbf{Wilke CO}. 2019. Cowplot: Streamlined plot theme and plot
-annotations for 'ggplot2'.
-
-\hypertarget{ref-markdown}{}
-11. \textbf{Allaire J}, \textbf{Horner J}, \textbf{Xie Y}, \textbf{Marti
-V}, \textbf{Porte N}. 2018. Markdown: 'Markdown' rendering for r.
-
-\hypertarget{ref-rmd_book}{}
-12. \textbf{Xie Y}, \textbf{Allaire J}, \textbf{Grolemund G}. 2018. R
-markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida.
-
-\hypertarget{ref-rmd_rstudio}{}
-13. \textbf{Allaire J}, \textbf{Xie Y}, \textbf{McPherson J},
-\textbf{Luraschi J}, \textbf{Ushey K}, \textbf{Atkins A},
-\textbf{Wickham H}, \textbf{Cheng J}, \textbf{Chang W}, \textbf{Iannone
-R}. 2018. Rmarkdown: Dynamic documents for r.
-
-\hypertarget{ref-knitr_2014}{}
-14. \textbf{Xie Y}. 2014. Knitr: A comprehensive tool for reproducible
-research in R. \emph{In} Stodden, V, Leisch, F, Peng, RD (eds.),
-Implementing reproducible computational research. Chapman; Hall/CRC.
-
-\hypertarget{ref-knitr_2018}{}
-15. \textbf{Xie Y}. 2018. Knitr: A general-purpose package for dynamic
-report generation in r.
-
-\hypertarget{ref-lubridate}{}
-16. \textbf{Grolemund G}, \textbf{Wickham H}. 2011. Dates and times made
-easy with lubridate. Journal of Statistical Software \textbf{40}:1--25.
-
-\hypertarget{ref-readxl}{}
-17. \textbf{Wickham H}, \textbf{Bryan J}. 2018. Readxl: Read excel
-files.
-
-\hypertarget{ref-pdftools}{}
-18. \textbf{Ooms J}. 2019. Pdftools: Text extraction, rendering and
-converting of pdf documents.
-
-\hypertarget{ref-wickham_scales_2018}{}
-19. \textbf{Wickham H}. 2018. Scales: Scale Functions for Visualization.
-
-\hypertarget{ref-neuwirth_rcolorbrewer_2014}{}
-20. \textbf{Neuwirth E}. 2014. RColorBrewer: ColorBrewer Palettes.
-
-\hypertarget{ref-allagnat_gender_2017}{}
-21. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
-HJ}, \textbf{Hanafi S}, \textbf{Herbert R}, \textbf{Huggett S},
-\textbf{Tobin S}. 2017. Gender in the global research landscape.
-
-\hypertarget{ref-nsf_survey_2017}{}
-22. \textbf{Science and Engineering Statistics NC for}. 2017. Survey of
-Doctorate Recipients, Survey Year 2017. National Science Foundation,
-Alexandria, VA.
-
-\hypertarget{ref-nittrouer_gender_2018}{}
-23. \textbf{Nittrouer CL}, \textbf{Hebl MR}, \textbf{Ashburn-Nardo L},
-\textbf{Trump-Steele RCE}, \textbf{Lane DM}, \textbf{Valian V}. 2018.
-Gender disparities in colloquium speakers at top universities.
-Proceedings of the National Academy of Sciences \textbf{115}:104--108.
-doi:\href{https://doi.org/10.1073/pnas.1708414115}{10.1073/pnas.1708414115}.
-
-\hypertarget{ref-BlairLoy2017}{}
-24. \textbf{Blair-Loy M}, \textbf{Rogers L}, \textbf{Glaser D},
-\textbf{Wong Y}, \textbf{Abraham D}, \textbf{Cosman P}. 2017. Gender in
-engineering departments: Are there gender differences in interruptions
-of academic job talks? Social Sciences \textbf{6}:29.
-doi:\href{https://doi.org/10.3390/socsci6010029}{10.3390/socsci6010029}.
-
-\hypertarget{ref-noauthor_seeking_2013}{}
-25. 2013. Seeking Solutions: Maximizing American Talent by Advancing
-Women of Color in Academia: Summary of a Conference. National Academies
-Press, Washington, D.C.
-
-\hypertarget{ref-Firth1982}{}
-26. \textbf{Firth M}. 1982. Sex discrimination in job opportunities for
-women. Sex Roles \textbf{8}:891--901.
-doi:\href{https://doi.org/10.1007/bf00287858}{10.1007/bf00287858}.
-
-\hypertarget{ref-Correll2007}{}
-27. \textbf{Correll SJ}, \textbf{Benard S}, \textbf{Paik I}. 2007.
-Getting a job: Is there a motherhood penalty? American Journal of
-Sociology \textbf{112}:1297--1339.
-doi:\href{https://doi.org/10.1086/511799}{10.1086/511799}.
-
-\hypertarget{ref-Fuegen2004}{}
-28. \textbf{Fuegen K}, \textbf{Biernat M}, \textbf{Haines E},
-\textbf{Deaux K}. 2004. Mothers and fathers in the workplace: How gender
-and parental status influence judgments of job-related competence.
-Journal of Social Issues \textbf{60}:737--754.
-doi:\href{https://doi.org/10.1111/j.0022-4537.2004.00383.x}{10.1111/j.0022-4537.2004.00383.x}.
-
-\hypertarget{ref-Hwang2008}{}
-29. \textbf{Hwang W-C}, \textbf{Goto S}. 2008. The impact of perceived
-racial discrimination on the mental health of asian american and latino
-college students. Cultural Diversity and Ethnic Minority Psychology
-\textbf{14}:326--335.
-doi:\href{https://doi.org/10.1037/1099-9809.14.4.326}{10.1037/1099-9809.14.4.326}.
-
-\hypertarget{ref-Tran2019}{}
-30. \textbf{Tran VC}, \textbf{Lee J}, \textbf{Huang TJ}. 2019.
-Revisiting the asian second-generation advantage. Ethnic and Racial
-Studies \textbf{42}:2248--2269.
-doi:\href{https://doi.org/10.1080/01419870.2019.1579920}{10.1080/01419870.2019.1579920}.
-
-\hypertarget{ref-Fang2000}{}
-31. \textbf{Fang D}. 2000. Racial and ethnic disparities in faculty
-promotion in academic medicine. JAMA \textbf{284}:1085.
-doi:\href{https://doi.org/10.1001/jama.284.9.1085}{10.1001/jama.284.9.1085}.
-
-\hypertarget{ref-Gibbs2016}{}
-32. \textbf{Gibbs KD}, \textbf{Basson J}, \textbf{Xierali IM},
-\textbf{Broniatowski DA}. 2016. Decoupling of the minority PhD talent
-pool and assistant professor hiring in medical school basic science
-departments in the US. eLife \textbf{5}.
-doi:\href{https://doi.org/10.7554/elife.21393}{10.7554/elife.21393}.
-
-\hypertarget{ref-whittaker_retention_2015}{}
-33. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
-Acosta VG}. 2015. Retention of Underrepresented Minority Faculty:
-Strategic Initiatives for Institutional Value Proposition Based on
-Perspectives from a Range of Academic Institutions. Journal of
-undergraduate neuroscience education: JUNE: a publication of FUN,
-Faculty for Undergraduate Neuroscience \textbf{13}:A136--145.
-
-\hypertarget{ref-pololi_race_2010}{}
-34. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
-Disadvantage and Faculty Experiences in Academic Medicine. Journal of
-General Internal Medicine \textbf{25}:1363--1369.
-doi:\href{https://doi.org/10.1007/s11606-010-1478-7}{10.1007/s11606-010-1478-7}.
-
-\hypertarget{ref-hassouneh_experiences_2014}{}
-35. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
-\textbf{Junkins EP}, \textbf{Horton LL}. 2014. The experiences of
-underrepresented minority faculty in schools of medicine. Medical
-Education Online \textbf{19}:24768.
-doi:\href{https://doi.org/10.3402/meo.v19.24768}{10.3402/meo.v19.24768}.
-
-\hypertarget{ref-johnson_msphere_2019}{}
-36. \textbf{Johnson MDL}. 2019. mSphere of Influence: Hiring of
-Underrepresented Minority Assistant Professors in Medical School Basic
-Science Departments Has a Long Way To Go. mSphere \textbf{4}.
-doi:\href{https://doi.org/10.1128/mSphere.00599-19}{10.1128/mSphere.00599-19}.
-
 \end{document}

### 2020-02-05 submission/Table_1.Rmd
add additional suggestions & fix formatting

@@
 \begin{center}
-\captionof{table}{List of suggestions and resources to increase invited speaker diversity.}
+\captionof{table}{Suggestions and resources to increase invited speaker diversity.}
 \small
-\begin{tabular}{|l|l|l|}
+\centering
+\begin{tabular}{>{\centering\arraybackslash}m{4cm}|>{\centering\arraybackslash}m{7cm}|>{}m{5cm}}
+
 \hline
@@
 \rowcolor{lightgray}
-\textbf{Suggestion} & \textbf{Description} & \textbf{Resource} \\ \hline
+\textbf{Suggestion} & \textbf{Description} & \textbf{Resource} \\\hline
 
-Lab-invited speakers & \makecell[l]{Faculty members can request \\suggestions from trainees} & \\ \hline
+Trainee-invited speakers & Request suggestions from trainees, increase number of trainee-group-invited speakers & \\\hline
 
-Use a list & \makecell[l]{Many lists of scientists from \\under-represented and under-served \\groups are available} &  \makecell[l]{https://DiversifyMicrobiology.\\github.io/resources}\\ \hline
+Use a list & Lists of scientists from under-represented and under-served groups are available in several fields &  https://DiversifyMicrobiology .github.io/resources \\\hline
 
-Create a list & \makecell[l]{Use the GitHub template \\ create a self-nomination list and \\resource for your field} & \makecell[l]{https://github.com/diversifymicrobiology/\\DiversifyMicrobiology.github.io} \\ \hline
+Create a list & Use the GitHub template to create a self-nomination list and resource for your field & https://github.com /diversifymicrobiology /DiversifyMicrobiology.github.io \\\hline
 
-Highlight the journey & \makecell[l]{Invite all speakers to spend \\a few moments describing their \\personal science journey} & \\ \hline
+Use resources from professional societies & Many scientific societies have a committee focused on serving individuals from under-represented and underserved backgrounds.
+Other societies (e.g., SACNAS) are dedicated to these issues.
+& SACNAS, ABRCMS, AISES, ASM Subcommittee on Minority Education \\\hline
+
+Think outside your sub-discipline & Speakers may introduce you to a technique that is not used in your sub-discipline & \\\hline
+
+Consider scientists outside research-focused universities & Scientists from industry, teaching-focused institutions, and non-profit orgs have different approaches to their research & \\\hline
+
+Communicate invitation expectations & Unit leadership should explicitly communicate expectations about who is invited to speak and the desired atmosphere & \\\hline
+
+Encourage trainees to engage & \makecell[l]{When a talk is over, ensure that \\trainees are the first to ask questions} & \\\hline
+
+Foster an inclusive atmosphere & Consider the identities of individuals the speaker is meeting with. Ask if the speaker would like to meet a particular student group & \\\hline
+
+Highlight the journey & Invite speakers to spend a few moments describing their personal science journey & \\\hline
 

### 2020-02-05 submission/Table_1.tex
add additional suggestions & fix formatting

@@
 \small
-\begin{tabular}{|l|l|l|}
+\centering
+\begin{tabular}{>{\centering\arraybackslash}m{4cm}|>{\centering\arraybackslash}m{7cm}|>{}m{5cm}}
+
 \hline

### 2020-02-05 submission/manuscript.Rmd
format for submission, fix typos
add revisions from google doc

@@
 ---
-title: '**Policy should change to improve invited speaker diversity and reflect trainee diversity**'
+title: '**Suggestions to improve invited speaker diversity and reflect trainee diversity**'
 csl: mbio.csl
@@
 
-Ada K. Hagan, Ph.D.${^1\dagger}$, Rebecca M. Pollet, Ph.D.${^1}$, and Josie Libertucci, Ph.D.${^2}$
+Ada K. Hagan, Ph.D.$^{1,2\dagger}$, Rebecca M. Pollet, Ph.D.${^2}$, and Josie Libertucci, Ph.D.${^3}$
 
@@
 
-$\dagger$ To whom correspondence should be addressed: akhagan@umich.edu
+$\dagger$ To whom correspondence should be addressed: akhagan@alliancescc.com
 
-1\. Department of Microbiology & Immunology, University of Michigan, Ann Arbor, Michigan
+1\. Alliance SciComm & Consulting, Linden, Michigan
 
-2\. Farncombe Family Digestive Health Research Institute, Department of Medicine, McMaster University, Hamilton, Ontario, Canada
+2\. Department of Microbiology & Immunology, University of Michigan, Ann Arbor, Michigan
+
+3\. Farncombe Family Digestive Health Research Institute, Department of Medicine, McMaster University, Hamilton, Ontario, Canada
 
@@
 
-## Conflicts of Interest
+## Conflict of Interest Notification Page
 
@@
 
-The biomedical sciences have a problem retaining white women and underrepresented minorities in academia.
+The biomedical sciences have a problem retaining women and underrepresented minorities in academia.
 Despite increases in the representation of these groups in faculty candidate pools, they are still underrepresented at the faculty level, particularly at the Full Professor level.
@@
 Policy changes are needed to support inclusion of all individuals, particularly in the biomedical sciences[@Coe2019].
-To increase retention of historically under-represented minorities (HURM), non-Caucasian/non-HURM (NCNH) individuals, and white women in biomedical fields, it is important for trainees to have visual representations of themselves as scientists.
+To increase retention of historically under-represented minorities (HURM), non-Caucasian/non-HURM (NCNH) individuals, and Caucasian women in biomedical fields, it is important for trainees to have visual representations of themselves as scientists.
 The importance of representation in retaining a diverse group of individuals in STEM fields is supported by social role theory [@Eagly1984].
@@
 
-In this study, we examine and compare the proportion of HURM, NCNH, and women invited speakers to white men in the Department of Microbiology and Immunology at the University of Michigan.
+In this study, we examine and compare the proportion of HURM, NCNH, and women invited speakers to Caucasian men in the Department of Microbiology and Immunology at the University of Michigan.
 Additionally, we compare invited-speaker demographics to the current trainee demographics as a means to gauge if trainee demographics are being represented accordingly throughout the seminar series.
 Following our investigation, we proposed a policy change to the Department of Microbiology and Immunology in how invited speakers are selected as a means to promote inclusion in our department and reduce unconscious bias.
-In order to facilitate inviting a more diverse group of scientists, we developed a set of resources that allow scientists, within the fields of microbiology and immunology, to self-identify as having an under-represented or under-served identity including: HURM, non-Caucasian/non-HURM, or a white woman.
+In order to facilitate inviting a more diverse group of scientists, we developed a set of resources that allow scientists, within the fields of microbiology and immunology, to self-identify as having an under-represented or under-served identity including: HURM, non-Caucasian/non-HURM, or a Caucasian woman.
 These resources will promote inclusion and diversity by providing greater representation of all scientists and will provide hosts an opportunity to invite a more diverse group of scientists.
@@
 We analyzed the demographics of invited speakers and faculty hosts for five academic years (Fall 2014 - Spring 2019), and compared them to the current trainees when the data were analyzed (Spring 2019).
-Each speaker was only counted once and those listed as departmental faculty members or as a "host" at any point could not also be considered "invited speakers".
+Each speaker was only counted once and those listed as departmental faculty members or as a “host” at any point could not also be considered “invited speakers”.
 The list of faculty hosts was used as a proxy for faculty demographics since as hosts, these faculty members are visible representatives of the department.
+There were a total of {`r`} invited speakers and paired hosts.
 The trainees were identified using departmental email lists that included masters students, doctoral students, and post-doctoral fellows.
+There were {`r`} students and {`r`} post-doctoral fellows.
 
 This is a retrospective study, thus speakers were not asked for their identities at the time of visit.
-Instead we hand-coded proxy demographics using personal knowledge, photos, and CVs.
+Instead we hand-coded proxy demographics of the speakers, faculty hosts and trainees using personal knowledge and publicly available photos, and CVs [@Broderick2019; @Kimery2011; @Helmer2017; @Fox2019; @Gilbert1994].
+Information from CVs, such as undergraduate institutions (e.g., Puerto Rico vs mainland U.S.) and activity in HURM groups (e.g., SACNAS) helped inform our demographics.
+Because these data were collected from publicly available sources, this study was not submitted to an IRB for consideration.
 The presenting gender of each individual was assigned using a binary system (man/woman).
@@
 Census definition where those of Middle Eastern, European, and Russian descent are included.
-HURM individuals were restricted to those with African-American, Indigenous, Alaskan/Hawaiian Native, Latinx and/or Hispanic heritage.
-All others were placed into the NCNH group.
-We recognize that our proxy demographics are a limitation of the analysis and want to acknowledge that biological sex (male/female) is not always equivalent to the gender that an individual presents as (man/woman), which is also distinct from the gender(s) that an individual self-identifies as.
-We also want to acknowledge that there are many other identities that are not captured in this limited analysis.
+URM individuals include those of African-American, Indigenous American, Alaskan/Hawaiian Native, Latinx and/or Hispanic heritage (20 U.S.
+Code § 1067k), we use the HURM designation to recognize the history of enslavement and active oppression in the U.S..
+The NCNH group predominantly included Asian/Asian-Americans, but also African immigrants [@Okonofua2013].
 
-Data were analyzed and figures generated in R Statistical Software, using relevant packages [@R_software_2017; @wickham_tidyverse_2017; @cowplot; @markdown; @rmd_book; @rmd_rstudio; @knitr_2014; @knitr_2018; @lubridate; @readxl; @pdftools; @wickham_scales_2018; @neuwirth_rcolorbrewer_2014].
+Data were compiled and figures generated in R Statistical Software, using relevant packages
+[@R_software_2017; @wickham_tidyverse_2017; @cowplot; @markdown; @rmd_book; @rmd_rstudio; @knitr_2014; @knitr_2018; @lubridate; @readxl; @pdftools; @wickham_scales_2018; @neuwirth_rcolorbrewer_2014].
 
@@
 Additionally, within the last 5 years, no HURM or NCNH woman was awarded a lectureship.
-This means that the department is not providing non-Caucasian trainees with adequate representation of successful scientists.
-Taking this into context of social role theory, by not adequately representing the diversity of all trainees, the department is not supporting an inclusive environment in terms of visual faculty representation.
+This means that the department is not providing non-Caucasian trainees with adequate representation of successful scientists and failing to support an inclusive environment in terms of visual faculty representation.
 We also found that the proportion of women as faculty hosts and speakers in our study population is equivalent to global estimates that 40% of microbiologists are women, though women only represent about 30% of academic biomedical faculty [@allagnat_gender_2017;@Jena2015].
@@
 
-Several papers have investigated the representation of women at scientific conferences, however, we have only identified one that focused on invited speakers at universities [@nittrouer_gender_2018].
-In their study, Nittrouer et al, examined 3,652 talks at 50 U.S.
-institutions in 2013 - 2014 and found that women faculty are less likely to be invited speakers, despite similar acceptance rates [@nittrouer_gender_2018].
-We have not been able to identify any publications examining scientific speaker diversity beyond gender.
+We have not been able to identify any publications examining scientific speaker diversity beyond gender [@nittrouer_gender_2018].
 This seems to be the first, which is concerning since conclusions drawn from gender-based studies are often framed, and considered, to be applicable to other marginalized groups (e.g., HURM).
@@
 While there is no doubt some overlap, each group remains marginalized due to a unique complex set of factors that cannot always be solved by gender-based solutions.
-U.S.
-institutions, such as the University of Michigan have a particular responsibility to the historically suppressed populations included in our definition of HURMs.
-We therefore implore U.S.
+The historical exclusion of HURMs by U.S.
+institutions means that they have a particular responsibility to improving the academic experience for these populations [@harvey_diversity_2011].
+We therefore call on  U.S.
 institutions to apply this framing to their discussions and research.
@@
 Departments have different processes and criteria for selecting invited speakers, but it is a matter of pride to bring the best scientists possible.
-It may be that the definition of "best" poses a problem to under-represented and under-served groups (e.g., white women, HURM, and Asian) who are held to stricter competency standards and report having to work harder than white men to be perceived as legitimate scholars [@BlairLoy2017;@noauthor_seeking_2013].
-Some departments only invite tenured faculty, which severely limits the number of potential speakers who are white women or non-Caucasian.
+The barriers to achieving faculty status for HURMs, Caucasian women, and NCNH may also impact their speaking invitations.
+For instance, the perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation, despite the prestigious nature of these invitations and evidence that men and women accept at similar rates [@nittrouer_gender_2018; @xu_gender_2008].
+As a result, the faculty member may invite a different colleague who they feel is more likely to agree (and is a man).
+It may also be that the definition of “best” poses a problem to under-represented and under-served groups (e.g., women, HURM, and Asian) who are held to stricter competency standards [@BlairLoy2017;@noauthor_seeking_2013].
+Some departments may only invite tenured faculty, which severely limits the number of potential speakers who are Caucasian women or non-Caucasian.
 Yet, another scenario is that pre-tenure faculty members invite prestigious, tenured faculty in their field to network and secure letters for their own tenure package.
-The increased burden of white women and non-Caucasian scientists to prove competency decreases their likelihood to be considered for either tenure or as possible source of tenure letters.
+The increased burden of women and non-Caucasian scientists to prove competency decreases their likelihood to be considered for either tenure or as possible source of tenure letters.
+In particular, the proportion of HURM faculty at the Assistant and Associate Professor level is currently higher than at Full Professor so it will be difficult to increase speaker diversity if early-career researchers are not being considered [@whittaker_retention_2015].
+Even when HURM speaker rates match the proportion of HURM faculty employment, HURM trainees will be represented at a significantly higher proportion.
+We argue that inclusion of marginalized faculty in seminar series is an important factor to increasing their representation among Associate and Full Professors.
+It is just one aspect of larger institutional change that is needed, but one that will benefit trainee experiences and the CVs of marginalized faculty [@johnson_msphere_2019].
 
-Each underrepresented group in our cohort faces a complex set of barriers to achieving faculty status.
-For instance, the decision to invite a woman may also be negatively impacted by assumptions about competency and dedication.
-The dedication of women who have children to their work is perceived to be less than that of their colleagues, i.e., men who also have children [@Firth1982; @Correll2007; @Fuegen2004].
-The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation, despite the prestigious nature of these invitations and evidence that men and women accept at similar rates [@nittrouer_gender_2018; @xu_gender_2008].
-As a result, the faculty member may invite a different colleague who they feel is more likely to agree (and is a man).
-Another large portion of our sample were the NCNH cohort, who are predominately Asian/Asian American individuals.
-Although Asian scientists are well-represented in the US scientific workforce, they face significant bias and barriers to inclusion in society and academia [@Hwang2008; @Tran2019].
-For instance, despite the higher employment rate of Asian scientists, they were not well-represented in the more prestigious lectureships.
-
-While HURM and NCNH share some experiences, differences including varying rates of hiring and tenure promotion mean unique considerations are important for inclusion of each group [@Fang2000].
-For instance, a major barrier to inclusion of HURM faculty at similar proportions to HURM trainees is the low transition rate of scientists from HURM backgrounds to faculty positions and the associated low proportion of HURM faculty [@Gibbs2016].
-The proportion of HURM faculty at the Assistant and Associate Professor level is currently higher than at Full Professor so it will be difficult to increase speaker diversity if early-career researchers are not being considered [@whittaker_retention_2015].
-Increased performance expectations and patterns of exclusions are consistent themes in studies characterizing the HURM faculty experience [@pololi_race_2010; @hassouneh_experiences_2014].
-Therefore, inclusion of HURM faculty in seminar series is likely essential to increasing the number of HURM Associate and Full Professors.
-Even when HURM speaker rates match the proportion of HURM faculty employment, HURM trainees will be represented at a significantly higher proportion.
-Inclusion of HURM faculty in these seminar series is just one aspect of larger institutional change that is needed [@johnson_msphere_2019].
+We recognize that our proxy demographics are a limitation of the analysis and want to acknowledge that biological sex (male/female) is not always equivalent to the gender that an individual presents as (man/woman), which is also distinct from the gender(s) that an individual self-identifies as.
+We also want to acknowledge that there are many other identities that are not captured in this limited analysis.
+While our pilot study combined 5 years worth of seminars, our n is still quite low and we did not have other departments for comparison.
+Consequently, our results can not be generalized to other departments, fields, or universities.
+Another limitation to looking at a single department is that trainees may interact with faculty from many other departments, depending on their research and interests.
+Therefore, the individual experience of representation would vary by trainee.
+Future research needs to consider multiple departments, universities, and/or fields to bolster generalizability.
+There is a paucity of research on speaker identities other than their gender, so this also needs to be addressed in future studies.
+However, we caution that representation is a shallow metric on which a single-minded focus can cause more harm than help [@Iverson2007].
+We recommend that future research also survey trainee and speaker experiences and trainee participation in seminar series to better understand the dynamics at play.
 
@@
 
-In an attempt to promote inclusion within the Department of Microbiology and Immunology at the University of Michigan, these data were presented to faculty members and the department chair (Dr.
-Mobley).
-Since trainee demographics were not represented by the seminar speaker demographics over the past 5 years, we proposed a policy change as to how seminar speakers were being invited.
-One suggestion was to switch from faculty-invited to lab-invited speakers in an attempt to allow trainees to choose a speaker that best represented themselves (Table 1).
+In an attempt to promote inclusion within the Department of Microbiology and Immunology at the University of Michigan, these data were presented to faculty members and the department chair.
+Since trainee demographics were not represented by the seminar speaker demographics over the past 5 years, we proposed a policy change as to how seminar speakers were being invited (Table 1).
+One suggestion was to switch from faculty-invited to lab-invited speakers to allow trainees to choose a speaker that best represented themselves.
+This is easy to implement as it does not change the overall structure of the department’s seminar series; however, for this same reason it may not have a significant impact on the diversity of invited speakers.
+Trainees may be pressured to invite the top individuals in their sub-field or may be influenced by the same unconscious biases as faculty members.
+This idea can be expanded by increasing the number of trainee-invited speakers and varying the trainee group that extend invitations, for instance by training program, career interest, and/or trainees and faculty in an identity-affinity group.
+Invitations from trainees are often seen as an honor by potential seminar speakers and nominating as a group may decrease the pressure to invite particular sub-fields or ranks.
 
-The implicit biases that affect perceptions of marginalized groups are an issue, but we must acknowledge that it is not always possible to identify members of historically under-served communities.
-For instance, after data analysis, we learned that at least one speaker in our data set should have been categorized as a HURM instead of Caucasian, but it wasn't readily apparent from their internet presence or CV.
-This limitation makes two important points: that perceived identity often plays a larger role than self-identification, and that we need better tools to identify members of marginalized groups.
-Another policy suggestion is for departments to invite their speakers to spend time discussing their personal journeys through science, in addition to their scientific stories (Table 1).
-This would enable those who wish, to discuss how their identity(ies) interacted with their careers.
-In addition to these suggestions for policy change, we have created resources that allow scientists to self-identify as under-served groups and thus provide host faculty with more diverse choices (Table 1).
+We also used this opportunity to begin a conversation about the purpose of seminar speakers.
+Seminar speakers are sometimes invited to highlight their latest high-impact paper or to share the arc of discoveries they have made over several years of their career.
+While both are certainly worthwhile, there are other benefits to be gained from interacting with seminar speakers such as how to apply new techniques and how research is framed outside research-focused universities (Table 1).
+Thinking more broadly about what material is valuable during a seminar series may lead to more speakers from under-represented and under-served backgrounds, as well as more diversity of career paths.
+For some institutions, these suggestions represent more of a structural change to the departmental seminar series as speakers focusing on techniques or from non-research-intensive universities are using invited as part of professional development series.
+If these changes are to be implemented, many members of the department must agree to the value of including these seminars in the main departmental seminar series and these expectations must be clearly communicated by the leadership (Table 1).
+Departmental leadership can also ask individuals and groups to consider their own unconscious biases that may be impacting their speaker nominee list to compact some of the barriers to inviting diverse speakers.
+Presented with these ideas, several members of the Department of Microbiology and Immunology at the University of Michigan expressed interest in specific resources they might use to identify individuals from diverse identities, careers, and institutions.
+One suggestion is to use resources that are being organized by professional societies such as the American Society for Microbiology (ASM) and the Society for Advancing Chicanos/Hispanics & Native Americans in Science (SACNAS) (Table 1).
+We also chose to develop “Diversify” resources for the microbiology and immunology fields that provide a list of scientists from under-represented and under-served groups, that is not associated with a specific professional society.
+More information on the type of resources and how to establish a Diversify list is below.
+Using list resources like those available from professional societies as well as our “Diversify” resources are particularly useful as social science research has shown that the human brain is much better at recognizing and using information (such as a strong scientific speaker) from a list than it is at recalling the same information from memory [@Loftus1971; @Johnson2014].
+
+We caution, however, that it is not enough to invite diverse speakers.
+An inclusive environment must be built within the department.
+Start by inviting all speakers to spend a few minutes describing their personal science journey and providing time for trainees to engage with the speaker.
+Trainee-speaker interactions can be encouraged by ensuring that trainees are the first to ask questions at the seminar’s conclusion and by scheduling a dedicated meeting time for trainees.
+As speaker schedules are being designed, departments should consider how they can foster an inclusive atmosphere during the speaker visits.
+Speakers should be asked prior to their visit if they have any dietary, movement, or other restrictions that should be accommodated during the visit.
+The identities of individuals the speaker is meeting with during their visit may also need to be considered; this is not to say that all identities of a speaker should be matched on their schedule or that a HURM speaker must have a meeting a HURM faculty member, but take care to ensure that speakers are meeting with faculty that reflect the diversity of thought and identity in the department.
+If a portion of the department is consistently not represented on speakers’ schedules (or extending invitations) this may reflect an opportunity for increased inclusivity in the department.
+Finally, speakers should be provided with ample opportunity to request meetings, not only with faculty but also with student groups or campus administrators who share similar interests.
+Through these steps departments can increase the diversity of speakers invited to their seminars while also increasing the impact of the seminar speakers.
 
@@
 
-This public spreadsheet is embedded in the website and can be open separately as a locked (uneditable) Google Sheet, allowing the list to be easily searched.
+This public spreadsheet is embedded in the website and can be opened separately as a locked (uneditable) Google Sheet, allowing the list to be easily searched.
 We have chosen to list individuals’ academic information first in the spreadsheet to encourage a focus on academic achievement rather than tokenization of marginalized identities.
@@
 A tutorial in the DiversifyMicrobiology repository on GitHub provides links to these resources and instructions for adapting the tool to your own field [@Hagan2019_micro].
+We caution creators of Diversify lists that the data voluntarily submitted to these lists is not eligible for study.
+IRB approval must be obtained prior to launching the list if that is a goal.
 
@@
 
-To increase the retention of white women, HURM and NCNH trainees in the biomedical sciences, they must also be represented as experts.
+To increase the retention of Caucasian women, HURM and NCNH trainees in the biomedical sciences, they must also be represented as experts.
 However, the invited speaker diversity at one department does not represent the diversity of trainees.
@@
 
-## Acknowledgements
+## Acknowledgments
 
@@
 We thank Bonnie Krey and former speaker series coordinators Drs.
-Nicole Koropatkin and Kathy Spindler for access to invited speaker data.
+Nicole Koropatkin and Kathy Spindler for providing compiled invited speaker data.
 We would also like to acknowledge and thank Nick Lesniak and Dr.
@@
 
-\newpage
-
-\begin{center}
-\captionof{table}{List of suggestions and resources to increase invited speaker diversity.}
-\small
-\begin{tabular}{|l|l|l|}
-\hline
-
-\rowcolor{lightgray}
-\textbf{Suggestion} & \textbf{Description} & \textbf{Resource} \\ \hline
-
-Lab-invited speakers & \makecell[l]{Faculty members can request \\suggestions from trainees} & \\ \hline
-
-Use a list & \makecell[l]{Many lists of scientists from \\under-represented and under-served \\groups are available} &  \makecell[l]{https://DiversifyMicrobiology.\\github.io/resources}\\ \hline
-
-Create a list & \makecell[l]{Use the GitHub template \\ create a self-nomination list and \\resource for your field} & \makecell[l]{https://github.com/diversifymicrobiology/\\DiversifyMicrobiology.github.io} \\ \hline
-
-Highlight the journey & \makecell[l]{Invite all speakers to spend \\a few moments describing their \\personal science journey} & \\ \hline
-
-\end{tabular}
-\end{center}
+![](Table_1.pdf)
 
@@
 B) The proportion of each academic role represented by individuals that are Caucasian (left), Historically Underrepresented Minorities (HURM, center) or Non-Caucasian/Non-HURM (NCNH, right).
-C-D)The percent of lectureships awarded to individuals that are C) Caucasian, HURM, or NCNH and D) Caucasian, HURM, or NCNH by gender.](Figure_1.png)
+C-D)The percent of lectureships awarded to individuals that are C) Caucasian, HURM, or NCNH and D) Caucasian, HURM, or NCNH by gender.](Figure_1.jpg)
 

### 2020-02-07 submission/Table_1.Rmd
finish revisions and format resubmission

@@
     keep_tex: yes
+  word_document: default
 ---
@@
 \centering
-\begin{tabular}{>{\centering\arraybackslash}m{4cm}|>{\centering\arraybackslash}m{7cm}|>{}m{5cm}}
+\begin{tabular}{>{\centering\arraybackslash}m{4cm}|>{\centering\arraybackslash}m{7cm}|>{\centering\arraybackslash}m{5cm}}
 
@@
 
-Create a list & Use the GitHub template to create a self-nomination list and resource for your field & https://github.com /diversifymicrobiology /DiversifyMicrobiology.github.io \\\hline
+Create a list & Use the GitHub template to create a self-nomination list and resource for your field & Template can be found at https://github.com /diversifymicrobiology /DiversifyMicrobiology.github.io \\\hline
 
@@
 
-Encourage trainees to engage & \makecell[l]{When a talk is over, ensure that \\trainees are the first to ask questions} & \\\hline
+Encourage trainees to engage & When a talk is over, ensure that trainees are the first to ask questions & \\\hline
 

### 2020-02-07 submission/Table_1.tex
finish revisions and format resubmission

@@
 \begin{center}
-\captionof{table}{List of suggestions and resources to increase invited speaker diversity.}
+\captionof{table}{Suggestions and resources to increase invited speaker diversity.}
 \small
 \centering
-\begin{tabular}{>{\centering\arraybackslash}m{4cm}|>{\centering\arraybackslash}m{7cm}|>{}m{5cm}}
+\begin{tabular}{>{\centering\arraybackslash}m{4cm}|>{\centering\arraybackslash}m{7cm}|>{\centering\arraybackslash}m{5cm}}
 

### 2020-02-07 submission/manuscript.Rmd
finish revisions and format resubmission

@@
 ---
-title: '**Suggestions to improve invited speaker diversity and reflect trainee diversity**'
+title: '**Suggestions for improving invited speaker diversity to reflect trainee diversity**'
 csl: mbio.csl
@@
     keep_tex: yes
+  html_document:
+    df_print: paged
 geometry: margin=1.0in
@@
 
-Running title: Suggestions to improve invited speaker diversity
+Running title: Suggestions for improving invited speaker diversity
 
@@
 
-Ada K. Hagan, Ph.D.$^{1,2\dagger}$, Rebecca M. Pollet, Ph.D.${^2}$, and Josie Libertucci, Ph.D.${^3}$
+Ada K. Hagan, Ph.D.$^{*1\dagger}$, Rebecca M. Pollet, Ph.D.${^1}$, and Josie Libertucci, Ph.D.$^{**1}$
 
@@
 
-1\. Alliance SciComm & Consulting, Linden, Michigan
+1\. Department of Microbiology & Immunology, University of Michigan, Ann Arbor, Michigan
 
-2\. Department of Microbiology & Immunology, University of Michigan, Ann Arbor, Michigan
+*Current address: Alliance SciComm & Consulting, Linden, Michigan
 
-3\. Farncombe Family Digestive Health Research Institute, Department of Medicine, McMaster University, Hamilton, Ontario, Canada
+**Current address: Farncombe Family Digestive Health Research Institute, Department of Medicine, McMaster University, Hamilton, Ontario, Canada
 
@@
 
-The biomedical sciences have a problem retaining women and underrepresented minorities in academia.
-Despite increases in the representation of these groups in faculty candidate pools, they are still underrepresented at the faculty level, particularly at the Full Professor level.
-The lack of diverse individuals at the Full Professor level contributes to the attrition of women and under-represented minorities, as it confirms unconscious biases.
-The presence of unconscious biases contribute to feelings of not belonging by trainees and are amplified by visual representation of who is presented as the “top scientist in their field”.
-Top scientists are not only defined by the attainment of Full Professorships, but also through invited seminar series.
-Invitations for faculty to present their research at other university departments is highly valued offer that provides an opportunity for collaborations and networking.
-However, if invited speakers do not represent the demographics of current trainees, these visual representations of successful scientists may contribute to decreased attitudes of self-identification as a scientist, ultimately resulting in trainees leaving the field or the academy.
-In this study, we compare invited-speaker demographics to the current trainee demographics in one microbiology and immunology department and find that trainees are not proportionally represented by speakers invited to the department.
-Our investigation prompted changes in policy for how invited speakers are selected in the future to invite a more diverse group of scientists.
-To facilitate this process, we developed a set of tips and a web-based resource that allows scientists, committees, and moderators to identify members of under-served groups.
+Within the field of biomedical research in the United States, the proportion of underrepresented minorities at the full professor level has remained consistently low, even though trainee demographics are becoming more diverse.
+Underrepresented groups face a complex set of barriers to achieving faculty status including imposter syndrome, increased performance expectations, and patterns of exclusion.
+Institutionalized racism and sexism have contributed to these barriers and perpetuated policy that excludes underrepresented minorities.
+These barriers can contribute to decreased feelings of belonging, which may result in decreased retention of underrepresented minorities.
+Though some universities have altered their hiring practices to increase the number of underrepresented minorities in the applicant pool, these changes have not been sufficient.
+Here we argue that departmental invited seminar series can be used to provide trainees with scientific role-models and increase their sense of belonging, while institutions work towards more inclusive policy.
+In this study, we investigated the demographics (gender and race) of invited seminar speakers over 5 years to the Department of Microbiology and Immunology at the University of Michigan.
+We also investigated current trainee demographics and compared them to invited speaker demographics to gauge if our trainees are being provided with representation of themselves.
+We found that invited speaker demographics were skewed towards Caucasian men, and our trainee demographics were not being  represented.
+From these findings, we proposed policy change within the department to address how speakers are being invited with the goal of increasing speaker diversity to better reflect trainee diversity.
+To facilitate this process, we developed a set of suggestions and a web-based resource that allows scientists, committees, and moderators to identify members of under-served groups.
 These resources can be easily adapted by other fields or sub-fields to promote inclusion and diversity at seminar series’, conferences, and colloquia.
@@
 Long-standing systemic bias, sexism, and racism have contributed to the under-representation of many racial and ethnic groups, as well as women, in science, technology, engineering, and math (STEM) fields [@Martinez2018; @AllenRamdial2014; @Fang2000; @Gibbs2014].
-Specifically, within the field of biomedical research in the United States, the proportion of underrepresented minorities at the full professor level has remained consistently low at 4% (survey data taken from the NIH from 2001 to 2013), compared to the U.S.
-population, which is 32.3% [@Meyers2018;@nsf_2014].
+Specifically, within the field of biomedical research in the United States, the proportion of underrepresented minorities at the full professor level has remained consistently low at 4% (survey data taken from the NIH from 2001 to 2013) [@Meyers2018;@nsf_2014].
 Similar discrepancies exist for women in biomedical sciences as full professorships are currently held mostly by men [@Jena2015; @Rotbart2012].
-As demographics of faculty within the biomedical sciences remains skewed towards Caucasian men, the demographics of trainees (graduate students and postdocs) are becoming more diverse [@Meyers2018].
+As demographics of faculty within the biomedical sciences remain skewed towards Caucasian men, the demographics of trainees (graduate students and postdocs) are becoming more diverse [@Meyers2018].
 
-Policy changes are needed to support inclusion of all individuals, particularly in the biomedical sciences[@Coe2019].
-To increase retention of historically under-represented minorities (HURM), non-Caucasian/non-HURM (NCNH) individuals, and Caucasian women in biomedical fields, it is important for trainees to have visual representations of themselves as scientists.
-The importance of representation in retaining a diverse group of individuals in STEM fields is supported by social role theory [@Eagly1984].
-Individuals make inferences about characteristics that are needed to be successful in a given role by examining individuals that most occupy that role [@Eagly1984; @Carter2018].
-However, there is a lack of diverse scientific experts in academia so underrepresented minorities are not seeing adequate visual representations of themselves at the faculty level.
-Therefore, trainees who do not see representation of themselves in senior faculty positions, may decide that they do not possess the characteristics that are required to succeed.
+Policy changes are needed to support inclusion of all individuals, particularly in the biomedical sciences, since underrepresented groups face a complex set of barriers to achieving faculty status [@Coe2019].
+For example, the dedication of women---who have children---to their work is perceived to be less than that of their colleagues, including men who also have children [@Firth1982; @Correll2007; @Fuegen2004].
+Historically under-represented minorities in the United States (HURM), Asian/Asian-Americans, and women are all held to stricter competency standards and report having to work harder than Caucasian men to be perceived as legitimate scholars [@BlairLoy2017; @noauthor_seeking_2013].
+Asian/Asian-Americans suffer from imposter syndrome at greater rates than other marginalized groups and Asian women report a lack of sponsors [@McGee2018; @wse_2016].
+Increased performance expectations and patterns of exclusions are consistent themes in studies characterizing the HURM faculty experience [@pololi_race_2010; @hassouneh_experiences_2014].
+While HURM and other marginalized groups share some experiences, differences including varying rates of hiring and tenure promotion mean that unique considerations are important for inclusion of each group [@Fang2000].
+
+Here, we argue that to support the retention of faculty from marginalized groups at the professor level, universities should provide trainees with visual representation of themselves as successful scientists.
+Recent studies show that women in STEM benefit from women role models through improved belonging and self-efficacy [@Herrmann2016; @Drury2011].
+Predictably, a lack of active inclusion also decreases self-efficacy in URMs, which can result in decreased feelings of belonging [@Lambert2020].
+However, as the demographics of trainees have become more diverse, those who are not Caucasian men are lacking role models.
+Institutionalized racism and sexism [@Hardeman2018], defined as policies, societal norms, and ideologies that reinforce inequities, have played a large role in access to, inclusion in, and hiring policies at U.S.
+universities [@harvey_diversity_2011; @Stack2019].
+Accordingly, faculty from marginalized groups are eliminated from the applicant pool and subsequent hires, leaving university policies and practices to be predominantly created by Caucasian men.
+Thus, institutionalized racism and sexism are perpetuated [@Iverson2007; @Tate2016].
+Universities have begun adjusting hiring practices and creating initiatives to address inequitable hiring practices, but have had limited results [@Gibbs2016].
+Considering that most faculties within the U.S.
+are still skewed towards Caucasian men, invited seminar series are a possible tool to provide marginalized trainees with representation of themselves as successful scientists.
 
 Invited seminar series are common within biomedical departments across the United States [@nittrouer_gender_2018].
-Usually, seminar series' consist of faculty members selecting a scientist from another institution to visit their university and present their research, as well as meet with other faculty members and trainees.
+Usually, seminar series’ consist of faculty members selecting a scientist from another institution to visit their university and present their research, as well as meet with other faculty members and trainees.
 Named lectureships follow the same format but are decided by committee and are considered more prestigious because they are named in honor of prominent local scientists.
@@
 Additionally, being an invited speaker provides the scientist with an opportunity to make future collaborations and build their own _curriculum vitae_ (CV).
-Scientists invited to give seminars are widely regarded as successful and the top in their field.
-Thus, if trainees are constantly being exposed to “the top scientist in their field”, according to social role theory, it signals who is successful in that field.
-While some have examined this issue by studying and promoting the inclusion of more women speakers at conferences, how department speaker series compare to the trainee diversity of that department is unknown [@kalejta_gender_2017; @casadevall_presence_2014; @klein_speaking_2017].
+Scientists invited to give seminars are widely regarded as successful and the top in their field, providing an opportunity for trainees to be exposed to successful scientists in that field.
+Some studies have examined the addition of more women speakers at conferences to promote inclusion [@kalejta_gender_2017; @casadevall_presence_2014; @klein_speaking_2017],  however,  we have only identified one other study that has focused on invited speakers at universities [@nittrouer_gender_2018].
+In their study, Nittrouer et al, examined 3,652 talks at 50 U.S.
+institutions in 2013 - 2014 and found that women faculty are less likely to be invited speakers [@nittrouer_gender_2018].
+We have not been able to identify any publications examining scientific speaker diversity beyond gender or how department speaker series compares to trainee diversity in that department.
 
-In this study, we examine and compare the proportion of HURM, NCNH, and women invited speakers to Caucasian men in the Department of Microbiology and Immunology at the University of Michigan.
-Additionally, we compare invited-speaker demographics to the current trainee demographics as a means to gauge if trainee demographics are being represented accordingly throughout the seminar series.
-Following our investigation, we proposed a policy change to the Department of Microbiology and Immunology in how invited speakers are selected as a means to promote inclusion in our department and reduce unconscious bias.
-In order to facilitate inviting a more diverse group of scientists, we developed a set of resources that allow scientists, within the fields of microbiology and immunology, to self-identify as having an under-represented or under-served identity including: HURM, non-Caucasian/non-HURM, or a Caucasian woman.
+In this study, we examine and compare the demographics of invited speakers to Caucasian men in the Department of Microbiology and Immunology at the University of Michigan.
+Additionally, we compare invited-speaker demographics to the current trainee demographics to gauge if trainee demographics are being represented throughout the seminar series.
+Following our investigation, we proposed a policy change to the Department of Microbiology and Immunology in how invited speakers are selected to promote inclusion in our department and reduce unconscious bias.
+In order to facilitate inviting a more diverse group of scientists, we developed a set of resources that allow scientists, within the fields of microbiology and immunology, to self-identify any under-represented or under-served identity including: HURM, non-Caucasian/non-HURM (NCNH), or a Caucasian woman.
 These resources will promote inclusion and diversity by providing greater representation of all scientists and will provide hosts an opportunity to invite a more diverse group of scientists.
@@
 ## Methods
+```{r method, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE, include=FALSE}
+num_pd <- trainee_data %>% filter(Trainee_type == "postdoc") %>% nrow()
+
+num_student <- trainee_data %>% filter(Trainee_type == "student") %>% nrow()
+
+num_speaker <- nrow(speaker_data)
+```
+
 Each academic year, each faculty member in the Department of Microbiology and Immunology at the University of Michigan has the opportunity to invite one speaker per year for a weekly seminar series.
@@
 The list of faculty hosts was used as a proxy for faculty demographics since as hosts, these faculty members are visible representatives of the department.
-There were a total of {`r`} invited speakers and paired hosts.
+There were a total of `r num_speaker` invited speakers and paired hosts.
 The trainees were identified using departmental email lists that included masters students, doctoral students, and post-doctoral fellows.
-There were {`r`} students and {`r`} post-doctoral fellows.
+There were `r num_student` students and `r num_pd` post-doctoral fellows.
 
 This is a retrospective study, thus speakers were not asked for their identities at the time of visit.
-Instead we hand-coded proxy demographics of the speakers, faculty hosts and trainees using personal knowledge and publicly available photos, and CVs [@Broderick2019; @Kimery2011; @Helmer2017; @Fox2019; @Gilbert1994].
-Information from CVs, such as undergraduate institutions (e.g., Puerto Rico vs mainland U.S.) and activity in HURM groups (e.g., SACNAS) helped inform our demographics.
+Instead we hand-coded proxy demographics of the speakers, faculty hosts and trainees using first names, publicly available photos, and CVs [@Broderick2019; @Kimery2011; @Helmer2017; @Fox2019; @Gilbert1994].
+Information from CVs, such as undergraduate institutions and activity in HURM groups helped inform our demographics by indicating identities that might be held by that individual.
+For instance, an undergraduate at a Puerto Rican university and activity in the non-profit Ciencia Puerto Rico suggests that even if the individual appears Caucasian, they probably identify as Puerto Rican and qualify as a URM.
 Because these data were collected from publicly available sources, this study was not submitted to an IRB for consideration.
-The presenting gender of each individual was assigned using a binary system (man/woman).
-Due to the low number of individuals in the study, race/ethnicity demographics were split in three groups: Caucasian, Historically Under-represented Minority (HURM), and Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibility.
-Caucasian was assigned using the current U.S.
+The presenting gender of each individual was inferred using a binary system (man/woman).
+Due to the low number of individuals in the study, race/ethnicity demographics were only split into three groups: Caucasian, Historically Under-represented Minority (HURM), and Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibility.
+Caucasian was inferred using the current U.S.
 Census definition where those of Middle Eastern, European, and Russian descent are included.
@@
 ```
+
 To understand the representation of women, we compared the proportion of women in each academic role.
@@
 This study found that the proportion of HURM and NCNH invited speakers were under-representative of the trainee populations for each group.
-Additionally, within the last 5 years, no HURM or NCNH woman was awarded a lectureship.
+Additionally, within the last 5 years, no HURM or NCNH woman was awarded a lectureship, despite that in 2017 non-Caucasians were 30% of the professoriate [@nsf_2019].
 This means that the department is not providing non-Caucasian trainees with adequate representation of successful scientists and failing to support an inclusive environment in terms of visual faculty representation.
@@
 This seems to be the first, which is concerning since conclusions drawn from gender-based studies are often framed, and considered, to be applicable to other marginalized groups (e.g., HURM).
-This is a flawed assumption.
+For instance, that African-American and Caucasian women benefit equally from the same policy change.
+This is a flawed assumption [@Armstrong2015].
 While there is no doubt some overlap, each group remains marginalized due to a unique complex set of factors that cannot always be solved by gender-based solutions.
@@
 We therefore call on U.S.
-institutions to apply this framing to their discussions and research.
+institutions to apply intersectional framing to their discussions and research.
 
@@
 We argue that inclusion of marginalized faculty in seminar series is an important factor to increasing their representation among Associate and Full Professors.
-It is just one aspect of larger institutional change that is needed, but one that will benefit trainee experiences and the CVs of marginalized faculty [@johnson_msphere_2019].
+It is just one aspect of larger institutional change that is needed, but one that will benefit trainee experiences and the CVs of faculty from marginalized groups [@johnson_msphere_2019].
 
 We recognize that our proxy demographics are a limitation of the analysis and want to acknowledge that biological sex (male/female) is not always equivalent to the gender that an individual presents as (man/woman), which is also distinct from the gender(s) that an individual self-identifies as.
-We also want to acknowledge that there are many other identities that are not captured in this limited analysis.
+We also want to acknowledge that there are many other identities that are not captured in this limited analysis and that our personal implicit biases may have impacted our assignment of demographics.
 While our pilot study combined 5 years worth of seminars, our n is still quite low and we did not have other departments for comparison.
@@
 Thinking more broadly about what material is valuable during a seminar series may lead to more speakers from under-represented and under-served backgrounds, as well as more diversity of career paths.
-For some institutions, these suggestions represent more of a structural change to the departmental seminar series as speakers focusing on techniques or from non-research-intensive universities are using invited as part of professional development series.
+For some institutions, these suggestions represent more of a structural change to the departmental seminar series as speakers focusing on techniques or from non-research-intensive universities are usually invited as part of a professional development series.
 If these changes are to be implemented, many members of the department must agree to the value of including these seminars in the main departmental seminar series and these expectations must be clearly communicated by the leadership (Table 1).
-Departmental leadership can also ask individuals and groups to consider their own unconscious biases that may be impacting their speaker nominee list to compact some of the barriers to inviting diverse speakers.
+Departmental leadership can also ask individuals and groups to consider the unconscious biases that may be impacting their own speaker nominee lists to combat some of the barriers to inviting diverse speakers.
+
 Presented with these ideas, several members of the Department of Microbiology and Immunology at the University of Michigan expressed interest in specific resources they might use to identify individuals from diverse identities, careers, and institutions.
@@
 
-We caution, however, that it is not enough to invite diverse speakers.
+We caution, however, that it is not enough to invite speakers from diverse identites`.
 An inclusive environment must be built within the department.
@@
 Basic tools and skills required to set up a Diversify site include knowledge of, or experience with, the version control tool git, the web-tool GitHub, and a text editor.
-A tutorial in the DiversifyMicrobiology repository on GitHub provides links to these resources and instructions for adapting the tool to your own field [@Hagan2019_micro].
+A tutorial in the DiversifyMicrobiology repository on GitHub provides links to these resources and instructions for adapting the tool to your own field (Table 1) [@Hagan2019_micro].
 We caution creators of Diversify lists that the data voluntarily submitted to these lists is not eligible for study.
@@
 However, the invited speaker diversity at one department does not represent the diversity of trainees.
-To facilitate the identification and recruitment of individuals in these historically under-served groups, we have built a tool to create self-nominated, field-specific lists.
+To facilitate the identification and recruitment of individuals in these, and other, under-served groups, we have built a tool to create self-nominated, field-specific lists.
 
@@
 A.K.H.
-collected the data, assigned demographics, analyzed the data, created the website, and wrote the methods and results.
+collected the data, inferred demographics, analyzed the data, created the website, and wrote the methods and results.
 R.M.P.
@@
 
-![](Table_1.pdf)
+\newpage
+## References
 
-![**The demographics of invited speakers, hosting faculty, and trainees.** A) The proportion of women in each academic role.
-B) The proportion of each academic role represented by individuals that are Caucasian (left), Historically Underrepresented Minorities (HURM, center) or Non-Caucasian/Non-HURM (NCNH, right).
-C-D)The percent of lectureships awarded to individuals that are C) Caucasian, HURM, or NCNH and D) Caucasian, HURM, or NCNH by gender.](Figure_1.jpg)
+<div id="refs"></div>
 
@@
 
-## References
+**Figure 1.
+The demographics of invited speakers, hosting faculty, and trainees.** A) The proportion of women in each academic role.
+B) The proportion of each academic role represented by individuals that are Caucasian (left), Historically Underrepresented Minorities (HURM, center) or Non-Caucasian/Non-HURM (NCNH, right).
+C-D) The percent of lectureships awarded to individuals that are C) Caucasian, HURM, or NCNH and D) Caucasian, HURM, or NCNH by gender.
 
-<div id="refs"></div>
+**Table 1. Suggestions and resources to increase invited speaker diversity.**

### 2020-02-07 submission/manuscript.tex
format for submission, fix typos
finish revisions and format resubmission

@@
 \hypersetup{unicode=true,
-            pdftitle={Policy should change to improve invited speaker diversity and reflect trainee diversity},
+            pdftitle={Suggestions for improving invited speaker diversity to reflect trainee diversity},
             pdfborder={0 0 0},
@@
 
-  \title{\textbf{Policy should change to improve invited speaker diversity and
-reflect trainee diversity}}
+  \title{\textbf{Suggestions for improving invited speaker diversity to reflect
+trainee diversity}}
     \pretitle{\vspace{\droptitle}\centering\huge}
@@
 
-Ada K. Hagan, Ph.D.\({^1\dagger}\), Rebecca M. Pollet, Ph.D.\({^1}\),
-and Josie Libertucci, Ph.D.\({^2}\)
+Ada K. Hagan, Ph.D.\(^{1,2\dagger}\), Rebecca M. Pollet, Ph.D.\({^2}\),
+and Josie Libertucci, Ph.D.\({^3}\)
 
@@
 \(\dagger\) To whom correspondence should be addressed:
-\href{mailto:akhagan@umich.edu}{\nolinkurl{akhagan@umich.edu}}
+\href{mailto:akhagan@alliancescc.com}{\nolinkurl{akhagan@alliancescc.com}}
 
-1. Department of Microbiology \& Immunology, University of Michigan, Ann
+1. Alliance SciComm \& Consulting, Linden, Michigan
+
+2. Department of Microbiology \& Immunology, University of Michigan, Ann
 Arbor, Michigan
 
-2. Farncombe Family Digestive Health Research Institute, Department of
+3. Farncombe Family Digestive Health Research Institute, Department of
 Medicine, McMaster University, Hamilton, Ontario, Canada
@@
 
-\subsection{Conflicts of Interest}\label{conflicts-of-interest}
+\subsection{Conflict of Interest Notification
+Page}\label{conflict-of-interest-notification-page}
 
@@
 
-The biomedical sciences have a problem retaining white women and
-underrepresented minorities in academia. Despite increases in the
-representation of these groups in faculty candidate pools, they are
-still underrepresented at the faculty level, particularly at the Full
-Professor level. The lack of diverse individuals at the Full Professor
-level contributes to the attrition of women and under-represented
-minorities, as it confirms unconscious biases. The presence of
-unconscious biases contribute to feelings of not belonging by trainees
-and are amplified by visual representation of who is presented as the
-``top scientist in their field''. Top scientists are not only defined by
-the attainment of Full Professorships, but also through invited seminar
-series. Invitations for faculty to present their research at other
-university departments is highly valued offer that provides an
-opportunity for collaborations and networking. However, if invited
-speakers do not represent the demographics of current trainees, these
-visual representations of successful scientists may contribute to
-decreased attitudes of self-identification as a scientist, ultimately
-resulting in trainees leaving the field or the academy. In this study,
-we compare invited-speaker demographics to the current trainee
-demographics in one microbiology and immunology department and find that
-trainees are not proportionally represented by speakers invited to the
-department. Our investigation prompted changes in policy for how invited
-speakers are selected in the future to invite a more diverse group of
-scientists. To facilitate this process, we developed a set of tips and a
-web-based resource that allows scientists, committees, and moderators to
-identify members of under-served groups. These resources can be easily
-adapted by other fields or sub-fields to promote inclusion and diversity
-at seminar series', conferences, and colloquia.
+Within the field of biomedical research in the United States, the
+proportion of underrepresented minorities at the full professor level
+has remained consistently low, even though trainee demographics are
+becoming more diverse. Underrepresented groups face a complex set of
+barriers to achieving faculty status including imposter syndrome,
+increased performance expectations, and patterns of exclusion.
+Institutionalized racism and sexism have contributed to these barriers
+and perpetuated policy that excludes underrepresented minorities. These
+barriers can contribute to decreased feelings of belonging, which may
+result in decreased retention of underrepresented minorities. Though
+some universities have altered their hiring practices to increase the
+number of underrepresented minorities in the applicant pool, these
+changes have not been sufficient. Here we argue that departmental
+invited seminar series can be used to provide trainees with scientific
+role-models and increase their sense of belonging, while institutions
+work towards more inclusive policy. In this study, we investigated the
+demographics (gender and race) of invited seminar speakers over 5 years
+to the Department of Microbiology and Immunology at the University of
+Michigan. We also investigated current trainee demographics and compared
+them to invited speaker demographics to gauge if our trainees are being
+provided with representation of themselves. We found that invited
+speaker demographics were skewed towards Caucasian men, and our trainee
+demographics were not being represented. From these findings, we
+proposed policy change within the department to address how speakers are
+being invited with the goal of increasing speaker diversity to better
+reflect trainee diversity. To facilitate this process, we developed a
+set of suggestions and a web-based resource that allows scientists,
+committees, and moderators to identify members of under-served groups.
+These resources can be easily adapted by other fields or sub-fields to
+promote inclusion and diversity at seminar series', conferences, and
+colloquia.
 
@@
 professor level has remained consistently low at 4\% (survey data taken
-from the NIH from 2001 to 2013), compared to the U.S. population, which
-is 32.3\% (5, 6). Similar discrepancies exist for women in biomedical
-sciences as full professorships are currently held mostly by men (7, 8).
-As demographics of faculty within the biomedical sciences remains skewed
-towards Caucasian men, the demographics of trainees (graduate students
-and postdocs) are becoming more diverse (5).
+from the NIH from 2001 to 2013) (5, 6). Similar discrepancies exist for
+women in biomedical sciences as full professorships are currently held
+mostly by men (7, 8). As demographics of faculty within the biomedical
+sciences remains skewed towards Caucasian men, the demographics of
+trainees (graduate students and postdocs) are becoming more diverse (5).
 
 Policy changes are needed to support inclusion of all individuals,
-particularly in the biomedical sciences(9). To increase retention of
-historically under-represented minorities (HURM), non-Caucasian/non-HURM
-(NCNH) individuals, and white women in biomedical fields, it is
-important for trainees to have visual representations of themselves as
-scientists. The importance of representation in retaining a diverse
-group of individuals in STEM fields is supported by social role theory
-(10). Individuals make inferences about characteristics that are needed
-to be successful in a given role by examining individuals that most
-occupy that role (10, 11). However, there is a lack of diverse
-scientific experts in academia so underrepresented minorities are not
-seeing adequate visual representations of themselves at the faculty
-level. Therefore, trainees who do not see representation of themselves
-in senior faculty positions, may decide that they do not possess the
-characteristics that are required to succeed.
+particularly in the biomedical sciences, since underrepresented groups
+face a complex set of barriers to achieving faculty status (9). For
+example, the dedication of women, who have children, to their work is
+perceived to be less than that of their colleagues, including men who
+also have children (10--12). Historically under-represented minorities
+in the United States (HURM), Asian/Asian-Americans, and women are all
+held to stricter competency standards and report having to work harder
+than Caucasian men to be perceived as legitimate scholars (13, 14).
+Asian/Asian-Americans suffer from imposter syndrome at greater rates
+than other marginalized groups and Asian women report a lack of sponsors
+(15, 16). Increased performance expectations and patterns of exclusions
+are consistent themes in studies characterizing the HURM faculty
+experience (17, 18). While HURM and other marginalized groups share some
+experiences, differences including varying rates of hiring and tenure
+promotion mean that unique considerations are important for inclusion of
+each group (3).
+
+Here, we argue that in order to increase the retention of faculty from
+marginalized groups at the professor level, universities should provide
+trainees with visual representation of themselves as successful
+scientists. Recent studies show that women in STEM benefit from women
+role models through improved belonging and self-efficacy (19, 20).
+Predictably, a lack of active inclusion decreases self-efficacy,
+eventually resulting in decreased feelings of belonging for URMs (21).
+However, as the demographics of trainees have become more diverse,
+students who are not Caucasian men, are lacking role models.
+Institutionalized racism and sexism (22), defined as policies, societal
+norms, and ideologies that reinforce inequities, have played a large
+role in access to, inclusion in, and hiring policies at U.S.
+universities (23, 24). Accordingly, faculty from marginalized groups are
+eliminated from the applicant pool and subsequent hires, leaving
+university policies and practices to be predominantly created by
+Caucasian men. Thus, institutionalized racism and sexism are perpetuated
+(25, 26). Universities have begun adjusting hiring practices and
+creating initiatives to address inequitable hiring practices, but have
+had limited results (27). Considering that most faculties within the
+U.S. are still skewed towards Caucaisan men, invited seminar series are
+a possible tool to provide marginalized trainees with representation of
+themselves as successful scientists.
 
 Invited seminar series are common within biomedical departments across
-the United States (12). Usually, seminar series' consist of faculty
+the United States (28). Usually, seminar series' consist of faculty
 members selecting a scientist from another institution to visit their
@@
 invited speaker provides the scientist with an opportunity to make
-future collaborations and build their own \emph{curriculum vitae} (CV).
+future collaborations and build their own curriculum vitae (CV).
 Scientists invited to give seminars are widely regarded as successful
-and the top in their field. Thus, if trainees are constantly being
-exposed to ``the top scientist in their field'', according to social
-role theory, it signals who is successful in that field. While some have
-examined this issue by studying and promoting the inclusion of more
-women speakers at conferences, how department speaker series compare to
-the trainee diversity of that department is unknown (13--15).
+and the top in their field, providing an opportunity for trainees to be
+exposed to successful scientists in that field. Some studies have
+examined the addition of more women speakers at conferences to promote
+inclusion (29--31), however, we have only identified one other study
+that has focused on invited speakers at universities (28). In their
+study, Nittrouer et al, examined 3,652 talks at 50 U.S. institutions in
+2013 - 2014 and found that women faculty are less likely to be invited
+speakers (28). We have not been able to identify any publications
+examining scientific speaker diversity beyond gender or how department
+speaker series compares to trainee diversity in that department.
 
-In this study, we examine and compare the proportion of HURM, NCNH, and
-women invited speakers to white men in the Department of Microbiology
-and Immunology at the University of Michigan. Additionally, we compare
-invited-speaker demographics to the current trainee demographics as a
-means to gauge if trainee demographics are being represented accordingly
-throughout the seminar series. Following our investigation, we proposed
-a policy change to the Department of Microbiology and Immunology in how
-invited speakers are selected as a means to promote inclusion in our
-department and reduce unconscious bias. In order to facilitate inviting
-a more diverse group of scientists, we developed a set of resources that
-allow scientists, within the fields of microbiology and immunology, to
-self-identify as having an under-represented or under-served identity
-including: HURM, non-Caucasian/non-HURM, or a white woman. These
-resources will promote inclusion and diversity by providing greater
-representation of all scientists and will provide hosts an opportunity
-to invite a more diverse group of scientists.
+In this study, we examine and compare the demographics of invited
+speakers to Caucasian men in the Department of Microbiology and
+Immunology at the University of Michigan. Additionally, we compare
+invited-speaker demographics to the current trainee demographics to
+gauge if trainee demographics are being represented throughout the
+seminar series. Following our investigation, we proposed a policy change
+to the Department of Microbiology and Immunology in how invited speakers
+are selected to promote inclusion in our department and reduce
+unconscious bias. In order to facilitate inviting a more diverse group
+of scientists, we developed a set of resources that allow scientists,
+within the fields of microbiology and immunology, to self-identify as
+having an under-represented or under-served identity including: HURM,
+non-Caucasian/non-HURM (NCNH), or a Caucasian woman. These resources
+will promote inclusion and diversity by providing greater representation
+of all scientists and will provide hosts an opportunity to invite a more
+diverse group of scientists.
 
@@
 demographics since as hosts, these faculty members are visible
-representatives of the department. The trainees were identified using
+representatives of the department. There were a total of \{\texttt{r}\}
+invited speakers and paired hosts. The trainees were identified using
 departmental email lists that included masters students, doctoral
-students, and post-doctoral fellows.
+students, and post-doctoral fellows. There were \{\texttt{r}\} students
+and \{\texttt{r}\} post-doctoral fellows.
 
@@
 identities at the time of visit. Instead we hand-coded proxy
-demographics using personal knowledge, photos, and CVs. The presenting
-gender of each individual was assigned using a binary system
+demographics of the speakers, faculty hosts and trainees using first
+names, publicly available photos, and CVs (32--36). Information from
+CVs, such as undergraduate institutions (e.g., Puerto Rico vs mainland
+U.S.) and activity in HURM groups (e.g., SACNAS) helped inform our
+demographics by indicating identities that might be held by that
+individual. Because these data were collected from publicly available
+sources, this study was not submitted to an IRB for consideration. The
+presenting gender of each individual was inferred using a binary system
 (man/woman). Due to the low number of individuals in the study,
-race/ethnicity demographics were split in three groups: Caucasian,
-Historically Under-represented Minority (HURM), and
+race/ethnicity demographics were only split into three groups:
+Caucasian, Historically Under-represented Minority (HURM), and
 Non-Caucasian/Non-HURM (NCNH), each with a binary (yes/no) possibility.
-Caucasian was assigned using the current U.S. Census definition where
-those of Middle Eastern, European, and Russian descent are included.
-HURM individuals were restricted to those with African-American,
-Indigenous, Alaskan/Hawaiian Native, Latinx and/or Hispanic heritage.
-All others were placed into the NCNH group. We recognize that our proxy
-demographics are a limitation of the analysis and want to acknowledge
-that biological sex (male/female) is not always equivalent to the gender
-that an individual presents as (man/woman), which is also distinct from
-the gender(s) that an individual self-identifies as. We also want to
-acknowledge that there are many other identities that are not captured
-in this limited analysis.
+Caucasian was inferred using the current U.S. Census definition where
+those of Middle Eastern, European, and Russian descent are included. URM
+individuals include those of African-American, Indigenous American,
+Alaskan/Hawaiian Native, Latinx and/or Hispanic heritage (20 U.S. Code
+§\,1067k), we use the HURM designation to recognize the history of
+enslavement and active oppression in the U.S.. The NCNH group
+predominantly included Asian/Asian-Americans, but also African
+immigrants (37).
 
-Data were analyzed and figures generated in R Statistical Software,
-using relevant packages (16--28).
+Data were compiled and figures generated in R Statistical Software,
+using relevant packages (38--50).
 
@@
 of the department, on track with the 11\% of U.S. microbiology and
-immunology doctorates awarded in 2017 (29). However, only 8.5\% of
+immunology doctorates awarded in 2017 (51). However, only 8.5\% of
 invited speakers, and none of the hosting faculty, were HURM scientists.
@@
 of U.S. microbiology and immunology doctorates in 2017), but only 19\%
-of hosting faculty and 10.5\% of invited speakers (29).
+of hosting faculty and 10.5\% of invited speakers (51).
 
@@
 and outcomes, we further examined the lectureships by gender and
-race/ethnicity status (30). Caucasian men and women accounted for
+race/ethnicity status (52). Caucasian men and women accounted for
 44.44\% and 37.04\% of the lectureships, respectively. Just 18.52\% of
@@
 Additionally, within the last 5 years, no HURM or NCNH woman was awarded
-a lectureship. This means that the department is not providing
+a lectureship, despite that in 2017 non-Caucasians were 30\% of the
+professoriate (53). This means that the department is not providing
 non-Caucasian trainees with adequate representation of successful
-scientists. Taking this into context of social role theory, by not
-adequately representing the diversity of all trainees, the department is
-not supporting an inclusive environment in terms of visual faculty
-representation. We also found that the proportion of women as faculty
-hosts and speakers in our study population is equivalent to global
-estimates that 40\% of microbiologists are women, though women only
-represent about 30\% of academic biomedical faculty (7, 31). Women are
-also over-represented as graduate students and postdoctoral fellows in
-this department. Overall, Caucasian scientists are over-represented as
-host faculty and invited speakers, compared to their presence as
-trainees, particularly when lectureships were considered.
+scientists and failing to support an inclusive environment in terms of
+visual faculty representation. We also found that the proportion of
+women as faculty hosts and speakers in our study population is
+equivalent to global estimates that 40\% of microbiologists are women,
+though women only represent about 30\% of academic biomedical faculty
+(7, 54). Women are also over-represented as graduate students and
+postdoctoral fellows in this department. Overall, Caucasian scientists
+are over-represented as host faculty and invited speakers, compared to
+their presence as trainees, particularly when lectureships were
+considered.
 
-Several papers have investigated the representation of women at
-scientific conferences, however, we have only identified one that
-focused on invited speakers at universities (12). In their study,
-Nittrouer et al, examined 3,652 talks at 50 U.S. institutions in 2013 -
-2014 and found that women faculty are less likely to be invited
-speakers, despite similar acceptance rates (12). We have not been able
-to identify any publications examining scientific speaker diversity
-beyond gender. This seems to be the first, which is concerning since
-conclusions drawn from gender-based studies are often framed, and
-considered, to be applicable to other marginalized groups (e.g., HURM).
-This is a flawed assumption. While there is no doubt some overlap, each
-group remains marginalized due to a unique complex set of factors that
-cannot always be solved by gender-based solutions. U.S. institutions,
-such as the University of Michigan have a particular responsibility to
-the historically suppressed populations included in our definition of
-HURMs. We therefore implore U.S. institutions to apply this framing to
-their discussions and research.
+We have not been able to identify any publications examining scientific
+speaker diversity beyond gender (28). This seems to be the first, which
+is concerning since conclusions drawn from gender-based studies are
+often framed, and considered, to be applicable to other marginalized
+groups (e.g., HURM). For instance, that African-American and Caucasian
+women benefit equally from the same policy change. This is a flawed
+assumption (55). While there is no doubt some overlap, each group
+remains marginalized due to a unique complex set of factors that cannot
+always be solved by gender-based solutions. The historical exclusion of
+HURMs by U.S. institutions means that they have a particular
+responsibility to improving the academic experience for these
+populations (23). We therefore call on U.S. institutions to apply
+intersectional framing to their discussions and research.
 
@@
 speakers, but it is a matter of pride to bring the best scientists
-possible. It may be that the definition of ``best'' poses a problem to
-under-represented and under-served groups (e.g., white women, HURM, and
-Asian) who are held to stricter competency standards and report having
-to work harder than white men to be perceived as legitimate scholars
-(32, 33). Some departments only invite tenured faculty, which severely
-limits the number of potential speakers who are white women or
-non-Caucasian. Yet, another scenario is that pre-tenure faculty members
-invite prestigious, tenured faculty in their field to network and secure
-letters for their own tenure package. The increased burden of white
-women and non-Caucasian scientists to prove competency decreases their
-likelihood to be considered for either tenure or as possible source of
-tenure letters.
+possible. The barriers to achieving faculty status for HURMs, Caucasian
+women, and NCNH may also impact their speaking invitations. For
+instance, the perceived prioritization and commitments of women to
+family over work may cause faculty to doubt their acceptance of a
+speaking invitation, despite the prestigious nature of these invitations
+and evidence that men and women accept at similar rates (28, 56). As a
+result, the faculty member may invite a different colleague who they
+feel is more likely to agree (and is a man). It may also be that the
+definition of ``best'' poses a problem to under-represented and
+under-served groups (e.g., women, HURM, and Asian) who are held to
+stricter competency standards (13, 14). Some departments may only invite
+tenured faculty, which severely limits the number of potential speakers
+who are Caucasian women or non-Caucasian. Yet, another scenario is that
+pre-tenure faculty members invite prestigious, tenured faculty in their
+field to network and secure letters for their own tenure package. The
+increased burden of women and non-Caucasian scientists to prove
+competency decreases their likelihood to be considered for either tenure
+or as possible source of tenure letters. In particular, the proportion
+of HURM faculty at the Assistant and Associate Professor level is
+currently higher than at Full Professor so it will be difficult to
+increase speaker diversity if early-career researchers are not being
+considered (57). Even when HURM speaker rates match the proportion of
+HURM faculty employment, HURM trainees will be represented at a
+significantly higher proportion. We argue that inclusion of marginalized
+faculty in seminar series is an important factor to increasing their
+representation among Associate and Full Professors. It is just one
+aspect of larger institutional change that is needed, but one that will
+benefit trainee experiences and the CVs of marginalized faculty (58).
 
-Each underrepresented group in our cohort faces a complex set of
-barriers to achieving faculty status. For instance, the decision to
-invite a woman may also be negatively impacted by assumptions about
-competency and dedication. The dedication of women who have children to
-their work is perceived to be less than that of their colleagues, i.e.,
-men who also have children (34--36). The perceived prioritization and
-commitments of women to family over work may cause faculty to doubt
-their acceptance of a speaking invitation, despite the prestigious
-nature of these invitations and evidence that men and women accept at
-similar rates (12, 37). As a result, the faculty member may invite a
-different colleague who they feel is more likely to agree (and is a
-man). Another large portion of our sample were the NCNH cohort, who are
-predominately Asian/Asian American individuals. Although Asian
-scientists are well-represented in the US scientific workforce, they
-face significant bias and barriers to inclusion in society and academia
-(38, 39). For instance, despite the higher employment rate of Asian
-scientists, they were not well-represented in the more prestigious
-lectureships.
-
-While HURM and NCNH share some experiences, differences including
-varying rates of hiring and tenure promotion mean unique considerations
-are important for inclusion of each group (3). For instance, a major
-barrier to inclusion of HURM faculty at similar proportions to HURM
-trainees is the low transition rate of scientists from HURM backgrounds
-to faculty positions and the associated low proportion of HURM faculty
-(40). The proportion of HURM faculty at the Assistant and Associate
-Professor level is currently higher than at Full Professor so it will be
-difficult to increase speaker diversity if early-career researchers are
-not being considered (41). Increased performance expectations and
-patterns of exclusions are consistent themes in studies characterizing
-the HURM faculty experience (42, 43). Therefore, inclusion of HURM
-faculty in seminar series is likely essential to increasing the number
-of HURM Associate and Full Professors. Even when HURM speaker rates
-match the proportion of HURM faculty employment, HURM trainees will be
-represented at a significantly higher proportion. Inclusion of HURM
-faculty in these seminar series is just one aspect of larger
-institutional change that is needed (44).
+We recognize that our proxy demographics are a limitation of the
+analysis and want to acknowledge that biological sex (male/female) is
+not always equivalent to the gender that an individual presents as
+(man/woman), which is also distinct from the gender(s) that an
+individual self-identifies as. We also want to acknowledge that there
+are many other identities that are not captured in this limited
+analysis. While our pilot study combined 5 years worth of seminars, our
+n is still quite low and we did not have other departments for
+comparison. Consequently, our results can not be generalized to other
+departments, fields, or universities. Another limitation to looking at a
+single department is that trainees may interact with faculty from many
+other departments, depending on their research and interests. Therefore,
+the individual experience of representation would vary by trainee.
+Future research needs to consider multiple departments, universities,
+and/or fields to bolster generalizability. There is a paucity of
+research on speaker identities other than their gender, so this also
+needs to be addressed in future studies. However, we caution that
+representation is a shallow metric on which a single-minded focus can
+cause more harm than help (25). We recommend that future research also
+survey trainee and speaker experiences and trainee participation in
+seminar series to better understand the dynamics at play.
 
@@
 and Immunology at the University of Michigan, these data were presented
-to faculty members and the department chair (Dr.~Mobley). Since trainee
-demographics were not represented by the seminar speaker demographics
-over the past 5 years, we proposed a policy change as to how seminar
-speakers were being invited. One suggestion was to switch from
-faculty-invited to lab-invited speakers in an attempt to allow trainees
-to choose a speaker that best represented themselves (Table 1).
+to faculty members and the department chair. Since trainee demographics
+were not represented by the seminar speaker demographics over the past 5
+years, we proposed a policy change as to how seminar speakers were being
+invited (Table 1). One suggestion was to switch from faculty-invited to
+lab-invited speakers to allow trainees to choose a speaker that best
+represented themselves. This is easy to implement as it does not change
+the overall structure of the department's seminar series; however, for
+this same reason it may not have a significant impact on the diversity
+of invited speakers. Trainees may be pressured to invite the top
+individuals in their sub-field or may be influenced by the same
+unconscious biases as faculty members. This idea can be expanded by
+increasing the number of trainee-invited speakers and varying the
+trainee group that extend invitations, for instance by training program,
+career interest, and/or trainees and faculty in an identity-affinity
+group. Invitations from trainees are often seen as an honor by potential
+seminar speakers and nominating as a group may decrease the pressure to
+invite particular sub-fields or ranks.
 
-The implicit biases that affect perceptions of marginalized groups are
-an issue, but we must acknowledge that it is not always possible to
-identify members of historically under-served communities. For instance,
-after data analysis, we learned that at least one speaker in our data
-set should have been categorized as a HURM instead of Caucasian, but it
-wasn't readily apparent from their internet presence or CV. This
-limitation makes two important points: that perceived identity often
-plays a larger role than self-identification, and that we need better
-tools to identify members of marginalized groups. Another policy
-suggestion is for departments to invite their speakers to spend time
-discussing their personal journeys through science, in addition to their
-scientific stories (Table 1). This would enable those who wish, to
-discuss how their identity(ies) interacted with their careers. In
-addition to these suggestions for policy change, we have created
-resources that allow scientists to self-identify as under-served groups
-and thus provide host faculty with more diverse choices (Table 1).
+We also used this opportunity to begin a conversation about the purpose
+of seminar speakers. Seminar speakers are sometimes invited to highlight
+their latest high-impact paper or to share the arc of discoveries they
+have made over several years of their career. While both are certainly
+worthwhile, there are other benefits to be gained from interacting with
+seminar speakers such as how to apply new techniques and how research is
+framed outside research-focused universities (Table 1). Thinking more
+broadly about what material is valuable during a seminar series may lead
+to more speakers from under-represented and under-served backgrounds, as
+well as more diversity of career paths. For some institutions, these
+suggestions represent more of a structural change to the departmental
+seminar series as speakers focusing on techniques or from
+non-research-intensive universities are using invited as part of
+professional development series. If these changes are to be implemented,
+many members of the department must agree to the value of including
+these seminars in the main departmental seminar series and these
+expectations must be clearly communicated by the leadership (Table 1).
+Departmental leadership can also ask individuals and groups to consider
+their own unconscious biases that may be impacting their speaker nominee
+list to compact some of the barriers to inviting diverse speakers.
+Presented with these ideas, several members of the Department of
+Microbiology and Immunology at the University of Michigan expressed
+interest in specific resources they might use to identify individuals
+from diverse identities, careers, and institutions. One suggestion is to
+use resources that are being organized by professional societies such as
+the American Society for Microbiology (ASM) and the Society for
+Advancing Chicanos/Hispanics \& Native Americans in Science (SACNAS)
+(Table 1). We also chose to develop ``Diversify'' resources for the
+microbiology and immunology fields that provide a list of scientists
+from under-represented and under-served groups, that is not associated
+with a specific professional society. More information on the type of
+resources and how to establish a Diversify list is below. Using list
+resources like those available from professional societies as well as
+our ``Diversify'' resources are particularly useful as social science
+research has shown that the human brain is much better at recognizing
+and using information (such as a strong scientific speaker) from a list
+than it is at recalling the same information from memory (59, 60).
+
+We caution, however, that it is not enough to invite diverse speakers.
+An inclusive environment must be built within the department. Start by
+inviting all speakers to spend a few minutes describing their personal
+science journey and providing time for trainees to engage with the
+speaker. Trainee-speaker interactions can be encouraged by ensuring that
+trainees are the first to ask questions at the seminar's conclusion and
+by scheduling a dedicated meeting time for trainees. As speaker
+schedules are being designed, departments should consider how they can
+foster an inclusive atmosphere during the speaker visits. Speakers
+should be asked prior to their visit if they have any dietary, movement,
+or other restrictions that should be accommodated during the visit. The
+identities of individuals the speaker is meeting with during their visit
+may also need to be considered; this is not to say that all identities
+of a speaker should be matched on their schedule or that a HURM speaker
+must have a meeting a HURM faculty member, but take care to ensure that
+speakers are meeting with faculty that reflect the diversity of thought
+and identity in the department. If a portion of the department is
+consistently not represented on speakers' schedules (or extending
+invitations) this may reflect an opportunity for increased inclusivity
+in the department. Finally, speakers should be provided with ample
+opportunity to request meetings, not only with faculty but also with
+student groups or campus administrators who share similar interests.
+Through these steps departments can increase the diversity of speakers
+invited to their seminars while also increasing the impact of the
+seminar speakers.
 
@@
 resources in other fields--DiversifyEEB and DiversifyChemistry--we
-created DiversifyMicrobiology and DiversifyImmunology (45--48). These
+created DiversifyMicrobiology and DiversifyImmunology (61--64). These
 resources are a tool for symposium organizers, award committees, search
@@
 
-This public spreadsheet is embedded in the website and can be open
+This public spreadsheet is embedded in the website and can be opened
 separately as a locked (uneditable) Google Sheet, allowing the list to
@@
 DiversifyMicrobiology repository on GitHub provides links to these
-resources and instructions for adapting the tool to your own field (47).
+resources and instructions for adapting the tool to your own field (63).
+We caution creators of Diversify lists that the data voluntarily
+submitted to these lists is not eligible for study. IRB approval must be
+obtained prior to launching the list if that is a goal.
 
@@
 
-To increase the retention of white women, HURM and NCNH trainees in the
-biomedical sciences, they must also be represented as experts. However,
-the invited speaker diversity at one department does not represent the
-diversity of trainees. To facilitate the identification and recruitment
-of individuals in these historically under-served groups, we have built
-a tool to create self-nominated, field-specific lists.
+To increase the retention of Caucasian women, HURM and NCNH trainees in
+the biomedical sciences, they must also be represented as experts.
+However, the invited speaker diversity at one department does not
+represent the diversity of trainees. To facilitate the identification
+and recruitment of individuals in these historically under-served
+groups, we have built a tool to create self-nominated, field-specific
+lists.
 
-\subsection{Acknowledgements}\label{acknowledgements}
+\subsection{Acknowledgments}\label{acknowledgments}
 
@@
 Bonnie Krey and former speaker series coordinators Drs. Nicole
-Koropatkin and Kathy Spindler for access to invited speaker data. We
-would also like to acknowledge and thank Nick Lesniak and Dr.~Ariangela
-Kozick for their comments and suggestions.
+Koropatkin and Kathy Spindler for providing compiled invited speaker
+data. We would also like to acknowledge and thank Nick Lesniak and
+Dr.~Ariangela Kozick for their comments and suggestions.
 
@@
 
-A.K.H. collected the data, assigned demographics, analyzed the data,
+A.K.H. collected the data, inferred demographics, analyzed the data,
 created the website, and wrote the methods and results. R.M.P. created
@@
 
-\newpage
-
-\begin{center}
-\captionof{table}{List of suggestions and resources to increase invited speaker diversity.}
-\small
-\begin{tabular}{|l|l|l|}
-\hline
-
-\rowcolor{lightgray}
-\textbf{Suggestion} & \textbf{Description} & \textbf{Resource} \\ \hline
-
-Lab-invited speakers & \makecell[l]{Faculty members can request \\suggestions from trainees} & \\ \hline
-
-Use a list & \makecell[l]{Many lists of scientists from \\under-represented and under-served \\groups are available} &  \makecell[l]{https://DiversifyMicrobiology.\\github.io/resources}\\ \hline
-
-Create a list & \makecell[l]{Use the GitHub template \\ create a self-nomination list and \\resource for your field} & \makecell[l]{https://github.com/diversifymicrobiology/\\DiversifyMicrobiology.github.io} \\ \hline
-
-Highlight the journey & \makecell[l]{Invite all speakers to spend \\a few moments describing their \\personal science journey} & \\ \hline
-
-\end{tabular}
-\end{center}
-
 \begin{figure}
 \centering
-\includegraphics{Figure_1.png}
+\includegraphics{Figure_1.jpg}
 \caption{\textbf{The demographics of invited speakers, hosting faculty,
@@
 
-\subsection{References}\label{references}
+\subsection*{References}\label{references}
+\addcontentsline{toc}{subsection}{References}
 
@@
 
-\hypertarget{ref-Eagly1984}{}
-10. \textbf{Eagly AH}, \textbf{Steffen VJ}. 1984. Gender stereotypes
-stem from the distribution of women and men into social roles. Journal
-of Personality and Social Psychology \textbf{46}:735--754.
-doi:\href{https://doi.org/10.1037/0022-3514.46.4.735}{10.1037/0022-3514.46.4.735}.
+\hypertarget{ref-Firth1982}{}
+10. \textbf{Firth M}. 1982. Sex discrimination in job opportunities for
+women. Sex Roles \textbf{8}:891--901.
+doi:\href{https://doi.org/10.1007/bf00287858}{10.1007/bf00287858}.
 
-\hypertarget{ref-Carter2018}{}
-11. \textbf{Carter AJ}, \textbf{Croft A}, \textbf{Lukas D},
-\textbf{Sandstrom GM}. 2018. Women's visibility in academic seminars:
-Women ask fewer questions than men. PLOS ONE \textbf{13}:e0202743.
-doi:\href{https://doi.org/10.1371/journal.pone.0202743}{10.1371/journal.pone.0202743}.
+\hypertarget{ref-Correll2007}{}
+11. \textbf{Correll SJ}, \textbf{Benard S}, \textbf{Paik I}. 2007.
+Getting a job: Is there a motherhood penalty? American Journal of
+Sociology \textbf{112}:1297--1339.
+doi:\href{https://doi.org/10.1086/511799}{10.1086/511799}.
+
+\hypertarget{ref-Fuegen2004}{}
+12. \textbf{Fuegen K}, \textbf{Biernat M}, \textbf{Haines E},
+\textbf{Deaux K}. 2004. Mothers and fathers in the workplace: How gender
+and parental status influence judgments of job-related competence.
+Journal of Social Issues \textbf{60}:737--754.
+doi:\href{https://doi.org/10.1111/j.0022-4537.2004.00383.x}{10.1111/j.0022-4537.2004.00383.x}.
+
+\hypertarget{ref-BlairLoy2017}{}
+13. \textbf{Blair-Loy M}, \textbf{Rogers L}, \textbf{Glaser D},
+\textbf{Wong Y}, \textbf{Abraham D}, \textbf{Cosman P}. 2017. Gender in
+engineering departments: Are there gender differences in interruptions
+of academic job talks? Social Sciences \textbf{6}:29.
+doi:\href{https://doi.org/10.3390/socsci6010029}{10.3390/socsci6010029}.
+
+\hypertarget{ref-noauthor_seeking_2013}{}
+14. \textbf{National Research Council \textnormal{Policy and Global
+Affairs}}, \textbf{Committee on Women in Science, Engineering, and
+Medicine}, \textbf{Committee on Advancing Institutional Transformation
+for Minority Women in Academia}, \textbf{Rapporteur KM}. 2013. Seeking
+Solutions: Maximizing American Talent by Advancing Women of Color in
+Academia: Summary of a Conference. National Academies Press, Washington,
+D.C.
+
+\hypertarget{ref-McGee2018}{}
+15. \textbf{McGee E}. 2018. Black genius, asian fail: The detriment of
+stereotype lift and stereotype threat in high-achieving asian and black
+STEM students. AERA Open \textbf{4}:233285841881665.
+doi:\href{https://doi.org/10.1177/2332858418816658}{10.1177/2332858418816658}.
+
+\hypertarget{ref-wse_2016}{}
+16. \textbf{Joan C. Williams RR \textnormal{Su Li}}, \textbf{Finn P}.
+2016. Climate control: Gender and racial bias in engineering. University
+of California Hastings College of the Law, San Francisco, CA.
+
+\hypertarget{ref-pololi_race_2010}{}
+17. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
+Disadvantage and Faculty Experiences in Academic Medicine. Journal of
+General Internal Medicine \textbf{25}:1363--1369.
+doi:\href{https://doi.org/10.1007/s11606-010-1478-7}{10.1007/s11606-010-1478-7}.
+
+\hypertarget{ref-hassouneh_experiences_2014}{}
+18. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
+\textbf{Junkins EP}, \textbf{Horton LL}. 2014. The experiences of
+underrepresented minority faculty in schools of medicine. Medical
+Education Online \textbf{19}:24768.
+doi:\href{https://doi.org/10.3402/meo.v19.24768}{10.3402/meo.v19.24768}.
+
+\hypertarget{ref-Herrmann2016}{}
+19. \textbf{Herrmann SD}, \textbf{Adelman RM}, \textbf{Bodford JE},
+\textbf{Graudejus O}, \textbf{Okun MA}, \textbf{Kwan VSY}. 2016. The
+effects of a female role model on academic performance and persistence
+of women in STEM courses. Basic and Applied Social Psychology
+\textbf{38}:258--268.
+doi:\href{https://doi.org/10.1080/01973533.2016.1209757}{10.1080/01973533.2016.1209757}.
+
+\hypertarget{ref-Drury2011}{}
+20. \textbf{Drury BJ}, \textbf{Siy JO}, \textbf{Cheryan S}. 2011. When
+do female role models benefit women? The importance of differentiating
+recruitment from retention in STEM. Psychological Inquiry
+\textbf{22}:265--269.
+doi:\href{https://doi.org/10.1080/1047840x.2011.620935}{10.1080/1047840x.2011.620935}.
+
+\hypertarget{ref-Lambert2020}{}
+21. \textbf{Lambert WM}, \textbf{Wells MT}, \textbf{Cipriano MF},
+\textbf{Sneva JN}, \textbf{Morris JA}, \textbf{Golightly LM}. 2020.
+Career choices of underrepresented and female postdocs in the biomedical
+sciences. eLife \textbf{9}.
+doi:\href{https://doi.org/10.7554/elife.48774}{10.7554/elife.48774}.
+
+\hypertarget{ref-Hardeman2018}{}
+22. \textbf{Hardeman RR}, \textbf{Murphy KA}, \textbf{Karbeah J},
+\textbf{Kozhimannil KB}. 2018. Naming institutionalized racism in the
+public health literature: A systematic literature review. Public Health
+Reports \textbf{133}:240--249.
+doi:\href{https://doi.org/10.1177/0033354918760574}{10.1177/0033354918760574}.
+
+\hypertarget{ref-harvey_diversity_2011}{}
+23. \textbf{Harvey WB}. 2011. Higher education and diversity: Ethical
+and practical responsiblity in the academy.
+
+\hypertarget{ref-Stack2019}{}
+24. \textbf{Stack M}. 2019. Academic stars and university rankings in
+higher education: Impacts on policy and practice. Policy Reviews in
+Higher Education \textbf{4}:4--24.
+doi:\href{https://doi.org/10.1080/23322969.2019.1667859}{10.1080/23322969.2019.1667859}.
+
+\hypertarget{ref-Iverson2007}{}
+25. \textbf{Iverson SV}. 2007. Camouflaging power and privilege: A
+critical race analysis of university diversity policies. Educational
+Administration Quarterly \textbf{43}:586--611.
+doi:\href{https://doi.org/10.1177/0013161x07307794}{10.1177/0013161x07307794}.
+
+\hypertarget{ref-Tate2016}{}
+26. \textbf{Tate SA}, \textbf{Bagguley P}. 2016. Building the
+anti-racist university: Next steps. Race Ethnicity and Education
+\textbf{20}:289--299.
+doi:\href{https://doi.org/10.1080/13613324.2016.1260227}{10.1080/13613324.2016.1260227}.
+
+\hypertarget{ref-Gibbs2016}{}
+27. \textbf{Gibbs KD}, \textbf{Basson J}, \textbf{Xierali IM},
+\textbf{Broniatowski DA}. 2016. Decoupling of the minority PhD talent
+pool and assistant professor hiring in medical school basic science
+departments in the US. eLife \textbf{5}.
+doi:\href{https://doi.org/10.7554/elife.21393}{10.7554/elife.21393}.
 
 \hypertarget{ref-nittrouer_gender_2018}{}
-12. \textbf{Nittrouer CL}, \textbf{Hebl MR}, \textbf{Ashburn-Nardo L},
+28. \textbf{Nittrouer CL}, \textbf{Hebl MR}, \textbf{Ashburn-Nardo L},
 \textbf{Trump-Steele RCE}, \textbf{Lane DM}, \textbf{Valian V}. 2018.
@@
 \hypertarget{ref-kalejta_gender_2017}{}
-13. \textbf{Kalejta RF}, \textbf{Palmenberg AC}. 2017. Gender Parity
+29. \textbf{Kalejta RF}, \textbf{Palmenberg AC}. 2017. Gender Parity
 Trends for Invited Speakers at Four Prominent Virology Conference
@@
 \hypertarget{ref-casadevall_presence_2014}{}
-14. \textbf{Casadevall A}, \textbf{Handelsman J}. 2014. The Presence of
+30. \textbf{Casadevall A}, \textbf{Handelsman J}. 2014. The Presence of
 Female Conveners Correlates with a Higher Proportion of Female Speakers
@@
 \hypertarget{ref-klein_speaking_2017}{}
-15. \textbf{Klein RS}, \textbf{Voskuhl R}, \textbf{Segal BM},
+31. \textbf{Klein RS}, \textbf{Voskuhl R}, \textbf{Segal BM},
 \textbf{Dittel BN}, \textbf{Lane TE}, \textbf{Bethea JR}, \textbf{Carson
@@
 
+\hypertarget{ref-Broderick2019}{}
+32. \textbf{Broderick NA}, \textbf{Casadevall A}. 2019. Gender
+inequalities among authors who contributed equally. eLife \textbf{8}.
+doi:\href{https://doi.org/10.7554/elife.36399}{10.7554/elife.36399}.
+
+\hypertarget{ref-Kimery2011}{}
+33. \textbf{Kimery KM}, \textbf{Mellon MJ}, \textbf{Rinehart SM}. 2011.
+Publishing in the accounting journals: Is there a gender bias? Journal
+of Business \& Economics Research (JBER) \textbf{2}.
+doi:\href{https://doi.org/10.19030/jber.v2i4.2872}{10.19030/jber.v2i4.2872}.
+
+\hypertarget{ref-Helmer2017}{}
+34. \textbf{Helmer M}, \textbf{Schottdorf M}, \textbf{Neef A},
+\textbf{Battaglia D}. 2017. Gender bias in scholarly peer review. eLife
+\textbf{6}.
+doi:\href{https://doi.org/10.7554/elife.21718}{10.7554/elife.21718}.
+
+\hypertarget{ref-Fox2019}{}
+35. \textbf{Fox CW}, \textbf{Paine CET}. 2019. Gender differences in
+peer review outcomes and manuscript impact at six journals of ecology
+and evolution. Ecology and Evolution \textbf{9}:3599--3619.
+doi:\href{https://doi.org/10.1002/ece3.4993}{10.1002/ece3.4993}.
+
+\hypertarget{ref-Gilbert1994}{}
+36. \textbf{Gilbert JR}. 1994. Is there gender bias in JAMAs peer review
+process? JAMA: The Journal of the American Medical Association
+\textbf{272}:139.
+doi:\href{https://doi.org/10.1001/jama.1994.03520020065018}{10.1001/jama.1994.03520020065018}.
+
+\hypertarget{ref-Okonofua2013}{}
+37. \textbf{Okonofua BA}. 2013. I am blacker than you. SAGE Open
+\textbf{3}:215824401349916.
+doi:\href{https://doi.org/10.1177/2158244013499162}{10.1177/2158244013499162}.
+
 \hypertarget{ref-R_software_2017}{}
-16. \textbf{R Core Team}. 2017. R: A language and environment for
+38. \textbf{R Core Team}. 2017. R: A language and environment for
 statistical computing. R Foundation for Statistical Computing, Vienna,
@@
 \hypertarget{ref-wickham_tidyverse_2017}{}
-17. \textbf{Wickham H}. 2017. Tidyverse: Easily Install and Load the
+39. \textbf{Wickham H}. 2017. Tidyverse: Easily Install and Load the
 'Tidyverse'.
@@
 \hypertarget{ref-cowplot}{}
-18. \textbf{Wilke CO}. 2019. Cowplot: Streamlined plot theme and plot
+40. \textbf{Wilke CO}. 2019. Cowplot: Streamlined plot theme and plot
 annotations for 'ggplot2'.
@@
 \hypertarget{ref-markdown}{}
-19. \textbf{Allaire J}, \textbf{Horner J}, \textbf{Xie Y}, \textbf{Marti
+41. \textbf{Allaire J}, \textbf{Horner J}, \textbf{Xie Y}, \textbf{Marti
 V}, \textbf{Porte N}. 2018. Markdown: 'Markdown' rendering for r.
@@
 \hypertarget{ref-rmd_book}{}
-20. \textbf{Xie Y}, \textbf{Allaire J}, \textbf{Grolemund G}. 2018. R
+42. \textbf{Xie Y}, \textbf{Allaire J}, \textbf{Grolemund G}. 2018. R
 markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida.
@@
 \hypertarget{ref-rmd_rstudio}{}
-21. \textbf{Allaire J}, \textbf{Xie Y}, \textbf{McPherson J},
+43. \textbf{Allaire J}, \textbf{Xie Y}, \textbf{McPherson J},
 \textbf{Luraschi J}, \textbf{Ushey K}, \textbf{Atkins A},
@@
 \hypertarget{ref-knitr_2014}{}
-22. \textbf{Xie Y}. 2014. Knitr: A comprehensive tool for reproducible
+44. \textbf{Xie Y}. 2014. Knitr: A comprehensive tool for reproducible
 research in R. \emph{In} Stodden, V, Leisch, F, Peng, RD (eds.),
@@
 \hypertarget{ref-knitr_2018}{}
-23. \textbf{Xie Y}. 2018. Knitr: A general-purpose package for dynamic
+45. \textbf{Xie Y}. 2018. Knitr: A general-purpose package for dynamic
 report generation in r.
@@
 \hypertarget{ref-lubridate}{}
-24. \textbf{Grolemund G}, \textbf{Wickham H}. 2011. Dates and times made
+46. \textbf{Grolemund G}, \textbf{Wickham H}. 2011. Dates and times made
 easy with lubridate. Journal of Statistical Software \textbf{40}:1--25.
@@
 \hypertarget{ref-readxl}{}
-25. \textbf{Wickham H}, \textbf{Bryan J}. 2018. Readxl: Read excel
+47. \textbf{Wickham H}, \textbf{Bryan J}. 2018. Readxl: Read excel
 files.
@@
 \hypertarget{ref-pdftools}{}
-26. \textbf{Ooms J}. 2019. Pdftools: Text extraction, rendering and
+48. \textbf{Ooms J}. 2019. Pdftools: Text extraction, rendering and
 converting of pdf documents.
@@
 \hypertarget{ref-wickham_scales_2018}{}
-27. \textbf{Wickham H}. 2018. Scales: Scale Functions for Visualization.
+49. \textbf{Wickham H}. 2018. Scales: Scale Functions for Visualization.
 
 \hypertarget{ref-neuwirth_rcolorbrewer_2014}{}
-28. \textbf{Neuwirth E}. 2014. RColorBrewer: ColorBrewer Palettes.
+50. \textbf{Neuwirth E}. 2014. RColorBrewer: ColorBrewer Palettes.
 
 \hypertarget{ref-nsf_survey_2017}{}
-29. \textbf{National Center for Science and Engineering Statistics}.
+51. \textbf{National Center for Science and Engineering Statistics}.
 2017. Survey of Doctorate Recipients, Survey Year 2017. National Science
@@
 \hypertarget{ref-Crenshaw1989}{}
-30. \textbf{Crenshaw K}. 1989. Demarginalizing the Intersection of Race
+52. \textbf{Crenshaw K}. 1989. Demarginalizing the Intersection of Race
 and Sex: A black feminist critique of antidiscrimination doctrine,
@@
 
+\hypertarget{ref-nsf_2019}{}
+53. \textbf{National Center for Science and Engineering Statistics
+Directorate for Social, Behavioral, and Economic Sciences}. 2019. Women,
+minorities, and persons with disabilities in science and engineering.
+National Science Foundation, Alexandria, VA.
+
 \hypertarget{ref-allagnat_gender_2017}{}
-31. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
+54. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
 HJ}, \textbf{Hanafi S}, \textbf{Herbert R}, \textbf{Huggett S},
@@
 
-\hypertarget{ref-BlairLoy2017}{}
-32. \textbf{Blair-Loy M}, \textbf{Rogers L}, \textbf{Glaser D},
-\textbf{Wong Y}, \textbf{Abraham D}, \textbf{Cosman P}. 2017. Gender in
-engineering departments: Are there gender differences in interruptions
-of academic job talks? Social Sciences \textbf{6}:29.
-doi:\href{https://doi.org/10.3390/socsci6010029}{10.3390/socsci6010029}.
-
-\hypertarget{ref-noauthor_seeking_2013}{}
-33. \textbf{National Research Council \textnormal{Policy and Global
-Affairs}}, \textbf{Committee on Women in Science, Engineering, and
-Medicine}, \textbf{Committee on Advancing Institutional Transformation
-for Minority Women in Academia}, \textbf{Rapporteur KM}. 2013. Seeking
-Solutions: Maximizing American Talent by Advancing Women of Color in
-Academia: Summary of a Conference. National Academies Press, Washington,
-D.C.
-
-\hypertarget{ref-Firth1982}{}
-34. \textbf{Firth M}. 1982. Sex discrimination in job opportunities for
-women. Sex Roles \textbf{8}:891--901.
-doi:\href{https://doi.org/10.1007/bf00287858}{10.1007/bf00287858}.
-
-\hypertarget{ref-Correll2007}{}
-35. \textbf{Correll SJ}, \textbf{Benard S}, \textbf{Paik I}. 2007.
-Getting a job: Is there a motherhood penalty? American Journal of
-Sociology \textbf{112}:1297--1339.
-doi:\href{https://doi.org/10.1086/511799}{10.1086/511799}.
-
-\hypertarget{ref-Fuegen2004}{}
-36. \textbf{Fuegen K}, \textbf{Biernat M}, \textbf{Haines E},
-\textbf{Deaux K}. 2004. Mothers and fathers in the workplace: How gender
-and parental status influence judgments of job-related competence.
-Journal of Social Issues \textbf{60}:737--754.
-doi:\href{https://doi.org/10.1111/j.0022-4537.2004.00383.x}{10.1111/j.0022-4537.2004.00383.x}.
+\hypertarget{ref-Armstrong2015}{}
+55. \textbf{Armstrong MA}, \textbf{Jovanovic J}. 2015. STARTING AT THE
+CROSSROADS: INTERSECTIONAL APPROACHES TO INSTITUTIONALLY SUPPORTING
+UNDERREPRESENTED MINORITY WOMEN STEM FACULTY. Journal of Women and
+Minorities in Science and Engineering \textbf{21}:141--157.
+doi:\href{https://doi.org/10.1615/jwomenminorscieneng.2015011275}{10.1615/jwomenminorscieneng.2015011275}.
 
 \hypertarget{ref-xu_gender_2008}{}
-37. \textbf{Xu YJ}. 2008. Gender Disparity in STEM Disciplines: A Study
+56. \textbf{Xu YJ}. 2008. Gender Disparity in STEM Disciplines: A Study
 of Faculty Attrition and Turnover Intentions. Research in Higher
@@
 
-\hypertarget{ref-Hwang2008}{}
-38. \textbf{Hwang W-C}, \textbf{Goto S}. 2008. The impact of perceived
-racial discrimination on the mental health of asian american and latino
-college students. Cultural Diversity and Ethnic Minority Psychology
-\textbf{14}:326--335.
-doi:\href{https://doi.org/10.1037/1099-9809.14.4.326}{10.1037/1099-9809.14.4.326}.
-
-\hypertarget{ref-Tran2019}{}
-39. \textbf{Tran VC}, \textbf{Lee J}, \textbf{Huang TJ}. 2019.
-Revisiting the asian second-generation advantage. Ethnic and Racial
-Studies \textbf{42}:2248--2269.
-doi:\href{https://doi.org/10.1080/01419870.2019.1579920}{10.1080/01419870.2019.1579920}.
-
-\hypertarget{ref-Gibbs2016}{}
-40. \textbf{Gibbs KD}, \textbf{Basson J}, \textbf{Xierali IM},
-\textbf{Broniatowski DA}. 2016. Decoupling of the minority PhD talent
-pool and assistant professor hiring in medical school basic science
-departments in the US. eLife \textbf{5}.
-doi:\href{https://doi.org/10.7554/elife.21393}{10.7554/elife.21393}.
-
 \hypertarget{ref-whittaker_retention_2015}{}
-41. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
+57. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
 Acosta VG}. 2015. Retention of Underrepresented Minority Faculty:
@@
 
-\hypertarget{ref-pololi_race_2010}{}
-42. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
-Disadvantage and Faculty Experiences in Academic Medicine. Journal of
-General Internal Medicine \textbf{25}:1363--1369.
-doi:\href{https://doi.org/10.1007/s11606-010-1478-7}{10.1007/s11606-010-1478-7}.
-
-\hypertarget{ref-hassouneh_experiences_2014}{}
-43. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
-\textbf{Junkins EP}, \textbf{Horton LL}. 2014. The experiences of
-underrepresented minority faculty in schools of medicine. Medical
-Education Online \textbf{19}:24768.
-doi:\href{https://doi.org/10.3402/meo.v19.24768}{10.3402/meo.v19.24768}.
-
 \hypertarget{ref-johnson_msphere_2019}{}
-44. \textbf{Johnson MDL}. 2019. mSphere of Influence: Hiring of
+58. \textbf{Johnson MDL}. 2019. mSphere of Influence: Hiring of
 Underrepresented Minority Assistant Professors in Medical School Basic
@@
 
+\hypertarget{ref-Loftus1971}{}
+59. \textbf{Loftus GR}. 1971. Comparison of recognition and recall in a
+continuous memory task. Journal of Experimental Psychology
+\textbf{91}:220--226.
+doi:\href{https://doi.org/10.1037/h0031841}{10.1037/h0031841}.
+
+\hypertarget{ref-Johnson2014}{}
+60. \textbf{Johnson J}. 2014. Recognition is easy\(\mathsemicolon\)
+recall is hard, pp. 121--129. \emph{In} Designing with the mind in mind.
+Elsevier.
+
 \hypertarget{ref-Baucom_2019}{}
-45. \textbf{Baucom R}, \textbf{Duffy M}. 2019. DiversifyEEB.
+61. \textbf{Baucom R}, \textbf{Duffy M}. 2019. DiversifyEEB.
 \url{https://diversifyeeb.com}.
@@
 \hypertarget{ref-Duffy_2019}{}
-46. \textbf{Duffy M}, \textbf{McNeil AJ}. 2019. DiversifyChemistry.
+62. \textbf{Duffy M}, \textbf{McNeil AJ}. 2019. DiversifyChemistry.
 \url{https://diversifychemistry.com}.
@@
 \hypertarget{ref-Hagan2019_micro}{}
-47. \textbf{Hagan AK}, \textbf{Pollet RM}. 2019. DiversifyMicrobiology.
+63. \textbf{Hagan AK}, \textbf{Pollet RM}. 2019. DiversifyMicrobiology.
 GitHub repository.
@@
 \hypertarget{ref-Hagan2019_immuno}{}
-48. \textbf{Hagan AK}, \textbf{Pollet RM}. 2019. DiversifyImmunology.
+64. \textbf{Hagan AK}, \textbf{Pollet RM}. 2019. DiversifyImmunology.
 GitHub repository.
